### 2017-12-08 abstract.tex
nov 27, nico's changes introduced
nico's last changes from nov 25 introduced

X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in a solution. In this work we use a combination of these spectroscopies to study the electronic structure and decay of aqueous KCl at the K-edges of \ki~and \cli. Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features. To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of \ki, \cli~and their microsolvated clusters. Our calculations show that the energy order of the 3d and 4p orbitals is inverted in \ki~with respect to \cli. The reverse orbital order in the two ions is reflected in both the ordering of the core excited states and in the final states populated in the resonant Auger decay. Furthermore, the energetic proximity of the 3d and 4p virtual states in the bare \ki~ion leads to their mixing in the presence of the solvent, and to the population of the dipole forbidden 1s$\,\rightarrow\,$3d state upon K-shell excitation in an aqueous solution. The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.

### 2017-12-08 introduction.tex
nov 27, nico's changes introduced
nico's last changes from nov 25 introduced

\section{Introduction}

X-ray absorption and Auger electron spectroscopies are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase. Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions \citep{Pokapanich09:7264}, and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}. Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy. The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decay. Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes such as interatomic Coulombic decay (ICD) and related processes \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708} are possible.

The course of a decay cascade depends on the character of the initially populated states. This has been well understood in atoms and molecules in gas phase (REFS) \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,Miteva14:064307}. In the case of a core ionized state, the Auger decay process, designated as normal Auger decay (see Fig.\ \ref{fg:auger}), leads to the population of doubly ionized final states localized on the initially ionized unit \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415}. Auger processes in rare gas clusters have been also investigated (refs). The normal Auger decay process in clusters proceeds similarly to that in atoms or molecules. However, in the case of a core excited state, the resonant Auger process competes with the process of delocalization of the excited electron in clusters \citep{Bjorneholm95:3017}. If the initially core excited electron delocalizes within the lifetime of the core hole, then normal instead of resonant Auger decay is observed \citep{Bjorneholm95:3017}.

In a solution, the electronic decay cascades initiated by x-ray photoabsorption are different compared to those in rare gas clusters due to the shorter distances and stronger interatomic interactions. In particular, the solvent molecules have two effects -- first, they strongly affect the excited \citep{miteva16:16671} or ionized states of the ion and second, they can participate in the decay processes, leading to the population of delocalized final states, and thus ionizing the surrounding environment \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237}. Moreover, the process of delocalization of the initially excited electron also occurs in aqueous solutions \citep{Nordlund07:217406,Ottosson11:13489}.
%Moreover, the process of delocalization of the initially excited electron is not specific to rare gas clusters, but it also occurs in aqueous solutions \citep{Nordlund07:217406,Ottosson11:13489}. 
In the case of pure water, the rate of delocalization of the O1s excited electron takes place on a femtosecond to sub-femtosecond time scale depending on the photon energy, thus being commensurate with the lifetime of the O1s core hole which is 6\,fs \citep{Nordlund07:217406}. The O K-edge is located in the soft x-ray range of photon energies. Going higher in photon energy, in the hard x-ray regime, the lifetimes of the core ionized or core excited states become even shorter, on the order of 1\,fs (REF). And thus, it is even more imperative to reveal whether the delocalization of the core excited electron occurs within the lifetime of the core hole.

The aim of this work is to elucidate the nature of the states populated upon x-ray irradiation of solvated ions in the hard x-ray regime, and furthermore, to understand whether the process of delocalization influences the resonant Auger decay. To this end, we used Auger electron spectroscopy together with x-ray absorption spectroscopy in the hard x-ray regime to study aqueous potassium chloride at the K-edges of both \ki~and \cli. In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, localized core excited states are populated. These states undergo resonant Auger decay within less than 1\,fs. In both ions, there is a competition between resonant Auger decay and delocalization of the excited electron. Using the core-hole clock method (REFS), we show that in \ki~delocalization at the pre-edge is weak, whereas in the case of \cli, due to the energetic proximity of the core excited state to the K-edge, the rate of delocalization is of the same order as that of the resonant Auger process. Moreover, we observe that although the \ki~and \cli~ions are isoelectronic, they have different fingerprints in the resonant Auger spectra. With the aid of high-level {\it ab initio} calculations of the initial and final states of the resonant Auger process of both the bare ions and their microsolvated clusters, we demonstrate that these differences are a result of the different electronic structure of the two ions, thus confirming that the XAS/AES technique is a sensitive probe of the electronic structure of solutions.

\begin{figure}
\includegraphics{figures/auger_process.eps}
\caption{Schematic representation of the normal and resonant Auger processes.}
\label{fg:auger}
\end{figure}

### 2017-12-08 results.tex
nov 27, nico's changes introduced
nico's last changes from nov 25 introduced

\section{Results and discussion}\label{sec:rnd}

\begin{figure}%[h]
\centering
\includegraphics[scale=0.55]{figures/k_2dmap.pdf}
\caption{2D map showing the kinetic energy of the electrons emitted in KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous K$^{+}$. The black curve on the left represents the experimental partial electron yield spectrum of K$^{+}$ obtained after integrating over the kinetic energies of the Auger electrons in the energy range presented on the figure. The upper panel shows two spectra at photon energies 3610.7\,eV, and 3616\,eV below and above the ionization potential at 3611.9\,eV, respectively. The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p(red) doublet resonant Auger states of K$^{+}$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details). The states are shifted with respect to the lowest quartet state with electron configuration K$^{2+}$(2p$^{-2}$($^3$P) 4s).}
\label{fg:2dmap_k}
\end{figure}

\begin{figure}%[h]
\centering
\includegraphics[scale=0.55]{figures/cl_2dmap.pdf}
\caption{2D map showing the kinetic energy of the electrons emitted in KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous Cl$^{-}$. The black curve on the left represents the experimental partial electron yield spectrum of Cl$^{-}$ obtained after integrating over the kinetic energies of the Auger electrons in the energy range presented on the figure. The upper panel shows two spectra at photon energies 2825.2\,eV, and 2830.0\,eV below and above the ionization potential at 2825.4\,eV, respectively. The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p(red) doublet resonant Auger states of K$^{+}$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details). The states are shifted with respect to the lowest quartet state with electron configuration Cl$^{0}$(2p$^{-2}$($^3$P) 4s).}
\label{fg:2dmap_cl}
\end{figure}

\subsection{Normal Auger decay}\label{ssec:na}

The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization in \ki~and \cli~results in the population of 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states. The $^3$P final states are not observed in the experiment since they are forbidden {\color{red}from parity conservation rules} (REF?). In the case of Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ (2p$^{-2}$) $^1$S and $^1$D states are located at 2373.2\,eV and 2382.1\,eV kinetic energy (see Fig.\ \ref{fg:2dmap_cl}). For K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines are located at 2958\,eV and 2968.4\,eV, respectively (see Fig.\ \ref{fg:2dmap_k}).

The KL$_{2,3}$L$_{2,3}$ Auger lines are not supposed to disperse with photon energy except close to threshold due to the interaction between the photoelectron and Auger electron, i.e.\ the so-called post-collision interaction (PCI). As a result of this interaction, first, the peaks in the Auger spectrum become asymmetric with a shoulder at high kinetic energies, and second, they are shifted to higher kinetic energies close to threshold \citep{russek86:911,guillemin15:012503}. Consequently, one can attribute the high kinetic energy shoulder of the $^1$D and $^1$S peaks on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} as resulting from PCI effect. In order to minimize this effect we recorded the KLL Auger spectrum of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ at higher photon energies, $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17} for details). The maxima of the $^1$D and $^1$S states were found at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively. The lines observed at photon energies far from threshold and close to it appear to be shifted by $\sim$1\,eV. The magnitude of the shift is the same for both ions, thus, we can conclude that it does not depend on the initial charge of the ion. The observed PCI shift of 1\,eV is larger than in the case of the isoelectronic Ar, where its value is $\sim$0.5\,eV at a photon energy of 10 \,eV above threshold \citep{guillemin15:012503}. The shift in the energies of the photo- and Auger electrons is proportional to the change in the ionic field during the Auger process. In a solution, both the single and double ionization potentials change due to the polarization of the water molecules and the stabilization of the ionic species through ion-dipole interaction with the polarized solvent. For example, in \ki, the ionization potential of the bare ion was experimentally determined to be 3619.4\,eV \citep{hertlein06:062715}, whereas in an aqueous solution, its value drops by about 7.5\,eV. The magnitude of this effect increases with the ionic charge, consequently, there will be an even greater difference for the double ionization potential. Thus, one can expect a larger change in the ionic field in an aqueous solution compared to that in a van der Waals cluster, which can, therefore, account for the large PCI shift of the Auger lines in a solution.

The normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder (A on Fig.\ \ref{fg:2dmap_k}) on the low kinetic energy side at about 2965\,eV kinetic energy. This shoulder is a result of charge transfer to the solvent molecules \citep{ceolin17}. Such charge-transfer-to-solvent states are also present in \cli, but they were found at lower kinetic energies, and are therefore not observed in the kinetic energy region shown on Fig.\ \ref{fg:2dmap_cl} \citep{ceolin17}.

\subsection{Resonant Auger decay} \label{ssec:ra}

The pre-edge regions of the x-ray absorption spectra of \ki~and \cli~shown to the left on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} do not exhibit any high intensity features {\color{red}Here, I mean sharp resonances if it's called like this, compared to Ar for example}. Consequently, solely from these spectra, one cannot conclude whether there are core excited states in the pre-edge structure, which can undergo resonant Auger decay. Due to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold they do not appear as separate peaks. However, one can determine their excitation energies from the maxima of the resonant Auger features. Thus, for \cli, the lowest core excited state is located at 2825.2\,eV, which agrees very well with the position of the Cl$^{-}$ 1s$\,\rightarrow\,$4p excitation determined from Cl K-edge XAS experiments in MgCl$_2$.6H$_2$O and of SrCl$_2$/SrCl$_2$.6H$_2$O \citep{sugiura82:681} and MCl$_{4}^{-}$ compounds \citep{shadle95:2259}. In the case of \ki, there are two dispersive features with maxima at photon energies of 3611.2\,eV (B) and 3611.6\,eV (C), respectively (Fig.\ \ref{fg:2dmap_k}). The positions of these two core excited states are close to the energy of the 1s$\,\rightarrow\,$4p excitation in bare \ki, 3610.7\,eV \citep{hertlein06:062715}.

Unlike the normal Auger decay, which proceeds in a fairly similar way in the two ions, the resonant Auger features appear to be quite different for \cli~and \ki. In the spectrum of \cli~shown in Fig.\ \ref{fg:2dmap_cl} there are two dispersive features on the high kinetic energy side of the main $^1$S and $^1$D lines, i.e.\ at 2825.2\,eV photon energy and 2374.6 and 2383.4\,eV kinetic energy. In the case of \ki, only a dispersive feature close to the $^1$D main peak is observed (feature B) with a maximum located at $h\nu = $3611.2 \,eV and 2969.2 \,eV kinetic energy. An additional feature appears as a separate island away from the main lines on the 2D map of \ki. It is located at $h\nu = $3611.6\,eV and 2978.1\,eV kinetic energy (feature C), thus it is separated by approximately 400\,meV photon energy and 8.3\,eV kinetic energy from the feature B. 
%Unlike in the case Cl$^{-}$ the dispersive feature close to the $^1$S main line is not observed in K$^{+}$ due to presence of a strong {\color{red}background (@DENIS?)}.

%In order to get a better understanding of these features, we will first consider the Auger spectrum of the isoelectronic Ar presented in Refs.\ \citep{ceolin15:022502,guillemin15:012503}.

%First, from the 2D map of Ar one can extract information about the nature of the core excited states below threshold. The pre-edge structure in the XAS spectrum of Ar consists of the 1s$\,\rightarrow\,$4p and 1s$\,\rightarrow\,$5p excitations. Higher core excited states cannot be identified in the XAS spectrum due to their lifetime broadening and proximity to the ionization threshold. The same excitations were observed in the XAS spectrum of bare \ki~ions \citep{hertlein06:062715}. Again, the identification of 1s$\,\rightarrow\,$np states with n$\,>\,$5 was not possible in the case of \ki.

%Second, the 2D map of Ar carries information about the states populated in the resonant Auger processes following core excitation. In the case of Ar, the Ar 1s$\,\rightarrow\,$4p and 1s$\,\rightarrow\,$5p core excited states undergo both pure spectator and shake-up resonant Auger decay leading to the population of Ar$^{2+}$(2p$^{-2}$np) (n$ = 4 - 6$) final states. As a result, apart from the main Ar$^{2+}(2p^{-2})$ $^1$D and $^1$S lines which result from normal Auger decay, additional dispersive features are observed. For example, the 1s$\,\rightarrow\,$4p core excited state undergoes both pure spectator and shake-up resonant Auger decay. The former results in an island shifted with respect to the main $^1$D line by $\sim$4-5\,eV kinetic energy, whereas the fingerprint of the shake-up process is a feature appearing at the same kinetic energy as the  main $^1$D line. Moreover, the intensities of the observed shake-up features are lower compared to those of the pure spectator Auger decay. In aqueous solutions, one can expect the 2D map to be fairly different as both the initial core excited states and the final Auger states will be influenced by the presence of the solvent.

\begin{figure}[h]
\centering
\includegraphics[scale=0.6]{figures/xas_spectra.eps}
\caption{
XAS spectra of the lowest K-shell transitions in the bare K$^{+}$ (lower left panel) and Cl$^{-}$ (lower right panel) ions and their 6-coordinated clusters (upper left panel, \ki(H$_2$O)$_6$, and upper right panel, \cli(H$_2$O)$_6$). The theoretical stick spectra were convolved with a Lorentzian profile of FWHM 0.74\,eV for \ki~and 0.62\,eV for \cli~in order to account for the lifetime broadening. The stick spectrum corresponds to the projections $|a_{nl}^{i}|^2$ of the SONOs corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$\,\rightarrow\,$3d, 1s$\,\rightarrow\,$4p, and 1s$\,\rightarrow\,$5p states in the bare K$^+$ and \cli~ions (Eq.\ \ref{eq:sono_proj}). The theoretical XAS spectra of \ki~were shifted to higher photon energies by 6.7\,eV, which corresponds to the difference between the computed and experimental core excitation energies of the 1s $\rightarrow$ 4p excitation in the bare ion taken from Ref.\ \citep{hertlein06:062715}.}
\label{fg:xas_kcl}
\end{figure}

In order to rationalize the pre-edge region of the experimental XAS spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core excited states of the bare \ki~and \cli~ions and their hexa-coordinated clusters. The theoretical XAS spectra are presented in Fig.\ \ref{fg:xas_kcl}. In the bare ions (lowermost panels on Fig.\ \ref{fg:xas_kcl}), the lowest energy peak corresponds to the dipole allowed 1s$\,\rightarrow\,$4p state. The next dipole allowed state, 1s$\,\rightarrow\,$5p, is located 4.3\,eV and 10.8\,eV higher in the cases of \ki~and \cli, respectively. Together with the two dipole allowed transitions, we show the dipole forbidden 1s$\,\rightarrow\,$3d state on the XAS spectra of the bare ions. It is noteworthy that the positions of the 1s$\,\rightarrow\,$4p and 1s$\,\rightarrow\,$3d states are inverted in \ki~and \cli. In the case of Cl$^{-}$ the 1s$\,\rightarrow\,$4p excitation has lower energy and the 1s$\,\rightarrow\,$3d excitation is close to the 1s$\,\rightarrow\,$5p state. On the contrary, in K$^{+}$ the 1s$\,\rightarrow\,$3d excitation has lower energy and lies below the 1s$\,\rightarrow\,$4p state. We note in passing that the intensity of the Cl$^{-}$(1s$\,\rightarrow\,$4p) state is lower than that of the \cli(1s$\,\rightarrow\,$5p) state contrary to what is observed in \ki. This difference can be explained with the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$\,\rightarrow\,$4p compared to the 1s$\,\rightarrow\,$5p transition in \cli~(see Fig.\ \ref{fg:rdens_ions}).

The water molecules in the first solvation shell have several effects on the core excited states. First, upon addition of water molecules, the degeneracy of the 1s$\,\rightarrow\,$4p state is lifted and the intensity of the resulting states in the cluster drops. Moreover, the character of these states changes -- they are no longer of pure atomic character but they rather interact with states of the neighboring water molecules (shown as grey bars) and with other closely lying states of the bare ion, such as the dipole allowed 1s$\,\rightarrow\,$5p and dipole forbidden 1s$\,\rightarrow\,$3d state. Thus, the latter also acquire intensity in the cluster due to mixing with the dipole allowed states in the ligand field of the solvent. A similar effect was observed in the XAS spectra of microsolvated clusters of Na$^{+}$ and Mg$^{2+}$ \citep{miteva16:16671}.

Further we assume that only the lowest peak in the theoretical XAS spectra is populated in the experiment for two reasons. First, due to the lifetime broadening, it spreads over approximately 2\,eV which coincides with the width of the pre-edge structure in the experimental XAS spectra. Second, the splitting between the first core excited state and the ionization threshold in the experiment is 0.7\,eV for \ki~and 0.2\,eV for \cli, and thus it is smaller than the splitting between the first and second peak in the theoretical spectra (1.5\,eV for \ki~and $\sim$3\,eV for \cli, Fig.\ \ref{fg:xas_kcl}). In the 6-coordinated cluster (Fig.\ \ref{fg:xas_kcl} upper left panel), which represents the complete first solvation shell around \ki, the lowest peak in the spectrum contains three states. The lowest and highest lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character. The low intensity state in between these two states has a predominantly 1s$\,\rightarrow\,$3d character. Since the dispersive feature B appears at lower excitation energies compared to the feature C, we assume that it is produced in the resonant Auger decay of the lowest core excited states of \ki, which are predominantly of 1s$\,\rightarrow\,$4p character. Moreover, we can attribute the feature C to the resonant Auger decay of the low intensity dipole forbidden 1s$\,\rightarrow\,$3d state. Thus, we explain both the energy splitting of $\sim$400\,meV photon energy of the two features, and the fact that island C has lower intensity than feature B.

In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first peak. Since there are no other ionic states close the the 1s$\,\rightarrow\,$4p state in the ion, this state preserves its character in the cluster and interacts with states of the nearest water molecules. We attribute the two dispersive features on the 2D map of \cli~to the resonant Auger decay of this core excited state. {\color{red}Since the photon energy step in the experimental spectrum coincides with the splitting between the two dispersive features, we assume that they originate from the decay of the same core excited state.}

To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest K$^{2+}$(2p$^{-2}$nl) and Cl$^{0}$(2p$^{-2}$nl) states of the bare ions corresponding to the lowest final spectator resonant Auger states. They are shown as bars in the upper panels on the experimental resonant Auger spectra on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}. In both cases of \ki~and \cli, we shifted the lowest 2p$^{-2}$4p states such that they coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line. Out of all final states we show only the doublets assuming that the quartet states are populated with a very low probability (REFS). The 2p$^{-2}$nl states of \ki~and \cli~are substantially different and they reflect the fact that the 3d unoccupied orbitals of \ki~are lower than the 4p orbitals, which is the opposite of what is observed in \cli.

%As mentioned above, we assume that the island B is produced in the decay of the lowest lying core excited state of the hexa-hydrated \ki~cluster, which is of predominantly 1s$\,\rightarrow\,$4p character. 
As mentioned above, we attribute the island B to the decay of the lowest lying core excited state of the hexa-hydrated \ki~cluster, which is of predominantly 1s$\,\rightarrow\,$4p character. 
Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$\,\rightarrow\,$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character located between 2969 and 2970\,eV are populated in this case. As can be seen from the Auger electron spectrum at $h\nu = $3610.7\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki~are separated by 5 and 13\,eV from the lowest 2p$^{-2}$3d states. Thus, the lower-kinetic energy group of 2p$^{-2}$3d states almost coincides with the position of the island C. Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the dipole forbidden 1s$\,\rightarrow\,$3d state of the 6-coordinated \ki~cluster to the group of 2p$^{-2}$3d states lying around 2975\,eV. The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C. This difference may be due to the fact that we do not account for the effect of the solvent molecules in our calculation.

In the Cl$^{0}$(2p$^{-2}$nl) spectrum there are two groups of states split by about 7\,eV (see upper panel of Fig.\ \ref{fg:2dmap_cl}). The lower kinetic energy group corresponds to the 2p$^{-2}$($^1$S)4p states, whereas the higher kinetic energy group corresponds to the 2p$^{-2}$($^1$D)4p states. The splitting between the two groups is in good agreement with the experimental splitting between the dispersive features on the high kinetic energy sides of the $^1$S and $^1$D main peaks. Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$\,\rightarrow\,$4p core excited state of \cli~to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.

\subsection{Delocalization vs resonant Auger decay}

As mentioned above, the delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay. In order to estimate the rate of delocalization of the core excited electron at the pre-edges of \ki~and \cli, we used the core hole clock method. {\color{red}Here, our peaks are not separated as it should be to use the core-hole clock method}

In the case of \cli, a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV at photon energy corresponding to the lowest core excitation, $h\nu = $2825.2\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel). The position of the first peak coincides with the main $^1$D line resulting from normal Auger, whereas the second peak at 2383.5\,eV corresponds to the final resonant Auger states 2p$^{-2}$($^1$D)4p. By fitting the peak with two Voigt functions, we determine the ratio of the intensities of these peaks to be $\sim$1. Consequently, the delocalization time is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs. The fast delocalization in this case is a result of the fact that the energy splitting between the \cli~(1s$\,\rightarrow\,$4p) resonance and the ionization threshold is 0.2\,eV, and thus, smaller than the lifetime broadening of 0.62\,eV.

In the case of \ki, the resonant Auger process is faster and moreover, the core excited state appears 1.2\,eV below the ionization threshold, thus one can expect slower delocalization compared to \cli$_{\text{aq}}$. The normal and resonant Auger parts of the peak between 2967 and 2972\,eV taken at the photon energy corresponding to the first resonance are not separated. Thus, the application of the core-hole clock method is not rigorous. Our estimate of the intensity ratio using the core-hole clock method shows that the delocalization at the pre-edge is indeed slower, taking place within 2 -- 3\,fs, compared to the resonant Auger decay, which occurs within 0.9\,fs.

%
%
%The formation of such an island on the 2D map of \ki$_{\text{aq}}$ can result from several processes: shake-up resonant Auger decay, similar to the case of Ar \citep{ceolin15:022502}, spin-orbit splitting in the final states, core-like ICD process, or population of dipole forbidden states, which is a result of symmetry breaking in the presence of the solvent. 
%
%\begin{enumerate}
%
%\item[a)] Shake-up resonant Auger decay
%
%A separate island at 2666\,eV kinetic energy and 3203.5\,eV photon energy is observed on the 2D map of Ar (see Fig.\ 2 in \citep{ceolin15:022502}. This island results from resonant Auger decay of the Ar 1s$\,\rightarrow\,$4p state to Ar$^{2+}$(2p$^{-2}$4p) states. The 1s$\,\rightarrow\,$4p state undergoes also shake-up resonant Auger decay, resulting in the population of Ar$^{2+}$(2p$^{-2}$5p) states which appear as a separate feature at the same photon energy, but at lower kinetic energies, 2662\,eV.
%
%
%A similar shake-up decay can be expected for the 1s$\,\rightarrow\,$4p state of \ki. As a first step, we estimate the splitting between the 2p$^{-2}$4p and 2p$^{-2}$5p final states. Using the $(Z+2)$-approximation, the splitting between the 2p$^{-2}$4p and 2p$^{-2}$5p states of K$^{3+}$ is equal to the splitting between the 3p$^6$4p and 3p$^6$5p states of Sc$^{3+}$. From the NIST database \citep{NIST_ASD} for the bare ion we obtain $\sim$8.2\,eV, which agrees with the splitting between the island and the dispersive feature close to the $^1$D main line on the 2D map of \ki$_\text{aq}$ (Fig.\ \ref{fg:2dmap_k}). As a second step, we compare the intensity ratio between the two dispersive features in \ki$_{\text{aq}}$ with that in Ar. As can be seen from Fig.\ \ref{fg:intensity_ratio} the lower-lying peak, which is attributed to the K$^{3+}$(2p$^{-2}$5p) state has higher intensity compared to the higher-lying peak. The intensity of the two peaks in Ar is exactly the opposite implying a lower shake-up probability. Another counterargument against the shake-up origin of the island is that if one compares the maxima of the two dispersive features B and C, one sees that the feature B appears at lower photon energies than C. This is opposed to Ar, where the island originating from normal Auger decay appears at lower photon energies.
%
%Another question is whether the 2p$^{-2}$5p states can be populated in a solution. To address this issue, on Fig.\ \ref{fg:k_2p4nl_raddens} we compare the radial density distributions of the natural orbitals occupied by the excited electron in the K$^{3+}$(2p$^{-2}$4p) and K$^{3+}$(2p$^{-2}$5p) states. The former distribution is quite compact, with 86\% of the electron density within the first solvation shell, whereas only about 20\% of the electron density in the  K$^{3+}$(2p$^{-2}$5p) state is within the first solvation shell.
%
%
%Therefore, we conclude that the features B and C on the 2D map of \ki$_{\text{aq}}$ Fig.\ \ref{fg:2dmap_k} are not a result of a shake-up and normal Auger decay of the \ki(1s$\,\rightarrow\,$4p) state.
%
%\end{enumerate}
%
%
%{\color{blue}\bf Discuss the possibility for non-local Auger decay! Spin-orbit splitting of the final states: it cannot give such a big difference (of 8\,eV)}

### 2018-01-09 abstract.tex
Kolya's changes (Jan 9)
Auger figure, author list

@@
+%Kolya and Nico corrected Jan 8
 X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in a solution.
-In this work we use a combination of these spectroscopies to study the electronic structure and decay of aqueous KCl at the K-edges of \ki~and \cli.
+In this work we use a combination of these spectroscopies to study the electronic structure and decay in aqueous KCl at the K-edges of \ki~and \cli.
 Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features.
@@
 The reverse orbital order in the two ions is reflected in both the ordering of the core excited states and in the final states populated in the resonant Auger decay.
-Furthermore, the energetic proximity of the 3d and 4p virtual states in the bare \ki~ion leads to their mixing in the presence of the solvent, and to the population of the dipole forbidden 1s$\,\rightarrow\,$3d state upon K-shell excitation in an aqueous solution.
+The energetic proximity of the 3d and 4p virtual states in the bare \ki~ion leads to their mixing in the presence of the solvent, and to the population of the dipole forbidden 1s$\,\rightarrow\,$3d state upon K-shell excitation in an aqueous solution.
 The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.

### 2018-01-09 introduction.tex
Kolya's changes (Jan 9)
Auger figure, author list

@@
 X-ray absorption and Auger electron spectroscopies are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase.
-Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions \citep{Pokapanich09:7264}, and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
+Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions \citep{nagasaka14:4388}, and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
 Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy.

### 2018-01-09 master.tex
Kolya's changes (Jan 9)
Auger figure, author list

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=jacsat,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings

\usepackage{color}
\usepackage{xr}
\externaldocument{suppinfo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

\newcommand{\cli}{Cl$^{-}$}
\newcommand{\ki}{K$^{+}$}

\newcommand{\tsveta}[1]{\textcolor{red}{#1}}
\newcommand{\nico}[1]{\textcolor{red}{#1}}
\newcommand{\kolya}[1]{\textcolor{blue}{#1}}
\newcommand{\denis}[1]{\textcolor{green}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Tsveta Miteva}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Nikolai Kryzhevoi}
\affiliation{Theoretische Chemie, Physikalisch-Chemisches Institut, Universit\"at Heidelberg, Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}

\author{Nicolas Sisourat}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Ch. Nicolas}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Wandared Pokapanich}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Th. Saisopa}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{P. Songsiriritthigul}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Y. Rattanachai}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Andreas Dreuw}
\affiliation{Interdisciplinary Center for Scientific Computing, Ruprecht-Karls University, Im Neuenheimer Feld 205A, D-69120 Heidelberg, Germany}

\author{Jan Wenzel}
\affiliation{Interdisciplinary Center for Scientific Computing, Ruprecht-Karls University, Im Neuenheimer Feld 205A, D-69120 Heidelberg, Germany}

\author{Ralph P\"{u}ttner}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{J\'{e}r\^ome Palaudoux}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Gunnar \"{O}hrwall}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Lorenz S. Cederbaum}
\affiliation{Theoretische Chemie, Physikalisch-Chemisches Institut, Universit\"at Heidelberg, Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}

\author{Jean Pascal Rueff}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}

\author{Denis C\'{e}olin}
\email{denis.ceolin@synchrotron-soleil.fr}
\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
  {The electronic structure of aqueous KCl revealed by X-ray absorption and Auger electron spectroscopy
\\  
  The all-seeing eye of Auger electron spectroscopy: a study on aqueous KCl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{AES,XAS}
\keywords{Solvated ions, Auger spectroscopy, X-ray absorption spectroscopy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

\includegraphics[scale=0.82]{figures/graphical.png}
%Some journals require a graphical entry for the Table of Contents.
%This should be laid out ``print ready'' so that the sizing of the
%text is correct.
%
%Inside the \texttt{tocentry} environment, the font used is Helvetica
%8\,pt, as required by \emph{Journal of the American Chemical
%Society}.
%
%The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
%permitted for  \emph{Journal of the American Chemical Society}
%graphical table of content entries. The box will not resize if the
%content is too big: instead it will overflow the edge of the box.
%
%This box and the associated title will always be printed on a
%separate page at the end of the document.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
 \input{abstract.tex}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{introduction.tex}

\input{methods.tex}

\input{results.tex}

\input{conclusion.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "Acknowledgement" section can be given in all manuscript
%% classes.  This should be given within the "acknowledgement"
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Acknowledgement}

\begin{acknowledgement}

\tsveta{We thank Prof.\ Nobuhiro Kosugi and Dr.\ Matja\v{z} \v{Z}itnik for the fruitful discussions?.}
Experiments were performed at the GALAXIES beamline, SOLEIL Synchrotron, France (Proposal No. 20140160). The authors are grateful to the SOLEIL staff for assistance during the beamtime. This project has received funding from the Research Executive Agency (REA) under the European Union$'$s Horizon 2020 research and innovation programme Grant agreement No 705515. Campus France and the PHC SIAM exchange program are acknowledged for financial support.

\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The same is true for Supporting Information, which should use the
%% suppinfo environment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{suppinfo}

\begin{itemize}
  \item suppinfo.pdf: contains the radial density distributions of the core excited states of the bare ions.
\end{itemize}

\end{suppinfo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{Bibliography}

\end{document}

### 2018-01-11 conclusion.tex
kolya's changes introduced (jan 11)
All of Kolya's changes introduced, conclusion done, Gildas paper
included

% w Kolya's and Nico's corrections
\section{Conclusion}\label{sec:concl}

Using a combination of x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, in this work we studied the electronic structure of aqueous solution of KCl at the K-edges of both K and Cl. The Auger electron spectra of both ions as a function of photon energy exhibit features of normal as well as resonant Auger processes. To interpret the resonant Auger features in the experimental spectrum, we performed {\it ab initio} calculations on microsolvated clusters of \ki~and \cli. Our calculations show that the energy ordering of the 3d and 4p virtual orbitals of \cli~is inverted compared to \ki, and also that the energy splitting between the bright 1s$\,\rightarrow\,$4p and dark 1s$\,\rightarrow\,$3d core excited states is larger in the chlorine case. Thus, the energetic proximity of the 3d and 4p orbitals in the bare \ki~ion results in the dipole forbidden 1s$\,\rightarrow\,$3d state acquiring intensity in a solution as a result of mixing with the dipole allowed 1s$\,\rightarrow\,$4p excitation. The spectator Auger decay of this state produces an additional dispersive feature which is manifest as a separate island in the Auger electron spectrum at high kinetic energies. In the case of \cli~the two core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$\,\rightarrow\,$4p state are observed in the spectrum. Moreover, using the core-hole clock method we estimated the time of delocalization of the core excited electron at the pre-edge region of both ions. Whereas in \ki$_{\text{aq}}$ the delocalization of the core excited electron is slower than the resonant Auger process, in the case of \cli$_{\text{aq}}$ the two processes occur on a comparable timescale.

%{\bf\color{red}A nice concluding ``wow'' sentence}
Our work shows that the combination of x-ray absorption and resonant Auger spectroscopies is a sensitive probe of the electronic structure of solvated ions. The reported results are an important first step in the study of the electronic decay processes following photoabsorption in the tender x-ray regime, and they can have implications in revealing the mechanisms of radiation damage in biologically relevant systems.

### 2018-01-11 introduction.tex
kolya's changes introduced (jan 11)
All of Kolya's changes introduced, conclusion done, Gildas paper
included

@@
 X-ray absorption and Auger electron spectroscopies are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase.
-Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions \citep{nagasaka14:4388}, and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
+Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
 Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy.
 The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decay.
-Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes such as interatomic Coulombic decay (ICD) and related processes \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708} are possible.
+Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes charge and energy transfer \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003} are possible.
 
 The course of a decay cascade depends on the character of the initially populated states.
-This has been well understood in atoms and molecules in gas phase (REFS) \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,Miteva14:064307}.
-In the case of a core ionized state, the Auger decay process, designated as normal Auger decay (see Fig.\ \ref{fg:auger}), leads to the population of doubly ionized final states localized on the initially ionized unit \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415}.
+This has been well understood in atoms and molecules in gas phase  \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001}.
+In the case of a core ionized state, the Auger decay process, designated as normal Auger decay (see Fig.\ \ref{fg:auger}), leads to the population of doubly ionized final states localized on the initially ionized unit {\color{red}\citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415}}.
 Auger processes in rare gas clusters have been also investigated (refs).
 The normal Auger decay process in clusters proceeds similarly to that in atoms or molecules.
-However, in the case of a core excited state, the resonant Auger process competes with the process of delocalization of the excited electron in clusters \citep{Bjorneholm95:3017}.
+However, in the case of a core excited state, the resonant Auger process competes with the process of delocalization of the excited electron in clusters.
 If the initially core excited electron delocalizes within the lifetime of the core hole, then normal instead of resonant Auger decay is observed \citep{Bjorneholm95:3017}.
 
-In a solution, the electronic decay cascades initiated by x-ray photoabsorption are different compared to those in rare gas clusters due to the shorter distances and stronger interatomic interactions.
-In particular, the solvent molecules have two effects -- first, they strongly affect the excited \citep{miteva16:16671} or ionized states of the ion and second, they can participate in the decay processes, leading to the population of delocalized final states, and thus ionizing the surrounding environment \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237}.
+In a solution, the electronic decay processes initiated by x-ray photoabsorption are different compared to those in rare gas clusters due to the shorter distances and stronger interatomic interactions.
+In particular, the solvent molecules have two effects -- first, they strongly affect the excited \citep{miteva16:16671} or ionized states of the ion and second, they can participate in the decay processes, leading to the population of charge-separated final states, and ionization of the surrounding environment \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,ceolin17:263003}.
 Moreover, the process of delocalization of the initially excited electron also occurs in aqueous solutions \citep{Nordlund07:217406,Ottosson11:13489}.
@@
 The O K-edge is located in the soft x-ray range of photon energies.
-Going higher in photon energy, in the hard x-ray regime, the lifetimes of the core ionized or core excited states become even shorter, on the order of 1\,fs (REF).
+Going higher in photon energy, in the tender and hard x-ray regimes, the lifetimes of the core ionized or core excited states become even shorter, on the order of 1\,fs.
 And thus, it is even more imperative to reveal whether the delocalization of the core excited electron occurs within the lifetime of the core hole.
 
-The aim of this work is to elucidate the nature of the states populated upon x-ray irradiation of solvated ions in the hard x-ray regime, and furthermore, to understand whether the process of delocalization influences the resonant Auger decay.
-To this end, we used Auger electron spectroscopy together with x-ray absorption spectroscopy in the hard x-ray regime to study aqueous potassium chloride at the K-edges of both \ki~and \cli.
+The aim of this work is to elucidate the nature of the states populated upon x-ray irradiation of solvated ions in the tender x-ray regime, and furthermore, to understand whether the process of delocalization influences the resonant Auger decay.
+To this end, we used Auger electron spectroscopy together with x-ray absorption spectroscopy in the tender x-ray regime to study aqueous potassium chloride at the K-edges of both \ki~and \cli.
 In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, localized core excited states are populated.
@@
 In both ions, there is a competition between resonant Auger decay and delocalization of the excited electron.
-Using the core-hole clock method (REFS), we show that in \ki~delocalization at the pre-edge is weak, whereas in the case of \cli, due to the energetic proximity of the core excited state to the K-edge, the rate of delocalization is of the same order as that of the resonant Auger process.
+Using the core-hole clock method 	 we show that in \ki~delocalization at the pre-edge is weak, whereas in the case of \cli, due to the energetic proximity of the core excited state to the K-edge, the rate of delocalization is of the same order as that of the resonant Auger process.
 Moreover, we observe that although the \ki~and \cli~ions are isoelectronic, they have different fingerprints in the resonant Auger spectra.
-With the aid of high-level {\it ab initio} calculations of the initial and final states of the resonant Auger process of both the bare ions and their microsolvated clusters, we demonstrate that these differences are a result of the different electronic structure of the two ions, thus confirming that the XAS/AES technique is a sensitive probe of the electronic structure of solutions.
+With the aid of high-level {\it ab initio} calculations of the initial and final states of the resonant Auger process of both the bare ions and their microsolvated clusters, we demonstrate that these differences result from different electronic structures of the two ions, thus confirming that the combination of XAS and AES techniques is a sensitive probe of the electronic structure of solutions.
 
@@
 \includegraphics{figures/auger_process.eps}
-\caption{Schematic representation of the normal and resonant Auger processes.}
+\caption{Schematic representation of the normal and resonant Auger processes of the isoelectronic \ki~and \cli~ions. The charges of the final Auger states in the two ions are also shown.}
 \label{fg:auger}

### 2018-01-11 master.tex
kolya's changes introduced (jan 11)
All of Kolya's changes introduced, conclusion done, Gildas paper
included

@@
 
-\tsveta{We thank Prof.\ Nobuhiro Kosugi and Dr.\ Matja\v{z} \v{Z}itnik for the fruitful discussions?.}
+We thank Prof.\ Nobuhiro Kosugi and Dr.\ Matja\v{z} \v{Z}itnik for the fruitful discussions.
 Experiments were performed at the GALAXIES beamline, SOLEIL Synchrotron, France (Proposal No.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{Bibliography}
+\bibliography{F:/Articles/bibliography/Bibliography}
 

### 2018-01-11 methods.tex
kolya's changes introduced (jan 11)
All of Kolya's changes introduced, conclusion done, Gildas paper
included

\section{Methods} \label{sec:methods}
\subsection{Experimental}
% Denis, please have a look at the experimental part and see if all the references have been correctly included

For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline, in collaboration with the Microliquids Company. Details of the beamline are given in the reference [JPR] and details on the electron spectrometer are given in the reference \citep{ceolin15:022502,ceolin13:188}. Due to the limited amount of space available \kolya{in} front of the analyzer lens and due to the limited number of ports available on the main vacuum chamber, the challenge was to arrange all the elements composing the microjet setup in a very compact manner. A differentially-pumped tube in which the microjet assembly is inserted, is installed in front of the spectrometer lens and can be moved independently from the main vacuum chamber by means of a three axes motorized manipulator. Two holes of 2 mm diameter allow the photons to go in and out of the tube\kolya{. A third hole,} on which is mounted a skimmer having a 500$\mu$m diameter hole, allows the electrons created at the interaction point to go in the direction of the spectrometer lens. To ensure a proper vacuum in the differentially pumped tube, a {\color{red}5-way cross} is connected to it and holds a 1200 l/s turbo pump, a liquid nitrogen trap, a vacuum gage and the liquid/electrical feedthroughs. A rail, fixed at the bottom of the tube, is used to {\kolya slides} precisely an insert on which the different elements necessary for the injection, control, collection and visualization of the liquid are mounted.

The head of this insert is mostly composed by: a glass capillary fixed by a dedicated peek-piece, a catcher in CuBe with a 300$\mu$m hole, a piezo motors stage allowing a precise control of these last two parts, and a camera. The catcher is placed at a distance of about 5mm from the capillary and is permanently pumped in order to extract the liquid from the vacuum chamber. For the present experiment, a 0.5M KCl aqueous solution is injected in a capillary having a 30$\mu$m diameter, by a HPLC pump with a constant flux of 1.6 ml/min. The catcher temperature is controlled so that the liquid does not freeze before its extraction. Considering that the photon propagation axis, the spectrometer lens axis and the liquid microjet form an \kolya{orthogonal trihedron}, the piezo motorization allows moving the liquid microjet along the photon propagation and the lens axes during the experiment if necessary. The catcher can be moved by the piezo motors along the photon propagation axis only. A simple camera is used to control the liquid jet positioning as compared with the catcher hole. The alignment of the full head (particularly capillary plus catcher) as compared with the X-ray beam is performed by moving the whole system using the 3-axes motorized manipulator. The alignment of the setup is performed by measuring the O1s XPS peak intensity of a simple salt aqueous solution, and by optimizing the liquid phase vs gas phase ratio. The pressure in the main chamber was kept below the 10$^{-5}$ mbar range whereas it was kept at about 10$^{-4}$ mbar in the differentially pumped tube when the HPLC pump \kolya{was ON}. Our equipment is an updated version of the equipment used in the references {\color{red}WHAT r these refs [3-5]?}. The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water. Filtering and degazing procedures were systematically performed before injecting the solution into the microjet by the HPLC pump.

\subsection{{\bf{\it Ab initio}} calculations}

The theoretical X-ray absorption spectra were computed \tsveta{for the hexa-coordinated clusters of both ions, \ki(H$_2$O)$_6$ and \cli(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \citep{Ohtaki93:1157,soper06:180,ma14:1006}}. The two structures were optimized at the DFT level of theory using the B3LYP functional and the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,Blaudeau97:5016}. The geometry optimization was performed with the Gaussian 09 package \citep{g09}. In order to obtain more realistic structures corresponding to the bulk solution, we carried out constrained geometry optimization starting with the equilibrium gas-phase geometries \citep{lee99:3995}(REF for Cl-) belonging to the D$_3$ point group and increasing the angle $\theta$ between the K-O/Cl-O bond and the $C_3$ axis to 55$^{\circ}$ in the case of \ki~and 50$^{\circ}$ in the case of \cli. This angle was chosen such that the O-K-O and O-Cl-O angles are around the maxima of the angular distributions obtained from quantum mechanics / molecular mechanics dynamical simulations in Ref.\ \citep{ma14:1006}. Moreover, we fixed the K-O and Cl-O distances to 2.840~\AA~and 3.140~\AA, respectively, such that they correspond to the distances from other theoretical and experimental works \citep{ge13:13169,gora00:7,Ohtaki93:1157,soper06:180,ma14:1006}. The hexa-coordinated structures are presented in Fig.\ \ref{fg:xas_kcl}. %In both cases, they belong D$_3$ point group \citep{rao08:12944,ge13:13169}.

The energies and transition moments of the core excited states of the microsolvated clusters were computed with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}. In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding the f functions) was used for all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and an additional set of 2s, 2p and 2d diffuse functions was added on K. In our calculations the core space comprises the 1s orbital of K$^{+}$ or \cli, whereas the remaining occupied orbitals are included in the valence space. For the calculations of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and \cli(H$_2$O)$_6$. To account for the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Lorentzian of FWHM 0.74\,eV and 0.62\,eV in the case of \ki~and \cli, respectively \citep{Krause79:329}. We analyzed the core excited states by expanding the singly occupied natural orbitals (SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or \cli~ion $\chi_{nl}$
%
\begin{equation}\label{eq:sono_proj}
\psi_{i} = \sum_{nl} a^{i}_{nl} \chi_{nl}
\end{equation}
%
where $n$ and $l$ stand for the principal and orbital quantum numbers as described in Ref.\ \citep{miteva16:16671}. The expansion coefficients $a^{i}_{nl}$ show the degree of delocalization of the excited electron and the mixing of the core excited states in the crystal field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl}).

The final states following KLL resonant Auger decay of K$^{+}$ and \cli~were computed at the Configuration Interaction Singles (CIS) level using the Graphical Unitary Group Approach (GUGA) as implemented in the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS}. In order to account for the relaxation effects upon core ionization, we used a restricted open-shell Hartree-Fock reference wave function with a hole in the 2s orbital of both \ki~and \cli.  We used the 6-311++G(2d,2p) basis set \citep{Blaudeau97:5016} augmented with 2s, 2p, 2d diffuse functions on \ki, and the cc-pVTZ basis set augmented with 6s, 6p, 6d diffuse Kaufmann-Baumeister-Jungen continuum-like functions \citep{Kaufmann89:2223} on \cli. The active space comprises the 2s and 2p orbitals of K/Cl with occupancy fixed to 6 and all virtual orbitals with occupancy fixed to 1. The remaining doubly occupied orbitals were frozen in the calculation. \citep{mosnier16:061401}

### 2018-01-11 results.tex
kolya's changes introduced (jan 11)
All of Kolya's changes introduced, conclusion done, Gildas paper
included

@@
 The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p(red) doublet resonant Auger states of K$^{+}$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).
-The states are shifted with respect to the lowest quartet state with electron configuration K$^{2+}$(2p$^{-2}$($^3$P) 4s).}
+The features A, B and C are discussed in the text.}
 \label{fg:2dmap_k}
@@
 The upper panel shows two spectra at photon energies 2825.2\,eV, and 2830.0\,eV below and above the ionization potential at 2825.4\,eV, respectively.
-The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p(red) doublet resonant Auger states of K$^{+}$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).
-The states are shifted with respect to the lowest quartet state with electron configuration Cl$^{0}$(2p$^{-2}$($^3$P) 4s).}
+The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p(red) doublet resonant Auger states of K$^{+}$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).}
 \label{fg:2dmap_cl}
@@
 
-The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization in \ki~and \cli~results in the population of 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
-The $^3$P final states are not observed in the experiment since they are forbidden {\color{red}from parity conservation rules} (REF?).
+The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization of aqueous \ki~and \cli~can be written as follows
+%
+\begin{align*}
+\gamma + \text{K}^{+}_{\text{aq}} \rightarrow \text{K}^{2+}_{\text{aq}} (1s^{-1}) \rightarrow \text{K}^{3+}_{\text{aq}} (2p^{-2}) + e^{-}_{\text{Auger}}\\
+\gamma + \text{Cl}^{-}_{\text{aq}} \rightarrow \text{Cl}^{0}_{\text{aq}} (1s^{-1}) \rightarrow \text{Cl}^{+}_{\text{aq}}(2p^{-2}) + e^{-}_{\text{Auger}}
+\end{align*}
+%
+It results in the population of 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
+The $^3$P final states are not observed in the experiment since they are forbidden from parity conservation rules.
 In the case of Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ (2p$^{-2}$) $^1$S and $^1$D states are located at 2373.2\,eV and 2382.1\,eV kinetic energy (see Fig.\ \ref{fg:2dmap_cl}).
@@
 
-The KL$_{2,3}$L$_{2,3}$ Auger lines are not supposed to disperse with photon energy except close to threshold due to the interaction between the photoelectron and Auger electron, i.e.\ the so-called post-collision interaction (PCI).
+The KL$_{2,3}$L$_{2,3}$ Auger lines do not disperse with photon energy except close to threshold due to the interaction between the photoelectron and Auger electron, i.e.\ the so-called post-collision interaction (PCI).
 As a result of this interaction, first, the peaks in the Auger spectrum become asymmetric with a shoulder at high kinetic energies, and second, they are shifted to higher kinetic energies close to threshold \citep{russek86:911,guillemin15:012503}.
 Consequently, one can attribute the high kinetic energy shoulder of the $^1$D and $^1$S peaks on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} as resulting from PCI effect.
-In order to minimize this effect we recorded the KLL Auger spectrum of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ at higher photon energies, $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17} for details).
-The maxima of the $^1$D and $^1$S states were found at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
+In order to quantify this effect we recorded the KLL Auger spectrum of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ at higher photon energies, $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
+In this case, the maxima of the $^1$D and $^1$S states were found at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
 The lines observed at photon energies far from threshold and close to it appear to be shifted by $\sim$1\,eV.
-The magnitude of the shift is the same for both ions, thus, we can conclude that it does not depend on the initial charge of the ion.
+The magnitude of the shift is the same for both ions suggesting that it does not depend on the initial charge of the ion.
 The observed PCI shift of 1\,eV is larger than in the case of the isoelectronic Ar, where its value is $\sim$0.5\,eV at a photon energy of 10 \,eV above threshold \citep{guillemin15:012503}.
@@
 The normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder (A on Fig.\ \ref{fg:2dmap_k}) on the low kinetic energy side at about 2965\,eV kinetic energy.
-This shoulder is a result of charge transfer to the solvent molecules \citep{ceolin17}.
-Such charge-transfer-to-solvent states are also present in \cli, but they were found at lower kinetic energies, and are therefore not observed in the kinetic energy region shown on Fig.\ \ref{fg:2dmap_cl} \citep{ceolin17}.
+This shoulder is attributed to electron transfer from the solvent molecules \citep{ceolin17:263003}.
+In the case of \cli, there is no experimental evidence of such electron transfer processes.
 
@@
 
-The pre-edge regions of the x-ray absorption spectra of \ki~and \cli~shown to the left on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} do not exhibit any high intensity features {\color{red}Here, I mean sharp resonances if it's called like this, compared to Ar for example}.
+\kolya{XAS of Cl- and K+ from previous works?}
+
+The KL$_{2,3}$L$_{2,3}$ Auger decay following resonant K-shell excitation of solvated \ki~and \cli~can be written as follows
+%
+\begin{align*}
+\gamma + \text{K}^{+}_{\text{aq}} \rightarrow \text{K}^{+*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{K}^{2+}_{\text{aq}} (2p^{-2}V') + e^{-}_{\text{Auger}}\\
+\gamma + \text{Cl}^{-}_{\text{aq}} \rightarrow \text{Cl}^{-*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{Cl}^{0}_{\text{aq}}(2p^{-2}V') + e^{-}_{\text{Auger}}
+\end{align*}
+%
+where $V$ and $V'$ denote the virtual orbitals in the excited and singly ionized excited states, i.\ e.\ in the presence of the $1s^{-1}$ and $2p^{-2}$ core holes.
+The character of these states will be discussed below.
+
+The pre-edge regions of the x-ray absorption spectra of \ki~and \cli~shown to the left on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} do not exhibit any high intensity features due to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold.
 Consequently, solely from these spectra, one cannot conclude whether there are core excited states in the pre-edge structure, which can undergo resonant Auger decay.
-Due to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold they do not appear as separate peaks.
 However, one can determine their excitation energies from the maxima of the resonant Auger features.
@@
 
-Unlike the normal Auger decay, which proceeds in a fairly similar way in the two ions, the resonant Auger features appear to be quite different for \cli~and \ki.
+%Unlike the normal Auger decay, which proceeds in a fairly similar way in the two ions, 
+The resonant Auger features produced in the decay of these core excited states appear to be quite different for \cli~and \ki.
 In the spectrum of \cli~shown in Fig.\ \ref{fg:2dmap_cl} there are two dispersive features on the high kinetic energy side of the main $^1$S and $^1$D lines, i.e.\ at 2825.2\,eV photon energy and 2374.6 and 2383.4\,eV kinetic energy.
-In the case of \ki, only a dispersive feature close to the $^1$D main peak is observed (feature B) with a maximum located at $h\nu = $3611.2 \,eV and 2969.2 \,eV kinetic energy.
+In the case of \ki, the $^1$S dispersive line cannot be clearly identified due to the presence of strong background.
+The dispersive feature close to the $^1$D main peak is observed (feature B) with a maximum located at $h\nu = $3611.2 \,eV and 2969.2 \,eV kinetic energy.
 An additional feature appears as a separate island away from the main lines on the 2D map of \ki.
@@
 The stick spectrum corresponds to the projections $|a_{nl}^{i}|^2$ of the SONOs corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$\,\rightarrow\,$3d, 1s$\,\rightarrow\,$4p, and 1s$\,\rightarrow\,$5p states in the bare K$^+$ and \cli~ions (Eq.\ \ref{eq:sono_proj}).
-The theoretical XAS spectra of \ki~were shifted to higher photon energies by 6.7\,eV, which corresponds to the difference between the computed and experimental core excitation energies of the 1s $\rightarrow$ 4p excitation in the bare ion taken from Ref.\ \citep{hertlein06:062715}.}
+The theoretical XAS spectra of \ki~were shifted to higher photon energies by 6.7\,eV, which corresponds to the difference between the computed and experimental core excitation energies of the 1s $\rightarrow$ 4p excitation in the bare ion taken from Ref.\ \citep{hertlein06:062715}.
+\tsveta{A DARKER SHADE OF GREY}}
 \label{fg:xas_kcl}
@@
 The next dipole allowed state, 1s$\,\rightarrow\,$5p, is located 4.3\,eV and 10.8\,eV higher in the cases of \ki~and \cli, respectively.
-Together with the two dipole allowed transitions, we show the dipole forbidden 1s$\,\rightarrow\,$3d state on the XAS spectra of the bare ions.
+Together with the two dipole allowed transitions, we show the dipole forbidden 1s$\,\rightarrow\,$3d states of the bare ions as blue crosses at photon energies \tsveta{3609.XX\,eV in the case of \ki~and 2831\,eV in the case of \cli, respectively}.
 It is noteworthy that the positions of the 1s$\,\rightarrow\,$4p and 1s$\,\rightarrow\,$3d states are inverted in \ki~and \cli.
@@
 In both cases of \ki~and \cli, we shifted the lowest 2p$^{-2}$4p states such that they coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.
-Out of all final states we show only the doublets assuming that the quartet states are populated with a very low probability (REFS).
+Out of all final states we show only the doublets.
+Since the initial core excited states are populated by photon excitation, only doublet states are populated in the resonant Auger decay.
 The 2p$^{-2}$nl states of \ki~and \cli~are substantially different and they reflect the fact that the 3d unoccupied orbitals of \ki~are lower than the 4p orbitals, which is the opposite of what is observed in \cli.
@@
 This difference may be due to the fact that we do not account for the effect of the solvent molecules in our calculation.
+There is a group of 2p$^{-2}$3d states at kinetic energies of 2982\,eV.
+Since no additional experimental features are observed, we conclude that these states are not populated.
 
@@
 Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$\,\rightarrow\,$4p core excited state of \cli~to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.
+Similar dispersive features originating from the decay of the Cl (1s$\,\rightarrow\,$4p) state were observed on the 2D map of chloromethane CH$_3$Cl recorded in the vicinity of the Cl K-edge in gas phase \cite{gold16:133001}.
+In this case, however, additional lower-lying core excited state are observed.
+They result from excitation to the LUMO of CH$_3$Cl, which is a linear combination of the C $2p$ and Cl $3p$ atomic orbitals.
+Since the 3p shell is fully occupied in \cli, such a core excited state is not observed in our experiment.
 
@@
 
+{\color{red}Here, our peaks are not separated as it should be to apply the core-hole clock method}
+
 As mentioned above, the delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
-In order to estimate the rate of delocalization of the core excited electron at the pre-edges of \ki~and \cli, we used the core hole clock method.
-{\color{red}Here, our peaks are not separated as it should be to use the core-hole clock method}
+In order to estimate the rate of delocalization of the core excited electron at the pre-edges of \ki~and \cli, we used the core hole clock method \cite{bjorneholm92:1892,karis96:1380}.
 
@@
 
-In the case of \ki, the resonant Auger process is faster and moreover, the core excited state appears 1.2\,eV below the ionization threshold, thus one can expect slower delocalization compared to \cli$_{\text{aq}}$.
+In the case of \ki, the resonant Auger process is faster than the delocalization and moreover, the core excited state appears 1.2\,eV below the ionization threshold.
+Therefore, one can expect slower delocalization compared to \cli$_{\text{aq}}$.
 The normal and resonant Auger parts of the peak between 2967 and 2972\,eV taken at the photon energy corresponding to the first resonance are not separated.

### 2018-01-11 suppinfo.tex
kolya's changes introduced (jan 11)
All of Kolya's changes introduced, conclusion done, Gildas paper
included

--- 2018-01-09 master.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "tocentry" environment can be used to create an entry for the
-%% graphical table of contents. It is given here as some journals
-%% require that it is printed as part of the abstract page. It will
-%% be automatically moved as appropriate.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tocentry}
+\begin{figure}
+\centering
+\includegraphics[scale=0.3]{figures/fg2_k_6w_okxx_55_rad_dens.eps}
+\caption{Radial density distributions of the singly-occupied natural orbitals occupied by the excited electron in the core excited states 3609.11\,eV (1\,$^{1}$A$_{2}$), 3609.41\,eV (2\,$^{1}$E) and 3609.64\,eV (3\,$^{1}$E) of K$^{+}$(H$_2$O)$_6$.
+The grey line at 2.816\,\AA~represents the equilibrium K-O distance.}
+\label{fg:rad_dens}
+\end{figure}
 
-\includegraphics[scale=0.82]{figures/graphical.png}
-%Some journals require a graphical entry for the Table of Contents.
-%This should be laid out ``print ready'' so that the sizing of the
-%text is correct.
-%
-%Inside the \texttt{tocentry} environment, the font used is Helvetica
-%8\,pt, as required by \emph{Journal of the American Chemical
-%Society}.
-%
-%The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-%permitted for  \emph{Journal of the American Chemical Society}
-%graphical table of content entries. The box will not resize if the
-%content is too big: instead it will overflow the edge of the box.
-%
-%This box and the associated title will always be printed on a
-%separate page at the end of the document.
-
-\end{tocentry}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
- \input{abstract.tex}
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{introduction.tex}
-
-\input{methods.tex}
-
-\input{results.tex}
-
-\input{conclusion.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "Acknowledgement" section can be given in all manuscript
-%% classes.  This should be given within the "acknowledgement"
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Acknowledgement}
-
-\begin{acknowledgement}
-
-\tsveta{We thank Prof.\ Nobuhiro Kosugi and Dr.\ Matja\v{z} \v{Z}itnik for the fruitful discussions?.}
-Experiments were performed at the GALAXIES beamline, SOLEIL Synchrotron, France (Proposal No.
-20140160).
-The authors are grateful to the SOLEIL staff for assistance during the beamtime.
-This project has received funding from the Research Executive Agency (REA) under the European Union$'$s Horizon 2020 research and innovation programme Grant agreement No 705515.
-Campus France and the PHC SIAM exchange program are acknowledged for financial support.
-
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{suppinfo}
-
-\begin{itemize}
-  \item suppinfo.pdf: contains the radial density distributions of the core excited states of the bare ions.
-\end{itemize}
-
-\end{suppinfo}
+\begin{figure}
+\centering
+\includegraphics[scale=1.0]{figures/rad_dens_kcl.eps}
+\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$\rightarrow$4p, 1s$\rightarrow$3d and 1s$\rightarrow$5p core excitations in \ki~(lower panel) and \cli~(upper panel).
+The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
+\label{fg:rdens_ions}
+\end{figure}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{Bibliography}
+%\bibliography{F:/Articles/biblography/Bibliography}
 

### 2018-01-19 master.tex
theoretical XAS spectra + corrections to the text (jan 19)
Denis' corrections from Jan 18, references fixed, new theoretical XAS
spectrum

@@
 \title[]
-  {The electronic structure of aqueous KCl revealed by X-ray absorption and Auger electron spectroscopy
-\\  
-  The all-seeing eye of Auger electron spectroscopy: a study on aqueous KCl}
+  {The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
 
@@
 \abbreviations{AES,XAS}
-\keywords{Solvated ions, Auger spectroscopy, X-ray absorption spectroscopy}
+\keywords{Solvated ions, resonant Auger spectroscopy, X-ray absorption spectroscopy}
 

### 2018-01-19 methods.tex
theoretical XAS spectra + corrections to the text (jan 19)
Denis' corrections from Jan 18, references fixed, new theoretical XAS
spectrum

@@
 % Denis, please have a look at the experimental part and see if all the references have been correctly included
+For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}.
+A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes manipulator in front of the spectrometer lens.
+Two holes of 2\,mm diameter allow the photons to go in and out of the tube.
+At the end of the tube and in front of the lens, a 500\,$\mu$m diameter hole skimmer allows the electrons created at the interaction point to go in the direction of the spectrometer.
+The microjet head is mostly composed of a 30\,$\mu$m diameter vertical glass capillary facing a temperature-controlled catcher in CuBe having a 300\,$\mu$m hole, and a camera.
+Piezo motors allow their precise alignment relative to each other and to the photon beam.
+The catcher is placed at a distance of about 5\,mm from the capillary and is permanently pumped in order to extract the liquid.
+For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a HPLC pump with a constant flux of 1.6\,ml/min.
+The alignment of the setup is performed on a salted aqueous solution by measuring the O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio.
+The pressure in the main chamber is kept below the 10$^{−5}$\,mbar range whereas it is kept at about 10$^{−4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
+Our equipment is an updated version of the equipment used in the reference \cite{faubel88:269}.
+The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water.
+Filtering and degazing procedures were systematically performed before injecting the solution.
+The spectrometer resolution of about 0.6 eV was achieved with the 500 eV pass energy and 0.5\,mm slits.
+The photon energy resolution achieved at 2.8\,keV and 3.6\,keV was about 0.3\,eV and 0.4\,eV, respectively
 
-For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline, in collaboration with the Microliquids Company.
+%
+%For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline, in collaboration with the Microliquids Company.
 Details of the beamline are given in the reference [JPR] and details on the electron spectrometer are given in the reference \citep{ceolin15:022502,ceolin13:188}.
@@
 A rail, fixed at the bottom of the tube, is used to {\kolya slides} precisely an insert on which the different elements necessary for the injection, control, collection and visualization of the liquid are mounted.
-
-The head of this insert is mostly composed by: a glass capillary fixed by a dedicated peek-piece, a catcher in CuBe with a 300$\mu$m hole, a piezo motors stage allowing a precise control of these last two parts, and a camera.
+%
+%
+%The head of this insert is mostly composed by: a glass capillary fixed by a dedicated peek-piece, a catcher in CuBe with a 300$\mu$m hole, a piezo motors stage allowing a precise control of these last two parts, and a camera.
 The catcher is placed at a distance of about 5mm from the capillary and is permanently pumped in order to extract the liquid from the vacuum chamber.

### 2018-01-19 results.tex
theoretical XAS spectra + corrections to the text (jan 19)
Denis' corrections from Jan 18, references fixed, new theoretical XAS
spectrum

@@
 XAS spectra of the lowest K-shell transitions in the bare K$^{+}$ (lower left panel) and Cl$^{-}$ (lower right panel) ions and their 6-coordinated clusters (upper left panel, \ki(H$_2$O)$_6$, and upper right panel, \cli(H$_2$O)$_6$).
-The theoretical stick spectra were convolved with a Lorentzian profile of FWHM 0.74\,eV for \ki~and 0.62\,eV for \cli~in order to account for the lifetime broadening.
+The theoretical stick spectra were convolved with a Lorentzian profile of FWHM 0.74\,eV for \ki~and 0.62\,eV for \cli~(dashed line) and a Voigt profile to account for the lifetime broadening and the experimental resolution.
 The stick spectrum corresponds to the projections $|a_{nl}^{i}|^2$ of the SONOs corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$\,\rightarrow\,$3d, 1s$\,\rightarrow\,$4p, and 1s$\,\rightarrow\,$5p states in the bare K$^+$ and \cli~ions (Eq.\ \ref{eq:sono_proj}).
-The theoretical XAS spectra of \ki~were shifted to higher photon energies by 6.7\,eV, which corresponds to the difference between the computed and experimental core excitation energies of the 1s $\rightarrow$ 4p excitation in the bare ion taken from Ref.\ \citep{hertlein06:062715}.
-\tsveta{A DARKER SHADE OF GREY}}
+The theoretical XAS spectra of both \ki~and \cli~were shifted to higher photon energies such that the excitation energies lowest core excited states correspond to the experimentally determined energies -- 3610.7\,eV in the case of \ki, and 2825.2\,eV in the case of \cli.
+The experimental ionization thresholds are depicted as grey boxes starting at photon energies of 3611.9\,eV (\ki$_{\text{aq}}$) and 2825.4\,eV (\cli$_{\text{aq}}$).}
 \label{fg:xas_kcl}
@@
 The next dipole allowed state, 1s$\,\rightarrow\,$5p, is located 4.3\,eV and 10.8\,eV higher in the cases of \ki~and \cli, respectively.
-Together with the two dipole allowed transitions, we show the dipole forbidden 1s$\,\rightarrow\,$3d states of the bare ions as blue crosses at photon energies \tsveta{3609.XX\,eV in the case of \ki~and 2831\,eV in the case of \cli, respectively}.
+Together with the two dipole allowed transitions, we show the dipole forbidden 1s$\,\rightarrow\,$3d states of the bare ions as blue crosses at photon energies 3611.17\,eV in the case of \ki~and 2831.68\,eV in the case of \cli, respectively.
 It is noteworthy that the positions of the 1s$\,\rightarrow\,$4p and 1s$\,\rightarrow\,$3d states are inverted in \ki~and \cli.
@@
 We attribute the two dispersive features on the 2D map of \cli~to the resonant Auger decay of this core excited state.
-{\color{red}Since the photon energy step in the experimental spectrum coincides with the splitting between the two dispersive features, we assume that they originate from the decay of the same core excited state.}
+{\color{red}%Since the photon energy step in the experimental spectrum coincides with the splitting between the two dispersive features, we assume that they originate from the decay of the same core excited state.
+We assume that the two dispersive features originate from the decay of the same core excited state, since the photon energy resolution at 2.8\,keV is 0.3\,eV and thus of the same magnitude as the difference between the core excited state and the ionization threshold.
+}
 
@@
 Out of all final states we show only the doublets.
-Since the initial core excited states are populated by photon excitation, only doublet states are populated in the resonant Auger decay.
+Since the initial core excited states are populated by photon excitation, only doublet states are efficiently populated in the resonant Auger decay.
 The 2p$^{-2}$nl states of \ki~and \cli~are substantially different and they reflect the fact that the 3d unoccupied orbitals of \ki~are lower than the 4p orbitals, which is the opposite of what is observed in \cli.
@@
 Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$\,\rightarrow\,$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character located between 2969 and 2970\,eV are populated in this case.
-As can be seen from the Auger electron spectrum at $h\nu = $3610.7\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki~are separated by 5 and 13\,eV from the lowest 2p$^{-2}$3d states.
-Thus, the lower-kinetic energy group of 2p$^{-2}$3d states almost coincides with the position of the island C.
+As can be seen from the Auger electron spectrum at $h\nu = $3610.7\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki~at electron energy of $\sim$2970\,eV are separated by $\sim$5 and $\sim$13\,eV from the two groups of 2p$^{-2}$3d states located at higher electron energies.
+Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV coincides with the position of island C.
 Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the dipole forbidden 1s$\,\rightarrow\,$3d state of the 6-coordinated \ki~cluster to the group of 2p$^{-2}$3d states lying around 2975\,eV.

### 2018-01-24 introduction.tex
jan 24 (denis' corrections & tsveta's)
Shift explained as resulting from internal ionization, an argument for
the attribution of island C as 2p-2 3d state based on the CT paper

@@
 Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy.
-The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decay.
-Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes charge and energy transfer \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003} are possible.
+The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decays.
+Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes such as charge and energy transfer \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003} are possible.
 
@@
 If the initially core excited electron delocalizes within the lifetime of the core hole, then normal instead of resonant Auger decay is observed \citep{Bjorneholm95:3017}.
+
+%refs clusters??:
+%A. Lindblad, R. F. Fink, H. Bergersen, M. Lundwall, T. Rander, R. Feifel, G. Öhrwall, M. Tchaplyguine, U.Hergenhahn, S. Svensson, O. Björneholm, The Journal of Chemical %Physics 123, 211101 (2005)
+%M.
+Tchaplyguine, A.
+Kivimäki, S.
+Peredkov, S.
+L.
+Sorensen, G.
+Öhrwall, J.
+Schulz, M.
+Lundwall, T.
+Rander, A.
+Lindblad, A.
+Rosso, S.
+Svensson, N.
+Mårtensson, O.
+%Björneholm, The Journal of Chemical Physics, 127, 124314 (2007)
 

### 2018-01-24 methods.tex
jan 24 (denis' corrections & tsveta's)
Shift explained as resulting from internal ionization, an argument for
the attribution of island C as 2p-2 3d state based on the CT paper

@@
 A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes manipulator in front of the spectrometer lens.
-Two holes of 2\,mm diameter allow the photons to go in and out of the tube.
+Two holes of 2\,mm diameter allow the photons to go in and out.
 At the end of the tube and in front of the lens, a 500\,$\mu$m diameter hole skimmer allows the electrons created at the interaction point to go in the direction of the spectrometer.
@@
 The alignment of the setup is performed on a salted aqueous solution by measuring the O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio.
-The pressure in the main chamber is kept below the 10$^{−5}$\,mbar range whereas it is kept at about 10$^{−4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
+The pressure in the main chamber is kept below the 10$^{-5}$\,mbar range whereas it is kept at about 10$^{-4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
 Our equipment is an updated version of the equipment used in the reference \cite{faubel88:269}.

### 2018-01-24 results.tex
jan 24 (denis' corrections & tsveta's)
Shift explained as resulting from internal ionization, an argument for
the attribution of island C as 2p-2 3d state based on the CT paper

@@
 The upper panel shows two spectra at photon energies 2825.2\,eV, and 2830.0\,eV below and above the ionization potential at 2825.4\,eV, respectively.
-The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p(red) doublet resonant Auger states of K$^{+}$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).}
+The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p(red) doublet resonant Auger states of Cl$^{-}$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).}
 \label{fg:2dmap_cl}
@@
 It results in the population of 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states. 
-The $^3$P final states are not observed in the experiment since they are forbidden from parity conservation rules.
+%The $^3$P final states are not observed in the experiment since they are forbidden from parity conservation rules.
+The $^3$P final states are expected to have very little intensity since at the first order they are forbidden from parity conservation rules.
+In addition, in our photon energy range of interest, the tail of the $^1$D state described in the next paragraph, and the $^1$D 2p$^{-2}$V' dispersive state (see next section) overlap in the same kinetic energy region making it impossible to properly determine the $^3$P state position.
 In the case of Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ (2p$^{-2}$) $^1$S and $^1$D states are located at 2373.2\,eV and 2382.1\,eV kinetic energy (see Fig.\ \ref{fg:2dmap_cl}).
@@
 Consequently, one can attribute the high kinetic energy shoulder of the $^1$D and $^1$S peaks on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} as resulting from PCI effect.
-In order to quantify this effect we recorded the KLL Auger spectrum of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ at higher photon energies, $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
+
+%In order to quantify this effect we recorded the KLL Auger spectrum of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ at higher photon energies, $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
 In this case, the maxima of the $^1$D and $^1$S states were found at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
 The lines observed at photon energies far from threshold and close to it appear to be shifted by $\sim$1\,eV.
-The magnitude of the shift is the same for both ions suggesting that it does not depend on the initial charge of the ion.
-The observed PCI shift of 1\,eV is larger than in the case of the isoelectronic Ar, where its value is $\sim$0.5\,eV at a photon energy of 10 \,eV above threshold \citep{guillemin15:012503}.
+The magnitude of the shift is the same for both ions suggesting that it does not depend on the initial charge of the ion, and it is almost constant in the photon energy range presented here.
+% Jan 24 Tsveta
+\tsveta{Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
+In this case, the maxima of the $^1$D and $^1$S states were found at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
+The lines observed at photon energies far from threshold and close to it appear to be shifted by $\sim$1\,eV.
+The magnitude of the shift is the same for both ions suggesting that it does not depend on the initial charge of the ion, and it is almost constant in the photon energy range presented here.
+}
+\tsveta{A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314}, which focuses on the Auger decay of large Kr clusters on and just above the 3d$_{5/2}$ ionization threshold.
+The observed 4d$^{4}$($^1$D) Auger peak was found to be shifted by 0.7\,eV to higher kinetic energies compared to the position of the peak far above threshold.
+Moreover, the shift did not vary with the photon energy close to threshold.
+Consequently, it was proposed that this feature originates from a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band.
+Further investigations are, however, planned in the case of liquid samples.}
+%\denis{A possible explanation was given in the reference M.
+Tchaplyguine et al., The Journal of Chemical Physics 127, 124314 (2007) focusing on the Auger decay of large Kr clusters following ionization of the 3d$_{5/2}$ orbital.
+Considering that the observed PCI shift was not varying with the photon energy close to threshold, a process of excitation of the photoelectron into the conduction band was thus proposed.
+Further investigation are however planned in the case of liquid samples.}
+% The observed PCI shift of 1\,eV is larger than in the case of the isoelectronic Ar, where its value is $\sim$0.5\,eV at a photon energy of 10 \,eV above threshold \citep{guillemin15:012503}.
 The shift in the energies of the photo- and Auger electrons is proportional to the change in the ionic field during the Auger process.
@@
 The magnitude of this effect increases with the ionic charge, consequently, there will be an even greater difference for the double ionization potential.
-Thus, one can expect a larger change in the ionic field in an aqueous solution compared to that in a van der Waals cluster, which can, therefore, account for the large PCI shift of the Auger lines in a solution.
+Thus, one can expect a larger change in the ionic field in an aqueous solution compared to that in a Van der Waals cluster, which can, therefore, account for the large PCI shift of the Auger lines in a solution.
 
-The normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder (A on Fig.\ \ref{fg:2dmap_k}) on the low kinetic energy side at about 2965\,eV kinetic energy.
-This shoulder is attributed to electron transfer from the solvent molecules \citep{ceolin17:263003}.
-In the case of \cli, there is no experimental evidence of such electron transfer processes.
+Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder (A on Fig.\ \ref{fg:2dmap_k}) on the low kinetic energy side at about 2965\,eV kinetic energy.
+This shoulder is attributed to electron transfer from the water solvent molecules \citep{ceolin17:263003} to the 3d orbital of K$^{+}$.
+In the case of \cli, there was no experimental evidence of such intense localized electron transfer processes.
 
@@
 
-\kolya{XAS of Cl- and K+ from previous works?}
+%\kolya{XAS of Cl- and K+ from previous works?}
 
@@
 It is located at $h\nu = $3611.6\,eV and 2978.1\,eV kinetic energy (feature C), thus it is separated by approximately 400\,meV photon energy and 8.3\,eV kinetic energy from the feature B.
-%Unlike in the case Cl$^{-}$ the dispersive feature close to the $^1$S main line is not observed in K$^{+}$ due to presence of a strong {\color{red}background (@DENIS?)}.
-
-%In order to get a better understanding of these features, we will first consider the Auger spectrum of the isoelectronic Ar presented in Refs.\ \citep{ceolin15:022502,guillemin15:012503}.
-
-%First, from the 2D map of Ar one can extract information about the nature of the core excited states below threshold.
-The pre-edge structure in the XAS spectrum of Ar consists of the 1s$\,\rightarrow\,$4p and 1s$\,\rightarrow\,$5p excitations.
-Higher core excited states cannot be identified in the XAS spectrum due to their lifetime broadening and proximity to the ionization threshold.
-The same excitations were observed in the XAS spectrum of bare \ki~ions \citep{hertlein06:062715}.
-Again, the identification of 1s$\,\rightarrow\,$np states with n$\,>\,$5 was not possible in the case of \ki.
-
-%Second, the 2D map of Ar carries information about the states populated in the resonant Auger processes following core excitation.
-In the case of Ar, the Ar 1s$\,\rightarrow\,$4p and 1s$\,\rightarrow\,$5p core excited states undergo both pure spectator and shake-up resonant Auger decay leading to the population of Ar$^{2+}$(2p$^{-2}$np) (n$ = 4 - 6$) final states.
-As a result, apart from the main Ar$^{2+}(2p^{-2})$ $^1$D and $^1$S lines which result from normal Auger decay, additional dispersive features are observed.
-For example, the 1s$\,\rightarrow\,$4p core excited state undergoes both pure spectator and shake-up resonant Auger decay.
-The former results in an island shifted with respect to the main $^1$D line by $\sim$4-5\,eV kinetic energy, whereas the fingerprint of the shake-up process is a feature appearing at the same kinetic energy as the  main $^1$D line.
-Moreover, the intensities of the observed shake-up features are lower compared to those of the pure spectator Auger decay.
-In aqueous solutions, one can expect the 2D map to be fairly different as both the initial core excited states and the final Auger states will be influenced by the presence of the solvent.
 
@@
 First, due to the lifetime broadening, it spreads over approximately 2\,eV which coincides with the width of the pre-edge structure in the experimental XAS spectra.
-Second, the splitting between the first core excited state and the ionization threshold in the experiment is 0.7\,eV for \ki~and 0.2\,eV for \cli, and thus it is smaller than the splitting between the first and second peak in the theoretical spectra (1.5\,eV for \ki~and $\sim$3\,eV for \cli, Fig.\ \ref{fg:xas_kcl}).
+Second, the splitting between the first core excited state and the ionization threshold in the experiment is 1.2\,eV for \ki~and 0.2\,eV for \cli, and thus it is smaller than the splitting between the first and second peak in the theoretical spectra (1.5\,eV for \ki~and $\sim$3\,eV for \cli, Fig.\ \ref{fg:xas_kcl}).
 In the 6-coordinated cluster (Fig.\ \ref{fg:xas_kcl} upper left panel), which represents the complete first solvation shell around \ki, the lowest peak in the spectrum contains three states.
@@
 Since there are no other ionic states close the the 1s$\,\rightarrow\,$4p state in the ion, this state preserves its character in the cluster and interacts with states of the nearest water molecules.
-We attribute the two dispersive features on the 2D map of \cli~to the resonant Auger decay of this core excited state.
-{\color{red}%Since the photon energy step in the experimental spectrum coincides with the splitting between the two dispersive features, we assume that they originate from the decay of the same core excited state.
-We assume that the two dispersive features originate from the decay of the same core excited state, since the photon energy resolution at 2.8\,keV is 0.3\,eV and thus of the same magnitude as the difference between the core excited state and the ionization threshold.
-}
+We attribute the two dispersive features on the 2D map of \cli~ and associated with the $^{1}$S and $^{1}$D terms, to the resonant Auger decay of these core-excited states involving mostly the 4p orbitals of chloride.
+% {\color{red}%Since the photon energy step in the experimental spectrum coincides with the splitting between the two dispersive features, we assume that they originate from the decay of the same core excited state.
+% We assume that the two dispersive features originate from the decay of the same core excited state, since the photon energy resolution at 2.8\,keV is 0.3\,eV and thus of the same magnitude as the difference between the core excited state and the ionization threshold.
+% }
 
@@
 As mentioned above, we attribute the island B to the decay of the lowest lying core excited state of the hexa-hydrated \ki~cluster, which is of predominantly 1s$\,\rightarrow\,$4p character.
-Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$\,\rightarrow\,$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character located between 2969 and 2970\,eV are populated in this case.
-As can be seen from the Auger electron spectrum at $h\nu = $3610.7\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki~at electron energy of $\sim$2970\,eV are separated by $\sim$5 and $\sim$13\,eV from the two groups of 2p$^{-2}$3d states located at higher electron energies.
-Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV coincides with the position of island C.
+Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$\,\rightarrow\,$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character located between 2969 and 2970\,eV are populated.
+As can be seen from the Auger electron spectrum at $h\nu = $3610.7\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki~at electron energy of $\sim$2970\,eV are separated by $\sim$5 and $\sim$13\,eV from the two groups of 2p$^{-2}$3d states located at higher electron kinetic energies.
+Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV almost coincides with the position of island C.
 Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the dipole forbidden 1s$\,\rightarrow\,$3d state of the 6-coordinated \ki~cluster to the group of 2p$^{-2}$3d states lying around 2975\,eV.
 The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C.
-This difference may be due to the fact that we do not account for the effect of the solvent molecules in our calculation.
+This difference may be due to the fact that we do not account for the effect of the solvent molecules in our calculation {\color{red}In the figure we need to show the calculations on K+(H2O)6, and we need to interpret differently the next sentence}.
 There is a group of 2p$^{-2}$3d states at kinetic energies of 2982\,eV.
 Since no additional experimental features are observed, we conclude that these states are not populated.
+
+\tsveta{Another argument supporting the attribution of the island C as being of 2p$^{-2}$ 3d character can be found by considering the electron transfer from the water molecules (W) discussed in reference \cite{ceolin17:263003}.
+As a result of this process, an additional feature A is observed on the low-kinetic energy side of the $^1$D main peak in \ki.
+This feature has the configuration K$^{2+}$2p$^{-2}$3d W$^{-1}$.
+...}
+\denis{Another argument playing in favor of the the attribution of the island C as being of 2p$^{-2}$ 3d character comes from the attribution of the A area as given in reference \cite{ceolin17:263003} and from the energy splitting between A and C.
+The A area originates from a charge transfer process between water (W) and core-excited potassium and has the configuration K$^{2+}$2p$^{-2}$3d W$^{-1}$.
+The ionization potential of water in the liquid phase is about 11 eV which fits well with the observed A-C splitting.
+Based only on these two simple energetic arguments we can attribute the C island to the a K$^{2+}$ 2p$^{-2}$ 3d configuration and note that neither 2p$^{-2}$ 3d nor charge transfer states are present in the Cl$^{-}$ case.}
 
@@
 
+% Jan 24 Tsveta: this is already written two paragraphs above.
+
+%{\color{red}we do not say anything about the 3d contribution in blue.
+Am I correct if I am saying: "The calculated 2p-2 3d states represented by blue vertical lines are not populated during the decay of the first core-excited state of solvated chloride involving mostly its 4p orbitals with some water contribution."}
+
 \subsection{Delocalization vs resonant Auger decay}
 
-{\color{red}Here, our peaks are not separated as it should be to apply the core-hole clock method}
+As mentioned above, the delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
+In order to estimate the delocalization rate of the core-excited electron at the pre-edges of \ki~and \cli, we used the core-hole clock method as in the reference  \cite{bjorneholm92:1892,karis96:1380}.
 
-As mentioned above, the delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
-In order to estimate the rate of delocalization of the core excited electron at the pre-edges of \ki~and \cli, we used the core hole clock method \cite{bjorneholm92:1892,karis96:1380}.
-
-In the case of \cli, a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV at photon energy corresponding to the lowest core excitation, $h\nu = $2825.2\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel).
+In the case of \cli, and contrary to \ki, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} (\tsveta{do you want to explain this data treatment in 1 sentence.
+now the reader is forced to check the other paper.}), i.e.
+for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated and their intensity integrated to get a partial electron yield as a function of the photon energy.
+The result is shown in the SI.
+The figure shows that there is a large overlap between the resonant and normal Auger contributions, due to the proximity of the resonance to the ionization potential and due to the very short lifetime of the corresponding states.
+At the specific photon energy corresponding to the lowest core excitation, $h\nu = $2825.2\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel) a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV .
 The position of the first peak coincides with the main $^1$D line resulting from normal Auger, whereas the second peak at 2383.5\,eV corresponds to the final resonant Auger states 2p$^{-2}$($^1$D)4p.
@@
 
-In the case of \ki, the resonant Auger process is faster than the delocalization and moreover, the core excited state appears 1.2\,eV below the ionization threshold.
-Therefore, one can expect slower delocalization compared to \cli$_{\text{aq}}$.
-The normal and resonant Auger parts of the peak between 2967 and 2972\,eV taken at the photon energy corresponding to the first resonance are not separated.
-Thus, the application of the core-hole clock method is not rigorous.
-Our estimate of the intensity ratio using the core-hole clock method shows that the delocalization at the pre-edge is indeed slower, taking place within 2 -- 3\,fs, compared to the resonant Auger decay, which occurs within 0.9\,fs.
+For potassium the treatment is more complex due to the presence of multiple simultaneous processes -- normal, resonant Auger decay, charge transfer (CT) from solvent.
+To extract the intensity of each component from the 2D map shown in Fig.\ \ref{fg:2dmap_k}, one needs the spectral fingerprints of each process to be separated.
+However, as can be seen, this is not the case especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
+For instance at 3610.7\,eV photon energy on the high-kinetic-energy side of the 2p$^{-2}$($^1$D) state, there are contributions from the PCI tail and from the dispersive 2p$^{-2}$($^1$D)4p state related to the B island.
+On the low-kinetic-energy side, the charge transfer process leads to a very large structure that unfortunately cannot be easily simulated by a known profile.
+However, the 1s core-hole lifetime is shorter for potassium than for chloride (0.9 vs.
+1\,fs) and moreover, the core-excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
+Therefore, one can expect a much less efficient delocalization process compared to \cli$_{\text{aq}}$.
 
-%
-%
-%The formation of such an island on the 2D map of \ki$_{\text{aq}}$ can result from several processes: shake-up resonant Auger decay, similar to the case of Ar \citep{ceolin15:022502}, spin-orbit splitting in the final states, core-like ICD process, or population of dipole forbidden states, which is a result of symmetry breaking in the presence of the solvent.
-%
-%\begin{enumerate}
-%
-%\item[a)] Shake-up resonant Auger decay
-%
-%A separate island at 2666\,eV kinetic energy and 3203.5\,eV photon energy is observed on the 2D map of Ar (see Fig.\ 2 in \citep{ceolin15:022502}.
-This island results from resonant Auger decay of the Ar 1s$\,\rightarrow\,$4p state to Ar$^{2+}$(2p$^{-2}$4p) states.
-The 1s$\,\rightarrow\,$4p state undergoes also shake-up resonant Auger decay, resulting in the population of Ar$^{2+}$(2p$^{-2}$5p) states which appear as a separate feature at the same photon energy, but at lower kinetic energies, 2662\,eV.
-%
-%
-%A similar shake-up decay can be expected for the 1s$\,\rightarrow\,$4p state of \ki.
-As a first step, we estimate the splitting between the 2p$^{-2}$4p and 2p$^{-2}$5p final states.
-Using the $(Z+2)$-approximation, the splitting between the 2p$^{-2}$4p and 2p$^{-2}$5p states of K$^{3+}$ is equal to the splitting between the 3p$^6$4p and 3p$^6$5p states of Sc$^{3+}$.
-From the NIST database \citep{NIST_ASD} for the bare ion we obtain $\sim$8.2\,eV, which agrees with the splitting between the island and the dispersive feature close to the $^1$D main line on the 2D map of \ki$_\text{aq}$ (Fig.\ \ref{fg:2dmap_k}).
-As a second step, we compare the intensity ratio between the two dispersive features in \ki$_{\text{aq}}$ with that in Ar.
-As can be seen from Fig.\ \ref{fg:intensity_ratio} the lower-lying peak, which is attributed to the K$^{3+}$(2p$^{-2}$5p) state has higher intensity compared to the higher-lying peak.
-The intensity of the two peaks in Ar is exactly the opposite implying a lower shake-up probability.
-Another counterargument against the shake-up origin of the island is that if one compares the maxima of the two dispersive features B and C, one sees that the feature B appears at lower photon energies than C.
-This is opposed to Ar, where the island originating from normal Auger decay appears at lower photon energies.
-%
-%Another question is whether the 2p$^{-2}$5p states can be populated in a solution.
-To address this issue, on Fig.\ \ref{fg:k_2p4nl_raddens} we compare the radial density distributions of the natural orbitals occupied by the excited electron in the K$^{3+}$(2p$^{-2}$4p) and K$^{3+}$(2p$^{-2}$5p) states.
-The former distribution is quite compact, with 86\% of the electron density within the first solvation shell, whereas only about 20\% of the electron density in the  K$^{3+}$(2p$^{-2}$5p) state is within the first solvation shell.
-%
-%
-%Therefore, we conclude that the features B and C on the 2D map of \ki$_{\text{aq}}$ Fig.\ \ref{fg:2dmap_k} are not a result of a shake-up and normal Auger decay of the \ki(1s$\,\rightarrow\,$4p) state.
-%
-%\end{enumerate}
-%
-%
-%{\color{blue}\bf Discuss the possibility for non-local Auger decay! Spin-orbit splitting of the final states: it cannot give such a big difference (of 8\,eV)}
+% Jan 24, Tsveta This is Denis' original sentence
+%\denis{For potassium the treatment was more complex in reason of multiple overlaps.
+To extract the intensity of each component of the 2D map shown in figure 2, one needs to isolate them.
+However this operation was not possible especially close to threshold.
+On one side of the $^1$D state, there are contributions of the PCI tail and of the dispersive state related to the B island, and on the other side, the charge transfer process leads to a very large structure that unfortunately cannot be easily simulated by a known profile.
+Below threshold, as for instance at 3610.7eV photon energy, we cannot exclude a superposition of the 2p$^{-2}$($^1$D)4p, 2p$^{-2}$($^1$D) and CT states in the kinetic energy region 2965-2970eV.
+However, we know that the 1s core-hole lifetime is shorter for potassium than for chloride (0.9 vs.
+1fs) and moreover, the core-excited state appears 1.2\,eV below the ionization threshold whereas it was only 0.2eV for chloride.
+Therefore, one can expect a much less efficient delocalization process compared to \cli$_{\text{aq}}$.}

### 2018-01-24 master.tex
jan 24 (small correction in the master file)

@@
 
+\author{Ralph P\"{u}ttner}
+\affiliation{Fachbereich Physik, Freie Universit\"at Berlin, Arnimallee 14, D-14195, Berlin, Germany}
+
 \author{Ch. Nicolas}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}
 
 \author{Wandared Pokapanich}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Faculty of Science, Nakhon Phanom University, Nakhon Phanom 48000 Thailand}
 
 \author{Th. Saisopa}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
+Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}
 
 \author{P. Songsiriritthigul}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
+Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}
 
 \author{Y. Rattanachai}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Department of Applied Physics, Faculty of Sciences and Liberal Arts, Rajamangala University of Technology Isan, Nakhon Ratchasima 30000, Thailand}
 
@@
 \affiliation{Interdisciplinary Center for Scientific Computing, Ruprecht-Karls University, Im Neuenheimer Feld 205A, D-69120 Heidelberg, Germany}
-
-\author{Ralph P\"{u}ttner}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
 

### 2018-02-02 methods.tex
feb 2 (version sent to co-authors)
Changes made by Denis, new figures for SI, text changed.

@@
 \subsection{Experimental}
-% Denis, please have a look at the experimental part and see if all the references have been correctly included
+
 For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}.
@@
 Filtering and degazing procedures were systematically performed before injecting the solution.
-The spectrometer resolution of about 0.6 eV was achieved with the 500 eV pass energy and 0.5\,mm slits.
+The spectrometer resolution of about 0.6\,eV was achieved with the 500\,eV pass energy and 0.5\,mm slits.
 The photon energy resolution achieved at 2.8\,keV and 3.6\,keV was about 0.3\,eV and 0.4\,eV, respectively
-
-%
-%For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline, in collaboration with the Microliquids Company.
-Details of the beamline are given in the reference [JPR] and details on the electron spectrometer are given in the reference \citep{ceolin15:022502,ceolin13:188}.
-Due to the limited amount of space available \kolya{in} front of the analyzer lens and due to the limited number of ports available on the main vacuum chamber, the challenge was to arrange all the elements composing the microjet setup in a very compact manner.
-A differentially-pumped tube in which the microjet assembly is inserted, is installed in front of the spectrometer lens and can be moved independently from the main vacuum chamber by means of a three axes motorized manipulator.
-Two holes of 2 mm diameter allow the photons to go in and out of the tube\kolya{.
-A third hole,} on which is mounted a skimmer having a 500$\mu$m diameter hole, allows the electrons created at the interaction point to go in the direction of the spectrometer lens.
-To ensure a proper vacuum in the differentially pumped tube, a {\color{red}5-way cross} is connected to it and holds a 1200 l/s turbo pump, a liquid nitrogen trap, a vacuum gage and the liquid/electrical feedthroughs.
-A rail, fixed at the bottom of the tube, is used to {\kolya slides} precisely an insert on which the different elements necessary for the injection, control, collection and visualization of the liquid are mounted.
-%
-%
-%The head of this insert is mostly composed by: a glass capillary fixed by a dedicated peek-piece, a catcher in CuBe with a 300$\mu$m hole, a piezo motors stage allowing a precise control of these last two parts, and a camera.
-The catcher is placed at a distance of about 5mm from the capillary and is permanently pumped in order to extract the liquid from the vacuum chamber.
-For the present experiment, a 0.5M KCl aqueous solution is injected in a capillary having a 30$\mu$m diameter, by a HPLC pump with a constant flux of 1.6 ml/min.
-The catcher temperature is controlled so that the liquid does not freeze before its extraction.
-Considering that the photon propagation axis, the spectrometer lens axis and the liquid microjet form an \kolya{orthogonal trihedron}, the piezo motorization allows moving the liquid microjet along the photon propagation and the lens axes during the experiment if necessary.
-The catcher can be moved by the piezo motors along the photon propagation axis only.
-A simple camera is used to control the liquid jet positioning as compared with the catcher hole.
-The alignment of the full head (particularly capillary plus catcher) as compared with the X-ray beam is performed by moving the whole system using the 3-axes motorized manipulator.
-The alignment of the setup is performed by measuring the O1s XPS peak intensity of a simple salt aqueous solution, and by optimizing the liquid phase vs gas phase ratio.
-The pressure in the main chamber was kept below the 10$^{-5}$ mbar range whereas it was kept at about 10$^{-4}$ mbar in the differentially pumped tube when the HPLC pump \kolya{was ON}.
-Our equipment is an updated version of the equipment used in the references {\color{red}WHAT r these refs [3-5]?}.
-The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water.
-Filtering and degazing procedures were systematically performed before injecting the solution into the microjet by the HPLC pump.
 
@@
 
-The theoretical X-ray absorption spectra were computed \tsveta{for the hexa-coordinated clusters of both ions, \ki(H$_2$O)$_6$ and \cli(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \citep{Ohtaki93:1157,soper06:180,ma14:1006}}.
+The theoretical X-ray absorption spectra were computed for the hexa-coordinated clusters of both ions, \ki(H$_2$O)$_6$ and \cli(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
 The two structures were optimized at the DFT level of theory using the B3LYP functional and the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,Blaudeau97:5016}.
@@
 The energies and transition moments of the core excited states of the microsolvated clusters were computed with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}.
-In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding the f functions) was used for all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and an additional set of 2s, 2p and 2d diffuse functions was added on K.
+In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding the f functions) was used for all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
 In our calculations the core space comprises the 1s orbital of K$^{+}$ or \cli, whereas the remaining occupied orbitals are included in the valence space.
@@
 
-The final states following KLL resonant Auger decay of K$^{+}$ and \cli~were computed at the Configuration Interaction Singles (CIS) level using the Graphical Unitary Group Approach (GUGA) as implemented in the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS}.
+The final states following KLL resonant Auger decay of K$^{+}$(H$_2$O)$_6$ and \cli(H$_2$O)$_6$ were computed at the Configuration Interaction Singles (CIS) level using the Graphical Unitary Group Approach (GUGA) as implemented in the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS}.
 In order to account for the relaxation effects upon core ionization, we used a restricted open-shell Hartree-Fock reference wave function with a hole in the 2s orbital of both \ki~and \cli.
-We used the 6-311++G(2d,2p) basis set \citep{Blaudeau97:5016} augmented with 2s, 2p, 2d diffuse functions on \ki, and the cc-pVTZ basis set augmented with 6s, 6p, 6d diffuse Kaufmann-Baumeister-Jungen continuum-like functions \citep{Kaufmann89:2223} on \cli.
+We used the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,McLean80:5639,Blaudeau97:5016} on all atoms.
+Additionally, the basis set was augmented with 2 sets of s, p, d diffuse functions in the case of \ki, and 3 sets of s, p, d diffuse functions in the case of \cli.
 The active space comprises the 2s and 2p orbitals of K/Cl with occupancy fixed to 6 and all virtual orbitals with occupancy fixed to 1.

### 2018-02-02 results.tex
feb 2 (version sent to co-authors)
Changes made by Denis, new figures for SI, text changed.

@@
 The upper panel shows two spectra at photon energies 3610.7\,eV, and 3616\,eV below and above the ionization potential at 3611.9\,eV, respectively.
-The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p(red) doublet resonant Auger states of K$^{+}$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).
+The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) doublet resonant Auger states of K$^{+}$(H$_2$O)$_6$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).
 The features A, B and C are discussed in the text.}
@@
 The upper panel shows two spectra at photon energies 2825.2\,eV, and 2830.0\,eV below and above the ionization potential at 2825.4\,eV, respectively.
-The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p(red) doublet resonant Auger states of Cl$^{-}$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).}
+The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) doublet resonant Auger states of Cl$^{-}$(H$_2$O)$_6$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).}
 \label{fg:2dmap_cl}
@@
 % Jan 24 Tsveta
-\tsveta{Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
-In this case, the maxima of the $^1$D and $^1$S states were found at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
-The lines observed at photon energies far from threshold and close to it appear to be shifted by $\sim$1\,eV.
+Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
+In this case, the maxima of the $^1$D and $^1$S states were found at lower values at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
+The lines observed at photon energies far from threshold and close to it appear thus to be shifted by $\sim$1\,eV.
 The magnitude of the shift is the same for both ions suggesting that it does not depend on the initial charge of the ion, and it is almost constant in the photon energy range presented here.
-}
-\tsveta{A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314}, which focuses on the Auger decay of large Kr clusters on and just above the 3d$_{5/2}$ ionization threshold.
+A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314}, which focuses on the Auger decay of large Kr clusters on and just above the 3d$_{5/2}$ ionization threshold.
 The observed 4d$^{4}$($^1$D) Auger peak was found to be shifted by 0.7\,eV to higher kinetic energies compared to the position of the peak far above threshold.
@@
 Consequently, it was proposed that this feature originates from a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band.
-Further investigations are, however, planned in the case of liquid samples.}
+Further investigations are, however, planned in the case of liquid samples.
 %\denis{A possible explanation was given in the reference M.
@@
 %
-where $V$ and $V'$ denote the virtual orbitals in the excited and singly ionized excited states, i.\ e.\ in the presence of the $1s^{-1}$ and $2p^{-2}$ core holes.
+where $V$ and $V'$ denote the virtual orbitals in the excited and singly ionized excited states, i.\ e.\ in the presence of the 1s$^{-1}$ and 2p$^{-2}$ core holes.
 The character of these states will be discussed below.
@@
 We note in passing that the intensity of the Cl$^{-}$(1s$\,\rightarrow\,$4p) state is lower than that of the \cli(1s$\,\rightarrow\,$5p) state contrary to what is observed in \ki.
-This difference can be explained with the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$\,\rightarrow\,$4p compared to the 1s$\,\rightarrow\,$5p transition in \cli~(see Fig.\ \ref{fg:rdens_ions}).
+This difference can be explained with the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$\,\rightarrow\,$4p compared to the 1s$\,\rightarrow\,$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
 
@@
 
-To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest K$^{2+}$(2p$^{-2}$nl) and Cl$^{0}$(2p$^{-2}$nl) states of the bare ions corresponding to the lowest final spectator resonant Auger states.
+To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ states of the hexa-coordinated clusters corresponding to the lowest final spectator resonant Auger states.
 They are shown as bars in the upper panels on the experimental resonant Auger spectra on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}.
-In both cases of \ki~and \cli, we shifted the lowest 2p$^{-2}$4p states such that they coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.
+In both the case of \ki~and \cli, we shifted the lowest 2p$^{-2}$4p states such that they coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.
 Out of all final states we show only the doublets.
 Since the initial core excited states are populated by photon excitation, only doublet states are efficiently populated in the resonant Auger decay.
-The 2p$^{-2}$nl states of \ki~and \cli~are substantially different and they reflect the fact that the 3d unoccupied orbitals of \ki~are lower than the 4p orbitals, which is the opposite of what is observed in \cli.
+The 2p$^{-2}$nl states of \ki(H$_2$O)$_6$ and \cli(H$_2$O)$_6$ are substantially different and they reflect the fact that the 3d unoccupied orbitals of \ki~are lower than the 4p orbitals, which is the opposite of what is observed in \cli.
 
@@
 As mentioned above, we attribute the island B to the decay of the lowest lying core excited state of the hexa-hydrated \ki~cluster, which is of predominantly 1s$\,\rightarrow\,$4p character.
-Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$\,\rightarrow\,$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character located between 2969 and 2970\,eV are populated.
-As can be seen from the Auger electron spectrum at $h\nu = $3610.7\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki~at electron energy of $\sim$2970\,eV are separated by $\sim$5 and $\sim$13\,eV from the two groups of 2p$^{-2}$3d states located at higher electron kinetic energies.
-Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV almost coincides with the position of island C.
+Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$\,\rightarrow\,$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character located between 2969 and 2970.5\,eV are populated.
+As can be seen from the Auger electron spectrum at $h\nu = 3610.7$\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki(H$_2$O)$_6$ starting at electron energy of 2969\,eV are separated by $\sim$5 and 12-13\,eV from the two groups of 2p$^{-2}$3d states located at higher electron kinetic energies.
+Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV lies closer to the position of island C.
 Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the dipole forbidden 1s$\,\rightarrow\,$3d state of the 6-coordinated \ki~cluster to the group of 2p$^{-2}$3d states lying around 2975\,eV.
 The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C.
-This difference may be due to the fact that we do not account for the effect of the solvent molecules in our calculation {\color{red}In the figure we need to show the calculations on K+(H2O)6, and we need to interpret differently the next sentence}.
-There is a group of 2p$^{-2}$3d states at kinetic energies of 2982\,eV.
-Since no additional experimental features are observed, we conclude that these states are not populated.
+This difference may be due to the fact that we do not account for the effect of the solvent molecules in our calculation.
+Concerning the higher lying group of 2p$^{-2}$3d states at kinetic energies between 2982 and 2983\,eV, we conclude that these states are not populated since no additional experimental features are observed.
 
-\tsveta{Another argument supporting the attribution of the island C as being of 2p$^{-2}$ 3d character can be found by considering the electron transfer from the water molecules (W) discussed in reference \cite{ceolin17:263003}.
+% \tsveta{Another argument supporting the attribution of the island C as being of 2p$^{-2}$ 3d character can be found by considering the electron transfer from the water molecules (W) discussed in reference \cite{ceolin17:263003}.
 As a result of this process, an additional feature A is observed on the low-kinetic energy side of the $^1$D main peak in \ki.
@@
 ...}
-\denis{Another argument playing in favor of the the attribution of the island C as being of 2p$^{-2}$ 3d character comes from the attribution of the A area as given in reference \cite{ceolin17:263003} and from the energy splitting between A and C.
-The A area originates from a charge transfer process between water (W) and core-excited potassium and has the configuration K$^{2+}$2p$^{-2}$3d W$^{-1}$.
+Another argument supporting the attribution of the island C as being of 2p$^{-2}$ 3d character comes from the attribution of the A area as given in reference \cite{ceolin17:263003} and from the energy splitting between A and C.
+The A area originates from a charge transfer process between water (W) and core-excited potassium and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
 The ionization potential of water in the liquid phase is about 11 eV which fits well with the observed A-C splitting.
-Based only on these two simple energetic arguments we can attribute the C island to the a K$^{2+}$ 2p$^{-2}$ 3d configuration and note that neither 2p$^{-2}$ 3d nor charge transfer states are present in the Cl$^{-}$ case.}
+Based only on these two simple energetic arguments we can attribute the C island to the a K$^{2+}$ 2p$^{-2}$3d configuration and note that neither 2p$^{-2}$3d nor charge transfer states are present in the Cl$^{-}$ case.
 
-In the Cl$^{0}$(2p$^{-2}$nl) spectrum there are two groups of states split by about 7\,eV (see upper panel of Fig.\ \ref{fg:2dmap_cl}).
+In the Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (see upper panel of Fig.\ \ref{fg:2dmap_cl}).
 The lower kinetic energy group corresponds to the 2p$^{-2}$($^1$S)4p states, whereas the higher kinetic energy group corresponds to the 2p$^{-2}$($^1$D)4p states.
 The splitting between the two groups is in good agreement with the experimental splitting between the dispersive features on the high kinetic energy sides of the $^1$S and $^1$D main peaks.
-Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$\,\rightarrow\,$4p core excited state of \cli~to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.
+Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$\,\rightarrow\,$4p core excited state of \cli$_{\texttt{aq}}$ to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.
 Similar dispersive features originating from the decay of the Cl (1s$\,\rightarrow\,$4p) state were observed on the 2D map of chloromethane CH$_3$Cl recorded in the vicinity of the Cl K-edge in gas phase \cite{gold16:133001}.
 In this case, however, additional lower-lying core excited state are observed.
-They result from excitation to the LUMO of CH$_3$Cl, which is a linear combination of the C $2p$ and Cl $3p$ atomic orbitals.
+They result from excitation to the LUMO of CH$_3$Cl, which is a linear combination of the C 2p and Cl 3p atomic orbitals.
 Since the 3p shell is fully occupied in \cli, such a core excited state is not observed in our experiment.
@@
 
-In the case of \cli, and contrary to \ki, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} (\tsveta{do you want to explain this data treatment in 1 sentence.
-now the reader is forced to check the other paper.}), i.e.
-for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated and their intensity integrated to get a partial electron yield as a function of the photon energy.
-The result is shown in the SI.
+In the case of \cli, and contrary to \ki, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502}, %(\tsveta{do you want to explain this data treatment in 1 sentence.
+now the reader is forced to check the other paper.}\denis{Tsveta, I think that what is just after the i.e.
+is enough.
+If you agree let's see what the others are saying}),
+i.e.
+for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get a partial electron yield as a function of the photon energy.
+The result is shown on Fig.\ \ref{fg:si_ct_time} in the SI.
 The figure shows that there is a large overlap between the resonant and normal Auger contributions, due to the proximity of the resonance to the ionization potential and due to the very short lifetime of the corresponding states.
-At the specific photon energy corresponding to the lowest core excitation, $h\nu = $2825.2\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel) a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV .
+At the specific photon energy corresponding to the lowest core excitation, $h\nu = 2825.2$\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel) a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV .
 The position of the first peak coincides with the main $^1$D line resulting from normal Auger, whereas the second peak at 2383.5\,eV corresponds to the final resonant Auger states 2p$^{-2}$($^1$D)4p.
@@
 On the low-kinetic-energy side, the charge transfer process leads to a very large structure that unfortunately cannot be easily simulated by a known profile.
-However, the 1s core-hole lifetime is shorter for potassium than for chloride (0.9 vs.
-1\,fs) and moreover, the core-excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
+However, the 1s core-hole lifetime is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and moreover, the core-excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
 Therefore, one can expect a much less efficient delocalization process compared to \cli$_{\text{aq}}$.

### 2018-02-02 suppinfo.tex
feb 2 (version sent to co-authors)
Changes made by Denis, new figures for SI, text changed.

@@
 
-\author{Ch. Nicolas}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\author{Christophe Nicolas}
+\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}
 
 \author{Wandared Pokapanich}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Faculty of Science, Nakhon Phanom University, Nakhon Phanom 48000 Thailand}
 
 \author{Th. Saisopa}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
+Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}
 
 \author{P. Songsiriritthigul}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
+Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}
 
 \author{Y. Rattanachai}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Department of Applied Physics, Faculty of Sciences and Liberal Arts, Rajamangala University of Technology Isan, Nakhon Ratchasima 30000, Thailand}
 
@@
 
-\author{Ralph P\"{u}ttner}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
-
 \author{J\'{e}r\^ome Palaudoux}
@@
 \affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+
+\author{Ralph P\"{u}ttner}
+\affiliation{Fachbereich Physik, Freie Universit\"at Berlin, Arnimallee 14, D-14195, Berlin, Germany}
 
@@
 \title[]
-  {The electronic structure of aqueous KCl revealed by X-ray absorption and Auger electron spectroscopy
-\\  
-  The all-seeing eye of Auger electron spectroscopy: a study on aqueous KCl}
+  {The all-seeing eye of Auger electron spectroscopy: a study on aqueous KCl}
 
@@
 
-\begin{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[scale=0.3]{figures/fg2_k_6w_okxx_55_rad_dens.eps}
+%\caption{Radial density distributions of the singly-occupied natural orbitals occupied by the excited electron in the core excited states 3609.11\,eV (1\,$^{1}$A$_{2}$), 3609.41\,eV (2\,$^{1}$E) and 3609.64\,eV (3\,$^{1}$E) of K$^{+}$(H$_2$O)$_6$.
+The grey line at 2.816\,\AA~represents the equilibrium K-O distance.}
+%\label{fg:rad_dens}
+%\end{figure}
+
+\begin{figure}[h!]
 \centering
-\includegraphics[scale=0.3]{figures/fg2_k_6w_okxx_55_rad_dens.eps}
-\caption{Radial density distributions of the singly-occupied natural orbitals occupied by the excited electron in the core excited states 3609.11\,eV (1\,$^{1}$A$_{2}$), 3609.41\,eV (2\,$^{1}$E) and 3609.64\,eV (3\,$^{1}$E) of K$^{+}$(H$_2$O)$_6$.
-The grey line at 2.816\,\AA~represents the equilibrium K-O distance.}
-\label{fg:rad_dens}
+\includegraphics[scale=0.8]{figures/rad_dens_kcl.eps}
+\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$\rightarrow$4p, 1s$\rightarrow$3d and 1s$\rightarrow$5p core excitations in \ki~(lower panel) and \cli~(upper panel).
+The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
+\label{fg:si_rdens_ions}
 \end{figure}
@@
 \centering
-\includegraphics[scale=1.0]{figures/rad_dens_kcl.eps}
-\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$\rightarrow$4p, 1s$\rightarrow$3d and 1s$\rightarrow$5p core excitations in \ki~(lower panel) and \cli~(upper panel).
-The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
-\label{fg:rdens_ions}
+\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
+\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}.
+The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step.
+From these curves we determine the charge transfer time $\tau_{\texttt{CT}}$ according to the formula $\tau_{\texttt{CT}} = \tau l/d$, with $\tau$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$ 4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
+The green line defines the Cl$^{-}_{\texttt{aq}}$(1s) ionization potential.}
+\label{fg:si_ct_time}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\bibliography{F:/Articles/biblography/Bibliography}
+\bibliography{F:/Articles/bibliography/Bibliography}
+%\bibliography{Bibliography}
 

### 2018-02-05 abstract.tex
jan 24 (denis' corrections & tsveta's)
Shift explained as resulting from internal ionization, an argument for
the attribution of island C as 2p-2 3d state based on the CT paper
feb 5 (nico's corrections)
Nico's final corrections included; new graphical abstract

@@
 X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in a solution.
-In this work we use a combination of these spectroscopies to study the electronic structure and decay in aqueous KCl at the K-edges of \ki~and \cli.
+In this work we use a combination of these methods to study the electronic structure and decay in aqueous KCl at the K-edges of \ki~and \cli.
 Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features.
@@
 The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.
+{\color{red}The results of this work represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids and are thus of importance in unveiling the mechanisms of radiation damage in biologically relevant systems.}
+%Denis: line 2, I replaced spectroscopies by methods

### 2018-02-05 conclusion.tex
feb 5 (nico's corrections)
Nico's final corrections included; new graphical abstract

@@
 In the case of \cli~the two core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$\,\rightarrow\,$4p state are observed in the spectrum.
-Moreover, using the core-hole clock method we estimated the time of delocalization of the core excited electron at the pre-edge region of both ions.
-Whereas in \ki$_{\text{aq}}$ the delocalization of the core excited electron is slower than the resonant Auger process, in the case of \cli$_{\text{aq}}$ the two processes occur on a comparable timescale.
+{\color{red}Moreover, using the core-hole clock method we estimated the time of delocalization of the core excited electron at the pre-edge region of \cli$_{\text{aq}}$.
+Our results show that in this case, the resonant Auger decay and the delocalization of the excited electron occur on a comparable timescale.
+In the case of \ki$_{\text{aq}}$, we cannot make an accurate estimate, however, one can expect a much less efficient delocalization of the core excited electron.}
 

### 2018-02-05 introduction.tex
feb 2 (version sent to co-authors)
Changes made by Denis, new figures for SI, text changed.
feb 5 (nico's corrections)
Nico's final corrections included; new graphical abstract

@@
 X-ray absorption and Auger electron spectroscopies are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase.
-Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
+Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (see Ref.\ \citep{smith17:13909} and references therein), and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
 Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy.
@@
 This has been well understood in atoms and molecules in gas phase  \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001}.
-In the case of a core ionized state, the Auger decay process, designated as normal Auger decay (see Fig.\ \ref{fg:auger}), leads to the population of doubly ionized final states localized on the initially ionized unit {\color{red}\citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415}}.
+In the case of a core ionized state, the Auger decay process, designated as normal Auger decay (see Fig.\ \ref{fg:auger}), leads to the population of doubly ionized final states localized on the initially ionized unit \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415}.
 Auger processes in rare gas clusters have been also investigated (refs).
@@
 \begin{figure}
-\includegraphics{figures/auger_process.eps}
+\includegraphics[scale=0.8]{figures/auger_process.pdf}
 \caption{Schematic representation of the normal and resonant Auger processes of the isoelectronic \ki~and \cli~ions. The charges of the final Auger states in the two ions are also shown.}

### 2018-02-05 methods.tex
feb 5 (nico's corrections)
Nico's final corrections included; new graphical abstract

@@
 The catcher is placed at a distance of about 5\,mm from the capillary and is permanently pumped in order to extract the liquid.
-For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a HPLC pump with a constant flux of 1.6\,ml/min.
+For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a high performance liquid chromatography (HPLC) pump with a constant flux of 1.6\,ml/min.
 The alignment of the setup is performed on a salted aqueous solution by measuring the O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio.
@@
 The spectrometer resolution of about 0.6\,eV was achieved with the 500\,eV pass energy and 0.5\,mm slits.
-The photon energy resolution achieved at 2.8\,keV and 3.6\,keV was about 0.3\,eV and 0.4\,eV, respectively
+The photon energy resolution achieved at 2.8\,keV and 3.6\,keV was about 0.3\,eV and 0.4\,eV, respectively.
+The experimental 2D maps representing the dependence of the electron kinetic energy on the photon energy of KCl at the K-edges of \ki~and \cli, are shown in Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}, respectively.
 
@@
 The geometry optimization was performed with the Gaussian 09 package \citep{g09}.
-In order to obtain more realistic structures corresponding to the bulk solution, we carried out constrained geometry optimization starting with the equilibrium gas-phase geometries \citep{lee99:3995}(REF for Cl-) belonging to the D$_3$ point group and increasing the angle $\theta$ between the K-O/Cl-O bond and the $C_3$ axis to 55$^{\circ}$ in the case of \ki~and 50$^{\circ}$ in the case of \cli.
+In order to obtain more realistic structures corresponding to the bulk solution, we carried out constrained geometry optimization starting with the equilibrium gas-phase geometries \citep{lee99:3995}{\color{red}(REF for Cl-)} belonging to the D$_3$ point group and increasing the angle $\theta$ between the K-O/Cl-O bond and the $C_3$ axis to 55$^{\circ}$ in the case of \ki~and 50$^{\circ}$ in the case of \cli.
 This angle was chosen such that the O-K-O and O-Cl-O angles are around the maxima of the angular distributions obtained from quantum mechanics / molecular mechanics dynamical simulations in Ref.\ \citep{ma14:1006}.
@@
 In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding the f functions) was used for all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
+{\color{red}The use of a smaller basis set in the case of K is due to the higher number of virtual orbitals compared to the case of Cl, and therefore, prohibitively high cost of the CVS-ADC(2)x computation.}
 In our calculations the core space comprises the 1s orbital of K$^{+}$ or \cli, whereas the remaining occupied orbitals are included in the valence space.
 For the calculations of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and \cli(H$_2$O)$_6$.
-To account for the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Lorentzian of FWHM 0.74\,eV and 0.62\,eV in the case of \ki~and \cli, respectively \citep{Krause79:329}.
+To account for the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of \ki~and \cli, respectively \citep{Krause79:329}.
 We analyzed the core excited states by expanding the singly occupied natural orbitals (SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or \cli~ion $\chi_{nl}$
@@
 Additionally, the basis set was augmented with 2 sets of s, p, d diffuse functions in the case of \ki, and 3 sets of s, p, d diffuse functions in the case of \cli.
+{\color{red}The larger basis set employed in the case of Cl was necessary in order to ensure the convergence of the excited states.}
 The active space comprises the 2s and 2p orbitals of K/Cl with occupancy fixed to 6 and all virtual orbitals with occupancy fixed to 1.

### 2018-02-05 results.tex
feb 5 (nico's corrections)
Nico's final corrections included; new graphical abstract

@@
 %The $^3$P final states are not observed in the experiment since they are forbidden from parity conservation rules.
-The $^3$P final states are expected to have very little intensity since at the first order they are forbidden from parity conservation rules.
-In addition, in our photon energy range of interest, the tail of the $^1$D state described in the next paragraph, and the $^1$D 2p$^{-2}$V' dispersive state (see next section) overlap in the same kinetic energy region making it impossible to properly determine the $^3$P state position.
-In the case of Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ (2p$^{-2}$) $^1$S and $^1$D states are located at 2373.2\,eV and 2382.1\,eV kinetic energy (see Fig.\ \ref{fg:2dmap_cl}).
-For K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines are located at 2958\,eV and 2968.4\,eV, respectively (see Fig.\ \ref{fg:2dmap_k}).
+The $^3$P final states are expected to have a very low intensity since at the first order they are forbidden from parity conservation rules.
+In addition, in the photon energy range of interest, the tail of the $^1$D state described in the next paragraph, and the $^1$D 2p$^{-2}$V' dispersive state (see next section) {\color{red}overlap with the $^3$P state in the kinetic energy region where it is expected to occur, thus making it impossible to properly determine its position.} In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines are located at 2958\,eV and 2968.4\,eV, respectively (see Fig.\ \ref{fg:2dmap_k}).
+For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ (2p$^{-2}$) $^1$S and $^1$D states are located at 2373.2\,eV and 2382.1\,eV kinetic energy (see Fig.\ \ref{fg:2dmap_cl}).
 
@@
 Consequently, one can attribute the high kinetic energy shoulder of the $^1$D and $^1$S peaks on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} as resulting from PCI effect.
+{\color{red}The asymmetric tail of the peaks resulting from PCI can be clearly seen on the cuts taken at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.}
 
@@
 This shoulder is attributed to electron transfer from the water solvent molecules \citep{ceolin17:263003} to the 3d orbital of K$^{+}$.
-In the case of \cli, there was no experimental evidence of such intense localized electron transfer processes.
+In the case of \cli, there is no experimental evidence of such intense electron transfer processes.
 
@@
 %
-where $V$ and $V'$ denote the virtual orbitals in the excited and singly ionized excited states, i.\ e.\ in the presence of the 1s$^{-1}$ and 2p$^{-2}$ core holes.
-The character of these states will be discussed below.
+where $V$ and $V'$ denote the unoccupied orbitals in the excited and singly ionized excited states, i.\ e.\ in the presence of the 1s$^{-1}$ and 2p$^{-2}$ core holes.
+The character of these states is discussed below.
 
+{\color{red}How are the IPs determined? 2D maps reveal the core excited states.}
 The pre-edge regions of the x-ray absorption spectra of \ki~and \cli~shown to the left on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} do not exhibit any high intensity features due to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold.
-Consequently, solely from these spectra, one cannot conclude whether there are core excited states in the pre-edge structure, which can undergo resonant Auger decay.
+Consequently, solely from these absorption spectra, one cannot conclude whether there are core excited states in the pre-edge structure, which can undergo resonant Auger decay.
 However, one can determine their excitation energies from the maxima of the resonant Auger features.
@@
 XAS spectra of the lowest K-shell transitions in the bare K$^{+}$ (lower left panel) and Cl$^{-}$ (lower right panel) ions and their 6-coordinated clusters (upper left panel, \ki(H$_2$O)$_6$, and upper right panel, \cli(H$_2$O)$_6$).
-The theoretical stick spectra were convolved with a Lorentzian profile of FWHM 0.74\,eV for \ki~and 0.62\,eV for \cli~(dashed line) and a Voigt profile to account for the lifetime broadening and the experimental resolution.
+The theoretical stick spectra were convolved with a Lorentzian profile of FWHM 0.74\,eV for \ki~and 0.62\,eV for \cli~(dashed line) and a Voigt profile to account for the lifetime broadening and the experimental resolution (full line).
 The stick spectrum corresponds to the projections $|a_{nl}^{i}|^2$ of the SONOs corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$\,\rightarrow\,$3d, 1s$\,\rightarrow\,$4p, and 1s$\,\rightarrow\,$5p states in the bare K$^+$ and \cli~ions (Eq.\ \ref{eq:sono_proj}).
-The theoretical XAS spectra of both \ki~and \cli~were shifted to higher photon energies such that the excitation energies lowest core excited states correspond to the experimentally determined energies -- 3610.7\,eV in the case of \ki, and 2825.2\,eV in the case of \cli.
+The theoretical XAS spectra of both \ki~and \cli~were shifted to higher photon energies such that the excitation energies of the lowest core excited states correspond to the experimentally determined energies -- 3610.7\,eV in the case of \ki, and 2825.2\,eV in the case of \cli.
 The experimental ionization thresholds are depicted as grey boxes starting at photon energies of 3611.9\,eV (\ki$_{\text{aq}}$) and 2825.4\,eV (\cli$_{\text{aq}}$).}
@@
 In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first peak.
-Since there are no other ionic states close the the 1s$\,\rightarrow\,$4p state in the ion, this state preserves its character in the cluster and interacts with states of the nearest water molecules.
-We attribute the two dispersive features on the 2D map of \cli~ and associated with the $^{1}$S and $^{1}$D terms, to the resonant Auger decay of these core-excited states involving mostly the 4p orbitals of chloride.
+Since there are no other ionic states close the 1s$\,\rightarrow\,$4p state in the bare ion, this state preserves its character in the cluster and interacts with states of the nearest water molecules.
+We attribute the two dispersive features on the 2D map of \cli~ and associated with the $^{1}$S and $^{1}$D terms, to the resonant Auger decay of these core excited states involving mostly the 4p orbitals of chloride.
 % {\color{red}%Since the photon energy step in the experimental spectrum coincides with the splitting between the two dispersive features, we assume that they originate from the decay of the same core excited state.
@@
 They are shown as bars in the upper panels on the experimental resonant Auger spectra on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}.
-In both the case of \ki~and \cli, we shifted the lowest 2p$^{-2}$4p states such that they coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.
+In both cases, we shifted the lowest 2p$^{-2}$4p states such that they coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.
 Out of all final states we show only the doublets.
@@
 Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV lies closer to the position of island C.
-Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the dipole forbidden 1s$\,\rightarrow\,$3d state of the 6-coordinated \ki~cluster to the group of 2p$^{-2}$3d states lying around 2975\,eV.
+Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$\,\rightarrow\,$3d state of the 6-coordinated \ki~cluster to the group of 2p$^{-2}$3d states lying around 2975\,eV.
 The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C.
-This difference may be due to the fact that we do not account for the effect of the solvent molecules in our calculation.
-Concerning the higher lying group of 2p$^{-2}$3d states at kinetic energies between 2982 and 2983\,eV, we conclude that these states are not populated since no additional experimental features are observed.
+This difference may be due to the fact that we do not account for the effect of distant solvent shells in our calculation.
+Concerning the higher lying group of 2p$^{-2}$3d states at kinetic energies between 2982 and 2983\,eV, we conclude that these states are not populated via the Auger process since no additional experimental features are observed.
 
@@
 Another argument supporting the attribution of the island C as being of 2p$^{-2}$ 3d character comes from the attribution of the A area as given in reference \cite{ceolin17:263003} and from the energy splitting between A and C.
-The A area originates from a charge transfer process between water (W) and core-excited potassium and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
+The A area originates from a charge transfer process between water (W) and core excited potassium and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
 The ionization potential of water in the liquid phase is about 11 eV which fits well with the observed A-C splitting.
@@
 %{\color{red}we do not say anything about the 3d contribution in blue.
-Am I correct if I am saying: "The calculated 2p-2 3d states represented by blue vertical lines are not populated during the decay of the first core-excited state of solvated chloride involving mostly its 4p orbitals with some water contribution."}
+Am I correct if I am saying: "The calculated 2p-2 3d states represented by blue vertical lines are not populated during the decay of the first core excited state of solvated chloride involving mostly its 4p orbitals with some water contribution."}
 
@@
 As mentioned above, the delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
-In order to estimate the delocalization rate of the core-excited electron at the pre-edges of \ki~and \cli, we used the core-hole clock method as in the reference  \cite{bjorneholm92:1892,karis96:1380}.
+In order to estimate the delocalization rate of the core excited electron at the pre-edges of \ki~and \cli, we used the core-hole clock method as in the reference  \cite{bjorneholm92:1892,karis96:1380}.
 
@@
 On the low-kinetic-energy side, the charge transfer process leads to a very large structure that unfortunately cannot be easily simulated by a known profile.
-However, the 1s core-hole lifetime is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and moreover, the core-excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
+However, the 1s core-hole lifetime is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and moreover, the core excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
 Therefore, one can expect a much less efficient delocalization process compared to \cli$_{\text{aq}}$.
@@
 However, we know that the 1s core-hole lifetime is shorter for potassium than for chloride (0.9 vs.
-1fs) and moreover, the core-excited state appears 1.2\,eV below the ionization threshold whereas it was only 0.2eV for chloride.
+1fs) and moreover, the core excited state appears 1.2\,eV below the ionization threshold whereas it was only 0.2eV for chloride.
 Therefore, one can expect a much less efficient delocalization process compared to \cli$_{\text{aq}}$.}

### 2018-02-06 abstract.tex
feb 6 (nico's corrections included)
Nico's corrections approved by him, 2 new references, new graphical
abstract

@@
 The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.
-{\color{red}The results of this work represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids and are thus of importance in unveiling the mechanisms of radiation damage in biologically relevant systems.}
+The results of this work represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids and are thus of importance in unveiling the mechanisms of radiation damage in biologically relevant systems.
 %Denis: line 2, I replaced spectroscopies by methods

### 2018-02-06 conclusion.tex
feb 6 (nico's corrections included)
Nico's corrections approved by him, 2 new references, new graphical
abstract

@@
 In the case of \cli~the two core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$\,\rightarrow\,$4p state are observed in the spectrum.
-{\color{red}Moreover, using the core-hole clock method we estimated the time of delocalization of the core excited electron at the pre-edge region of \cli$_{\text{aq}}$.
+Moreover, using the core-hole clock method we estimated the time of delocalization of the core excited electron at the pre-edge region of \cli$_{\text{aq}}$.
 Our results show that in this case, the resonant Auger decay and the delocalization of the excited electron occur on a comparable timescale.
-In the case of \ki$_{\text{aq}}$, we cannot make an accurate estimate, however, one can expect a much less efficient delocalization of the core excited electron.}
+In the case of \ki$_{\text{aq}}$, we cannot make an accurate estimate, however, one can expect a much less efficient delocalization of the core excited electron.
 

### 2018-02-06 introduction.tex
feb 6 (nico's corrections included)
Nico's corrections approved by him, 2 new references, new graphical
abstract

@@
 The course of a decay cascade depends on the character of the initially populated states.
-This has been well understood in atoms and molecules in gas phase  \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001}.
+This has been well understood in atoms and molecules in gas phase  \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}.
 In the case of a core ionized state, the Auger decay process, designated as normal Auger decay (see Fig.\ \ref{fg:auger}), leads to the population of doubly ionized final states localized on the initially ionized unit \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415}.

### 2018-02-06 methods.tex
feb 6 (nico's corrections included)
Nico's corrections approved by him, 2 new references, new graphical
abstract

@@
 In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding the f functions) was used for all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
-{\color{red}The use of a smaller basis set in the case of K is due to the higher number of virtual orbitals compared to the case of Cl, and therefore, prohibitively high cost of the CVS-ADC(2)x computation.}
+The use of a smaller basis set in the case of K is due to the higher number of atomic orbitals compared to the case of Cl, and therefore, prohibitively high cost of the CVS-ADC(2)x computation.
 In our calculations the core space comprises the 1s orbital of K$^{+}$ or \cli, whereas the remaining occupied orbitals are included in the valence space.
@@
 Additionally, the basis set was augmented with 2 sets of s, p, d diffuse functions in the case of \ki, and 3 sets of s, p, d diffuse functions in the case of \cli.
-{\color{red}The larger basis set employed in the case of Cl was necessary in order to ensure the convergence of the excited states.}
+The larger basis set employed in the case of Cl was necessary in order to ensure the convergence of the excited states.
 The active space comprises the 2s and 2p orbitals of K/Cl with occupancy fixed to 6 and all virtual orbitals with occupancy fixed to 1.

### 2018-02-06 results.tex
feb 6 (nico's corrections included)
Nico's corrections approved by him, 2 new references, new graphical
abstract

@@
 The $^3$P final states are expected to have a very low intensity since at the first order they are forbidden from parity conservation rules.
-In addition, in the photon energy range of interest, the tail of the $^1$D state described in the next paragraph, and the $^1$D 2p$^{-2}$V' dispersive state (see next section) {\color{red}overlap with the $^3$P state in the kinetic energy region where it is expected to occur, thus making it impossible to properly determine its position.} In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines are located at 2958\,eV and 2968.4\,eV, respectively (see Fig.\ \ref{fg:2dmap_k}).
+In addition, in the photon energy range of interest, the tail of the $^1$D state described in the next paragraph, and the $^1$D 2p$^{-2}$V' dispersive state (see next section) overlap with the $^3$P state in the kinetic energy region where it is expected to occur, thus making it impossible to properly determine its position.
+In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines are located at 2958\,eV and 2968.4\,eV, respectively (see Fig.\ \ref{fg:2dmap_k}).
 For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ (2p$^{-2}$) $^1$S and $^1$D states are located at 2373.2\,eV and 2382.1\,eV kinetic energy (see Fig.\ \ref{fg:2dmap_cl}).
@@
 Consequently, one can attribute the high kinetic energy shoulder of the $^1$D and $^1$S peaks on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} as resulting from PCI effect.
-{\color{red}The asymmetric tail of the peaks resulting from PCI can be clearly seen on the cuts taken at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.}
+The asymmetric tail of the peaks resulting from PCI can be clearly seen on the cuts taken at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.
 

### 2018-02-06 suppinfo.tex
feb 5 (nico's corrections)
Nico's final corrections included; new graphical abstract
feb 6 (nico's corrections included)
Nico's corrections approved by him, 2 new references, new graphical
abstract

@@
 \author{Tsveta Miteva}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
 
@@
 \author{Nicolas Sisourat}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
 
@@
 \author{J\'{e}r\^ome Palaudoux}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
 
 \author{Gunnar \"{O}hrwall}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
 
@@
 
-\author{Jean Pascal Rueff}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\author{Jean-Pascal Rueff}
+\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
 \affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}
@@
 \title[]
-  {The all-seeing eye of Auger electron spectroscopy: a study on aqueous KCl}
+  {The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
 

### 2018-02-14 abstract.tex
feb 14 (kolya's corrections included)
Kolya's corrections are included, several things left for D. to correct

@@
-%Kolya and Nico corrected Jan 8
 X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in a solution.
@@
 Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features.
-To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of \ki, \cli~and their microsolvated clusters.
+To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of bare \ki, \cli~and their microsolvated clusters.
 Our calculations show that the energy order of the 3d and 4p orbitals is inverted in \ki~with respect to \cli.

### 2018-02-14 conclusion.tex
feb 14 (kolya's corrections included)
Kolya's corrections are included, several things left for D. to correct

@@
-% w Kolya's and Nico's corrections
 \section{Conclusion}\label{sec:concl}
 
-Using a combination of x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, in this work we studied the electronic structure of aqueous solution of KCl at the K-edges of both K and Cl.
+Using a combination of x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, we studied the electronic structure of aqueous solution of KCl at the K-edges of both K and Cl.
 The Auger electron spectra of both ions as a function of photon energy exhibit features of normal as well as resonant Auger processes.
 To interpret the resonant Auger features in the experimental spectrum, we performed {\it ab initio} calculations on microsolvated clusters of \ki~and \cli.
-Our calculations show that the energy ordering of the 3d and 4p virtual orbitals of \cli~is inverted compared to \ki, and also that the energy splitting between the bright 1s$\,\rightarrow\,$4p and dark 1s$\,\rightarrow\,$3d core excited states is larger in the chlorine case.
+Our calculations show that the energy ordering of the 3d and 4p virtual orbitals of \cli~is inverted compared to \ki, and also that the energy splitting between the bright 1s$\,\rightarrow\,$4p and dark 1s$\,\rightarrow\,$3d core excited states is larger in the chloride case.
 Thus, the energetic proximity of the 3d and 4p orbitals in the bare \ki~ion results in the dipole forbidden 1s$\,\rightarrow\,$3d state acquiring intensity in a solution as a result of mixing with the dipole allowed 1s$\,\rightarrow\,$4p excitation.
-The spectator Auger decay of this state produces an additional dispersive feature which is manifest as a separate island in the Auger electron spectrum at high kinetic energies.
-In the case of \cli~the two core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$\,\rightarrow\,$4p state are observed in the spectrum.
+The spectator Auger decay of this state produces an additional dispersive feature which is manifested as a separate peak in the Auger electron spectrum at high kinetic energies.
+In the case of \cli~the 4p and 3d core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$\,\rightarrow\,$4p state are observed in the spectrum.
 Moreover, using the core-hole clock method we estimated the time of delocalization of the core excited electron at the pre-edge region of \cli$_{\text{aq}}$.
@@
 
-%{\bf\color{red}A nice concluding ``wow'' sentence}
 Our work shows that the combination of x-ray absorption and resonant Auger spectroscopies is a sensitive probe of the electronic structure of solvated ions.

### 2018-02-14 introduction.tex
feb 14 (kolya's corrections included)
Kolya's corrections are included, several things left for D. to correct

@@
 Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (see Ref.\ \citep{smith17:13909} and references therein), and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
-Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy.
+Upon absorption of an x-ray photon, either core excited or core ionized states of a specific atom are populated depending on the photon energy.
 The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decays.
@@
 In the case of a core ionized state, the Auger decay process, designated as normal Auger decay (see Fig.\ \ref{fg:auger}), leads to the population of doubly ionized final states localized on the initially ionized unit \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415}.
-Auger processes in rare gas clusters have been also investigated (refs).
 The normal Auger decay process in clusters proceeds similarly to that in atoms or molecules.
@@
 In a solution, the electronic decay processes initiated by x-ray photoabsorption are different compared to those in rare gas clusters due to the shorter distances and stronger interatomic interactions.
-In particular, the solvent molecules have two effects -- first, they strongly affect the excited \citep{miteva16:16671} or ionized states of the ion and second, they can participate in the decay processes, leading to the population of charge-separated final states, and ionization of the surrounding environment \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,ceolin17:263003}.
+In particular, the solvent molecules have two effects -- first, they strongly affect the excited \citep{miteva16:16671} or ionized states of the ion and second, they can participate in the decay processes, leading to the population of charge-separated final states, and ionization of the surrounding environment \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,ceolin17:263003,unger17:708}.
 Moreover, the process of delocalization of the initially excited electron also occurs in aqueous solutions \citep{Nordlund07:217406,Ottosson11:13489}.
 %Moreover, the process of delocalization of the initially excited electron is not specific to rare gas clusters, but it also occurs in aqueous solutions \citep{Nordlund07:217406,Ottosson11:13489}. 
-In the case of pure water, the rate of delocalization of the O1s excited electron takes place on a femtosecond to sub-femtosecond time scale depending on the photon energy, thus being commensurate with the lifetime of the O1s core hole which is 6\,fs \citep{Nordlund07:217406}.
-The O K-edge is located in the soft x-ray range of photon energies.
+In the case of pure water, the delocalization of the O1s excited electron takes place on a femtosecond to sub-femtosecond time scale depending on the photon energy, thus being commensurate with the lifetime of the O1s core hole which is $\sim$3.6\,fs \citep{Nordlund07:217406}.
+The O K-edge is located in the soft x-ray range of photon energies, $\sim$533\,eV in water vapor \citep{wagner80:1445}.
 Going higher in photon energy, in the tender and hard x-ray regimes, the lifetimes of the core ionized or core excited states become even shorter, on the order of 1\,fs.
@@
 In both ions, there is a competition between resonant Auger decay and delocalization of the excited electron.
-Using the core-hole clock method we show that in \ki~delocalization at the pre-edge is weak, whereas in the case of \cli, due to the energetic proximity of the core excited state to the K-edge, the rate of delocalization is of the same order as that of the resonant Auger process.
+Using the core-hole clock method we show that in \ki~delocalization at the pre-edge is weak, whereas in the case of \cli, due to the energetic proximity of the core excited state to the ionization threshold, the rate of delocalization is of the same order as that of the resonant Auger process.
 Moreover, we observe that although the \ki~and \cli~ions are isoelectronic, they have different fingerprints in the resonant Auger spectra.
@@
 \includegraphics[scale=0.8]{figures/auger_process.pdf}
-\caption{Schematic representation of the normal and resonant Auger processes of the isoelectronic \ki~and \cli~ions. The charges of the final Auger states in the two ions are also shown.}
+\caption{Schematic representation of the resonant (left) and normal (right) Auger processes of the isoelectronic \ki~and \cli~ions.
+The charges of the final Auger states in the two ions are also shown.}
 \label{fg:auger}

### 2018-02-14 master.tex
feb 2 (version sent to co-authors)
Changes made by Denis, new figures for SI, text changed.
feb 5 (nico's corrections)
Nico's final corrections included; new graphical abstract
feb 6 (nico's corrections included)
Nico's corrections approved by him, 2 new references, new graphical
abstract
feb 14 (kolya's corrections included)
Kolya's corrections are included, several things left for D. to correct

--- 2018-01-19 master.tex
@@
 \newcommand{\tsveta}[1]{\textcolor{red}{#1}}
-\newcommand{\nico}[1]{\textcolor{red}{#1}}
-\newcommand{\kolya}[1]{\textcolor{blue}{#1}}
 \newcommand{\denis}[1]{\textcolor{green}{#1}}
@@
 \author{Tsveta Miteva}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
+\email{tsveta.miteva@upmc.fr}
 
-\author{Nikolai Kryzhevoi}
+\author{Nikolai V. Kryzhevoi}
 \affiliation{Theoretische Chemie, Physikalisch-Chemisches Institut, Universit\"at Heidelberg, Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
@@
 \author{Nicolas Sisourat}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
 
-\author{Ch. Nicolas}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\author{Christophe Nicolas}
+\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}
 
 \author{Wandared Pokapanich}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
-
-\author{Th. Saisopa}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
-
-\author{P. Songsiriritthigul}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
-
-\author{Y. Rattanachai}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Faculty of Science, Nakhon Phanom University, Nakhon Phanom 48000, Thailand}
+%
+\author{Thanit Saisopa}
+\author{Prayoon Songsiriritthigul}
+\affiliation{School of Physics, Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}
+%
+\author{Yuttakarn Rattanachai}
+\affiliation{Department of Applied Physics, Faculty of Sciences and Liberal Arts, Rajamangala University of Technology Isan, Nakhon Ratchasima 30000, Thailand}
 
 \author{Andreas Dreuw}
-\affiliation{Interdisciplinary Center for Scientific Computing, Ruprecht-Karls University, Im Neuenheimer Feld 205A, D-69120 Heidelberg, Germany}
-
 \author{Jan Wenzel}
@@
 
-\author{Ralph P\"{u}ttner}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
-
 \author{J\'{e}r\^ome Palaudoux}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
 
 \author{Gunnar \"{O}hrwall}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
+\affiliation{MAX IV Laboratory, Lund University, P.O. Box 118, SE-22100 Lund, Sweden}
+
+\author{Ralph P\"{u}ttner}
+\affiliation{Fachbereich Physik, Freie Universit\"at Berlin, Arnimallee 14, D-14195, Berlin, Germany}
 
@@
 
-\author{Jean Pascal Rueff}
-\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}
-\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}
+\author{Jean-Pascal Rueff}
+\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
+\alsoaffiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title[]
-  {The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
+\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
 
@@
 
-\includegraphics[scale=0.82]{figures/graphical.png}
+\includegraphics[scale=0.105]{figures/graphical.png}
 %Some journals require a graphical entry for the Table of Contents.
@@
 Campus France and the PHC SIAM exchange program are acknowledged for financial support.
+N.
+V.
+Kryzhevoi and L.
+S.
+Cederbaum acknowledge the financial support of the European Research Council (ERC) (Advanced Investigator Grant No.
+692657) and the Deutsche Forschungsgemeinschaft (DFG research unit 1789).
 
@@
 \bibliography{F:/Articles/bibliography/Bibliography}
+%\bibliography{Bibliography}
 

### 2018-02-14 methods.tex
feb 14 (kolya's corrections included)
Kolya's corrections are included, several things left for D. to correct

@@
 For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}.
-A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes manipulator in front of the spectrometer lens.
+A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes motorized manipulator in front of the spectrometer lens.
 Two holes of 2\,mm diameter allow the photons to go in and out.
@@
 For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a high performance liquid chromatography (HPLC) pump with a constant flux of 1.6\,ml/min.
-The alignment of the setup is performed on a salted aqueous solution by measuring the O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio.
+The {\color{red}calibration} of the setup is performed on the KCl aqueous solution by measuring the water O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio.
 The pressure in the main chamber is kept below the 10$^{-5}$\,mbar range whereas it is kept at about 10$^{-4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
@@
 The photon energy resolution achieved at 2.8\,keV and 3.6\,keV was about 0.3\,eV and 0.4\,eV, respectively.
-The experimental 2D maps representing the dependence of the electron kinetic energy on the photon energy of KCl at the K-edges of \ki~and \cli, are shown in Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}, respectively.
+The experimental 2D maps representing the evolution of the KLL Auger spectra in the vicinity of the \cli and \ki~K-edges, as a function of the photon energy, are shown in Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}, respectively.
+The aqueous \ki~and \cli~1s ionization potentials were measured at h$\nu$=5keV and calibrated on the liquid contribution of the O1s XPS spectrum \cite{winter06:1176}.
+The maps were also calibrated using the O1s photoelectron line of liquid water but at photon energies close to the potassium and chloride 1s ionization thresholds.
 
@@
 The theoretical X-ray absorption spectra were computed for the hexa-coordinated clusters of both ions, \ki(H$_2$O)$_6$ and \cli(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
-The two structures were optimized at the DFT level of theory using the B3LYP functional and the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,Blaudeau97:5016}.
+The two structures shown in Fig.\ \ref{fg:xas_kcl} were optimized at the DFT level of theory using the B3LYP functional and the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,Blaudeau97:5016}.
 The geometry optimization was performed with the Gaussian 09 package \citep{g09}.
-In order to obtain more realistic structures corresponding to the bulk solution, we carried out constrained geometry optimization starting with the equilibrium gas-phase geometries \citep{lee99:3995}{\color{red}(REF for Cl-)} belonging to the D$_3$ point group and increasing the angle $\theta$ between the K-O/Cl-O bond and the $C_3$ axis to 55$^{\circ}$ in the case of \ki~and 50$^{\circ}$ in the case of \cli.
+In order to obtain realistic structures corresponding to the bulk solution, we carried out constrained geometry optimization by choosing the equilibrium gas-phase geometries \citep{lee99:3995,lee02:5509} belonging to the D$_3$ point group and then increasing the angle $\theta$ between the K-O/Cl-O bond and the $C_3$ axis to 55$^{\circ}$ in the case of \ki~and 50$^{\circ}$ in the case of \cli.
 This angle was chosen such that the O-K-O and O-Cl-O angles are around the maxima of the angular distributions obtained from quantum mechanics / molecular mechanics dynamical simulations in Ref.\ \citep{ma14:1006}.
 Moreover, we fixed the K-O and Cl-O distances to 2.840~\AA~and 3.140~\AA, respectively, such that they correspond to the distances from other theoretical and experimental works \citep{ge13:13169,gora00:7,Ohtaki93:1157,soper06:180,ma14:1006}.
-The hexa-coordinated structures are presented in Fig.\ \ref{fg:xas_kcl}.
+%The hexa-coordinated structures are presented in Fig.\ \ref{fg:xas_kcl}.
 %In both cases, they belong D$_3$ point group \citep{rao08:12944,ge13:13169}.
 
-The energies and transition moments of the core excited states of the microsolvated clusters were computed with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}.
-In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding the f functions) was used for all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
+The energies and transition moments of the core excited states of the bare ions and microsolvated clusters were computed with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}.
+In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding f functions) was used for all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
 The use of a smaller basis set in the case of K is due to the higher number of atomic orbitals compared to the case of Cl, and therefore, prohibitively high cost of the CVS-ADC(2)x computation.
@@
 To account for the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of \ki~and \cli, respectively \citep{Krause79:329}.
+Additionally, we convolved the theoretical spectra with a Voigt profile to also account for the experimental resolution (see Fig.\ \ref{fg:xas_kcl}).
 We analyzed the core excited states by expanding the singly occupied natural orbitals (SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or \cli~ion $\chi_{nl}$
@@
 where $n$ and $l$ stand for the principal and orbital quantum numbers as described in Ref.\ \citep{miteva16:16671}.
-The expansion coefficients $a^{i}_{nl}$ show the degree of delocalization of the excited electron and the mixing of the core excited states in the crystal field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl}).
+The expansion coefficients $a^{i}_{nl}$ show the degree of delocalization of the excited electron and the mixing of the core excited states in the ligand field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl}).
 
@@
 We used the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,McLean80:5639,Blaudeau97:5016} on all atoms.
-Additionally, the basis set was augmented with 2 sets of s, p, d diffuse functions in the case of \ki, and 3 sets of s, p, d diffuse functions in the case of \cli.
+Additionally, the basis set was augmented with two sets of s, p, d diffuse functions in the case of \ki, and three sets of s, p, d diffuse functions in the case of \cli.
 The larger basis set employed in the case of Cl was necessary in order to ensure the convergence of the excited states.

### 2018-02-14 results.tex
feb 14 (kolya's corrections included)
Kolya's corrections are included, several things left for D. to correct

@@
 The upper panel shows two spectra at photon energies 3610.7\,eV, and 3616\,eV below and above the ionization potential at 3611.9\,eV, respectively.
-The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) doublet resonant Auger states of K$^{+}$(H$_2$O)$_6$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).
+The bars in the pre-edge cut correspond to the theoretical final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) doublet resonant Auger states of K$^{+}$(H$_2$O)$_6$ (see Sec.\ \ref{sec:methods} for details).
 The features A, B and C are discussed in the text.}
@@
 The upper panel shows two spectra at photon energies 2825.2\,eV, and 2830.0\,eV below and above the ionization potential at 2825.4\,eV, respectively.
-The bars in the pre-edge cut correspond to the final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) doublet resonant Auger states of Cl$^{-}$(H$_2$O)$_6$ computed at the CIS level (see Sec.\ \ref{sec:methods} for details).}
+The red bars in the pre-edge cut correspond to the theoretical final 2p$^{-2}$4p doublet resonant Auger states of Cl$^{-}$(H$_2$O)$_6$ (see Sec.\ \ref{sec:methods} for details).}
 \label{fg:2dmap_cl}
@@
 \begin{align*}
-\gamma + \text{K}^{+}_{\text{aq}} \rightarrow \text{K}^{2+}_{\text{aq}} (1s^{-1}) \rightarrow \text{K}^{3+}_{\text{aq}} (2p^{-2}) + e^{-}_{\text{Auger}}\\
-\gamma + \text{Cl}^{-}_{\text{aq}} \rightarrow \text{Cl}^{0}_{\text{aq}} (1s^{-1}) \rightarrow \text{Cl}^{+}_{\text{aq}}(2p^{-2}) + e^{-}_{\text{Auger}}
+h\nu + \text{K}^{+}_{\text{aq}} \rightarrow 
+	\text{K}^{2+}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
+	\text{K}^{3+}_{\text{aq}} (2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}\\
+h\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow
+	\text{Cl}^{0}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
+	\text{Cl}^{+}_{\text{aq}}(2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}
 \end{align*}
 %
-It results in the population of 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states. 
-%The $^3$P final states are not observed in the experiment since they are forbidden from parity conservation rules.
-The $^3$P final states are expected to have a very low intensity since at the first order they are forbidden from parity conservation rules.
-In addition, in the photon energy range of interest, the tail of the $^1$D state described in the next paragraph, and the $^1$D 2p$^{-2}$V' dispersive state (see next section) overlap with the $^3$P state in the kinetic energy region where it is expected to occur, thus making it impossible to properly determine its position.
+It populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
+The $^3$P final states are expected to have a very low intensity since the corresponding transitions are forbidden from parity conservation rules.
+However, these states are not observed in the experimental spectra presented on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} because they overlap with the 2p$^{-2}$($^1$D) and 2p$^{-2}$($^1$D)$V'$ states in the kinetic energy region where they are expected to occur.
 In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines are located at 2958\,eV and 2968.4\,eV, respectively (see Fig.\ \ref{fg:2dmap_k}).
-For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ (2p$^{-2}$) $^1$S and $^1$D states are located at 2373.2\,eV and 2382.1\,eV kinetic energy (see Fig.\ \ref{fg:2dmap_cl}).
+For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at 2373.2\,eV and 2382.1\,eV kinetic energy (see Fig.\ \ref{fg:2dmap_cl}).
+{\color{red}Which photon energy?}
 
-The KL$_{2,3}$L$_{2,3}$ Auger lines do not disperse with photon energy except close to threshold due to the interaction between the photoelectron and Auger electron, i.e.\ the so-called post-collision interaction (PCI).
-As a result of this interaction, first, the peaks in the Auger spectrum become asymmetric with a shoulder at high kinetic energies, and second, they are shifted to higher kinetic energies close to threshold \citep{russek86:911,guillemin15:012503}.
-Consequently, one can attribute the high kinetic energy shoulder of the $^1$D and $^1$S peaks on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} as resulting from PCI effect.
-The asymmetric tail of the peaks resulting from PCI can be clearly seen on the cuts taken at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.
+The KL$_{2,3}$L$_{2,3}$ Auger lines may disperse with photon energy close to threshold due to energy exchange between the photoelectron and Auger electron called post-collision interaction (PCI).
+As a result of this interaction, first, an Auger peak becomes asymmetric with a high kinetic energy shoulder, and second, its intensity maximum is shifted to higher kinetic energies close to threshold \citep{russek86:911,guillemin15:012503}.
+These effects are seen in our spectra -- the asymmetric tail of the peaks resulting from PCI is clearly shown on the cuts taken at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.
 
-%In order to quantify this effect we recorded the KLL Auger spectrum of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ at higher photon energies, $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
-In this case, the maxima of the $^1$D and $^1$S states were found at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
-The lines observed at photon energies far from threshold and close to it appear to be shifted by $\sim$1\,eV.
-The magnitude of the shift is the same for both ions suggesting that it does not depend on the initial charge of the ion, and it is almost constant in the photon energy range presented here.
-% Jan 24 Tsveta
 Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
-In this case, the maxima of the $^1$D and $^1$S states were found at lower values at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
+In the latter case, the maxima of the $^1$D and $^1$S states were found at lower values at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
 The lines observed at photon energies far from threshold and close to it appear thus to be shifted by $\sim$1\,eV.
-The magnitude of the shift is the same for both ions suggesting that it does not depend on the initial charge of the ion, and it is almost constant in the photon energy range presented here.
-A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314}, which focuses on the Auger decay of large Kr clusters on and just above the 3d$_{5/2}$ ionization threshold.
-The observed 4d$^{4}$($^1$D) Auger peak was found to be shifted by 0.7\,eV to higher kinetic energies compared to the position of the peak far above threshold.
+The magnitude of the shift is constant in the photon energy range of {\color{red}XX\,eV above threshold.} Moreover, it is the same for both ions suggesting that it does not depend on the initial charge of the ion.
+A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314}, which focuses on the Auger decay of large Kr clusters near the 3d$_{5/2}$ ionization threshold.
+The observed 4d$^{-2}$($^1$D) Auger peak was found to be shifted by 0.7\,eV to higher kinetic energies compared to the position of the peak far above threshold.
 Moreover, the shift did not vary with the photon energy close to threshold.
-Consequently, it was proposed that this feature originates from a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band.
-Further investigations are, however, planned in the case of liquid samples.
-%\denis{A possible explanation was given in the reference M.
-Tchaplyguine et al., The Journal of Chemical Physics 127, 124314 (2007) focusing on the Auger decay of large Kr clusters following ionization of the 3d$_{5/2}$ orbital.
-Considering that the observed PCI shift was not varying with the photon energy close to threshold, a process of excitation of the photoelectron into the conduction band was thus proposed.
-Further investigation are however planned in the case of liquid samples.}
-% The observed PCI shift of 1\,eV is larger than in the case of the isoelectronic Ar, where its value is $\sim$0.5\,eV at a photon energy of 10 \,eV above threshold \citep{guillemin15:012503}.
-The shift in the energies of the photo- and Auger electrons is proportional to the change in the ionic field during the Auger process.
-In a solution, both the single and double ionization potentials change due to the polarization of the water molecules and the stabilization of the ionic species through ion-dipole interaction with the polarized solvent.
-For example, in \ki, the ionization potential of the bare ion was experimentally determined to be 3619.4\,eV \citep{hertlein06:062715}, whereas in an aqueous solution, its value drops by about 7.5\,eV.
-The magnitude of this effect increases with the ionic charge, consequently, there will be an even greater difference for the double ionization potential.
-Thus, one can expect a larger change in the ionic field in an aqueous solution compared to that in a Van der Waals cluster, which can, therefore, account for the large PCI shift of the Auger lines in a solution.
+{\color{red}Consequently, it was proposed that this feature originates from a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band, and that the observed shift is a result of the PCI-like interaction between the electron excited in the conduction band and the Auger electron.} Further investigations are, however, planned in the case of liquid samples.
 
-Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder (A on Fig.\ \ref{fg:2dmap_k}) on the low kinetic energy side at about 2965\,eV kinetic energy.
-This shoulder is attributed to electron transfer from the water solvent molecules \citep{ceolin17:263003} to the 3d orbital of K$^{+}$.
+Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder (feature A on Fig.\ \ref{fg:2dmap_k}) on the low kinetic energy side at about 2965\,eV kinetic energy.
+This shoulder is attributed to electron transfer from the solvent water molecules to the 3d orbital of K$^{+}$ \citep{ceolin17:263003}.
 In the case of \cli, there is no experimental evidence of such intense electron transfer processes.
@@
 \begin{align*}
-\gamma + \text{K}^{+}_{\text{aq}} \rightarrow \text{K}^{+*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{K}^{2+}_{\text{aq}} (2p^{-2}V') + e^{-}_{\text{Auger}}\\
-\gamma + \text{Cl}^{-}_{\text{aq}} \rightarrow \text{Cl}^{-*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{Cl}^{0}_{\text{aq}}(2p^{-2}V') + e^{-}_{\text{Auger}}
+h\nu + \text{K}^{+}_{\text{aq}} \rightarrow \text{K}^{+*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{K}^{2+}_{\text{aq}} (2p^{-2}V') + e^{-}_{\text{Auger}}\\
+%
+h\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow \text{Cl}^{-*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{Cl}^{0}_{\text{aq}}(2p^{-2}V') + e^{-}_{\text{Auger}}
 \end{align*}
 %
-where $V$ and $V'$ denote the unoccupied orbitals in the excited and singly ionized excited states, i.\ e.\ in the presence of the 1s$^{-1}$ and 2p$^{-2}$ core holes.
-The character of these states is discussed below.
+where $V$ and $V'$ denote the unoccupied orbitals in the excited and singly ionized excited states. The character of these states is discussed below.
 
-{\color{red}How are the IPs determined? 2D maps reveal the core excited states.}
-The pre-edge regions of the x-ray absorption spectra of \ki~and \cli~shown to the left on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} do not exhibit any high intensity features due to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold.
+The pre-edge regions of the x-ray absorption spectra of \ki~and \cli~shown to the left on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} do not exhibit any high intensity peaks owing to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold.
 Consequently, solely from these absorption spectra, one cannot conclude whether there are core excited states in the pre-edge structure, which can undergo resonant Auger decay.
@@
 The resonant Auger features produced in the decay of these core excited states appear to be quite different for \cli~and \ki.
-In the spectrum of \cli~shown in Fig.\ \ref{fg:2dmap_cl} there are two dispersive features on the high kinetic energy side of the main $^1$S and $^1$D lines, i.e.\ at 2825.2\,eV photon energy and 2374.6 and 2383.4\,eV kinetic energy.
+In the spectrum of \cli~shown in Fig.\ \ref{fg:2dmap_cl} there are two dispersive features, each on the high kinetic energy side of the main $^1$S and $^1$D lines, i.e.\ at 2825.2\,eV photon energy and 2374.6 and 2383.4\,eV kinetic energy.
 In the case of \ki, the $^1$S dispersive line cannot be clearly identified due to the presence of strong background.
-The dispersive feature close to the $^1$D main peak is observed (feature B) with a maximum located at $h\nu = $3611.2 \,eV and 2969.2 \,eV kinetic energy.
+The dispersive feature close to the $^1$D main peak is however well observed (feature B) with a maximum located at $h\nu = $3611.2 \,eV and 2969.2 \,eV kinetic energy.
 An additional feature appears as a separate island away from the main lines on the 2D map of \ki.
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
 \centering
-\includegraphics[scale=0.6]{figures/xas_spectra.eps}
+\includegraphics[scale=0.8]{figures/xas_spectra.eps}
 \caption{
@@
 The stick spectrum corresponds to the projections $|a_{nl}^{i}|^2$ of the SONOs corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$\,\rightarrow\,$3d, 1s$\,\rightarrow\,$4p, and 1s$\,\rightarrow\,$5p states in the bare K$^+$ and \cli~ions (Eq.\ \ref{eq:sono_proj}).
+The grey sticks in the stick spectrum correspond to contributions from higher-lying atomic core excitations or from excitations to the solvent molecules.
 The theoretical XAS spectra of both \ki~and \cli~were shifted to higher photon energies such that the excitation energies of the lowest core excited states correspond to the experimentally determined energies -- 3610.7\,eV in the case of \ki, and 2825.2\,eV in the case of \cli.
@@
 We note in passing that the intensity of the Cl$^{-}$(1s$\,\rightarrow\,$4p) state is lower than that of the \cli(1s$\,\rightarrow\,$5p) state contrary to what is observed in \ki.
-This difference can be explained with the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$\,\rightarrow\,$4p compared to the 1s$\,\rightarrow\,$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
+This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$\,\rightarrow\,$4p compared to the 1s$\,\rightarrow\,$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
 
@@
 First, upon addition of water molecules, the degeneracy of the 1s$\,\rightarrow\,$4p state is lifted and the intensity of the resulting states in the cluster drops.
-Moreover, the character of these states changes -- they are no longer of pure atomic character but they rather interact with states of the neighboring water molecules (shown as grey bars) and with other closely lying states of the bare ion, such as the dipole allowed 1s$\,\rightarrow\,$5p and dipole forbidden 1s$\,\rightarrow\,$3d state.
+Moreover, the character of these states changes -- they are no longer of pure atomic character but they rather interact with states of the neighboring water molecules (shown as grey bars in Fig.\ \ref{fg:xas_kcl}) and with other closely lying states of the bare ion, such as the dipole allowed 1s$\,\rightarrow\,$5p and dipole forbidden 1s$\,\rightarrow\,$3d state.
 Thus, the latter also acquire intensity in the cluster due to mixing with the dipole allowed states in the ligand field of the solvent.
@@
 We attribute the two dispersive features on the 2D map of \cli~ and associated with the $^{1}$S and $^{1}$D terms, to the resonant Auger decay of these core excited states involving mostly the 4p orbitals of chloride.
-% {\color{red}%Since the photon energy step in the experimental spectrum coincides with the splitting between the two dispersive features, we assume that they originate from the decay of the same core excited state.
-% We assume that the two dispersive features originate from the decay of the same core excited state, since the photon energy resolution at 2.8\,keV is 0.3\,eV and thus of the same magnitude as the difference between the core excited state and the ionization threshold.
-% }
 
@@
 
-%As mentioned above, we assume that the island B is produced in the decay of the lowest lying core excited state of the hexa-hydrated \ki~cluster, which is of predominantly 1s$\,\rightarrow\,$4p character.
-As mentioned above, we attribute the island B to the decay of the lowest lying core excited state of the hexa-hydrated \ki~cluster, which is of predominantly 1s$\,\rightarrow\,$4p character.
+As mentioned above, we attribute the island B to the decay of the lowest lying core excited state, which is of predominantly 1s$\,\rightarrow\,$4p character.
 Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$\,\rightarrow\,$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character located between 2969 and 2970.5\,eV are populated.
@@
 Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV lies closer to the position of island C.
-Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$\,\rightarrow\,$3d state of the 6-coordinated \ki~cluster to the group of 2p$^{-2}$3d states lying around 2975\,eV.
+Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$\,\rightarrow\,$3d state to the group of 2p$^{-2}$3d states lying around 2975\,eV.
 The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C.
@@
 
-% \tsveta{Another argument supporting the attribution of the island C as being of 2p$^{-2}$ 3d character can be found by considering the electron transfer from the water molecules (W) discussed in reference \cite{ceolin17:263003}.
-As a result of this process, an additional feature A is observed on the low-kinetic energy side of the $^1$D main peak in \ki.
-This feature has the configuration K$^{2+}$2p$^{-2}$3d W$^{-1}$.
-...}
-Another argument supporting the attribution of the island C as being of 2p$^{-2}$ 3d character comes from the attribution of the A area as given in reference \cite{ceolin17:263003} and from the energy splitting between A and C.
-The A area originates from a charge transfer process between water (W) and core excited potassium and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
-The ionization potential of water in the liquid phase is about 11 eV which fits well with the observed A-C splitting.
-Based only on these two simple energetic arguments we can attribute the C island to the a K$^{2+}$ 2p$^{-2}$3d configuration and note that neither 2p$^{-2}$3d nor charge transfer states are present in the Cl$^{-}$ case.
+The energy difference between the spectral features A and C provides another argument in favor of the 2p$^{-2}$ 3d character of the feature C.
+The feature A originates from electron transfer processes from water molecules (W) to the doubly core ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
+The lowest ionization potential of liquid water in the liquid phase is about 11.16\,eV \cite{winter04:2625} which fits well with the observed A-C splitting.
+Based on the above energetic arguments we attribute the island C to the K$^{2+}$ 2p$^{-2}$3d configuration.
 
@@
 The lower kinetic energy group corresponds to the 2p$^{-2}$($^1$S)4p states, whereas the higher kinetic energy group corresponds to the 2p$^{-2}$($^1$D)4p states.
-The splitting between the two groups is in good agreement with the experimental splitting between the dispersive features on the high kinetic energy sides of the $^1$S and $^1$D main peaks.
-Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$\,\rightarrow\,$4p core excited state of \cli$_{\texttt{aq}}$ to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.
+The splitting between these two groups is in good agreement with the experimental splitting between the dispersive features on the high kinetic energy sides of the $^1$S and $^1$D main peaks.
+Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$\,\rightarrow\,$4p core excited state of \cli$_{\text{aq}}$ to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.
 Similar dispersive features originating from the decay of the Cl (1s$\,\rightarrow\,$4p) state were observed on the 2D map of chloromethane CH$_3$Cl recorded in the vicinity of the Cl K-edge in gas phase \cite{gold16:133001}.
-In this case, however, additional lower-lying core excited state are observed.
+In this case, however, additional lower-lying core excited states are observed.
 They result from excitation to the LUMO of CH$_3$Cl, which is a linear combination of the C 2p and Cl 3p atomic orbitals.
-Since the 3p shell is fully occupied in \cli, such a core excited state is not observed in our experiment.
-
-% Jan 24 Tsveta: this is already written two paragraphs above.
-
-%{\color{red}we do not say anything about the 3d contribution in blue.
-Am I correct if I am saying: "The calculated 2p-2 3d states represented by blue vertical lines are not populated during the decay of the first core excited state of solvated chloride involving mostly its 4p orbitals with some water contribution."}
+Since the 3p shell is fully occupied in \cli, such core excited states are not observed in our experiment.
+We note that neither 2p$^{-2}$3d nor charge transfer states are found in the Cl$^{-}_{\text{aq}}$ case.
 
@@
 As mentioned above, the delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
-In order to estimate the delocalization rate of the core excited electron at the pre-edges of \ki~and \cli, we used the core-hole clock method as in the reference  \cite{bjorneholm92:1892,karis96:1380}.
+In order to estimate the delocalization rate of the core excited electron at the pre-edges of \ki~and \cli, we used the core-hole clock method as in references \cite{bjorneholm92:1892,karis96:1380}.
 
-In the case of \cli, and contrary to \ki, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502}, %(\tsveta{do you want to explain this data treatment in 1 sentence.
-now the reader is forced to check the other paper.}\denis{Tsveta, I think that what is just after the i.e.
-is enough.
-If you agree let's see what the others are saying}),
-i.e.
-for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get a partial electron yield as a function of the photon energy.
+In the case of \cli, and contrary to \ki, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502}, i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get a partial electron yield as a function of the photon energy.
 The result is shown on Fig.\ \ref{fg:si_ct_time} in the SI.
@@
 The position of the first peak coincides with the main $^1$D line resulting from normal Auger, whereas the second peak at 2383.5\,eV corresponds to the final resonant Auger states 2p$^{-2}$($^1$D)4p.
-By fitting the peak with two Voigt functions, we determine the ratio of the intensities of these peaks to be $\sim$1.
+By fitting this double-peak structure with two Voigt functions, we determine the ratio of the intensities of these peaks to be $\sim$1.
 Consequently, the delocalization time is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs.
@@
 
-For potassium the treatment is more complex due to the presence of multiple simultaneous processes -- normal, resonant Auger decay, charge transfer (CT) from solvent.
+For potassium, the treatment is more complex due to the presence of multiple simultaneous processes -- normal, resonant Auger decay, charge transfer from solvent.
 To extract the intensity of each component from the 2D map shown in Fig.\ \ref{fg:2dmap_k}, one needs the spectral fingerprints of each process to be separated.
-However, as can be seen, this is not the case especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
-For instance at 3610.7\,eV photon energy on the high-kinetic-energy side of the 2p$^{-2}$($^1$D) state, there are contributions from the PCI tail and from the dispersive 2p$^{-2}$($^1$D)4p state related to the B island.
-On the low-kinetic-energy side, the charge transfer process leads to a very large structure that unfortunately cannot be easily simulated by a known profile.
-However, the 1s core-hole lifetime is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and moreover, the core excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
-Therefore, one can expect a much less efficient delocalization process compared to \cli$_{\text{aq}}$.
-
-% Jan 24, Tsveta This is Denis' original sentence
-%\denis{For potassium the treatment was more complex in reason of multiple overlaps.
-To extract the intensity of each component of the 2D map shown in figure 2, one needs to isolate them.
-However this operation was not possible especially close to threshold.
-On one side of the $^1$D state, there are contributions of the PCI tail and of the dispersive state related to the B island, and on the other side, the charge transfer process leads to a very large structure that unfortunately cannot be easily simulated by a known profile.
-Below threshold, as for instance at 3610.7eV photon energy, we cannot exclude a superposition of the 2p$^{-2}$($^1$D)4p, 2p$^{-2}$($^1$D) and CT states in the kinetic energy region 2965-2970eV.
-However, we know that the 1s core-hole lifetime is shorter for potassium than for chloride (0.9 vs.
-1fs) and moreover, the core excited state appears 1.2\,eV below the ionization threshold whereas it was only 0.2eV for chloride.
-Therefore, one can expect a much less efficient delocalization process compared to \cli$_{\text{aq}}$.}
+However, as can be seen, this is hardly possible especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
+For instance at 3610.7\,eV photon energy on the high-kinetic-energy side of the 2p$^{-2}$($^1$D) state, there are contributions from the PCI tail and from the 2p$^{-2}$($^1$D)4p resonant Auger state.
+On the low-kinetic-energy side, the charge transfer processes lead to a very large structure whose shape unfortunately cannot be easily simulated by a known profile.
+However, the lifetime of the 1s core hole is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and, moreover, the core excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
+Therefore, one can expect much less efficient delocalization compared to \cli$_{\text{aq}}$.

### 2018-02-14 suppinfo.tex
feb 14 (kolya's corrections included)
Kolya's corrections are included, several things left for D. to correct

@@
 \affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
+\email{tsveta.miteva@upmc.fr}
 
-\author{Nikolai Kryzhevoi}
+\author{Nikolai V. Kryzhevoi}
 \affiliation{Theoretische Chemie, Physikalisch-Chemisches Institut, Universit\"at Heidelberg, Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
@@
 \author{Wandared Pokapanich}
-\affiliation{Faculty of Science, Nakhon Phanom University, Nakhon Phanom 48000 Thailand}
-
-\author{Th. Saisopa}
-\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
-Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}
-
-\author{P. Songsiriritthigul}
-\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
-Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}
-
-\author{Y. Rattanachai}
+\affiliation{Faculty of Science, Nakhon Phanom University, Nakhon Phanom 48000, Thailand}
+%
+\author{Thanit Saisopa}
+\author{Prayoon Songsiriritthigul}
+\affiliation{School of Physics, Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}
+%
+\author{Yuttakarn Rattanachai}
 \affiliation{Department of Applied Physics, Faculty of Sciences and Liberal Arts, Rajamangala University of Technology Isan, Nakhon Ratchasima 30000, Thailand}
@@
 \author{Andreas Dreuw}
-\affiliation{Interdisciplinary Center for Scientific Computing, Ruprecht-Karls University, Im Neuenheimer Feld 205A, D-69120 Heidelberg, Germany}
-
 \author{Jan Wenzel}
@@
 \author{Gunnar \"{O}hrwall}
-\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
+\affiliation{MAX IV Laboratory, Lund University, P.O. Box 118, SE-22100 Lund, Sweden}
 
@@
 \affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
-\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}
+\alsoaffiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}
 
@@
 The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step.
-From these curves we determine the charge transfer time $\tau_{\texttt{CT}}$ according to the formula $\tau_{\texttt{CT}} = \tau l/d$, with $\tau$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$ 4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
-The green line defines the Cl$^{-}_{\texttt{aq}}$(1s) ionization potential.}
+From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau l/d$, with $\tau$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$ 4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
+The green line defines the Cl$^{-}_{\text{aq}}$(1s) ionization potential.}
 \label{fg:si_ct_time}

### 2018-02-19 abstract.tex
feb 16 (ralph's corrections included)
Ralph's corrections, theoretical figures changed, 1s -> nl replaced by
1s-1 nl

@@
 The reverse orbital order in the two ions is reflected in both the ordering of the core excited states and in the final states populated in the resonant Auger decay.
-The energetic proximity of the 3d and 4p virtual states in the bare \ki~ion leads to their mixing in the presence of the solvent, and to the population of the dipole forbidden 1s$\,\rightarrow\,$3d state upon K-shell excitation in an aqueous solution.
+The energetic proximity of the 3d and 4p virtual states in the bare \ki~ion leads to their mixing in the presence of the solvent, and to the population of the dipole forbidden 1s$^{-1}$3d state upon K-shell excitation in an aqueous solution.
 The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.

### 2018-02-19 conclusion.tex
feb 16 (ralph's corrections included)
Ralph's corrections, theoretical figures changed, 1s -> nl replaced by
1s-1 nl

@@
 To interpret the resonant Auger features in the experimental spectrum, we performed {\it ab initio} calculations on microsolvated clusters of \ki~and \cli.
-Our calculations show that the energy ordering of the 3d and 4p virtual orbitals of \cli~is inverted compared to \ki, and also that the energy splitting between the bright 1s$\,\rightarrow\,$4p and dark 1s$\,\rightarrow\,$3d core excited states is larger in the chloride case.
-Thus, the energetic proximity of the 3d and 4p orbitals in the bare \ki~ion results in the dipole forbidden 1s$\,\rightarrow\,$3d state acquiring intensity in a solution as a result of mixing with the dipole allowed 1s$\,\rightarrow\,$4p excitation.
+Our calculations show that the energy ordering of the 3d and 4p virtual orbitals of \cli~is inverted compared to \ki, and also that the energy splitting between the bright 1s$^{-1}$4p and dark 1s$^{-1}$3d core excited states is larger in the chloride case.
+Thus, the energetic proximity of the 3d and 4p orbitals in the bare \ki~ion results in the dipole forbidden 1s$^{-1}$3d state acquiring intensity in a solution as a result of mixing with the dipole allowed 1s$^{-1}$4p excitation.
 The spectator Auger decay of this state produces an additional dispersive feature which is manifested as a separate peak in the Auger electron spectrum at high kinetic energies.
-In the case of \cli~the 4p and 3d core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$\,\rightarrow\,$4p state are observed in the spectrum.
+In the case of \cli~the 1s$^{-1}$4p and 1s$^{-1}$3d core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$^{-1}$4p excitation are observed in the spectrum.
 Moreover, using the core-hole clock method we estimated the time of delocalization of the core excited electron at the pre-edge region of \cli$_{\text{aq}}$.
@@
 
-Our work shows that the combination of x-ray absorption and resonant Auger spectroscopies is a sensitive probe of the electronic structure of solvated ions.
-The reported results are an important first step in the study of the electronic decay processes following photoabsorption in the tender x-ray regime, and they can have implications in revealing the mechanisms of radiation damage in biologically relevant systems.
+Our work shows that the combination of x-ray absorption and resonant Auger spectroscopy is a sensitive probe of the electronic structure of solvated ions.
+The reported results are an important first step in the study of the electronic decay processes following photoabsorption in the tender x-ray regime.
+The final Auger states inevitably undergo subsequent multiple electronic decay processes, such as ICD and ETMD.
+As a result of these processes, the surrounding environment becomes damaged, i.e.\ it is ionized, and moreover, slow electrons are emitted, which can inflict further damage upon the surroundings.
+The magnitude of the damage and the energies of the emitted electrons depend on the initial Auger step, and can therefore be controlled by varying the photon energy.
+Consequently, the results of this work can have implications in revealing the mechanisms of radiation damage in biologically relevant systems.

### 2018-02-19 introduction.tex
feb 16 (ralph's corrections included)
Ralph's corrections, theoretical figures changed, 1s -> nl replaced by
1s-1 nl

@@
 
-X-ray absorption and Auger electron spectroscopies are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase.
+X-ray absorption and Auger electron spectroscopy are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase.
 Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (see Ref.\ \citep{smith17:13909} and references therein), and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
@@
 
-%refs clusters??:
-%A. Lindblad, R. F. Fink, H. Bergersen, M. Lundwall, T. Rander, R. Feifel, G. Öhrwall, M. Tchaplyguine, U.Hergenhahn, S. Svensson, O. Björneholm, The Journal of Chemical %Physics 123, 211101 (2005)
-%M.
-Tchaplyguine, A.
-Kivimäki, S.
-Peredkov, S.
-L.
-Sorensen, G.
-Öhrwall, J.
-Schulz, M.
-Lundwall, T.
-Rander, A.
-Lindblad, A.
-Rosso, S.
-Svensson, N.
-Mårtensson, O.
-%Björneholm, The Journal of Chemical Physics, 127, 124314 (2007)
-
 In a solution, the electronic decay processes initiated by x-ray photoabsorption are different compared to those in rare gas clusters due to the shorter distances and stronger interatomic interactions.
@@
 Moreover, the process of delocalization of the initially excited electron also occurs in aqueous solutions \citep{Nordlund07:217406,Ottosson11:13489}.
-%Moreover, the process of delocalization of the initially excited electron is not specific to rare gas clusters, but it also occurs in aqueous solutions \citep{Nordlund07:217406,Ottosson11:13489}. 
 In the case of pure water, the delocalization of the O1s excited electron takes place on a femtosecond to sub-femtosecond time scale depending on the photon energy, thus being commensurate with the lifetime of the O1s core hole which is $\sim$3.6\,fs \citep{Nordlund07:217406}.

### 2018-02-19 methods.tex
feb 16 (ralph's corrections included)
Ralph's corrections, theoretical figures changed, 1s -> nl replaced by
1s-1 nl

@@
 For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a high performance liquid chromatography (HPLC) pump with a constant flux of 1.6\,ml/min.
-The {\color{red}calibration} of the setup is performed on the KCl aqueous solution by measuring the water O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio.
+The alignment of the setup is performed on the KCl aqueous solution by measuring the water O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio.
 The pressure in the main chamber is kept below the 10$^{-5}$\,mbar range whereas it is kept at about 10$^{-4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
@@
 Moreover, we fixed the K-O and Cl-O distances to 2.840~\AA~and 3.140~\AA, respectively, such that they correspond to the distances from other theoretical and experimental works \citep{ge13:13169,gora00:7,Ohtaki93:1157,soper06:180,ma14:1006}.
-%The hexa-coordinated structures are presented in Fig.\ \ref{fg:xas_kcl}.
-%In both cases, they belong D$_3$ point group \citep{rao08:12944,ge13:13169}.
 
@@
 Additionally, we convolved the theoretical spectra with a Voigt profile to also account for the experimental resolution (see Fig.\ \ref{fg:xas_kcl}).
-We analyzed the core excited states by expanding the singly occupied natural orbitals (SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or \cli~ion $\chi_{nl}$
+We analyzed the core excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or \cli~ion $\chi_{nl}$
 %

### 2018-02-19 results.tex
feb 16 (ralph's corrections included)
Ralph's corrections, theoretical figures changed, 1s -> nl replaced by
1s-1 nl

@@
 The upper panel shows two spectra at photon energies 3610.7\,eV, and 3616\,eV below and above the ionization potential at 3611.9\,eV, respectively.
-The bars in the pre-edge cut correspond to the theoretical final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) doublet resonant Auger states of K$^{+}$(H$_2$O)$_6$ (see Sec.\ \ref{sec:methods} for details).
+The vertical bars in the resonant Auger spectrum measured at 3610.7\,eV indicate the energy positions of the theoretical final 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) resonant Auger states of K$^{+}$(H$_2$O)$_6$ of doublet spin multiplicity.
 The features A, B and C are discussed in the text.}
@@
 The upper panel shows two spectra at photon energies 2825.2\,eV, and 2830.0\,eV below and above the ionization potential at 2825.4\,eV, respectively.
-The red bars in the pre-edge cut correspond to the theoretical final 2p$^{-2}$4p doublet resonant Auger states of Cl$^{-}$(H$_2$O)$_6$ (see Sec.\ \ref{sec:methods} for details).}
+The vertical bars in the resonant Auger spectrum at 2825.2\,eV indicate the energy positions of the theoretical 2p$^{-2}$4p states of Cl$^{-}$(H$_2$O)$_6$ of doublet spin multiplicity.}
 \label{fg:2dmap_cl}
@@
 It populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
-The $^3$P final states are expected to have a very low intensity since the corresponding transitions are forbidden from parity conservation rules.
+The $^3$P final states are expected to have a very low intensity since the corresponding transitions are forbidden from angular momentum and parity conservation rules.
 However, these states are not observed in the experimental spectra presented on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} because they overlap with the 2p$^{-2}$($^1$D) and 2p$^{-2}$($^1$D)$V'$ states in the kinetic energy region where they are expected to occur.
@@
 
-The KL$_{2,3}$L$_{2,3}$ Auger lines may disperse with photon energy close to threshold due to energy exchange between the photoelectron and Auger electron called post-collision interaction (PCI).
+The KL$_{2,3}$L$_{2,3}$ normal Auger lines may disperse with photon energy close to threshold due to energy exchange between the photoelectron and Auger electron called post-collision interaction (PCI).
 As a result of this interaction, first, an Auger peak becomes asymmetric with a high kinetic energy shoulder, and second, its intensity maximum is shifted to higher kinetic energies close to threshold \citep{russek86:911,guillemin15:012503}.
-These effects are seen in our spectra -- the asymmetric tail of the peaks resulting from PCI is clearly shown on the cuts taken at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.
+These effects are seen in our spectra -- the asymmetric tail of the peaks resulting from PCI is clearly shown on the resonant Auger spectra at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.
 
 Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
-In the latter case, the maxima of the $^1$D and $^1$S states were found at lower values at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV kinetic energy for K$^{+}_{\text{aq}}$, respectively.
-The lines observed at photon energies far from threshold and close to it appear thus to be shifted by $\sim$1\,eV.
+In the latter case, the maxima of the $^1$D and $^1$S states appear at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV for K$^{+}_{\text{aq}}$, respectively.
+The maxima were found to be shifted by $\sim$1\,eV towards lower kinetic energies as compared to the spectra measured close to threshold.
 The magnitude of the shift is constant in the photon energy range of {\color{red}XX\,eV above threshold.} Moreover, it is the same for both ions suggesting that it does not depend on the initial charge of the ion.
-A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314}, which focuses on the Auger decay of large Kr clusters near the 3d$_{5/2}$ ionization threshold.
-The observed 4d$^{-2}$($^1$D) Auger peak was found to be shifted by 0.7\,eV to higher kinetic energies compared to the position of the peak far above threshold.
+A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314}, which focuses on the Auger decay of large Kr clusters close to the 3d$_{5/2}$ ionization threshold.
+The observed 4p$^{-2}$($^1$S, $^1$D, $^3$P) Auger peaks were found to be shifted by 0.7\,eV to higher kinetic energies compared to the positions of the peaks far above threshold.
 Moreover, the shift did not vary with the photon energy close to threshold.
-{\color{red}Consequently, it was proposed that this feature originates from a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band, and that the observed shift is a result of the PCI-like interaction between the electron excited in the conduction band and the Auger electron.} Further investigations are, however, planned in the case of liquid samples.
+Consequently, it was proposed that these features originate from a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band, followed by normal Auger decay.
+The observed shift was explained as resulting from the PCI-like interaction between the electron excited in the conduction band and the Auger electron.
+Further investigations are, however, planned in the case of liquid samples.
 
@@
 %
-where $V$ and $V'$ denote the unoccupied orbitals in the excited and singly ionized excited states. The character of these states is discussed below.
+where $V$ and $V'$ denote the unoccupied orbitals in the presence of the 1s$^{-1}$ and 2p$^{-2}$ core holes, respectively. The character of these states is discussed below.
 
-The pre-edge regions of the x-ray absorption spectra of \ki~and \cli~shown to the left on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} do not exhibit any high intensity peaks owing to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold.
-Consequently, solely from these absorption spectra, one cannot conclude whether there are core excited states in the pre-edge structure, which can undergo resonant Auger decay.
-However, one can determine their excitation energies from the maxima of the resonant Auger features.
+The pre-edge regions of the x-ray absorption spectra of \ki~and \cli~shown in the left panels of Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} do not exhibit any high intensity peaks owing to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold.
+Consequently, solely from these absorption spectra, one cannot conclude whether there are core excited states in the pre-edge structure.
+Instead these states have to be identified by their resonant Auger features which differ from the normal Auger features of core ionized states.
 Thus, for \cli, the lowest core excited state is located at 2825.2\,eV, which agrees very well with the position of the Cl$^{-}$ 1s$\,\rightarrow\,$4p excitation determined from Cl K-edge XAS experiments in MgCl$_2$.6H$_2$O and of SrCl$_2$/SrCl$_2$.6H$_2$O \citep{sugiura82:681} and MCl$_{4}^{-}$ compounds \citep{shadle95:2259}.
 In the case of \ki, there are two dispersive features with maxima at photon energies of 3611.2\,eV (B) and 3611.6\,eV (C), respectively (Fig.\ \ref{fg:2dmap_k}).
-The positions of these two core excited states are close to the energy of the 1s$\,\rightarrow\,$4p excitation in bare \ki, 3610.7\,eV \citep{hertlein06:062715}.
+The positions of these two core excited states are close to the energy of the 1s$^{-1}$4p excitation in bare \ki~at 3610.7\,eV \citep{hertlein06:062715}.
 
-%Unlike the normal Auger decay, which proceeds in a fairly similar way in the two ions, 
-The resonant Auger features produced in the decay of these core excited states appear to be quite different for \cli~and \ki.
-In the spectrum of \cli~shown in Fig.\ \ref{fg:2dmap_cl} there are two dispersive features, each on the high kinetic energy side of the main $^1$S and $^1$D lines, i.e.\ at 2825.2\,eV photon energy and 2374.6 and 2383.4\,eV kinetic energy.
-In the case of \ki, the $^1$S dispersive line cannot be clearly identified due to the presence of strong background.
-The dispersive feature close to the $^1$D main peak is however well observed (feature B) with a maximum located at $h\nu = $3611.2 \,eV and 2969.2 \,eV kinetic energy.
-An additional feature appears as a separate island away from the main lines on the 2D map of \ki.
-It is located at $h\nu = $3611.6\,eV and 2978.1\,eV kinetic energy (feature C), thus it is separated by approximately 400\,meV photon energy and 8.3\,eV kinetic energy from the feature B.
+The resonant Auger features produced in the decay of these core excited states are quite different for \cli~and \ki.
+In the 2D map of \cli~shown in Fig.\ \ref{fg:2dmap_cl} there are two dispersive features, indicated with diagonal dashed lines, each on the high kinetic energy side of the $^1$S and $^1$D main lines.
+The maxima of these features are at 2825.2\,eV photon energy and 2374.6 and 2383.4\,eV kinetic energy, respectively.
+In the case of \ki (see Fig.\ \ref{fg:2dmap_k}), the dispersive line related to the $^1$S main line cannot be clearly identified due to the presence of strong background.
+Instead two dispersive features related to the $^1$D main line are observed (features B and C indicated with diagonal dashed lines on Fig.\ \ref{fg:2dmap_k}).
+Feature B exhibits a maximum at $h\nu = $3611.2 \,eV and 2969.2 \,eV kinetic energy.
+The additional feature C appears as a separate island away from the main lines on the 2D map of \ki.
+It is located at $h\nu = $3611.6\,eV and 2978.1\,eV kinetic energy, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.
 
@@
 \includegraphics[scale=0.8]{figures/xas_spectra.eps}
-\caption{
-XAS spectra of the lowest K-shell transitions in the bare K$^{+}$ (lower left panel) and Cl$^{-}$ (lower right panel) ions and their 6-coordinated clusters (upper left panel, \ki(H$_2$O)$_6$, and upper right panel, \cli(H$_2$O)$_6$).
-The theoretical stick spectra were convolved with a Lorentzian profile of FWHM 0.74\,eV for \ki~and 0.62\,eV for \cli~(dashed line) and a Voigt profile to account for the lifetime broadening and the experimental resolution (full line).
-The stick spectrum corresponds to the projections $|a_{nl}^{i}|^2$ of the SONOs corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$\,\rightarrow\,$3d, 1s$\,\rightarrow\,$4p, and 1s$\,\rightarrow\,$5p states in the bare K$^+$ and \cli~ions (Eq.\ \ref{eq:sono_proj}).
+\caption{XAS spectra of the lowest K-shell resonant transitions in the bare K$^{+}$ (lower left panel) and Cl$^{-}$ (lower right panel) ions and their 6-coordinated clusters (upper left panel, \ki(H$_2$O)$_6$, and upper right panel, \cli(H$_2$O)$_6$).
+The theoretical stick spectra were convolved with a Lorentzian profile of FWHM 0.74\,eV for \ki~and 0.62\,eV for \cli~(dashed line)\citep{ceolin17:263003} and a Voigt profile to account for the lifetime broadening and the experimental resolution (full line).
+The stick spectrum corresponds to the projections $|a_{nl}^{i}|^2$ of the SONOs corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$^{-1}$3d, 1s$^{-1}$4p, and 1s$^{-1}$5p states in the bare K$^+$ and \cli~ions (Eq.\ \ref{eq:sono_proj}).
 The grey sticks in the stick spectrum correspond to contributions from higher-lying atomic core excitations or from excitations to the solvent molecules.
@@
 The theoretical XAS spectra are presented in Fig.\ \ref{fg:xas_kcl}.
-In the bare ions (lowermost panels on Fig.\ \ref{fg:xas_kcl}), the lowest energy peak corresponds to the dipole allowed 1s$\,\rightarrow\,$4p state.
-The next dipole allowed state, 1s$\,\rightarrow\,$5p, is located 4.3\,eV and 10.8\,eV higher in the cases of \ki~and \cli, respectively.
-Together with the two dipole allowed transitions, we show the dipole forbidden 1s$\,\rightarrow\,$3d states of the bare ions as blue crosses at photon energies 3611.17\,eV in the case of \ki~and 2831.68\,eV in the case of \cli, respectively.
-It is noteworthy that the positions of the 1s$\,\rightarrow\,$4p and 1s$\,\rightarrow\,$3d states are inverted in \ki~and \cli.
-In the case of Cl$^{-}$ the 1s$\,\rightarrow\,$4p excitation has lower energy and the 1s$\,\rightarrow\,$3d excitation is close to the 1s$\,\rightarrow\,$5p state.
-On the contrary, in K$^{+}$ the 1s$\,\rightarrow\,$3d excitation has lower energy and lies below the 1s$\,\rightarrow\,$4p state.
-We note in passing that the intensity of the Cl$^{-}$(1s$\,\rightarrow\,$4p) state is lower than that of the \cli(1s$\,\rightarrow\,$5p) state contrary to what is observed in \ki.
-This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$\,\rightarrow\,$4p compared to the 1s$\,\rightarrow\,$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
+In the bare ions (lowermost panels on Fig.\ \ref{fg:xas_kcl}), the lowest energy peak corresponds to the dipole allowed 1s$^{-1}$4p state.
+The next dipole allowed state, 1s$^{-1}$5p, is located 4.3\,eV and 10.8\,eV higher in the cases of \ki~and \cli, respectively.
+Together with the two dipole allowed transitions, we show the dipole forbidden 1s$^{-1}$3d states of the bare ions as blue crosses at photon energies 3611.17\,eV in the case of \ki~and 2831.68\,eV in the case of \cli, respectively.
+It is noteworthy that the positions of the 1s$^{-1}$4p and 1s$^{-1}$3d states are inverted in \ki~and \cli.
+In the case of Cl$^{-}$ the 1s$^{-1}$4p excitation has lower energy and the 1s$^{-1}$3d excitation is close to the 1s$^{-1}$5p state.
+On the contrary, in K$^{+}$ the 1s$^{-1}$3d excitation has lower energy and lies below the 1s$^{-1}$4p state.
+We note in passing that the intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state contrary to what is observed in \ki.
+This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$^{-1}$4p compared to the 1s$^{-1}$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
 
 The water molecules in the first solvation shell have several effects on the core excited states.
-First, upon addition of water molecules, the degeneracy of the 1s$\,\rightarrow\,$4p state is lifted and the intensity of the resulting states in the cluster drops.
-Moreover, the character of these states changes -- they are no longer of pure atomic character but they rather interact with states of the neighboring water molecules (shown as grey bars in Fig.\ \ref{fg:xas_kcl}) and with other closely lying states of the bare ion, such as the dipole allowed 1s$\,\rightarrow\,$5p and dipole forbidden 1s$\,\rightarrow\,$3d state.
+First, upon addition of water molecules, the degeneracy of the 1s$^{-1}$4p state is lifted and the intensity of the resulting states in the cluster drops.
+Moreover, the character of these states changes as can be seen on the upper panels of Fig.\ \ref{fg:xas_kcl}.
+They are no longer of pure atomic character but they rather interact with states of the neighboring water molecules (shown as grey bars in Fig.\ \ref{fg:xas_kcl}) and with other closely lying states of the bare ion, such as the dipole allowed 1s$^{-1}$5p and dipole forbidden 1s$^{-1}$3d state.
 Thus, the latter also acquire intensity in the cluster due to mixing with the dipole allowed states in the ligand field of the solvent.
@@
 The lowest and highest lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character.
-The low intensity state in between these two states has a predominantly 1s$\,\rightarrow\,$3d character.
-Since the dispersive feature B appears at lower excitation energies compared to the feature C, we assume that it is produced in the resonant Auger decay of the lowest core excited states of \ki, which are predominantly of 1s$\,\rightarrow\,$4p character.
-Moreover, we can attribute the feature C to the resonant Auger decay of the low intensity dipole forbidden 1s$\,\rightarrow\,$3d state.
+The low intensity state in between these two states has a predominantly 1s$^{-1}$3d character.
+Since the dispersive feature B appears at lower excitation energies compared to the feature C, we assume that it is produced in the resonant Auger decay of the lowest core excited states of \ki, which are predominantly of 1s$^{-1}$4p character.
+Moreover, we can attribute the feature C to the resonant Auger decay of the low intensity dipole forbidden 1s$^{-1}$3d state.
 Thus, we explain both the energy splitting of $\sim$400\,meV photon energy of the two features, and the fact that island C has lower intensity than feature B.
 
-In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first peak.
-Since there are no other ionic states close the 1s$\,\rightarrow\,$4p state in the bare ion, this state preserves its character in the cluster and interacts with states of the nearest water molecules.
-We attribute the two dispersive features on the 2D map of \cli~ and associated with the $^{1}$S and $^{1}$D terms, to the resonant Auger decay of these core excited states involving mostly the 4p orbitals of chloride.
+In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first state.
+Due to the large energy separation from other \cli~states it has mainly \cli~1s$^{-1}$4p character with some admixture of states of the nearest water molecules.
+We therefore attribute the two dispersive features associated with the $^1$S and $^1$D main lines on the 2D map of \cli~to the resonant Auger decay of this core excited state involving mostly the 4p orbitals of chloride.
 
 To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ states of the hexa-coordinated clusters corresponding to the lowest final spectator resonant Auger states.
-They are shown as bars in the upper panels on the experimental resonant Auger spectra on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}.
-In both cases, we shifted the lowest 2p$^{-2}$4p states such that they coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.
-Out of all final states we show only the doublets.
+The energy positions of these lines are shown as bars on the experimental resonant Auger spectra in the upper panels of Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}.
+In both cases, we shifted the lowest 2p$^{-2}$($^1$D)4p states such that the kinetic energies coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.
+Note that we only indicate resonant Auger transitions to the spin-allowed final states of doublet multiplicity.
 Since the initial core excited states are populated by photon excitation, only doublet states are efficiently populated in the resonant Auger decay.
-The 2p$^{-2}$nl states of \ki(H$_2$O)$_6$ and \cli(H$_2$O)$_6$ are substantially different and they reflect the fact that the 3d unoccupied orbitals of \ki~are lower than the 4p orbitals, which is the opposite of what is observed in \cli.
+The energetic positions of the 2p$^{-2}$nl states of \ki(H$_2$O)$_6$ and \cli(H$_2$O)$_6$ are substantially different, reflecting the fact that the 3d unoccupied orbitals of \ki~are lower than the 4p orbitals.
+This is the opposite of what is observed in \cli, where the 2p$^{-2}$3d states (not shown) are located on the lower kinetic energy side of the respective 2p$^{-2}$4p states.
 
-As mentioned above, we attribute the island B to the decay of the lowest lying core excited state, which is of predominantly 1s$\,\rightarrow\,$4p character.
-Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$\,\rightarrow\,$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character located between 2969 and 2970.5\,eV are populated.
+As mentioned above, we attribute the island B to the decay of the lowest lying core excited state, which has predominantly 1s$^{-1}$4p character.
+Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$^{-1}$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character are populated resulting in resonant Auger lines located between 2969 and 2970.5\,eV.
 As can be seen from the Auger electron spectrum at $h\nu = 3610.7$\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki(H$_2$O)$_6$ starting at electron energy of 2969\,eV are separated by $\sim$5 and 12-13\,eV from the two groups of 2p$^{-2}$3d states located at higher electron kinetic energies.
 Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV lies closer to the position of island C.
-Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$\,\rightarrow\,$3d state to the group of 2p$^{-2}$3d states lying around 2975\,eV.
+Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$^{-1}$3d excitation to the group of 2p$^{-2}$3d states lying around 2975\,eV.
 The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C.
@@
 The lowest ionization potential of liquid water in the liquid phase is about 11.16\,eV \cite{winter04:2625} which fits well with the observed A-C splitting.
-Based on the above energetic arguments we attribute the island C to the K$^{2+}$ 2p$^{-2}$3d configuration.
+Based on the above energetic arguments we attribute the island C as originating from resonant Auger decay to the K$^{2+}$ 2p$^{-2}$3d final state.
 
-In the Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (see upper panel of Fig.\ \ref{fg:2dmap_cl}).
-The lower kinetic energy group corresponds to the 2p$^{-2}$($^1$S)4p states, whereas the higher kinetic energy group corresponds to the 2p$^{-2}$($^1$D)4p states.
+In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (see upper panel of Fig.\ \ref{fg:2dmap_cl}).
+The lower kinetic energy group corresponds to the 2p$^{-2}$($^1$S)4p final states, whereas the higher kinetic energy group corresponds to the 2p$^{-2}$($^1$D)4p final states.
 The splitting between these two groups is in good agreement with the experimental splitting between the dispersive features on the high kinetic energy sides of the $^1$S and $^1$D main peaks.
-Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$\,\rightarrow\,$4p core excited state of \cli$_{\text{aq}}$ to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.
-Similar dispersive features originating from the decay of the Cl (1s$\,\rightarrow\,$4p) state were observed on the 2D map of chloromethane CH$_3$Cl recorded in the vicinity of the Cl K-edge in gas phase \cite{gold16:133001}.
+Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$^{-1}$4p core excited state of \cli$_{\text{aq}}$ to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.
+Similar dispersive features originating from the decay of the Cl (1s$^{-1}$4p) state were observed on the 2D map of chloromethane CH$_3$Cl recorded in the vicinity of the Cl K-edge in gas phase \cite{gold16:133001}.
 In this case, however, additional lower-lying core excited states are observed.
@@
 
-In the case of \cli, and contrary to \ki, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502}, i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get a partial electron yield as a function of the photon energy.
+In the case of \cli, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502}, i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get a partial electron yield as a function of the photon energy.
 The result is shown on Fig.\ \ref{fg:si_ct_time} in the SI.
@@
 At the specific photon energy corresponding to the lowest core excitation, $h\nu = 2825.2$\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel) a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV .
-The position of the first peak coincides with the main $^1$D line resulting from normal Auger, whereas the second peak at 2383.5\,eV corresponds to the final resonant Auger states 2p$^{-2}$($^1$D)4p.
-By fitting this double-peak structure with two Voigt functions, we determine the ratio of the intensities of these peaks to be $\sim$1.
-Consequently, the delocalization time is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs.
-The fast delocalization in this case is a result of the fact that the energy splitting between the \cli~(1s$\,\rightarrow\,$4p) resonance and the ionization threshold is 0.2\,eV, and thus, smaller than the lifetime broadening of 0.62\,eV.
+The position of the first peak coincides with the $^1$D main line resulting from normal Auger decay, whereas the second peak at 2383.5\,eV corresponds to the resonant Auger decay to the 2p$^{-2}$($^1$D)4p states.
+By fitting this double-peak structure with two Voigt functions, we determine the ratio of the intensities of these peaks to be $l/d \approx 1$.
+From the ratio $l/d$ and the Auger lifetime $\tau_{\text{c}}$, one can determine the delocalization time $\tau_{\text{CT}}$ according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l/d$ \citep{foehlisch05:373}{\color{red}MORE REFS}.
+Consequently, the delocalization time $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs.
+The fast delocalization in this case is a result of the fact that the energy splitting between the \cli~(1s$^{-1}$4p) resonance and the ionization threshold is 0.2\,eV, and thus, smaller than the lifetime broadening of 0.62\,eV \citep{ceolin17:263003}.
 
@@
 However, as can be seen, this is hardly possible especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
-For instance at 3610.7\,eV photon energy on the high-kinetic-energy side of the 2p$^{-2}$($^1$D) state, there are contributions from the PCI tail and from the 2p$^{-2}$($^1$D)4p resonant Auger state.
+For instance at 3610.7\,eV photon energy on the high-kinetic-energy side of the $^1$D main line, there are contributions from the PCI tail and from the 2p$^{-2}$($^1$D)4p resonant Auger state.
 On the low-kinetic-energy side, the charge transfer processes lead to a very large structure whose shape unfortunately cannot be easily simulated by a known profile.

### 2018-02-19 suppinfo.tex
feb 16 (ralph's corrections included)
Ralph's corrections, theoretical figures changed, 1s -> nl replaced by
1s-1 nl

@@
 
-%\begin{figure}
-%\centering
-%\includegraphics[scale=0.3]{figures/fg2_k_6w_okxx_55_rad_dens.eps}
-%\caption{Radial density distributions of the singly-occupied natural orbitals occupied by the excited electron in the core excited states 3609.11\,eV (1\,$^{1}$A$_{2}$), 3609.41\,eV (2\,$^{1}$E) and 3609.64\,eV (3\,$^{1}$E) of K$^{+}$(H$_2$O)$_6$.
-The grey line at 2.816\,\AA~represents the equilibrium K-O distance.}
-%\label{fg:rad_dens}
-%\end{figure}
-
 \begin{figure}[h!]
@@
 \includegraphics[scale=0.8]{figures/rad_dens_kcl.eps}
-\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$\rightarrow$4p, 1s$\rightarrow$3d and 1s$\rightarrow$5p core excitations in \ki~(lower panel) and \cli~(upper panel).
+\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$^{-1}$4p, 1s$^{-1}$3d and 1s$^{-1}$5p core excitations in \ki~(lower panel) and \cli~(upper panel).
 The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
@@
 \end{figure}
+{\color{red}
+In what follows we give a tentative explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli.
+In the case of \ki, the excited electron mainly sees a $2/r$ potential.
+In addition, it sees a short range potential coming from the pointlike nucleus and the screening electrons.
+The latter one normally leads to a quantum defect different from 0.
+Beside this one has Rydberg series with an infinite number of states.
+However, in case of Cl- the outer electron does not see a Coulomb potential and the short-range potential becomes dominant.
+As a result we see the unusual behaviour, like e.g.
+a finite number of bound states (here obviously 4p).
+In contrast to this 3d and 5p are in the continuum.}
 

### 2018-02-21 master.tex
feb 19 (gunnar, andreas, christophe)
Gunnar's, Andreas' and Christophe's corrections

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
+%\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
+\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}
 
@@
 This project has received funding from the Research Executive Agency (REA) under the European Union$'$s Horizon 2020 research and innovation programme Grant agreement No 705515.
-Campus France and the PHC SIAM exchange program are acknowledged for financial support.
+Campus France and the PHC SIAM exchange program are acknowledged for financial support (project No.
+38282QB).
 N.
@@
 \begin{itemize}
-  \item suppinfo.pdf: contains the radial density distributions of the core excited states of the bare ions.
+  \item suppinfo.pdf: contains 1) the radial density distributions of the core excited states of the bare ions; 2) partial cross sections  and charge transfer time extracted from the experimental 2D map near the Cl 1s edge.
 \end{itemize}

### 2018-02-21 methods.tex
feb 19 (gunnar, andreas, christophe)
Gunnar's, Andreas' and Christophe's corrections

@@
 For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a high performance liquid chromatography (HPLC) pump with a constant flux of 1.6\,ml/min.
-The alignment of the setup is performed on the KCl aqueous solution by measuring the water O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio.
+The alignment of the setup is performed on the KCl aqueous solution by measuring the water O1s XPS peak intensity and by optimizing the liquid vs gas phase ratio.
 The pressure in the main chamber is kept below the 10$^{-5}$\,mbar range whereas it is kept at about 10$^{-4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
-Our equipment is an updated version of the equipment used in the reference \cite{faubel88:269}.
+Our equipment is an updated version of the equipment used in Ref.\ \cite{faubel88:269}.
 The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water.

### 2018-02-21 results.tex
feb 19 (gunnar, andreas, christophe)
Gunnar's, Andreas' and Christophe's corrections

@@
 
+{\color{red}Gunnar: Including this discussion will invite questions about the energy calibration, and I’m not sure how this was done in these cases.
+Photoinduced charging may introduce shifts, that can vary with cross section}
+
 Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
@@
 Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder (feature A on Fig.\ \ref{fg:2dmap_k}) on the low kinetic energy side at about 2965\,eV kinetic energy.
-This shoulder is attributed to electron transfer from the solvent water molecules to the 3d orbital of K$^{+}$ \citep{ceolin17:263003}.
+This shoulder is attributed to electron transfer from the solvent water molecules to the unoccupied 3d orbitals of K$^{+}$ \citep{ceolin17:263003}.
 In the case of \cli, there is no experimental evidence of such intense electron transfer processes.
@@
 Moreover, we can attribute the feature C to the resonant Auger decay of the low intensity dipole forbidden 1s$^{-1}$3d state.
-Thus, we explain both the energy splitting of $\sim$400\,meV photon energy of the two features, and the fact that island C has lower intensity than feature B.
+Thus, we explain both the energy splitting of $\sim$400\,meV photon energy of the two features, and the fact that island C has lower intensity than feature B (Fig.\ \ref{fg:2dmap_k}).
 
@@
 As mentioned above, the delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
-In order to estimate the delocalization rate of the core excited electron at the pre-edges of \ki~and \cli, we used the core-hole clock method as in references \cite{bjorneholm92:1892,karis96:1380}.
+In order to estimate the delocalization rate of the core excited electron at the pre-edges of \ki~and \cli, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380}.
 
-In the case of \cli, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502}, i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get a partial electron yield as a function of the photon energy.
+In the case of \cli, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get a partial electron yield as a function of the photon energy.
 The result is shown on Fig.\ \ref{fg:si_ct_time} in the SI.

### 2018-04-23 abstract.tex
apr 23
preparation of jpcl draft started

@@
-X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in a solution.
-In this work we use a combination of these methods to study the electronic structure and decay in aqueous KCl at the K-edges of \ki~and \cli.
-Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features.
-To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of bare \ki, \cli~and their microsolvated clusters.
-Our calculations show that the energy order of the 3d and 4p orbitals is inverted in \ki~with respect to \cli.
-The reverse orbital order in the two ions is reflected in both the ordering of the core excited states and in the final states populated in the resonant Auger decay.
-The energetic proximity of the 3d and 4p virtual states in the bare \ki~ion leads to their mixing in the presence of the solvent, and to the population of the dipole forbidden 1s$^{-1}$3d state upon K-shell excitation in an aqueous solution.
+X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in solution.
+In this work we use a combination of these methods together with {\it ab initio} calculations to study the electronic structure and decay in aqueous KCl at the K-edges of \ki~and \cli.
+Although the two ions are isoelectronic, their Auger electron spectra exhibit notably different features.
+%To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of bare \ki, \cli~and their microsolvated clusters.
+This is due to the fact that the energetic order of the 1s$^{-1}$3d and 1s$^{-1}$4p core excited states is inverted in \ki~with respect to \cli, and moreover the two states lie energetically close in the bare \ki~ion leading to their mixing in the presence of the solvent.
+As a result, the dipole forbidden 1s$^{-1}$3d state is populated upon K-shell excitation of aqueous K$^{+}$.
 The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.

### 2018-04-23 conclusion.tex
apr 23
preparation of jpcl draft started

--- 2018-02-14 conclusion.tex
@@
-\section{Conclusion}\label{sec:concl}
+%\section{Conclusion}\label{sec:concl}
 
-Using a combination of x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, we studied the electronic structure of aqueous solution of KCl at the K-edges of both K and Cl.
+In summary, we studied the electronic structure of aqueous solution of KCl at the K-edges of both K and Cl using a combination of x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, and {\it ab initio} calculations.
+The Auger electron spectra of both ions as a function of photon energy exhibit features of normal as well as resonant Auger processes.
+The latter process proceeds differently for aqueous K$^{+}$ and Cl$^{-}$ due to the population of the dipole forbidden K$^{+}$ 1s$^{-1}$3d state in a solution.
+The spectator Auger decay of this state produces an additional dispersive feature which is manifested as a separate peak in the Auger electron spectrum.
+In the case of \cli~only fingerprints of the population and Auger decay of the dipole allowed 1s$^{-1}$4p excitation are observed in the spectrum.
+
+%Using a combination of x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, we studied the electronic structure of aqueous solution of KCl at the K-edges of both K and Cl.
 The Auger electron spectra of both ions as a function of photon energy exhibit features of normal as well as resonant Auger processes.
 To interpret the resonant Auger features in the experimental spectrum, we performed {\it ab initio} calculations on microsolvated clusters of \ki~and \cli.
-Our calculations show that the energy ordering of the 3d and 4p virtual orbitals of \cli~is inverted compared to \ki, and also that the energy splitting between the bright 1s$\,\rightarrow\,$4p and dark 1s$\,\rightarrow\,$3d core excited states is larger in the chloride case.
-Thus, the energetic proximity of the 3d and 4p orbitals in the bare \ki~ion results in the dipole forbidden 1s$\,\rightarrow\,$3d state acquiring intensity in a solution as a result of mixing with the dipole allowed 1s$\,\rightarrow\,$4p excitation.
+Our calculations show that the energy ordering of the 3d and 4p virtual orbitals of \cli~is inverted compared to \ki, and also that the energy splitting between the bright 1s$^{-1}$4p and dark 1s$^{-1}$3d core excited states is larger in the chloride case.
+Thus, the energetic proximity of the 3d and 4p orbitals in the bare \ki~ion results in the dipole forbidden 1s$^{-1}$3d state acquiring intensity in a solution as a result of mixing with the dipole allowed 1s$^{-1}$4p excitation.
 The spectator Auger decay of this state produces an additional dispersive feature which is manifested as a separate peak in the Auger electron spectrum at high kinetic energies.
-In the case of \cli~the 4p and 3d core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$\,\rightarrow\,$4p state are observed in the spectrum.
+In the case of \cli~the 1s$^{-1}$4p and 1s$^{-1}$3d core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$^{-1}$4p excitation are observed in the spectrum.
 Moreover, using the core-hole clock method we estimated the time of delocalization of the core excited electron at the pre-edge region of \cli$_{\text{aq}}$.
 Our results show that in this case, the resonant Auger decay and the delocalization of the excited electron occur on a comparable timescale.
-In the case of \ki$_{\text{aq}}$, we cannot make an accurate estimate, however, one can expect a much less efficient delocalization of the core excited electron.
+In the case of \ki$_{\text{aq}}$, an accurate estimate is difficult, however, one can expect a much less efficient delocalization of the core excited electron.
 
-Our work shows that the combination of x-ray absorption and resonant Auger spectroscopies is a sensitive probe of the electronic structure of solvated ions.
-The reported results are an important first step in the study of the electronic decay processes following photoabsorption in the tender x-ray regime, and they can have implications in revealing the mechanisms of radiation damage in biologically relevant systems.
+Our work shows that the combination of x-ray absorption and resonant Auger spectroscopy is a sensitive probe of the electronic structure of solvated ions.
+The reported results are an important first step in the study of the chains of relaxation steps triggered by photoabsorption in the tender x-ray regime.
+The Auger processes considered here are inevitably followed by multiple intra- and interatomic electronic decays, such as interatomic Coulombic decay (ICD) and electron-transfer mediated decay (ETMD).
+As a result of the latter processes, genotoxic free radicals and slow electrons are formed in the vicinity of the metal center.
+The magnitude of the damage inflicted upon the environment and the energies of the emitted electrons depend on the initial Auger step, and can therefore be controlled by tuning the energy of the radiation.
+Consequently, the results of this work can have implications in understanding radiation chemistry and radiation damage in biologically relevant systems.

### 2018-04-23 introduction.tex
apr 23
preparation of jpcl draft started

@@
-\section{Introduction}
+%\section{Introduction}
 
-X-ray absorption and Auger electron spectroscopy are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase.
+X-ray absorption (XAS) and Auger electron spectroscopies (AES) are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase.
 Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (see Ref.\ \citep{smith17:13909} and references therein), and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
@@
 
-The course of a decay cascade depends on the character of the initially populated states.
+It has been well understood in atoms and molecules in gas phase that the course of a decay cascade depends on the character of the initially populated states \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}.
+%The course of a decay cascade depends on the character of the initially populated states.
 This has been well understood in atoms and molecules in gas phase  \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}.
@@
 The normal Auger decay process in clusters proceeds similarly to that in atoms or molecules.
-However, in the case of a core excited state, the resonant Auger process competes with the process of delocalization of the excited electron in clusters.
+However, in the case of a core excited state, the resonant Auger process competes with the process of delocalization of the excited electron within the cluster.
 If the initially core excited electron delocalizes within the lifetime of the core hole, then normal instead of resonant Auger decay is observed \citep{Bjorneholm95:3017}.
-
+%
+%
 In a solution, the electronic decay processes initiated by x-ray photoabsorption are different compared to those in rare gas clusters due to the shorter distances and stronger interatomic interactions.
@@
 The O K-edge is located in the soft x-ray range of photon energies, $\sim$533\,eV in water vapor \citep{wagner80:1445}.
-Going higher in photon energy, in the tender and hard x-ray regimes, the lifetimes of the core ionized or core excited states become even shorter, on the order of 1\,fs.
+Going higher in photon energy, to the tender and hard x-ray regimes, the lifetimes of the core ionized or core excited states become even shorter, on the order of 1\,fs.
 And thus, it is even more imperative to reveal whether the delocalization of the core excited electron occurs within the lifetime of the core hole.
@@
 To this end, we used Auger electron spectroscopy together with x-ray absorption spectroscopy in the tender x-ray regime to study aqueous potassium chloride at the K-edges of both \ki~and \cli.
-In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, localized core excited states are populated.
+In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, core excited states are populated.
 These states undergo resonant Auger decay within less than 1\,fs.
 In both ions, there is a competition between resonant Auger decay and delocalization of the excited electron.
-Using the core-hole clock method we show that in \ki~delocalization at the pre-edge is weak, whereas in the case of \cli, due to the energetic proximity of the core excited state to the ionization threshold, the rate of delocalization is of the same order as that of the resonant Auger process.
+Using the core-hole clock method we show that in \ki~delocalization at the pre-edge is slower than the Auger process.
+However, in the case of \cli, the rate of delocalization is of the same order as that of the resonant Auger process due to the energetic proximity of the core excited state to the ionization threshold.
 Moreover, we observe that although the \ki~and \cli~ions are isoelectronic, they have different fingerprints in the resonant Auger spectra.

### 2018-04-23 master.tex
apr 23
preparation of jpcl draft started

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[journal=jacsat,manuscript=article]{achemso}
+\documentclass[journal=jpclcd,manuscript=letter]{achemso}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
-\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}
+\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
+%\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}
 
@@
 We thank Prof.\ Nobuhiro Kosugi and Dr.\ Matja\v{z} \v{Z}itnik for the fruitful discussions.
-Experiments were performed at the GALAXIES beamline, SOLEIL Synchrotron, France (Proposal No.
-20140160).
+Experiments were performed at the GALAXIES beamline, SOLEIL Synchrotron, France (Proposal No.\ 20140160).
 The authors are grateful to the SOLEIL staff for assistance during the beamtime.
-This project has received funding from the Research Executive Agency (REA) under the European Union$'$s Horizon 2020 research and innovation programme Grant agreement No 705515.
-Campus France and the PHC SIAM exchange program are acknowledged for financial support (project No.
-38282QB).
-N.
+This project has received funding from the Research Executive Agency (REA) under the European Union$'$s Horizon 2020 research and innovation programme Grant agreement No.\ 705515.
+Campus France and the PHC SIAM exchange program are acknowledged for financial support (project No.\ 38282QB).
+L.
+S.
+Cederbaum and N.
 V.
-Kryzhevoi and L.
-S.
-Cederbaum acknowledge the financial support of the European Research Council (ERC) (Advanced Investigator Grant No.
-692657) and the Deutsche Forschungsgemeinschaft (DFG research unit 1789).
+Kryzhevoi acknowledge the financial support of the European Research Council (ERC) (Advanced Investigator Grant No.\ 692657) and the Deutsche Forschungsgemeinschaft (DFG research unit 1789).
 

### 2018-04-23 methods.tex
apr 23
preparation of jpcl draft started

@@
-\section{Methods} \label{sec:methods}
-\subsection{Experimental}
+%\section{Methods} \label{sec:methods}
+%\subsection{Experimental}
 
@@
 For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a high performance liquid chromatography (HPLC) pump with a constant flux of 1.6\,ml/min.
-The alignment of the setup is performed on the KCl aqueous solution by measuring the water O1s XPS peak intensity and by optimizing the liquid vs gas phase ratio.
+The alignment of the setup is performed on the KCl aqueous solution by measuring the water O1s x-ray photoelectron peak intensity and by optimizing the liquid vs gas phase ratio.
 The pressure in the main chamber is kept below the 10$^{-5}$\,mbar range whereas it is kept at about 10$^{-4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
@@
 The experimental 2D maps representing the evolution of the KLL Auger spectra in the vicinity of the \cli and \ki~K-edges, as a function of the photon energy, are shown in Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}, respectively.
-The aqueous \ki~and \cli~1s ionization potentials were measured at h$\nu$=5keV and calibrated on the liquid contribution of the O1s XPS spectrum \cite{winter06:1176}.
+The aqueous \ki~and \cli~1s ionization potentials were measured at h$\nu = 5$\,keV and calibrated on the liquid contribution of the O1s XPS spectrum \cite{winter06:1176}.
 The maps were also calibrated using the O1s photoelectron line of liquid water but at photon energies close to the potassium and chloride 1s ionization thresholds.
 
-\subsection{{\bf{\it Ab initio}} calculations}
+%\subsection{{\bf{\it Ab initio}} calculations}
 
@@
 The geometry optimization was performed with the Gaussian 09 package \citep{g09}.
-In order to obtain realistic structures corresponding to the bulk solution, we carried out constrained geometry optimization by choosing the equilibrium gas-phase geometries \citep{lee99:3995,lee02:5509} belonging to the D$_3$ point group and then increasing the angle $\theta$ between the K-O/Cl-O bond and the $C_3$ axis to 55$^{\circ}$ in the case of \ki~and 50$^{\circ}$ in the case of \cli.
-This angle was chosen such that the O-K-O and O-Cl-O angles are around the maxima of the angular distributions obtained from quantum mechanics / molecular mechanics dynamical simulations in Ref.\ \citep{ma14:1006}.
-Moreover, we fixed the K-O and Cl-O distances to 2.840~\AA~and 3.140~\AA, respectively, such that they correspond to the distances from other theoretical and experimental works \citep{ge13:13169,gora00:7,Ohtaki93:1157,soper06:180,ma14:1006}.
+In order to obtain a realistic structure for \ki~corresponding to the bulk solution, we carried out constrained geometry optimization by choosing the equilibrium gas-phase geometries \citep{lee99:3995,lee02:5509} belonging to the D$_3$ point group and then increasing the angle $\theta$ between the K-O bond and the $C_3$ axis to 55$^{\circ}$.
+This angle was chosen such that the O-K-O angles are around the maxima of the angular distributions obtained from quantum mechanics/molecular mechanics simulations in Ref.\ \citep{ma14:1006}.
+Moreover, we fixed the K-O distance to 2.840~\AA, such that it corresponds to the distances from other theoretical and experimental works \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
+%\citep{ge13:13169,gora00:7,Ohtaki93:1157,soper06:180,ma14:1006}.
+%Moreover, we fixed the K-O and Cl-O distances to 2.840~\AA~and 3.140~\AA, respectively, such that they correspond to the distances from other theoretical and experimental works \citep{ge13:13169,gora00:7,Ohtaki93:1157,soper06:180,ma14:1006}.
 
 The energies and transition moments of the core excited states of the bare ions and microsolvated clusters were computed with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}.
-In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding f functions) was used for all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
+In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding f functions) was used on all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
 The use of a smaller basis set in the case of K is due to the higher number of atomic orbitals compared to the case of Cl, and therefore, prohibitively high cost of the CVS-ADC(2)x computation.
@@
 To account for the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of \ki~and \cli, respectively \citep{Krause79:329}.
-Additionally, we convolved the theoretical spectra with a Voigt profile to also account for the experimental resolution (see Fig.\ \ref{fg:xas_kcl}).
-We analyzed the core excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or \cli~ion $\chi_{nl}$
+Additionally, we convolved the theoretical spectra with a Gaussian profile to also account for the experimental resolution (see Fig.\ \ref{fg:xas_kcl}).
+We analyzed the core excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or \cli~ions, $\chi_{nl}$
 %
@@
 The final states following KLL resonant Auger decay of K$^{+}$(H$_2$O)$_6$ and \cli(H$_2$O)$_6$ were computed at the Configuration Interaction Singles (CIS) level using the Graphical Unitary Group Approach (GUGA) as implemented in the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS}.
-In order to account for the relaxation effects upon core ionization, we used a restricted open-shell Hartree-Fock reference wave function with a hole in the 2s orbital of both \ki~and \cli.
+In order to account for the relaxation effects upon core ionization, we employed a restricted open-shell Hartree-Fock reference wave function with a hole in the 2s orbital of both \ki~and \cli.
 We used the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,McLean80:5639,Blaudeau97:5016} on all atoms.

### 2018-04-23 results.tex
apr 23
preparation of jpcl draft started

@@
 
-\begin{figure}%[h]
+\subsection{Normal Auger decay}\label{ssec:na}
+
+The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization of aqueous \ki~and \cli~can be written as follows
+%
+\begin{align*}
+\text{h}\nu + \text{K}^{+}_{\text{aq}} \rightarrow 
+	\text{K}^{2+}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
+	\text{K}^{3+}_{\text{aq}} (2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}\\
+\text{h}\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow
+	\text{Cl}^{0}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
+	\text{Cl}^{+}_{\text{aq}}(2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}
+\end{align*}
+%
+It populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
+The $^3$P final states have a very low intensity since the corresponding transitions are forbidden from angular momentum and parity conservation rules.
+%However, these states are not observed in the experimental spectra presented on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} because they overlap with the 2p$^{-2}$($^1$D) and 2p$^{-2}$($^1$D)$V'$ states in the kinetic energy region where they are expected to occur.
+In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines at photon energy h$\nu = 3616.0$\,eV are located at 2958.0\,eV and 2968.5\,eV kinetic energy, respectively (see Fig.\ \ref{fg:2dmap_k}).
+For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at 2373.1\,eV and 2382.0\,eV kinetic energy for photon energy h$\nu = 2830.0$\,eV (see Fig.\ \ref{fg:2dmap_cl}).
+
+\begin{figure}[h!]
 \centering
@@
 
-\begin{figure}%[h]
+The KL$_{2,3}$L$_{2,3}$ normal Auger lines may disperse with photon energy close to threshold due to energy exchange between the photoelectron and Auger electron called post-collision interaction (PCI).
+As a result of this interaction, first, an Auger peak becomes asymmetric with a high kinetic energy tail, and second, its intensity maximum is shifted to higher kinetic energies close to threshold \citep{russek86:911,guillemin15:012503}.
+These effects are seen in our spectra -- the asymmetric tail of the peaks resulting from PCI is clearly shown on the Auger spectra at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.
+
+\begin{figure}[h!]
 \centering
@@
 
-\subsection{Normal Auger decay}\label{ssec:na}
-
-The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization of aqueous \ki~and \cli~can be written as follows
-%
-\begin{align*}
-h\nu + \text{K}^{+}_{\text{aq}} \rightarrow 
-	\text{K}^{2+}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
-	\text{K}^{3+}_{\text{aq}} (2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}\\
-h\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow
-	\text{Cl}^{0}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
-	\text{Cl}^{+}_{\text{aq}}(2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}
-\end{align*}
-%
-It populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
-The $^3$P final states are expected to have a very low intensity since the corresponding transitions are forbidden from angular momentum and parity conservation rules.
-However, these states are not observed in the experimental spectra presented on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} because they overlap with the 2p$^{-2}$($^1$D) and 2p$^{-2}$($^1$D)$V'$ states in the kinetic energy region where they are expected to occur.
-In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines are located at 2958\,eV and 2968.4\,eV, respectively (see Fig.\ \ref{fg:2dmap_k}).
-For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at 2373.2\,eV and 2382.1\,eV kinetic energy (see Fig.\ \ref{fg:2dmap_cl}).
-{\color{red}Which photon energy?}
-
-The KL$_{2,3}$L$_{2,3}$ normal Auger lines may disperse with photon energy close to threshold due to energy exchange between the photoelectron and Auger electron called post-collision interaction (PCI).
-As a result of this interaction, first, an Auger peak becomes asymmetric with a high kinetic energy shoulder, and second, its intensity maximum is shifted to higher kinetic energies close to threshold \citep{russek86:911,guillemin15:012503}.
-These effects are seen in our spectra -- the asymmetric tail of the peaks resulting from PCI is clearly shown on the resonant Auger spectra at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.
-
-{\color{red}Gunnar: Including this discussion will invite questions about the energy calibration, and I’m not sure how this was done in these cases.
+%{\color{red}Gunnar: Including this discussion will invite questions about the energy calibration, and I’m not sure how this was done in these cases.
 Photoinduced charging may introduce shifts, that can vary with cross section}
 
-Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies $h\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
-In the latter case, the maxima of the $^1$D and $^1$S states appear at 2381.1\,eV and 2372.3\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957\,eV for K$^{+}_{\text{aq}}$, respectively.
+Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies h$\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
+In the latter case, the maxima of the $^1$D and $^1$S states appear at 2381.0\,eV and 2372.0\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957.0\,eV for K$^{+}_{\text{aq}}$, respectively.
 The maxima were found to be shifted by $\sim$1\,eV towards lower kinetic energies as compared to the spectra measured close to threshold.
-The magnitude of the shift is constant in the photon energy range of {\color{red}XX\,eV above threshold.} Moreover, it is the same for both ions suggesting that it does not depend on the initial charge of the ion.
+The magnitude of the shift is constant in the photon energy range of $\sim$8\,eV above threshold (see Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}) and similar for the two ions.
+%Moreover, it is the same for both ions suggesting that it does not depend on the initial charge of the ion.
 A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314}, which focuses on the Auger decay of large Kr clusters close to the 3d$_{5/2}$ ionization threshold.
@@
 \begin{align*}
-h\nu + \text{K}^{+}_{\text{aq}} \rightarrow \text{K}^{+*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{K}^{2+}_{\text{aq}} (2p^{-2}V') + e^{-}_{\text{Auger}}\\
+\text{h}\nu + \text{K}^{+}_{\text{aq}} \rightarrow \text{K}^{+*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{K}^{2+}_{\text{aq}} (2p^{-2}V') + e^{-}_{\text{Auger}}\\
 %
-h\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow \text{Cl}^{-*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{Cl}^{0}_{\text{aq}}(2p^{-2}V') + e^{-}_{\text{Auger}}
+\text{h}\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow \text{Cl}^{-*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{Cl}^{0}_{\text{aq}}(2p^{-2}V') + e^{-}_{\text{Auger}}
 \end{align*}
@@
 Instead these states have to be identified by their resonant Auger features which differ from the normal Auger features of core ionized states.
-Thus, for \cli, the lowest core excited state is located at 2825.2\,eV, which agrees very well with the position of the Cl$^{-}$ 1s$\,\rightarrow\,$4p excitation determined from Cl K-edge XAS experiments in MgCl$_2$.6H$_2$O and of SrCl$_2$/SrCl$_2$.6H$_2$O \citep{sugiura82:681} and MCl$_{4}^{-}$ compounds \citep{shadle95:2259}.
+Thus, for \cli, the lowest core excited state is located at 2825.2\,eV, which agrees very well with the position of the Cl$^{-}$ 1s$\,\rightarrow\,$4p excitation determined from Cl K-edge XAS experiments in hydrated metal dichlorides, MgCl$_2$.6H$_2$O and SrCl$_2$.6H$_2$O \citep{sugiura82:681}, and tetrahedral MCl$_{4}^{-}$ complexes (where M $=$ Cu$^{\text{II}}$, Ni$^{\text{II}}$, Co$^{\text{II}}$, Fe$^{\text{II}}$ and Fe$^{\text{III}}$) \citep{shadle95:2259}.
 In the case of \ki, there are two dispersive features with maxima at photon energies of 3611.2\,eV (B) and 3611.6\,eV (C), respectively (Fig.\ \ref{fg:2dmap_k}).
@@
 Instead two dispersive features related to the $^1$D main line are observed (features B and C indicated with diagonal dashed lines on Fig.\ \ref{fg:2dmap_k}).
-Feature B exhibits a maximum at $h\nu = $3611.2 \,eV and 2969.2 \,eV kinetic energy.
+Feature B exhibits a maximum at h$\nu = 3611.2$\,eV and 2969.2\,eV kinetic energy.
 The additional feature C appears as a separate island away from the main lines on the 2D map of \ki.
-It is located at $h\nu = $3611.6\,eV and 2978.1\,eV kinetic energy, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.
+It is located at h$\nu = 3611.6$\,eV and 2978.1\,eV kinetic energy, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.
 
@@
 \centering
-\includegraphics[scale=0.8]{figures/xas_spectra.eps}
+\includegraphics[scale=0.55]{figures/xas_spectra.eps}
 \caption{XAS spectra of the lowest K-shell resonant transitions in the bare K$^{+}$ (lower left panel) and Cl$^{-}$ (lower right panel) ions and their 6-coordinated clusters (upper left panel, \ki(H$_2$O)$_6$, and upper right panel, \cli(H$_2$O)$_6$).
-The theoretical stick spectra were convolved with a Lorentzian profile of FWHM 0.74\,eV for \ki~and 0.62\,eV for \cli~(dashed line)\citep{ceolin17:263003} and a Voigt profile to account for the lifetime broadening and the experimental resolution (full line).
+The theoretical stick spectra are convolved with a Lorentzian profile of FWHM 0.74\,eV for \ki~and 0.62\,eV for \cli~(dashed line)\citep{ceolin17:263003} and a Voigt profile to account for both the lifetime broadening and the experimental resolution (full line).
 The stick spectrum corresponds to the projections $|a_{nl}^{i}|^2$ of the SONOs corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$^{-1}$3d, 1s$^{-1}$4p, and 1s$^{-1}$5p states in the bare K$^+$ and \cli~ions (Eq.\ \ref{eq:sono_proj}).
@@
 The theoretical XAS spectra are presented in Fig.\ \ref{fg:xas_kcl}.
-In the bare ions (lowermost panels on Fig.\ \ref{fg:xas_kcl}), the lowest energy peak corresponds to the dipole allowed 1s$^{-1}$4p state.
+In the bare ions (lowermost panels of Fig.\ \ref{fg:xas_kcl}), the lowest energy peak corresponds to the dipole allowed 1s$^{-1}$4p state.
 The next dipole allowed state, 1s$^{-1}$5p, is located 4.3\,eV and 10.8\,eV higher in the cases of \ki~and \cli, respectively.
-Together with the two dipole allowed transitions, we show the dipole forbidden 1s$^{-1}$3d states of the bare ions as blue crosses at photon energies 3611.17\,eV in the case of \ki~and 2831.68\,eV in the case of \cli, respectively.
+Together with the two dipole allowed transitions, we show the dipole forbidden 1s$^{-1}$3d states of the bare ions as blue crosses at photon energies 3611.2\,eV in the case of \ki~and 2831.7\,eV in the case of \cli, respectively.
 It is noteworthy that the positions of the 1s$^{-1}$4p and 1s$^{-1}$3d states are inverted in \ki~and \cli.
@@
 In both cases, we shifted the lowest 2p$^{-2}$($^1$D)4p states such that the kinetic energies coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.
-Note that we only indicate resonant Auger transitions to the spin-allowed final states of doublet multiplicity.
+Note that we only indicate resonant Auger transitions to the spin allowed final states of doublet multiplicity.
 Since the initial core excited states are populated by photon excitation, only doublet states are efficiently populated in the resonant Auger decay.
@@
 As mentioned above, we attribute the island B to the decay of the lowest lying core excited state, which has predominantly 1s$^{-1}$4p character.
-Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$^{-1}$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character are populated resulting in resonant Auger lines located between 2969 and 2970.5\,eV.
-As can be seen from the Auger electron spectrum at $h\nu = 3610.7$\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki(H$_2$O)$_6$ starting at electron energy of 2969\,eV are separated by $\sim$5 and 12-13\,eV from the two groups of 2p$^{-2}$3d states located at higher electron kinetic energies.
+Supposing that this state undergoes mostly pure spectator resonant Auger decay, which is the case of the 1s$^{-1}$4p state in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest states of 2p$^{-2}$4p character are populated resulting in resonant Auger lines located between 2969.0 and 2970.5\,eV kinetic energy.
+As can be seen from the Auger electron spectrum at h$\nu = 3610.7$\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki(H$_2$O)$_6$ starting at electron energy of 2969\,eV are separated by $\sim$5 and 12-13\,eV from the two groups of 2p$^{-2}$3d states located at higher electron kinetic energies.
 Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV lies closer to the position of island C.
-Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$^{-1}$3d excitation to the group of 2p$^{-2}$3d states lying around 2975\,eV.
+Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$^{-1}$3d excitation to the group of 2p$^{-2}$3d states.
 The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C.
@@
 
-The energy difference between the spectral features A and C provides another argument in favor of the 2p$^{-2}$ 3d character of the feature C.
+The energy difference between the spectral features A and C provides another argument in favor of the 2p$^{-2}$3d character of the feature C.
 The feature A originates from electron transfer processes from water molecules (W) to the doubly core ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
-The lowest ionization potential of liquid water in the liquid phase is about 11.16\,eV \cite{winter04:2625} which fits well with the observed A-C splitting.
+The lowest ionization potential of liquid water is about 11.16\,eV \cite{winter04:2625} which fits well with the observed A-C splitting.
 Based on the above energetic arguments we attribute the island C as originating from resonant Auger decay to the K$^{2+}$ 2p$^{-2}$3d final state.
@@
 Similar dispersive features originating from the decay of the Cl (1s$^{-1}$4p) state were observed on the 2D map of chloromethane CH$_3$Cl recorded in the vicinity of the Cl K-edge in gas phase \cite{gold16:133001}.
-In this case, however, additional lower-lying core excited states are observed.
+In this case, however, additional lower lying core excited states are observed.
 They result from excitation to the LUMO of CH$_3$Cl, which is a linear combination of the C 2p and Cl 3p atomic orbitals.
@@
 
-\subsection{Delocalization vs resonant Auger decay}
-
-As mentioned above, the delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
-In order to estimate the delocalization rate of the core excited electron at the pre-edges of \ki~and \cli, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380}.
-
-In the case of \cli, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get a partial electron yield as a function of the photon energy.
+%\subsection{Delocalization vs resonant Auger decay}
+%
+%As mentioned above, the delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
+In order to estimate the delocalization rate of the core excited electron at the pre-edges of \ki~and \cli, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+%
+%In the case of \cli, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get the partial electron yield as a function of the photon energy.
 The result is shown on Fig.\ \ref{fg:si_ct_time} in the SI.
 The figure shows that there is a large overlap between the resonant and normal Auger contributions, due to the proximity of the resonance to the ionization potential and due to the very short lifetime of the corresponding states.
-At the specific photon energy corresponding to the lowest core excitation, $h\nu = 2825.2$\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel) a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV .
+At the specific photon energy corresponding to the lowest core excitation, h$\nu = 2825.2$\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel) a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV .
 The position of the first peak coincides with the $^1$D main line resulting from normal Auger decay, whereas the second peak at 2383.5\,eV corresponds to the resonant Auger decay to the 2p$^{-2}$($^1$D)4p states.
 By fitting this double-peak structure with two Voigt functions, we determine the ratio of the intensities of these peaks to be $l/d \approx 1$.
-From the ratio $l/d$ and the Auger lifetime $\tau_{\text{c}}$, one can determine the delocalization time $\tau_{\text{CT}}$ according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l/d$ \citep{foehlisch05:373}{\color{red}MORE REFS}.
+From the ratio $l/d$ and the Auger lifetime $\tau_{\text{c}}$, one can determine the delocalization time $\tau_{\text{CT}}$ according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l/d$ \citep{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
 Consequently, the delocalization time $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs.
 The fast delocalization in this case is a result of the fact that the energy splitting between the \cli~(1s$^{-1}$4p) resonance and the ionization threshold is 0.2\,eV, and thus, smaller than the lifetime broadening of 0.62\,eV \citep{ceolin17:263003}.
-
-For potassium, the treatment is more complex due to the presence of multiple simultaneous processes -- normal, resonant Auger decay, charge transfer from solvent.
+%
+%
+%For potassium, the treatment is more complex due to the presence of multiple simultaneous processes -- normal, resonant Auger decay, charge transfer from solvent.
 To extract the intensity of each component from the 2D map shown in Fig.\ \ref{fg:2dmap_k}, one needs the spectral fingerprints of each process to be separated.
 However, as can be seen, this is hardly possible especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
-For instance at 3610.7\,eV photon energy on the high-kinetic-energy side of the $^1$D main line, there are contributions from the PCI tail and from the 2p$^{-2}$($^1$D)4p resonant Auger state.
-On the low-kinetic-energy side, the charge transfer processes lead to a very large structure whose shape unfortunately cannot be easily simulated by a known profile.
+For instance, at 3610.7\,eV photon energy on the high kinetic energy side of the $^1$D main line, there are contributions from the PCI tail and from the 2p$^{-2}$($^1$D)4p resonant Auger state.
+On the low kinetic energy side, the charge transfer processes lead to a very large structure whose shape unfortunately cannot be easily simulated by a known profile.
 However, the lifetime of the 1s core hole is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and, moreover, the core excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.

### 2018-04-25 abstract.tex
apr 25
jpcl draft

@@
 X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in solution.
+Using these techniques, we study the electronic structure and decay of aqueous KCl at the K-edges of \ki~and \cli.
+Although the two ions are isoelectronic, their Auger electron spectra exhibit notably different features.
+This is due to the energetic proximity of the 1s$^{-1}$3d and 1s$^{-1}$4p core excited states in the bare \ki~ion leading to their mixing in the presence of the solvent.
+As a result, the dipole forbidden 1s$^{-1}$3d state is populated upon K-shell excitation of aqueous K$^{+}$, and its resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.
+The results of this work represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids.
+
+%X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in solution.
 In this work we use a combination of these methods together with {\it ab initio} calculations to study the electronic structure and decay in aqueous KCl at the K-edges of \ki~and \cli.
 Although the two ions are isoelectronic, their Auger electron spectra exhibit notably different features.
-%To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of bare \ki, \cli~and their microsolvated clusters.
+To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of bare \ki, \cli~and their microsolvated clusters.
 This is due to the fact that the energetic order of the 1s$^{-1}$3d and 1s$^{-1}$4p core excited states is inverted in \ki~with respect to \cli, and moreover the two states lie energetically close in the bare \ki~ion leading to their mixing in the presence of the solvent.

### 2018-04-25 introduction.tex
apr 25
jpcl draft

@@
 In particular, the solvent molecules have two effects -- first, they strongly affect the excited \citep{miteva16:16671} or ionized states of the ion and second, they can participate in the decay processes, leading to the population of charge-separated final states, and ionization of the surrounding environment \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,ceolin17:263003,unger17:708}.
-Moreover, the process of delocalization of the initially excited electron also occurs in aqueous solutions \citep{Nordlund07:217406,Ottosson11:13489}.
+Moreover, the process of delocalization of the initially excited electron also occurs in aqueous solutions \citep{Nordlund07:217406,Ottosson11:13489} on a femtosecond to sub-femtosecond time scale.
+
+%.
 In the case of pure water, the delocalization of the O1s excited electron takes place on a femtosecond to sub-femtosecond time scale depending on the photon energy, thus being commensurate with the lifetime of the O1s core hole which is $\sim$3.6\,fs \citep{Nordlund07:217406}.

### 2018-04-25 methods.tex
apr 25
jpcl draft

@@
 For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}.
+{\color{red}CAN WE MAKE THIS SHORTER?
 A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes motorized manipulator in front of the spectrometer lens.
@@
 The pressure in the main chamber is kept below the 10$^{-5}$\,mbar range whereas it is kept at about 10$^{-4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
-Our equipment is an updated version of the equipment used in Ref.\ \cite{faubel88:269}.
-The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water.
+Our equipment is an updated version of the equipment used in Ref.\ \cite{faubel88:269}.} The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water.
 Filtering and degazing procedures were systematically performed before injecting the solution.
@@
 The geometry optimization was performed with the Gaussian 09 package \citep{g09}.
-In order to obtain a realistic structure for \ki~corresponding to the bulk solution, we carried out constrained geometry optimization by choosing the equilibrium gas-phase geometries \citep{lee99:3995,lee02:5509} belonging to the D$_3$ point group and then increasing the angle $\theta$ between the K-O bond and the $C_3$ axis to 55$^{\circ}$.
+In order to obtain a realistic structure for \ki(H$_2$O)$_6$ corresponding to the bulk solution, we carried out constrained geometry optimization by fixing the K-O distance to 2.840~\AA~and increasing the angle $\theta$ between the K-O bond and the $C_3$ axis to 55$^{\circ}$ using the equilibrium gas-phase geometry belonging to the D$_3$ point group as a starting point \citep{lee99:3995,lee02:5509}.
+%  and then increasing the angle $\theta$ between the K-O bond and the $C_3$ axis to 55$^{\circ}$.
 This angle was chosen such that the O-K-O angles are around the maxima of the angular distributions obtained from quantum mechanics/molecular mechanics simulations in Ref.\ \citep{ma14:1006}.
@@
 In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding f functions) was used on all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
-The use of a smaller basis set in the case of K is due to the higher number of atomic orbitals compared to the case of Cl, and therefore, prohibitively high cost of the CVS-ADC(2)x computation.
+%The use of a smaller basis set in the case of K is due to the higher number of atomic orbitals compared to the case of Cl, and therefore, prohibitively high cost of the CVS-ADC(2)x computation.
 In our calculations the core space comprises the 1s orbital of K$^{+}$ or \cli, whereas the remaining occupied orbitals are included in the valence space.
-For the calculations of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and \cli(H$_2$O)$_6$.
-To account for the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of \ki~and \cli, respectively \citep{Krause79:329}.
-Additionally, we convolved the theoretical spectra with a Gaussian profile to also account for the experimental resolution (see Fig.\ \ref{fg:xas_kcl}).
-We analyzed the core excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or \cli~ions, $\chi_{nl}$
-%
-\begin{equation}\label{eq:sono_proj}
-\psi_{i} = \sum_{nl} a^{i}_{nl} \chi_{nl}
-\end{equation}
-%
-where $n$ and $l$ stand for the principal and orbital quantum numbers as described in Ref.\ \citep{miteva16:16671}.
-The expansion coefficients $a^{i}_{nl}$ show the degree of delocalization of the excited electron and the mixing of the core excited states in the ligand field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl}).
+%For the calculations of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and \cli(H$_2$O)$_6$.
+To account for the experimental resolution and the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Gaussian profile and a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of \ki~and \cli, respectively \citep{Krause79:329}.
+In order to understand the mixing of the core excited states in the ligand field created by the surrounding water molecules, we analyzed the core excited states of the hexa-coordinated clusters by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) in the basis of SONOs of the bare K$^{+}$ or \cli~ions, as described in Ref.\ \citep{miteva16:16671}.
 
@@
 Additionally, the basis set was augmented with two sets of s, p, d diffuse functions in the case of \ki, and three sets of s, p, d diffuse functions in the case of \cli.
-The larger basis set employed in the case of Cl was necessary in order to ensure the convergence of the excited states.
+%The larger basis set employed in the case of Cl was necessary in order to ensure the convergence of the excited states.
 The active space comprises the 2s and 2p orbitals of K/Cl with occupancy fixed to 6 and all virtual orbitals with occupancy fixed to 1.

### 2018-04-25 results.tex
apr 25
jpcl draft

@@
-\section{Results and discussion}\label{sec:rnd}
+%\section{Results and discussion}\label{sec:rnd}
 
-\subsection{Normal Auger decay}\label{ssec:na}
+%\subsection{Normal Auger decay}\label{ssec:na}
 
-The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization of aqueous \ki~and \cli~can be written as follows
+The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization of aqueous \ki~and \cli~are shown in Fig.\ \ref{fg:auger} %can be written as follows
 %
-\begin{align*}
-\text{h}\nu + \text{K}^{+}_{\text{aq}} \rightarrow 
-	\text{K}^{2+}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
-	\text{K}^{3+}_{\text{aq}} (2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}\\
-\text{h}\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow
-	\text{Cl}^{0}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
-	\text{Cl}^{+}_{\text{aq}}(2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}
-\end{align*}
+%\begin{align*}
+%\text{h}\nu + \text{K}^{+}_{\text{aq}} \rightarrow 
+%	\text{K}^{2+}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
+%	\text{K}^{3+}_{\text{aq}} (2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}\\
+%\text{h}\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow
+%	\text{Cl}^{0}_{\text{aq}} (1s^{-1}) + e^{-}_{\text{ph}}\rightarrow
+%	\text{Cl}^{+}_{\text{aq}}(2p^{-2}) + e^{-}_{\text{ph}} + e^{-}_{\text{Auger}}
+%\end{align*}
 %
@@
 
-The KL$_{2,3}$L$_{2,3}$ normal Auger lines may disperse with photon energy close to threshold due to energy exchange between the photoelectron and Auger electron called post-collision interaction (PCI).
-As a result of this interaction, first, an Auger peak becomes asymmetric with a high kinetic energy tail, and second, its intensity maximum is shifted to higher kinetic energies close to threshold \citep{russek86:911,guillemin15:012503}.
+The KL$_{2,3}$L$_{2,3}$ normal Auger lines may be shifted to higher kinetic energies and also disperse with photon energy close to threshold due to energy exchange between the photoelectron and Auger electron called post-collision interaction (PCI).
+%As a result of this interaction, first, an Auger peak becomes asymmetric with a high kinetic energy tail, and second, its intensity maximum is shifted to higher kinetic energies close to threshold
+\citep{russek86:911,guillemin15:012503}.
 These effects are seen in our spectra -- the asymmetric tail of the peaks resulting from PCI is clearly shown on the Auger spectra at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli.
@@
 
-Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies h$\nu = 5$\,keV (see Ref.\ \citep{ceolin17:263003} for details).
-In the latter case, the maxima of the $^1$D and $^1$S states appear at 2381.0\,eV and 2372.0\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957.0\,eV for K$^{+}_{\text{aq}}$, respectively.
-The maxima were found to be shifted by $\sim$1\,eV towards lower kinetic energies as compared to the spectra measured close to threshold.
+Further, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies h$\nu = 5$\,keV \citep{ceolin17:263003}.
+%In the latter case, the maxima of the $^1$D and $^1$S states appear at 2381.0\,eV and 2372.0\,eV for Cl$^{-}_{\text{aq}}$, and 2967.4\,eV and 2957.0\,eV for K$^{+}_{\text{aq}}$, respectively.
+The maxima were found to be shifted by $\sim$1\,eV towards lower kinetic energies
+We observe a shift of $\sim$1\,eV of the maxima towards lower kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
 The magnitude of the shift is constant in the photon energy range of $\sim$8\,eV above threshold (see Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}) and similar for the two ions.
 %Moreover, it is the same for both ions suggesting that it does not depend on the initial charge of the ion.
-A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314}, which focuses on the Auger decay of large Kr clusters close to the 3d$_{5/2}$ ionization threshold.
+A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314} where it was proposed that a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band, followed by normal Auger decay.
+The observed shift was explained as resulting from the PCI-like interaction between the electron excited in the conduction band and the Auger electron.
+%, which focuses on the Auger decay of large Kr clusters close to the 3d$_{5/2}$ ionization threshold.
 The observed 4p$^{-2}$($^1$S, $^1$D, $^3$P) Auger peaks were found to be shifted by 0.7\,eV to higher kinetic energies compared to the positions of the peaks far above threshold.
@@
 
-\subsection{Resonant Auger decay} \label{ssec:ra}
+%\subsection{Resonant Auger decay} \label{ssec:ra}
 
@@
 
-The KL$_{2,3}$L$_{2,3}$ Auger decay following resonant K-shell excitation of solvated \ki~and \cli~can be written as follows
-%
-\begin{align*}
-\text{h}\nu + \text{K}^{+}_{\text{aq}} \rightarrow \text{K}^{+*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{K}^{2+}_{\text{aq}} (2p^{-2}V') + e^{-}_{\text{Auger}}\\
-%
-\text{h}\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow \text{Cl}^{-*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{Cl}^{0}_{\text{aq}}(2p^{-2}V') + e^{-}_{\text{Auger}}
-\end{align*}
-%
-where $V$ and $V'$ denote the unoccupied orbitals in the presence of the 1s$^{-1}$ and 2p$^{-2}$ core holes, respectively. The character of these states is discussed below.
+The KL$_{2,3}$L$_{2,3}$ Auger decay following resonant K-shell excitation of solvated \ki~and \cli~is presented on Fig.\ \ref{fg:auger}.
+%can be written as follows
+%%
+%\begin{align*}
+%\text{h}\nu + \text{K}^{+}_{\text{aq}} \rightarrow \text{K}^{+*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{K}^{2+}_{\text{aq}} (2p^{-2}V') + e^{-}_{\text{Auger}}\\
+%%
+%\text{h}\nu + \text{Cl}^{-}_{\text{aq}} \rightarrow \text{Cl}^{-*}_{\text{aq}} (1s^{-1}V) \rightarrow \text{Cl}^{0}_{\text{aq}}(2p^{-2}V') + e^{-}_{\text{Auger}}
+%\end{align*}
+%%
+%where $V$ and $V'$ denote the unoccupied orbitals in the presence of the 1s$^{-1}$ and 2p$^{-2}$ core holes, respectively. The character of these states is discussed below.
 
@@
 On the contrary, in K$^{+}$ the 1s$^{-1}$3d excitation has lower energy and lies below the 1s$^{-1}$4p state.
-We note in passing that the intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state contrary to what is observed in \ki.
+%We note in passing that the intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state contrary to what is observed in \ki.
 This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$^{-1}$4p compared to the 1s$^{-1}$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).

### 2018-04-25 suppinfo - Copy.tex
apr 25
jpcl draft

--- 2018-02-19 suppinfo.tex
@@
 \usepackage{xr}
-\externaldocument{suppinfo}
+\externaldocument{master}
 
@@
 \title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
+%\title{Tracking the hazy boundary between resonant and normal Auger decay in near the K-edges of aqueous \ki~and \cli}
 
@@
 \end{figure}
-{\color{red}
-In what follows we give a tentative explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli.
+
+In what follows we give a simple explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli.
 In the case of \ki, the excited electron mainly sees a $2/r$ potential.
-In addition, it sees a short range potential coming from the pointlike nucleus and the screening electrons.
-The latter one normally leads to a quantum defect different from 0.
-Beside this one has Rydberg series with an infinite number of states.
-However, in case of Cl- the outer electron does not see a Coulomb potential and the short-range potential becomes dominant.
-As a result we see the unusual behaviour, like e.g.
-a finite number of bound states (here obviously 4p).
-In contrast to this 3d and 5p are in the continuum.}
+In addition, it sees a short range potential originating from the point-like nucleus and the screening electrons.
+The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series.
+However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant.
+As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states (here obviously 4p) \citep{buckman94:539}.
+In contrast to this, the 3d and 5p states are not bound.
+% in the continuum.}
 
@@
 The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step.
-From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau l/d$, with $\tau$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$ 4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
+From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau_{c} l/d$, with $\tau_{c}$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
 The green line defines the Cl$^{-}_{\text{aq}}$(1s) ionization potential.}

### 2018-05-16 abstract.tex
may 16
new abstract from Kolya, SI and main text changed, version sent to Ralph

--- 2018-04-23 abstract.tex
@@
-X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in solution.
-In this work we use a combination of these methods together with {\it ab initio} calculations to study the electronic structure and decay in aqueous KCl at the K-edges of \ki~and \cli.
-Although the two ions are isoelectronic, their Auger electron spectra exhibit notably different features.
-%To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of bare \ki, \cli~and their microsolvated clusters.
-This is due to the fact that the energetic order of the 1s$^{-1}$3d and 1s$^{-1}$4p core excited states is inverted in \ki~with respect to \cli, and moreover the two states lie energetically close in the bare \ki~ion leading to their mixing in the presence of the solvent.
-As a result, the dipole forbidden 1s$^{-1}$3d state is populated upon K-shell excitation of aqueous K$^{+}$.
-The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.
-The results of this work represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids and are thus of importance in unveiling the mechanisms of radiation damage in biologically relevant systems.
-%Denis: line 2, I replaced spectroscopies by methods
+X-ray absorption and Auger electron spectroscopies are demonstrated to be powerful tools to unravel the electronic structure of solvated ions.
+In this work for the first time we use a combination of these methods in the tender x-ray regime.
+This allowed us to explore several hitherto unaddressed electronic transitions and to probe environmental effects, specifically in the bulk of the solution.
+In the considered exemplary aqueous KCl solution the solvated isoelectronic \ki~and \cli~ions exhibit notably different Auger electron spectra as a function of the photon energy.
+The differences appear due to dipole forbidden transitions in aqueous \ki~whose occurrence, according to the performed {\it ab initio} calculations, becomes possible only in the presence of solvent water molecules.
+
+%X-ray absorption (XAS) and Auger electron spectroscopies (AES) are powerful tools to probe the electronic structure and immediate surroundings of ions in solution.
+In this work we use a combination of these methods to study the electronic structure and decay of an exemplary aqueous KCl at the K-edges of \ki~and \cli.
+Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features resulting from the excitation and Auger decay of dipole forbidden states in aqueous \ki.
+The results of this work represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids.
+Using tender x-rays we can probe the bulk of the solution, whereas the combination of XAS and resonant Auger spectroscopy allows us to unambiguously disentangle the electronic structure of the solvated ions.
+
+%.
+These features result from the excitation and Auger decay of dipole forbidden states in aqueous \ki, which become dipole allowed due to mixing with the closely lying bright states in the presence of the solvent.
+The results of this work confirm the sensitivity of core level spectroscopies to the electronic structure of solvated species and represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids.

### 2018-05-16 article_text.tex
may 16
new abstract from Kolya, SI and main text changed, version sent to Ralph

X-ray absorption (XAS) and Auger electron spectroscopies (AES) are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase. Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanisms of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}. Upon absorption of an x-ray photon, either core excited or core ionized states of a specific atom are populated depending on the photon energy. The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decays, and it depends on the character of the initially populated states \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}. Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes %such as charge and energy transfer 
are possible  \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003}.

In a solution, the course of such electronic decay cascades initiated by x-ray photoabsorption differs from that in atomic and molecular clusters due to the shorter distances and stronger interatomic interactions.
%In particular, the solvent molecules have two effects -- first, they affect the intensity and character of the excited \citep{miteva16:16671} or ionized states of the ion and second, they can participate in the decay processes, leading to the population of charge-separated final states, and ionization of the surrounding environment \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,ceolin17:263003,unger17:708}. Moreover, a process of internal ionization of the initially excited electron can also occur in aqueous solutions on a femtosecond to sub-femtosecond time scale \citep{Nordlund07:217406,Ottosson11:13489}. {\color{blue}Going to the tender and hard x-ray regimes, the lifetimes of the core ionized or core excited states become shorter compared to the case of water, on the order of 1\,fs. And thus, it is even more imperative to reveal whether the delocalization of the core excited electron occurs within the lifetime of the core hole.}
In this work we used AES together with XAS in the tender x-ray regime to study the electronic decay processes following x-ray absorption of aqueous potassium chloride at the K-edges of both \ki~and \cli. In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, core excited states are populated. These states undergo resonant Auger decay within less than 1\,fs \citep{ceolin17:263003}. Although the \ki~and \cli~ions are isoelectronic, they have different fingerprints in the resonant Auger spectra. We demonstrate that these differences result from different electronic structures of the two ions, thus confirming that the combination of XAS and AES techniques is a sensitive probe of the electronic structure of solutions.

\begin{figure}
\includegraphics[scale=0.8]{figures/auger_process.pdf}
\caption{Schematic representation of the resonant (left) and normal (right) Auger processes of the isoelectronic \ki~and \cli~ions.}
\label{fg:auger}
\end{figure}

The resonant and normal Auger processes which we investigated in this work are schematically shown on Fig.\ \ref{fg:auger}. The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization of aqueous \ki~and \cli~populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states. The $^3$P final states have a very low intensity since the corresponding transitions are forbidden from angular momentum and parity conservation rules. In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines at photon energy h$\nu = 3616.0$\,eV are located at 2958.0\,eV and 2968.5\,eV kinetic energy, respectively (Fig.\ \ref{fg:2dmap_k}(a)). For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at 2373.1\,eV and 2382.0\,eV kinetic energy for a photon energy of 2830.0\,eV (Fig.\ \ref{fg:2dmap_cl}).

\begin{figure}[h!]
\centering
\includegraphics[scale=0.55]{figures/k_2dmap.pdf}
\caption{(a) 2D map showing the kinetic energy of the electrons emitted in KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous K$^{+}$. The features A, B and C are discussed in the text.
(b) Experimental partial electron yield spectrum of K$^{+}$ obtained after integrating over the kinetic energies of the Auger electrons.
(c) Auger spectra at photon energies 3610.7\,eV and 3616\,eV. The vertical bars in the resonant Auger spectrum measured at 3610.7\,eV indicate the energy positions of the calculated doublet 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) states of K$^{+}$(H$_2$O)$_6$.}
\label{fg:2dmap_k}
\end{figure}

The KL$_{2,3}$L$_{2,3}$ normal Auger lines may be shifted to higher kinetic energies and also disperse with photon energy close to threshold due to energy exchange between the photoelectron and Auger electron called post-collision interaction (PCI) \citep{russek86:911,guillemin15:012503}. In our spectra, the PCI effect is manifested as an asymmetric tail of the main peaks at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli, and as a shift of $\sim$1\,eV of the maxima towards lower kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}. An explanation of the shift is given in the SI.

Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder on the low kinetic energy side at about 2965\,eV kinetic energy, feature A (Fig.\ \ref{fg:2dmap_k}). This shoulder is attributed to electron transfer from the solvent water molecules to the unoccupied 3d orbitals of K$^{+}$ \citep{ceolin17:263003}. In the case of \cli, there is no experimental evidence of such intense electron transfer processes.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.55]{figures/cl_2dmap.pdf}
\caption{(a) 2D map showing the kinetic energy of the electrons emitted in KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous Cl$^{-}$. 
(b) Experimental partial electron yield spectrum of Cl$^{-}$ obtained after integrating over the kinetic energies of the Auger electrons. 
(c) Auger spectra at photon energies 2825.2\,eV and 2830.0\,eV. The vertical bars in the resonant Auger spectrum at 2825.2\,eV indicate the energy positions of the calculated doublet 2p$^{-2}$4p states of Cl$^{-}$(H$_2$O)$_6$.}
\label{fg:2dmap_cl}
\end{figure}

The KL$_{2,3}$L$_{2,3}$ Auger decay following resonant K-shell excitation of solvated \ki~and \cli~is schematically presented on Fig.\ \ref{fg:auger}. The pre-edge regions of the XAS spectra of \ki~and \cli~do not exhibit any high intensity peaks owing to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold (Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}). Consequently, solely from these spectra, one cannot conclude whether there are core excited states in the pre-edge structure. Instead these states have to be identified by their resonant Auger features, which differ from the normal Auger features. Thus, for \cli, the lowest core excited state is located at 2825.2\,eV, which is in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments \citep{sugiura82:681,shadle95:2259}. In the case of \ki, there are two dispersive features with maxima at photon energies of 3611.2\,eV (B) and 3611.6\,eV (C). The positions of these two core excited states are close to the energy of the 1s$^{-1}$4p excitation in bare \ki~at 3610.7\,eV \citep{hertlein06:062715}.

The resonant Auger features produced in the decay of these core excited states are quite different for \cli~and \ki. In the 2D map of \cli~shown in Fig.\ \ref{fg:2dmap_cl} there are two dispersive features indicated with diagonal dashed lines. The maxima of these features are at 2825.2\,eV photon energy and 2374.6 and 2383.4\,eV kinetic energy, respectively. In the case of \ki, the dispersive line related to the $^1$S main line cannot be clearly identified due to the presence of strong background. Instead two dispersive features related to the $^1$D main line are observed denoted as B and C on Fig.\ \ref{fg:2dmap_k}. Feature B exhibits a maximum at h$\nu = 3611.2$\,eV and 2969.2\,eV kinetic energy. The additional feature C appears at h$\nu = 3611.6$\,eV and 2978.1\,eV kinetic energy, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.75]{figures/xas_spectra.eps}
\caption{XAS spectra of the lowest K-shell resonant transitions in the bare K$^{+}$ (c) and Cl$^{-}$ (d) ions and their 6-coordinated clusters ((a) and (b)). For comparison with the experiment, the theoretical stick spectra are convolved with a Lorentzian of FWHM  0.74\,eV and 0.62\,eV in the case of \ki~and \cli \citep{Krause79:329} (dashed line)and a Voigt profile (solid line). The stick spectrum corresponds to the projections of the singly-occupied natural orbitals (SONOs) corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$^{-1}$3d, 1s$^{-1}$4p, and 1s$^{-1}$5p states of the bare ions. The remaining contributions from higher-lying atomic core excitations or from excitations to the solvent molecules are depicted as grey sticks. The theoretical XAS spectra of both \ki~and \cli~were shifted to higher photon energies such that the energies of the lowest core excited states correspond to the experimentally determined ones. The experimental ionization thresholds are depicted as grey boxes.}
\label{fg:xas_kcl}
\end{figure}

In order to rationalize the pre-edge region of the experimental XAS spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core excited states of the bare \ki~and \cli~ions and their hexa-coordinated clusters (Fig.\ \ref{fg:xas_kcl}). The lowest bright peak in the XAS spectra of the bare ions corresponds to the dipole allowed 1s$^{-1}$4p state followed by the second bright state, 1s$^{-1}$5p, which is located 4.3\,eV and 10.8\,eV higher in \ki~and \cli, respectively. We also show the dipole forbidden 1s$^{-1}$3d states of the bare ions as blue crosses. It is noteworthy that the positions of the 1s$^{-1}$4p and 1s$^{-1}$3d states are inverted in \ki~and \cli, and moreover, the splitting between these states is about two times smaller in \ki, which as explained later is crucial for understanding the Auger spectra of the two ions. Upon addition of water molecules, the degeneracy of the states is lifted, and moreover, they interact with other states of the ion or the neighboring water molecules (Fig.\ \ref{fg:xas_kcl}(a),(b)). Thus, dipole forbidden states acquire intensity in the cluster. A similar effect was observed in the XAS spectra of microsolvated clusters of Na$^{+}$ and Mg$^{2+}$ \citep{miteva16:16671}. Details on the calculations of the XAS spectra are given in the SI.

Further by comparison of the experimental and theoretical XAS spectra, we assume that only the lowest peak in the theoretical XAS spectra is populated in the experiment. In the 6-coordinated \ki~cluster the lowest peak in the spectrum contains three states. The lowest and highest lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character. The low intensity state lying between these two states has a predominantly 1s$^{-1}$3d character. Since the dispersive feature B appears at low excitation energies, we assume that it is produced in the resonant Auger decay of the lowest core excited states of \ki~of predominantly 1s$^{-1}$4p character. Moreover, we can attribute the feature C to the resonant Auger decay of the low intensity dipole forbidden 1s$^{-1}$3d state. Thus, we explain both the energy splitting of $\sim$400\,meV photon energy of B and C, and the fact that island C has lower intensity than B (Fig.\ \ref{fg:2dmap_k}). In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first state -- it has mainly \cli~1s$^{-1}$4p character with some admixture of states of the nearest water molecules. We therefore attribute the two dispersive features associated with the $^1$S and $^1$D main lines on the 2D map of \cli~to the resonant Auger decay of this core excited state involving mostly the 4p orbitals of chloride.

To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ doublet states corresponding to the lowest final spectator resonant Auger states. The energy positions of these lines are shown as bars in the upper panels of Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}. In both cases, the lowest 2p$^{-2}$($^1$D)4p states were shifted such that their energies coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.

As mentioned above, we attribute the island B on the 2D map of \ki$_{\text{aq}}$ to the decay of the lowest lying core excited state of predominantly 1s$^{-1}$4p character. Supposing that this state undergoes mostly pure spectator resonant Auger decay as in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest 2p$^{-2}$4p states are populated resulting in Auger electrons of between 2969.0 and 2970.5\,eV kinetic energy. As can be seen from the Auger spectrum at h$\nu = 3610.7$\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki(H$_2$O)$_6$ are separated by $\sim$5 and 12-13\,eV from two higher lying groups of 2p$^{-2}$3d states. Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV lies closer to the position of island C. Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$^{-1}$3d excitation to this group of 2p$^{-2}$3d states. The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C. This disagreement can be explained with the fact that we consider a single geometry with a fixed number of water molecules in the first solvation shell, and moreover, we do not theoretically account for the effect of distant solvent shells. Concerning the 2p$^{-2}$3d states at kinetic energies between 2982 and 2983\,eV, we conclude that they are not populated via the Auger process since no additional experimental features are observed.

Another argument in favor of the 2p$^{-2}$3d character of the feature C is the energy difference between the spectral features A and C. Feature A originates from electron transfer processes from water molecules (W) to the doubly core ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$. The lowest ionization potential of liquid water is about 11.16\,eV \cite{winter04:2625} which fits well with the observed A-C splitting. Thus, the above energetic arguments corroborate the attribution of island C as originating from resonant Auger decay to the K$^{2+}$ 2p$^{-2}$3d final states.

In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (upper panel of Fig.\ \ref{fg:2dmap_cl}). The lower kinetic energy group corresponds to the 2p$^{-2}$($^1$S)4p final states, whereas the higher kinetic energy group corresponds to the 2p$^{-2}$($^1$D)4p final states. The splitting between these two groups is in good agreement with the experimental splitting between the dispersive features on the high kinetic energy sides of the $^1$S and $^1$D main peaks. Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$^{-1}$4p core excited state of \cli$_{\text{aq}}$ to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.

In summary, we studied the electronic structure of aqueous solution of KCl at the K-edges of both \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$ using a combination of x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, and {\it ab initio} calculations. The Auger electron spectra of both ions exhibit features of both normal and resonant Auger processes. The latter process proceeds differently for aqueous K$^{+}$ and Cl$^{-}$ due to the population of the dipole forbidden K$^{+}$ 1s$^{-1}$3d state in a solution. The spectator Auger decay of this state produces an additional dispersive feature which is manifested as a separate peak in the Auger electron spectrum. In the case of \cli~only fingerprints of the population and Auger decay of the dipole allowed 1s$^{-1}$4p excitation are observed. These results are an important first step in the study of the chains of relaxation steps triggered by x-ray photoabsorption in liquids. The Auger processes considered here are inevitably followed by multiple intra- and interatomic electronic decays, such as interatomic Coulombic decay (ICD) and electron-transfer mediated decay (ETMD) \citep{unger17:708,Stumpf16:237}. As a result of the latter processes, genotoxic free radicals and slow electrons are formed in the vicinity of the metal center. The magnitude of the damage inflicted upon the environment and the energies of the emitted electrons depend on the initial Auger step, and can therefore be controlled by tuning the energy of the radiation. Consequently, the results of this work can have implications in understanding radiation chemistry and radiation damage in biologically relevant systems in which metallic centers are ubiquitous.

### 2018-05-16 jacs_version/abstract.tex
may 16
new abstract from Kolya, SI and main text changed, version sent to Ralph

X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in solution. In this work we use a combination of these methods to study the electronic structure and decay in aqueous KCl at the K-edges of \ki~and \cli. Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features. To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of bare \ki, \cli~and their microsolvated clusters. Our calculations show that the energetic order of the 3d and 4p orbitals is inverted in \ki~with respect to \cli. The reverse orbital order in the two ions is reflected in both the ordering of the core excited states and in the final states populated in the resonant Auger decay. The energetic proximity of the 3d and 4p virtual orbitals in the bare \ki~ion leads to their mixing in the presence of the solvent, and to the population of the dipole forbidden 1s$^{-1}$3d state upon K-shell excitation in aqueous solution. The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli. The results of this work represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids and are thus of importance in unveiling the mechanisms of radiation damage in biologically relevant systems.
%Denis: line 2, I replaced spectroscopies by methods

### 2018-05-16 jacs_version/conclusion.tex
may 16
new abstract from Kolya, SI and main text changed, version sent to Ralph

\section{Conclusion}\label{sec:concl}

Using a combination of x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, we studied the electronic structure of aqueous solution of KCl at the K-edges of both K and Cl. The Auger electron spectra of both ions as a function of photon energy exhibit features of normal as well as resonant Auger processes. To interpret the resonant Auger features in the experimental spectrum, we performed {\it ab initio} calculations on microsolvated clusters of \ki~and \cli. Our calculations show that the energy ordering of the 3d and 4p virtual orbitals of \cli~is inverted compared to \ki, and also that the energy splitting between the bright 1s$^{-1}$4p and dark 1s$^{-1}$3d core excited states is larger in the chloride case. Thus, the energetic proximity of the 3d and 4p orbitals in the bare \ki~ion results in the dipole forbidden 1s$^{-1}$3d state acquiring intensity in a solution as a result of mixing with the dipole allowed 1s$^{-1}$4p excitation. The spectator Auger decay of this state produces an additional dispersive feature which is manifested as a separate peak in the Auger electron spectrum at high kinetic energies. In the case of \cli~the 1s$^{-1}$4p and 1s$^{-1}$3d core excited states do not interact, and therefore, only fingerprints of the population and Auger decay of the dipole allowed 1s$^{-1}$4p excitation are observed in the spectrum. Moreover, using the core-hole clock method we estimated the time of delocalization of the core excited electron at the pre-edge region of \cli$_{\text{aq}}$. Our results show that in this case, the resonant Auger decay and the delocalization of the excited electron occur on a comparable timescale. In the case of \ki$_{\text{aq}}$, we cannot make an accurate estimate, however, one can expect a much less efficient delocalization of the core excited electron.

Our work shows that the combination of x-ray absorption and resonant Auger spectroscopy is a sensitive probe of the electronic structure of solvated ions. The reported results are an important first step in the study of the chains of relaxation steps triggered by photoabsorption in the tender x-ray regime. The Auger processes considered in this work are inevitably followed by multiple intra- and interatomic electronic decays, such as interatomic Coulombic decay (ICD) and electron-transfer mediated decay (ETMD). As a result of the latter processes, genotoxic free radicals and slow electrons are formed in the vicinity of the metal center. The magnitude of the damage inflicted upon the environment and the energies of the emitted electrons depend on the initial Auger step, and can therefore be controlled by tuning the energy of the radiation. Consequently, the results of this work can have implications in understanding radiation chemistry and radiation damage in biologically relevant systems.

### 2018-05-16 methods.tex
may 16
new abstract from Kolya, SI and main text changed, version sent to Ralph

--- 2018-02-21 methods.tex
@@
 For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}.
-A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes motorized manipulator in front of the spectrometer lens.
-Two holes of 2\,mm diameter allow the photons to go in and out.
-At the end of the tube and in front of the lens, a 500\,$\mu$m diameter hole skimmer allows the electrons created at the interaction point to go in the direction of the spectrometer.
-The microjet head is mostly composed of a 30\,$\mu$m diameter vertical glass capillary facing a temperature-controlled catcher in CuBe having a 300\,$\mu$m hole, and a camera.
-Piezo motors allow their precise alignment relative to each other and to the photon beam.
-The catcher is placed at a distance of about 5\,mm from the capillary and is permanently pumped in order to extract the liquid.
-For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a high performance liquid chromatography (HPLC) pump with a constant flux of 1.6\,ml/min.
-The alignment of the setup is performed on the KCl aqueous solution by measuring the water O1s XPS peak intensity and by optimizing the liquid vs gas phase ratio.
-The pressure in the main chamber is kept below the 10$^{-5}$\,mbar range whereas it is kept at about 10$^{-4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
-Our equipment is an updated version of the equipment used in Ref.\ \cite{faubel88:269}.
 The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water.
@@
 
-The theoretical X-ray absorption spectra were computed for the hexa-coordinated clusters of both ions, \ki(H$_2$O)$_6$ and \cli(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
+The theoretical X-ray absorption spectra were computed for the hexa-coordinated clusters of both ions, \ki(H$_2$O)$_6$ and \cli(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
 The two structures shown in Fig.\ \ref{fg:xas_kcl} were optimized at the DFT level of theory using the B3LYP functional and the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,Blaudeau97:5016}.
 The geometry optimization was performed with the Gaussian 09 package \citep{g09}.
-In order to obtain realistic structures corresponding to the bulk solution, we carried out constrained geometry optimization by choosing the equilibrium gas-phase geometries \citep{lee99:3995,lee02:5509} belonging to the D$_3$ point group and then increasing the angle $\theta$ between the K-O/Cl-O bond and the $C_3$ axis to 55$^{\circ}$ in the case of \ki~and 50$^{\circ}$ in the case of \cli.
-This angle was chosen such that the O-K-O and O-Cl-O angles are around the maxima of the angular distributions obtained from quantum mechanics / molecular mechanics dynamical simulations in Ref.\ \citep{ma14:1006}.
-Moreover, we fixed the K-O and Cl-O distances to 2.840~\AA~and 3.140~\AA, respectively, such that they correspond to the distances from other theoretical and experimental works \citep{ge13:13169,gora00:7,Ohtaki93:1157,soper06:180,ma14:1006}.
 
-The energies and transition moments of the core excited states of the bare ions and microsolvated clusters were computed with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}.
+The energies and transition moments of the core excited states of the bare ions and microsolvated clusters were computed with the Algebraic Diagrammatic Construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}.
 In the case of \cli~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding f functions) was used for all atoms, whereas in the case of \ki~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
-The use of a smaller basis set in the case of K is due to the higher number of atomic orbitals compared to the case of Cl, and therefore, prohibitively high cost of the CVS-ADC(2)x computation.
 In our calculations the core space comprises the 1s orbital of K$^{+}$ or \cli, whereas the remaining occupied orbitals are included in the valence space.
-For the calculations of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and \cli(H$_2$O)$_6$.
-To account for the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of \ki~and \cli, respectively \citep{Krause79:329}.
-Additionally, we convolved the theoretical spectra with a Voigt profile to also account for the experimental resolution (see Fig.\ \ref{fg:xas_kcl}).
-We analyzed the core excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or \cli~ion $\chi_{nl}$
-%
-\begin{equation}\label{eq:sono_proj}
-\psi_{i} = \sum_{nl} a^{i}_{nl} \chi_{nl}
-\end{equation}
-%
-where $n$ and $l$ stand for the principal and orbital quantum numbers as described in Ref.\ \citep{miteva16:16671}.
-The expansion coefficients $a^{i}_{nl}$ show the degree of delocalization of the excited electron and the mixing of the core excited states in the ligand field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl}).
+We analyzed the core excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) of the microsolvated clusters in the basis of SONOs of the bare ions as in \citep{miteva16:16671}.
 
@@
 In order to account for the relaxation effects upon core ionization, we used a restricted open-shell Hartree-Fock reference wave function with a hole in the 2s orbital of both \ki~and \cli.
-We used the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,McLean80:5639,Blaudeau97:5016} on all atoms.
-Additionally, the basis set was augmented with two sets of s, p, d diffuse functions in the case of \ki, and three sets of s, p, d diffuse functions in the case of \cli.
-The larger basis set employed in the case of Cl was necessary in order to ensure the convergence of the excited states.
+We used the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,McLean80:5639,Blaudeau97:5016} on all atoms augmented with two sets of s, p, d diffuse functions in the case of \ki, and three sets of s, p, d diffuse functions in the case of \cli.
 The active space comprises the 2s and 2p orbitals of K/Cl with occupancy fixed to 6 and all virtual orbitals with occupancy fixed to 1.

### 2018-05-16 suppinfo.tex
may 16
new abstract from Kolya, SI and main text changed, version sent to Ralph

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
+\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous solution using tender x-rays}
+%\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}
 
@@
 \abbreviations{AES,XAS}
-\keywords{Solvated ions, Auger spectroscopy, X-ray absorption spectroscopy}
-
+\keywords{Solvated ions, Auger electron spectroscopy, x-ray absorption spectroscopy}
+\renewcommand{\figurename}{Figure SI}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\section{Methods}
+\subsection{Experimental}
+
+For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}.
+A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes motorized manipulator in front of the spectrometer lens.
+Two holes of 2\,mm diameter allow the photons to go in and out.
+At the end of the tube and in front of the lens, a 500\,$\mu$m diameter hole skimmer allows the electrons created at the interaction point to go in the direction of the spectrometer.
+The microjet head is mostly composed of a 30\,$\mu$m diameter vertical glass capillary facing a temperature-controlled catcher in CuBe having a 300\,$\mu$m hole, and a camera.
+Piezo motors allow their precise alignment relative to each other and to the photon beam.
+The catcher is placed at a distance of about 5\,mm from the capillary and is permanently pumped in order to extract the liquid.
+For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a high performance liquid chromatography (HPLC) pump with a constant flux of 1.6\,ml/min.
+The alignment of the setup is performed on the KCl aqueous solution by measuring the water O1s x-ray photoelectron peak intensity and by optimizing the liquid vs gas phase ratio.
+The pressure in the main chamber is kept below the 10$^{-5}$\,mbar range whereas it is kept at about 10$^{-4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON.
+Our equipment is an updated version of the equipment used in Ref.\ \cite{faubel88:269}.
+The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water.
+Filtering and degazing procedures were systematically performed before injecting the solution.
+The spectrometer resolution of about 0.6\,eV was achieved with the 500\,eV pass energy and 0.5\,mm slits.
+The photon energy resolution achieved at 2.8\,keV and 3.6\,keV was about 0.3\,eV and 0.4\,eV, respectively.
+The experimental 2D maps representing the evolution of the KLL Auger spectra in the vicinity of the Cl$^{-}$ and K$^{+}$~K-edges, as a function of the photon energy, are shown in Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} in the main text, respectively.
+The aqueous K$^{+}$~and Cl$^{-}$~1s ionization potentials were measured at h$\nu = 5$\,keV and calibrated on the liquid contribution of the O1s XPS spectrum \cite{winter06:1176}.
+The maps were also calibrated using the O1s photoelectron line of liquid water but at photon energies close to the potassium and chloride 1s ionization thresholds.
+
+\subsection{{\bf{\it Ab initio}} calculations}
+
+The theoretical X-ray absorption spectra were computed for the hexa-coordinated clusters of both ions, K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
+The two structures shown in Fig.\ \ref{fg:xas_kcl} were optimized at the DFT level of theory using the B3LYP functional and the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,Blaudeau97:5016}.
+The geometry optimization was performed with the Gaussian 09 package \citep{g09}.
+In order to obtain a realistic structure for K$^{+}$~corresponding to the bulk solution, we carried out constrained geometry optimization by choosing the equilibrium gas-phase geometries \citep{lee99:3995,lee02:5509} belonging to the D$_3$ point group and then increasing the angle $\theta$ between the K-O bond and the $C_3$ axis to 55$^{\circ}$.
+This angle was chosen such that the O-K-O angles are around the maxima of the angular distributions obtained from quantum mechanics/molecular mechanics simulations in Ref.\ \citep{ma14:1006}.
+Moreover, we fixed the K-O distance to 2.840~\AA, such that it corresponds to the distances from other theoretical and experimental works \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
+
+The energies and transition moments of the core excited states of the bare ions and microsolvated clusters were computed with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}.
+In the case of Cl$^{-}$~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding f functions) was used on all atoms, whereas in the case of K$^{+}$~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
+The use of a smaller basis set in the case of K is due to the higher number of atomic orbitals compared to the case of Cl, and therefore, prohibitively high cost of the CVS-ADC(2)x computation.
+In our calculations the core space comprises the 1s orbital of K$^{+}$ or Cl$^{-}$, whereas the remaining occupied orbitals are included in the valence space.
+For the calculations of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$.
+To account for the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of K$^{+}$~and Cl$^{-}$, respectively \citep{Krause79:329}.
+Additionally, we convolved the theoretical spectra with a Gaussian profile to also account for the experimental resolution (see Fig.\ \ref{fg:xas_kcl} in the main text).
+We analyzed the core excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or Cl$^{-}$~ions, $\chi_{nl}$
+%
+\begin{equation}
+\psi_{i} = \sum_{nl} a^{i}_{nl} \chi_{nl}
+\end{equation}
+%
+where $n$ and $l$ stand for the principal and orbital quantum numbers as described in Ref.\ \citep{miteva16:16671}.
+The expansion coefficients $a^{i}_{nl}$ show the degree of delocalization of the excited electron and the mixing of the core excited states in the ligand field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl}).
+
+The final states following KLL resonant Auger decay of K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$ were computed at the Configuration Interaction Singles (CIS) level using the Graphical Unitary Group Approach (GUGA) as implemented in the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS}.
+In order to account for the relaxation effects upon core ionization, we employed a restricted open-shell Hartree-Fock reference wave function with a hole in the 2s orbital of both K$^{+}$~and Cl$^{-}$.
+We used the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,McLean80:5639,Blaudeau97:5016} on all atoms.
+Additionally, the basis set was augmented with two sets of s, p, d diffuse functions in the case of K$^{+}$, and three sets of s, p, d diffuse functions in the case of Cl$^{-}$.
+The larger basis set employed in the case of Cl was necessary in order to ensure the convergence of the excited states.
+The active space comprises the 2s and 2p orbitals of K/Cl with occupancy fixed to 6 and all virtual orbitals with occupancy fixed to 1.
+The remaining doubly occupied orbitals were frozen in the calculation.
+\citep{mosnier16:061401}
+
+\section{PCI shift}
+In order to estimate the maximum amplitude of the PCI shift, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies h$\nu = 5$\,keV \citep{ceolin17:263003}.
+We observe a shift of $\sim$1\,eV of the maxima towards lower kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
+The magnitude of the shift is constant in the photon energy range of $\sim$8\,eV above threshold and similar for the two ions.
+A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314} where it was proposed that it is due to a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band, followed by normal Auger decay.
+The observed shift was explained as resulting from the PCI-like interaction between the Auger electron and the electron excited to the conduction band.
+
+\section{Core-excited states of Cl$^{-}$}
 \begin{figure}[h!]
@@
 \end{figure}
-{\color{red}
-In what follows we give a tentative explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli.
+%
+%
+The intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state contrary to what is observed in \ki.
+This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$^{-1}$4p compared to the 1s$^{-1}$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
+In what follows we give a simple explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli.
 In the case of \ki, the excited electron mainly sees a $2/r$ potential.
-In addition, it sees a short range potential coming from the pointlike nucleus and the screening electrons.
-The latter one normally leads to a quantum defect different from 0.
-Beside this one has Rydberg series with an infinite number of states.
-However, in case of Cl- the outer electron does not see a Coulomb potential and the short-range potential becomes dominant.
-As a result we see the unusual behaviour, like e.g.
-a finite number of bound states (here obviously 4p).
-In contrast to this 3d and 5p are in the continuum.}
+In addition, it sees a short range potential originating from the point-like nucleus and the screening electrons.
+The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series.
+However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant.
+As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states (here obviously 4p) \citep{buckman94:539}.
+In contrast to this, the 3d and 5p states are not bound.
+% in the continuum.}
 
-\begin{figure}
-\centering
-\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
-\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}.
+%\section{Delocalization vs resonant Auger decay}
+%
+%The delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
+In order to estimate the delocalization rate of the core excited electron at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+%
+%In the case of Cl$^{-}$, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get the partial electron yield as a function of the photon energy.
+The result is shown on Fig.\ \ref{fg:si_ct_time} in the SI.
+The figure shows that there is a large overlap between the resonant and normal Auger contributions, due to the proximity of the resonance to the ionization potential and due to the very short lifetime of the corresponding states.
+At the specific photon energy corresponding to the lowest core excitation, h$\nu = 2825.2$\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel) a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV .
+The position of the first peak coincides with the $^1$D main line resulting from normal Auger decay, whereas the second peak at 2383.5\,eV corresponds to the resonant Auger decay to the 2p$^{-2}$($^1$D)4p states.
+By fitting this double-peak structure with two Voigt functions, we determine the ratio of the intensities of these peaks to be $l/d \approx 1$.
+From the ratio $l/d$ and the Auger lifetime $\tau_{\text{c}}$, one can determine the delocalization time $\tau_{\text{CT}}$ according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l/d$ \citep{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+Consequently, the delocalization time $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs.
+The fast delocalization in this case is a result of the fact that the energy splitting between the Cl$^{-}$~(1s$^{-1}$4p) resonance and the ionization threshold is 0.2\,eV, and thus, smaller than the lifetime broadening of 0.62\,eV \citep{ceolin17:263003}.
+%
+%
+%For potassium, the treatment is more complex due to the presence of multiple simultaneous processes -- normal, resonant Auger decay, charge transfer from solvent.
+To extract the intensity of each component from the 2D map shown in Fig.\ \ref{fg:2dmap_k}, one needs the spectral fingerprints of each process to be separated.
+However, as can be seen, this is hardly possible especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
+For instance, at 3610.7\,eV photon energy on the high kinetic energy side of the $^1$D main line, there are contributions from the PCI tail and from the 2p$^{-2}$($^1$D)4p resonant Auger state.
+On the low kinetic energy side, the charge transfer processes lead to a very large structure whose shape unfortunately cannot be easily simulated by a known profile.
+However, the lifetime of the 1s core hole is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and, moreover, the core excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
+Therefore, one can expect much less efficient delocalization compared to Cl$^{-}_{\text{aq}}$.
+%
+%
+%
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
+%\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}.
 The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step.
-From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau l/d$, with $\tau$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$ 4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
+From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau_{c} l/d$, with $\tau_{c}$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
 The green line defines the Cl$^{-}_{\text{aq}}$(1s) ionization potential.}
-\label{fg:si_ct_time}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\label{fg:si_ct_time}
+%\end{figure}
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% The appropriate \bibliography command should be placed here.
+%%% Notice that the class file automatically sets \bibliographystyle
+%%% and also names the section correctly.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliography{F:/Articles/bibliography/Bibliography}

### 2018-06-05 abstract.tex
june 5
Ralph's corrections included

@@
 In this work for the first time we use a combination of these methods in the tender x-ray regime.
-This allowed us to explore several hitherto unaddressed electronic transitions and to probe environmental effects, specifically in the bulk of the solution.
+%This allowed us to explore several hitherto unaddressed electronic transitions and to probe environmental effects, specifically in the bulk of the solution.
+{\color{red}
+This allowed us to address electronic transitions including deep core levels and to probe environmental effects, specifically in the bulk of solutions since the Auger electrons created by deep core levels possess large mean free paths.
 In the considered exemplary aqueous KCl solution the solvated isoelectronic \ki~and \cli~ions exhibit notably different Auger electron spectra as a function of the photon energy.
 The differences appear due to dipole forbidden transitions in aqueous \ki~whose occurrence, according to the performed {\it ab initio} calculations, becomes possible only in the presence of solvent water molecules.
-
-%X-ray absorption (XAS) and Auger electron spectroscopies (AES) are powerful tools to probe the electronic structure and immediate surroundings of ions in solution.
-In this work we use a combination of these methods to study the electronic structure and decay of an exemplary aqueous KCl at the K-edges of \ki~and \cli.
-Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features resulting from the excitation and Auger decay of dipole forbidden states in aqueous \ki.
-The results of this work represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids.
-Using tender x-rays we can probe the bulk of the solution, whereas the combination of XAS and resonant Auger spectroscopy allows us to unambiguously disentangle the electronic structure of the solvated ions.
-
-%.
-These features result from the excitation and Auger decay of dipole forbidden states in aqueous \ki, which become dipole allowed due to mixing with the closely lying bright states in the presence of the solvent.
-The results of this work confirm the sensitivity of core level spectroscopies to the electronic structure of solvated species and represent a pioneering study of the decay processes initiated by photoabsorption in the tender x-ray regime close to threshold in liquids.

### 2018-06-05 article_text.tex
june 5
Ralph's corrections included

@@
-X-ray absorption (XAS) and Auger electron spectroscopies (AES) are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase.
 Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanisms of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
-Upon absorption of an x-ray photon, either core excited or core ionized states of a specific atom are populated depending on the photon energy.
+Depending on the photon energy, the absorption of an x-ray photon results in the population of core excited or core ionized states.
 The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decays, and it depends on the character of the initially populated states \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}.
-Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes %such as charge and energy transfer
-are possible  \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003}.
+Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes are possible  \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003}.
 
-In a solution, the course of such electronic decay cascades initiated by x-ray photoabsorption differs from that in atomic and molecular clusters due to the shorter distances and stronger interatomic interactions.
-%In particular, the solvent molecules have two effects -- first, they affect the intensity and character of the excited \citep{miteva16:16671} or ionized states of the ion and second, they can participate in the decay processes, leading to the population of charge-separated final states, and ionization of the surrounding environment \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,ceolin17:263003,unger17:708}.
-Moreover, a process of internal ionization of the initially excited electron can also occur in aqueous solutions on a femtosecond to sub-femtosecond time scale \citep{Nordlund07:217406,Ottosson11:13489}.
-{\color{blue}Going to the tender and hard x-ray regimes, the lifetimes of the core ionized or core excited states become shorter compared to the case of water, on the order of 1\,fs.
-And thus, it is even more imperative to reveal whether the delocalization of the core excited electron occurs within the lifetime of the core hole.}
-In this work we used AES together with XAS in the tender x-ray regime to study the electronic decay processes following x-ray absorption of aqueous potassium chloride at the K-edges of both \ki~and \cli.
+X-ray absorption spectroscopy (XAS) is a powerful tool to study the nearest environment of atoms in gas phase as it probes core excited states below threshold which are highly sensitive to the surrounding.
+However, for atoms and molecules in liquid or solid phase, these core excited states overlap significantly in the XAS spectra inhibiting access to the available information {\color{red}(REF)}.
+This drawback can be overcome by detecting the electrons resulting from the subsequent resonant Auger decay and thus using this complementary information to separate the overlapping states \citep{goldsz16:15133}.
+In a liquid jet, this method applied to shallow core holes (like O 1s of the water molecule) mainly provides information from sites close to the liquid-solid interface, due to the short mean free path of the low-kinetic-energy Auger electrons.
+With a recently commissioned setup using tender X-rays {\color{red}\citep{ceolin13:188,rueff15:175}} we are now able to reach deeper core levels resulting in much faster Auger electrons, and as a consequence, one can have a significantly deeper look into the liquid.
+
+In this work we used Auger electron spectroscopy (AES) together with XAS in the tender x-ray regime to study the electronic decay processes following x-ray absorption of aqueous potassium chloride at the K-edges of both \ki~and \cli.
 In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, core excited states are populated.
@@
 The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization of aqueous \ki~and \cli~populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
-The $^3$P final states have a very low intensity since the corresponding transitions are forbidden from angular momentum and parity conservation rules.
-In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines at photon energy h$\nu = 3616.0$\,eV are located at 2958.0\,eV and 2968.5\,eV kinetic energy, respectively (Fig.\ \ref{fg:2dmap_k}(a)).
-For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at 2373.1\,eV and 2382.0\,eV kinetic energy for a photon energy of 2830.0\,eV (Fig.\ \ref{fg:2dmap_cl}).
+The transitions to $^3$P final states have a very low intensity since they are forbidden from parity conservation rules.
+In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines at photon energy h$\nu = 3616.0$\,eV are located at kinetic energy $E_{\text{kin}} = 2958.0$\,eV and 2968.5\,eV, respectively (Fig.\ \ref{fg:2dmap_k} (c)).
+For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at $E_{\text{kin}} = 2373.1$\,eV and 2382.0\,eV for a photon energy of 2830.0\,eV (Fig.\ \ref{fg:2dmap_cl} (c)).
 
@@
 (c) Auger spectra at photon energies 3610.7\,eV and 3616\,eV.
-The vertical bars in the resonant Auger spectrum measured at 3610.7\,eV indicate the energy positions of the calculated doublet 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) states of K$^{+}$(H$_2$O)$_6$.}
+The vertical bars in the resonant Auger spectrum measured at 3610.7\,eV indicate the spectator Auger energies of the calculated doublet 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) states of K$^{+}$(H$_2$O)$_6$.}
 \label{fg:2dmap_k}
@@
 In our spectra, the PCI effect is manifested as an asymmetric tail of the main peaks at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli, and as a shift of $\sim$1\,eV of the maxima towards lower kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
-An explanation of the shift is given in the SI.
+More details are given in the SI.
 
-Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder on the low kinetic energy side at about 2965\,eV kinetic energy, feature A (Fig.\ \ref{fg:2dmap_k}).
-This shoulder is attributed to electron transfer from the solvent water molecules to the unoccupied 3d orbitals of K$^{+}$ \citep{ceolin17:263003}.
+Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder on the low kinetic energy side at $E_{\text{kin}} \cong 2965$\,eV, feature A (Fig.\ \ref{fg:2dmap_k}(a)).
+This shoulder is attributed to electron transfer from the solvent water molecules to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) resulting in K$^{2+}$(2p$^{-2}$3d)W$^{-1}$ \citep{ceolin17:263003}.
 In the case of \cli, there is no experimental evidence of such intense electron transfer processes.
@@
 (c) Auger spectra at photon energies 2825.2\,eV and 2830.0\,eV.
-The vertical bars in the resonant Auger spectrum at 2825.2\,eV indicate the energy positions of the calculated doublet 2p$^{-2}$4p states of Cl$^{-}$(H$_2$O)$_6$.}
+The vertical bars in the resonant Auger spectrum at 2825.2\,eV indicate the the spectator Auger energies of the calculated doublet 2p$^{-2}$4p states of Cl$^{-}$(H$_2$O)$_6$.}
 \label{fg:2dmap_cl}
@@
 
-The KL$_{2,3}$L$_{2,3}$ Auger decay following resonant K-shell excitation of solvated \ki~and \cli~is schematically presented on Fig.\ \ref{fg:auger}.
-The pre-edge regions of the XAS spectra of \ki~and \cli~do not exhibit any high intensity peaks owing to the lifetime broadening and energetic proximity of the core excited states to the ionization threshold (Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}).
-Consequently, solely from these spectra, one cannot conclude whether there are core excited states in the pre-edge structure.
-Instead these states have to be identified by their resonant Auger features, which differ from the normal Auger features.
-Thus, for \cli, the lowest core excited state is located at 2825.2\,eV, which is in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments \citep{sugiura82:681,shadle95:2259}.
-In the case of \ki, there are two dispersive features with maxima at photon energies of 3611.2\,eV (B) and 3611.6\,eV (C).
-The positions of these two core excited states are close to the energy of the 1s$^{-1}$4p excitation in bare \ki~at 3610.7\,eV \citep{hertlein06:062715}.
-
-The resonant Auger features produced in the decay of these core excited states are quite different for \cli~and \ki.
-In the 2D map of \cli~shown in Fig.\ \ref{fg:2dmap_cl} there are two dispersive features indicated with diagonal dashed lines.
-The maxima of these features are at 2825.2\,eV photon energy and 2374.6 and 2383.4\,eV kinetic energy, respectively.
+The pre-edge regions of the XAS spectra of \ki~and \cli~shown in Figs.\ \ref{fg:2dmap_k}(b) and \ref{fg:2dmap_cl}(b) do not show any clear indication of core excited states due to their lifetime broadening and energetic proximity to the ionization threshold.
+Instead these states can be identified by their resonant Auger features, which disperse with photon energy and thus significantly differ from the normal Auger ones.
+In the 2D map of \cli~(Fig.\ \ref{fg:2dmap_cl}) there are two dispersive resonant Auger features indicated with diagonal dashed lines.
+Both of them have a maximum at photon energy $h\nu =  2825.2$\,eV, which is in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments on hydrated Mg and Sr chlorides\citep{sugiura82:681} and metal-chloride complexes \citep{shadle95:2259}.
+These features have $E_{\text{kin}} = 2374.6$ and 2383.4\,eV, respectively, which demonstrates that they are related to the $^1$S and $^1$D main lines.
 In the case of \ki, the dispersive line related to the $^1$S main line cannot be clearly identified due to the presence of strong background.
-Instead two dispersive features related to the $^1$D main line are observed denoted as B and C on Fig.\ \ref{fg:2dmap_k}.
-Feature B exhibits a maximum at h$\nu = 3611.2$\,eV and 2969.2\,eV kinetic energy.
-The additional feature C appears at h$\nu = 3611.6$\,eV and 2978.1\,eV kinetic energy, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.
+Instead two dispersive features related to the $^1$D main line are observed denoted as B and C on Fig.\ \ref{fg:2dmap_k}(a).
+Feature B exhibits a maximum at h$\nu = 3611.2$\,eV and $E_{\text{kin}} = 2969.2$\,eV.
+The additional feature C appears at h$\nu = 3611.6$\,eV and $E_{\text{kin}} = 2978.1$\,eV, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.
+The positions of these two core excited states are close to the energy of the 1s$^{-1}$4p excitation of gas-phase \ki~at 3610.7\,eV \citep{hertlein06:062715}.
 
@@
 \centering
-\includegraphics[scale=0.75]{figures/xas_spectra.eps}
-\caption{XAS spectra of the lowest K-shell resonant transitions in the bare K$^{+}$ (c) and Cl$^{-}$ (d) ions and their 6-coordinated clusters ((a) and (b)).
-For comparison with the experiment, the theoretical stick spectra are convolved with a Lorentzian of FWHM  0.74\,eV and 0.62\,eV in the case of \ki~and \cli \citep{Krause79:329} (dashed line)and a Voigt profile (solid line).
-The stick spectrum corresponds to the projections of the singly-occupied natural orbitals (SONOs) corresponding to the core excited states of the 6-coordinated clusters on the basis of SONOs corresponding to the 1s$^{-1}$3d, 1s$^{-1}$4p, and 1s$^{-1}$5p states of the bare ions.
+\includegraphics[scale=0.55]{figures/xas_spectra.eps}
+\caption{XAS spectra of the lowest K-shell resonant transitions in the isolated K$^{+}$ (a) and Cl$^{-}$ (b) ions and their 6-coordinated clusters ((c) and (d)).
+For comparison with the experiment, the theoretical stick spectra are convolved with a Lorentzian of FWHM 0.74\,eV and 0.62\,eV representing the lifetime broadening of \ki~and \cli \citep{Krause79:329} (dashed lines) and a Voigt profile (solid line) to account for both the lifetime and the experimental broadening (see text).
+The colors in the stick spectrum represent the projections of the singly-occupied natural orbitals (SONOs) of the core excited 6-coordinated clusters on the basis of SONOs belonging to the 1s$^{-1}$3d, 1s$^{-1}$4p, and 1s$^{-1}$5p states of the isolated ions.
 The remaining contributions from higher-lying atomic core excitations or from excitations to the solvent molecules are depicted as grey sticks.
@@
 
-In order to rationalize the pre-edge region of the experimental XAS spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core excited states of the bare \ki~and \cli~ions and their hexa-coordinated clusters (Fig.\ \ref{fg:xas_kcl}).
-The lowest bright peak in the XAS spectra of the bare ions corresponds to the dipole allowed 1s$^{-1}$4p state followed by the second bright state, 1s$^{-1}$5p, which is located 4.3\,eV and 10.8\,eV higher in \ki~and \cli, respectively.
-We also show the dipole forbidden 1s$^{-1}$3d states of the bare ions as blue crosses.
-It is noteworthy that the positions of the 1s$^{-1}$4p and 1s$^{-1}$3d states are inverted in \ki~and \cli, and moreover, the splitting between these states is about two times smaller in \ki, which as explained later is crucial for understanding the Auger spectra of the two ions.
-Upon addition of water molecules, the degeneracy of the states is lifted, and moreover, they interact with other states of the ion or the neighboring water molecules (Fig.\ \ref{fg:xas_kcl}(a),(b)).
+In order to rationalize the pre-edge region of the experimental XAS spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core excited states of the isolated \ki~and \cli~ions and their hexa-coordinated clusters (Fig.\ \ref{fg:xas_kcl}).
+The lowest peak in the XAS spectra of the isolated ions corresponds to the dipole allowed 1s$^{-1}$4p state followed by the second bright state, 1s$^{-1}$5p, which is higher in energy by 4.3\,eV and 10.8\,eV in \ki~and \cli, respectively.
+For both ions, the energy positions of the dipole forbidden 1s$^{-1}$3d states are indicated as blue crosses.
+It is noteworthy that the positions of the 1s$^{-1}$4p and 1s$^{-1}$3d states are inverted in \ki~and \cli, and moreover, the splitting between these states is about two times smaller in \ki.
+These findings are crucial for understanding the Auger spectra of the two ions as shown below.
+Upon addition of water molecules, the degeneracy of the states is lifted and they interact with other states of the ion or the neighboring water molecules (Fig.\ \ref{fg:xas_kcl}(c),(d)).
 Thus, dipole forbidden states acquire intensity in the cluster.
@@
 
-Further by comparison of the experimental and theoretical XAS spectra, we assume that only the lowest peak in the theoretical XAS spectra is populated in the experiment.
+Further by comparing the experimental and theoretical XAS spectra, we assume that only the states of the lowest peak in the theoretical XAS spectra are populated in the experiment.
 In the 6-coordinated \ki~cluster the lowest peak in the spectrum contains three states.
-The lowest and highest lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character.
-The low intensity state lying between these two states has a predominantly 1s$^{-1}$3d character.
+The lowest and highest lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character while the low intensity state in between has a predominantly 1s$^{-1}$3d character.
 Since the dispersive feature B appears at low excitation energies, we assume that it is produced in the resonant Auger decay of the lowest core excited states of \ki~of predominantly 1s$^{-1}$4p character.
@@
 In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first state -- it has mainly \cli~1s$^{-1}$4p character with some admixture of states of the nearest water molecules.
-We therefore attribute the two dispersive features associated with the $^1$S and $^1$D main lines on the 2D map of \cli~to the resonant Auger decay of this core excited state involving mostly the 4p orbitals of chloride.
+Consequently, we attribute the two dispersive features associated with the $^1$S and $^1$D main lines on the 2D map of \cli~to the resonant Auger decay of this core excited state.
+%involving mostly the 4p orbitals of chloride.
 
-To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ doublet states corresponding to the lowest final spectator resonant Auger states.
-The energy positions of these lines are shown as bars in the upper panels of Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl}.
-In both cases, the lowest 2p$^{-2}$($^1$D)4p states were shifted such that their energies coincide with the maxima of the dispersive features on the high kinetic energy part of the $^1$D main line.
-
-As mentioned above, we attribute the island B on the 2D map of \ki$_{\text{aq}}$ to the decay of the lowest lying core excited state of predominantly 1s$^{-1}$4p character.
-Supposing that this state undergoes mostly pure spectator resonant Auger decay as in the isoelectronic Ar atom \citep{ceolin15:022502}, then the lowest 2p$^{-2}$4p states are populated resulting in Auger electrons of between 2969.0 and 2970.5\,eV kinetic energy.
-As can be seen from the Auger spectrum at h$\nu = 3610.7$\,eV (upper panel of Fig.\ \ref{fg:2dmap_k}), the lowest 2p$^{-2}$4p states of \ki(H$_2$O)$_6$ are separated by $\sim$5 and 12-13\,eV from two higher lying groups of 2p$^{-2}$3d states.
-Thus, the group of 2p$^{-2}$3d states at $\sim$2975\,eV lies closer to the position of island C.
+To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest doublet states of the type K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$.
+These states are the final states of the spectator Auger decay.
+The latter is the predominant decay process for the low-lying core excited states in argon \citep{ceolin15:022502}, which is isoelectronic to K$^+$ and Cl$^-$.
+The energy positions of the states are adjusted to the kinetic-energy scale of the Auger spectra of both ions such that the lowest 2p$^{-2}$($^1$D)4p states coincide with the maxima of the dipsersive features related to the $^1$D main line.
+The results are shown as bars in Figs.\ \ref{fg:2dmap_k}(c) and \ref{fg:2dmap_cl}(c).
+As can be seen from the bars overlapping the Auger spectrum recorded at h$\nu = 3610.7$\,eV (Fig.\ \ref{fg:2dmap_k}(c)), the lowest 2p$^{-2}$4p states of \ki(H$_2$O)$_6$ are lower in energy by $\sim$5 and 12-13\,eV than two groups of 2p$^{-2}$3d states.
+Thus, the transitions to the group of 2p$^{-2}$3d final states at $E_{\text{kin}}\cong 2975$\,eV are closer to the kinetic energy of island C.
 Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$^{-1}$3d excitation to this group of 2p$^{-2}$3d states.
 The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C.
-This disagreement can be explained with the fact that we consider a single geometry with a fixed number of water molecules in the first solvation shell, and moreover, we do not theoretically account for the effect of distant solvent shells.
-Concerning the 2p$^{-2}$3d states at kinetic energies between 2982 and 2983\,eV, we conclude that they are not populated via the Auger process since no additional experimental features are observed.
+This disagreement can be explained with the fact that we consider a single geometry with a fixed number of water molecules in the first solvation shell.
+Moreover, we do not theoretically account for the effect of distant solvent shells.
+We assume that the transitions to the 2p$^{-2}$3d states with kinetic energies between 2982 and 2983\,eV have negligible Auger rates since no additional experimental features are observed.
 
-Another argument in favor of the 2p$^{-2}$3d character of the feature C is the energy difference between the spectral features A and C.
+Another argument supporting the assignment of feature C to the 1s$^{-1}$3d $\rightarrow$ 2p$^{-2}$3d Auger transition is the energy difference between the spectral features A and C.
 Feature A originates from electron transfer processes from water molecules (W) to the doubly core ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
-The lowest ionization potential of liquid water is about 11.16\,eV \cite{winter04:2625} which fits well with the observed A-C splitting.
+The lowest ionization potential of liquid water is about 11.16\,eV \cite{winter04:2625} which matches well the observed A-C splitting.
 Thus, the above energetic arguments corroborate the attribution of island C as originating from resonant Auger decay to the K$^{2+}$ 2p$^{-2}$3d final states.
 
-In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (upper panel of Fig.\ \ref{fg:2dmap_cl}).
-The lower kinetic energy group corresponds to the 2p$^{-2}$($^1$S)4p final states, whereas the higher kinetic energy group corresponds to the 2p$^{-2}$($^1$D)4p final states.
-The splitting between these two groups is in good agreement with the experimental splitting between the dispersive features on the high kinetic energy sides of the $^1$S and $^1$D main peaks.
-Consequently, we attribute these dispersive features as resulting from the resonant Auger decay of the 1s$^{-1}$4p core excited state of \cli$_{\text{aq}}$ to the 2p$^{-2}$($^1$S)4p and  2p$^{-2}$($^1$D)4p final states.
+In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (Fig.\ \ref{fg:2dmap_cl}(c)) which correspond to the 2p$^{-2}$($^1$S)4p and 2p$^{-2}$($^1$D)4p final states.
+The splitting between these two groups is in good agreement with the experimentally observed splitting between the dispersive features on the high kinetic energy sides of the $^1$S and $^1$D main peaks.
+Consequently, we assign the dispersive features on Fig.\ \ref{fg:2dmap_cl}(a) to the 1s$^{-1}$4p $\rightarrow$ 2p$^{-2}$($^1$S, $^1$D)4p resonant Auger transitions of Cl$^{-}_{\text{aq}}$.
 
-In summary, we studied the electronic structure of aqueous solution of KCl at the K-edges of both \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$ using a combination of x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, and {\it ab initio} calculations.
-The Auger electron spectra of both ions exhibit features of both normal and resonant Auger processes.
-The latter process proceeds differently for aqueous K$^{+}$ and Cl$^{-}$ due to the population of the dipole forbidden K$^{+}$ 1s$^{-1}$3d state in a solution.
-The spectator Auger decay of this state produces an additional dispersive feature which is manifested as a separate peak in the Auger electron spectrum.
-In the case of \cli~only fingerprints of the population and Auger decay of the dipole allowed 1s$^{-1}$4p excitation are observed.
+In summary, we studied the electronic structure of aqueous solution of KCl at the K-edges of both \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$ by combining x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, and {\it ab initio} calculations.
+The Auger electron spectra of the two ions exhibit features of normal and resonant Auger processes.
+The spectator resonant Auger decay following the 1s$^{-1}$4p excitation proceeds similarly for both aqueous K$^{+}$ and Cl$^{-}$ resulting in dispersive lines with maxima close to the normal Auger features.
+However, there is a clear difference between the two ions due to the non-negligible excitation of the dipole-forbidden 1s$^{-1}$3d state of \ki~in solution.
+The spectator Auger decay of this state produces an additional feature which is well separated from the remaining Auger features.
 These results are an important first step in the study of the chains of relaxation steps triggered by x-ray photoabsorption in liquids.

### 2018-06-05 suppinfo.tex
june 5
Ralph's corrections included

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%<<<<<<< HEAD:suppinfo.tex
 \title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous solution using tender x-rays}
 %\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}
+%=======
+\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
+%\title{Tracking the hazy boundary between resonant and normal Auger decay in near the K-edges of aqueous \ki~and \cli}
+%>>>>>>> origin/master:suppinfo - Copy.tex
 
@@
 \end{figure}
+%<<<<<<< HEAD:suppinfo.tex
 %
@@
 % in the continuum.}
+%=======
+
+In what follows we give a simple explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli.
+In the case of \ki, the excited electron mainly sees a $2/r$ potential.
+In addition, it sees a short range potential originating from the point-like nucleus and the screening electrons.
+The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series.
+However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant.
+As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states (here obviously 4p) \citep{buckman94:539}.
+In contrast to this, the 3d and 5p states are not bound.
+% in the continuum.}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
+\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}.
+The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step.
+From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau_{c} l/d$, with $\tau_{c}$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
+The green line defines the Cl$^{-}_{\text{aq}}$(1s) ionization potential.}
+\label{fg:si_ct_time}
+\end{figure}
+
+%>>>>>>> origin/master:suppinfo - Copy.tex
 

### 2018-06-08 abstract.tex
june 7
all of Ralph's corrections taken into account (main, SI)

@@
 In the considered exemplary aqueous KCl solution the solvated isoelectronic \ki~and \cli~ions exhibit notably different Auger electron spectra as a function of the photon energy.
-The differences appear due to dipole forbidden transitions in aqueous \ki~whose occurrence, according to the performed {\it ab initio} calculations, becomes possible only in the presence of solvent water molecules.
+The differences appear due to dipole-forbidden transitions in aqueous \ki~whose occurrence, according to the performed {\it ab initio} calculations, becomes possible only in the presence of solvent water molecules.

### 2018-06-08 article_text.tex
june 7
all of Ralph's corrections taken into account (main, SI)

@@
 Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanisms of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
-Depending on the photon energy, the absorption of an x-ray photon results in the population of core excited or core ionized states.
+Depending on the photon energy, the absorption of an x-ray photon results in the population of core-excited or core-ionized states.
 The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decays, and it depends on the character of the initially populated states \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}.
@@
 
-X-ray absorption spectroscopy (XAS) is a powerful tool to study the nearest environment of atoms in gas phase as it probes core excited states below threshold which are highly sensitive to the surrounding.
-However, for atoms and molecules in liquid or solid phase, these core excited states overlap significantly in the XAS spectra inhibiting access to the available information {\color{red}(REF)}.
+X-ray absorption spectroscopy (XAS) is a powerful tool to study the nearest environment of atoms in gas phase as it probes core-excited states below threshold which are highly sensitive to the surrounding.
+However, for atoms and molecules in liquid or solid phase, these core-excited states overlap significantly in the XAS spectra inhibiting access to the available information {\color{red}(REF)}.
 This drawback can be overcome by detecting the electrons resulting from the subsequent resonant Auger decay and thus using this complementary information to separate the overlapping states \citep{goldsz16:15133}.
 In a liquid jet, this method applied to shallow core holes (like O 1s of the water molecule) mainly provides information from sites close to the liquid-solid interface, due to the short mean free path of the low-kinetic-energy Auger electrons.
-With a recently commissioned setup using tender X-rays {\color{red}\citep{ceolin13:188,rueff15:175}} we are now able to reach deeper core levels resulting in much faster Auger electrons, and as a consequence, one can have a significantly deeper look into the liquid.
+With a recently commissioned setup using tender X-rays \citep{ceolin13:188,rueff15:175} we are now able to reach deeper core levels resulting in much faster Auger electrons, and as a consequence, one can have a significantly deeper look into the liquid.
 
 In this work we used Auger electron spectroscopy (AES) together with XAS in the tender x-ray regime to study the electronic decay processes following x-ray absorption of aqueous potassium chloride at the K-edges of both \ki~and \cli.
-In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, core excited states are populated.
+In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, core-excited states are populated.
 These states undergo resonant Auger decay within less than 1\,fs \citep{ceolin17:263003}.
@@
 
-The resonant and normal Auger processes which we investigated in this work are schematically shown on Fig.\ \ref{fg:auger}.
-The KL$_{2,3}$L$_{2,3}$ normal Auger decay following K-shell ionization of aqueous \ki~and \cli~populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
-The transitions to $^3$P final states have a very low intensity since they are forbidden from parity conservation rules.
-In the case of K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D KL$_{2,3}$L$_{2,3}$ Auger lines at photon energy h$\nu = 3616.0$\,eV are located at kinetic energy $E_{\text{kin}} = 2958.0$\,eV and 2968.5\,eV, respectively (Fig.\ \ref{fg:2dmap_k} (c)).
-For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at $E_{\text{kin}} = 2373.1$\,eV and 2382.0\,eV for a photon energy of 2830.0\,eV (Fig.\ \ref{fg:2dmap_cl} (c)).
+The resonant and normal Auger processes are schematically shown on Fig.\ \ref{fg:auger}.
+The KL$_{2,3}$L$_{2,3}$ normal Auger decay of aqueous \ki~and \cli~populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
+The transitions to $^3$P final states are weak since they are forbidden in LS coupling.
+For K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D Auger lines for a photon energy h$\nu = 3616.0$\,eV are located at kinetic energies $E_{\text{kin}} = 2958.0$\,eV and 2968.5\,eV, respectively (Fig.\ \ref{fg:2dmap_k}(c)).
+For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at $E_{\text{kin}} = 2373.1$\,eV and 2382.0\,eV for h$\nu = 2830.0$\,eV (Fig.\ \ref{fg:2dmap_cl}(c)).
+Close to threshold the KL$_{2,3}$L$_{2,3}$ normal Auger lines are asymmetric and also shifted to higher kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
+This is due to post-collision interaction \citep{russek86:911,guillemin15:012503}, which is discussed in more detail in the SI.
 
@@
 
-The KL$_{2,3}$L$_{2,3}$ normal Auger lines may be shifted to higher kinetic energies and also disperse with photon energy close to threshold due to energy exchange between the photoelectron and Auger electron called post-collision interaction (PCI) \citep{russek86:911,guillemin15:012503}.
-In our spectra, the PCI effect is manifested as an asymmetric tail of the main peaks at photon energies 3616\,eV in the case of \ki, and 2830\,eV in the case of \cli, and as a shift of $\sim$1\,eV of the maxima towards lower kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
-More details are given in the SI.
-
-Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder on the low kinetic energy side at $E_{\text{kin}} \cong 2965$\,eV, feature A (Fig.\ \ref{fg:2dmap_k}(a)).
+Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder on the low kinetic-energy side at $E_{\text{kin}} \cong 2965$\,eV, feature A (Fig.\ \ref{fg:2dmap_k}(a)).
 This shoulder is attributed to electron transfer from the solvent water molecules to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) resulting in K$^{2+}$(2p$^{-2}$3d)W$^{-1}$ \citep{ceolin17:263003}.
@@
 
-The pre-edge regions of the XAS spectra of \ki~and \cli~shown in Figs.\ \ref{fg:2dmap_k}(b) and \ref{fg:2dmap_cl}(b) do not show any clear indication of core excited states due to their lifetime broadening and energetic proximity to the ionization threshold.
+The pre-edge regions of the XAS spectra of \ki~and \cli~shown in Figs.\ \ref{fg:2dmap_k}(b) and \ref{fg:2dmap_cl}(b) do not show any clear indication of core-excited states due to their lifetime broadening and energetic proximity to the ionization threshold.
 Instead these states can be identified by their resonant Auger features, which disperse with photon energy and thus significantly differ from the normal Auger ones.
 In the 2D map of \cli~(Fig.\ \ref{fg:2dmap_cl}) there are two dispersive resonant Auger features indicated with diagonal dashed lines.
-Both of them have a maximum at photon energy $h\nu =  2825.2$\,eV, which is in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments on hydrated Mg and Sr chlorides\citep{sugiura82:681} and metal-chloride complexes \citep{shadle95:2259}.
+Both of them have a maximum at $h\nu =  2825.2$\,eV, which is in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments on hydrated Mg and Sr chlorides\citep{sugiura82:681} and metal-chloride complexes \citep{shadle95:2259}.
 These features have $E_{\text{kin}} = 2374.6$ and 2383.4\,eV, respectively, which demonstrates that they are related to the $^1$S and $^1$D main lines.
@@
 The additional feature C appears at h$\nu = 3611.6$\,eV and $E_{\text{kin}} = 2978.1$\,eV, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.
-The positions of these two core excited states are close to the energy of the 1s$^{-1}$4p excitation of gas-phase \ki~at 3610.7\,eV \citep{hertlein06:062715}.
+The positions of these two core-excited states are close to the energy of the 1s$^{-1}$4p excitation of gas-phase \ki~at 3610.7\,eV \citep{hertlein06:062715}.
 
@@
 For comparison with the experiment, the theoretical stick spectra are convolved with a Lorentzian of FWHM 0.74\,eV and 0.62\,eV representing the lifetime broadening of \ki~and \cli \citep{Krause79:329} (dashed lines) and a Voigt profile (solid line) to account for both the lifetime and the experimental broadening (see text).
-The colors in the stick spectrum represent the projections of the singly-occupied natural orbitals (SONOs) of the core excited 6-coordinated clusters on the basis of SONOs belonging to the 1s$^{-1}$3d, 1s$^{-1}$4p, and 1s$^{-1}$5p states of the isolated ions.
+The colors in the stick spectrum represent the projections of the singly-occupied natural orbitals (SONOs) of the core-excited 6-coordinated clusters on the basis of SONOs belonging to the 1s$^{-1}$3d, 1s$^{-1}$4p, and 1s$^{-1}$5p states of the isolated ions.
 The remaining contributions from higher-lying atomic core excitations or from excitations to the solvent molecules are depicted as grey sticks.
-The theoretical XAS spectra of both \ki~and \cli~were shifted to higher photon energies such that the energies of the lowest core excited states correspond to the experimentally determined ones.
+The theoretical XAS spectra of both \ki~and \cli~were shifted to higher photon energies such that the energies of the lowest core-excited states correspond to the experimentally determined ones.
 The experimental ionization thresholds are depicted as grey boxes.}
@@
 
-In order to rationalize the pre-edge region of the experimental XAS spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core excited states of the isolated \ki~and \cli~ions and their hexa-coordinated clusters (Fig.\ \ref{fg:xas_kcl}).
-The lowest peak in the XAS spectra of the isolated ions corresponds to the dipole allowed 1s$^{-1}$4p state followed by the second bright state, 1s$^{-1}$5p, which is higher in energy by 4.3\,eV and 10.8\,eV in \ki~and \cli, respectively.
-For both ions, the energy positions of the dipole forbidden 1s$^{-1}$3d states are indicated as blue crosses.
+In order to rationalize the pre-edge region of the experimental XAS spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core-excited states of the isolated \ki~and \cli~ions and their hexa-coordinated clusters (Fig.\ \ref{fg:xas_kcl}).
+The theoretical XAS spectra of the isolated ions show the two dipole-allowed states, 1s$^{-1}$4p and 1s$^{-1}$5p, which are split by 4.3\,eV and 10.8\,eV in \ki~and \cli, respectively.
+For both ions, the energy positions of the dipole-forbidden 1s$^{-1}$3d states are marked with blue crosses.
 It is noteworthy that the positions of the 1s$^{-1}$4p and 1s$^{-1}$3d states are inverted in \ki~and \cli, and moreover, the splitting between these states is about two times smaller in \ki.
@@
 Upon addition of water molecules, the degeneracy of the states is lifted and they interact with other states of the ion or the neighboring water molecules (Fig.\ \ref{fg:xas_kcl}(c),(d)).
-Thus, dipole forbidden states acquire intensity in the cluster.
+Thus, dipole-forbidden states acquire intensity in the cluster.
 A similar effect was observed in the XAS spectra of microsolvated clusters of Na$^{+}$ and Mg$^{2+}$ \citep{miteva16:16671}.
@@
 The lowest and highest lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character while the low intensity state in between has a predominantly 1s$^{-1}$3d character.
-Since the dispersive feature B appears at low excitation energies, we assume that it is produced in the resonant Auger decay of the lowest core excited states of \ki~of predominantly 1s$^{-1}$4p character.
-Moreover, we can attribute the feature C to the resonant Auger decay of the low intensity dipole forbidden 1s$^{-1}$3d state.
+Since the dispersive feature B appears at low excitation energies, we assume that it is produced in the resonant Auger decay of the lowest core-excited states of \ki~of predominantly 1s$^{-1}$4p character.
+Moreover, we can attribute the feature C to the resonant Auger decay of the low intensity dipole-forbidden 1s$^{-1}$3d state.
 Thus, we explain both the energy splitting of $\sim$400\,meV photon energy of B and C, and the fact that island C has lower intensity than B (Fig.\ \ref{fg:2dmap_k}).
 In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first state -- it has mainly \cli~1s$^{-1}$4p character with some admixture of states of the nearest water molecules.
-Consequently, we attribute the two dispersive features associated with the $^1$S and $^1$D main lines on the 2D map of \cli~to the resonant Auger decay of this core excited state.
+Consequently, we attribute the two dispersive features associated with the $^1$S and $^1$D main lines on the 2D map of \cli~to the resonant Auger decay of this core-excited state.
 %involving mostly the 4p orbitals of chloride.
@@
 These states are the final states of the spectator Auger decay.
-The latter is the predominant decay process for the low-lying core excited states in argon \citep{ceolin15:022502}, which is isoelectronic to K$^+$ and Cl$^-$.
+The latter is the predominant decay process for the low-lying core-excited states in argon \citep{ceolin15:022502}, which is isoelectronic to K$^+$ and Cl$^-$.
 The energy positions of the states are adjusted to the kinetic-energy scale of the Auger spectra of both ions such that the lowest 2p$^{-2}$($^1$D)4p states coincide with the maxima of the dipsersive features related to the $^1$D main line.
@@
 Another argument supporting the assignment of feature C to the 1s$^{-1}$3d $\rightarrow$ 2p$^{-2}$3d Auger transition is the energy difference between the spectral features A and C.
-Feature A originates from electron transfer processes from water molecules (W) to the doubly core ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
+Feature A originates from electron transfer processes from water molecules (W) to the doubly core-ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
 The lowest ionization potential of liquid water is about 11.16\,eV \cite{winter04:2625} which matches well the observed A-C splitting.
@@
 
-In summary, we studied the electronic structure of aqueous solution of KCl at the K-edges of both \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$ by combining x-ray absorption and Auger electron spectroscopy in the tender x-ray regime, and {\it ab initio} calculations.
-The Auger electron spectra of the two ions exhibit features of normal and resonant Auger processes.
+The delocalization of core-excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay \citep{Nordlund07:217406,ottosson12:1}.
+To estimate the delocalization time of the core-excited electron, $\tau_{\text{CT}}$, at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+Our analysis, presented in detail in SI, shows that in the case of \cli, $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, i.e.
+$\sim$1\,fs.
+The treatment is more complex in the \ki~case due to the presence of multiple competing processes.
+However, one can expect much less efficient delocalization in \ki~because the lifetime of the K1s core hole is shorter than for chloride (0.9 vs.\ 1\,fs) and, moreover, the core-excited states appear 1.2\,eV below the ionization threshold compared to 0.2\,eV for chloride.
+
+In summary, we studied the electronic structure of aqueous solution of KCl at the K-edges of both \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$ by combining XAS and AES in the tender x-ray regime, and {\it ab initio} calculations.
+The Auger electron spectra of both ions exhibit features of normal and resonant Auger processes.
 The spectator resonant Auger decay following the 1s$^{-1}$4p excitation proceeds similarly for both aqueous K$^{+}$ and Cl$^{-}$ resulting in dispersive lines with maxima close to the normal Auger features.
@@
 The spectator Auger decay of this state produces an additional feature which is well separated from the remaining Auger features.
-These results are an important first step in the study of the chains of relaxation steps triggered by x-ray photoabsorption in liquids.
+These results are an important first step in the study of relaxation cascades triggered by x-ray photoabsorption in liquids.
 The Auger processes considered here are inevitably followed by multiple intra- and interatomic electronic decays, such as interatomic Coulombic decay (ICD) and electron-transfer mediated decay (ETMD) \citep{unger17:708,Stumpf16:237}.

### 2018-06-08 suppinfo - Copy.tex
june 7
all of Ralph's corrections taken into account (main, SI)

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%<<<<<<< HEAD:suppinfo.tex
+\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous solution using tender x-rays}
+%\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}
+%=======
 \title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
 %\title{Tracking the hazy boundary between resonant and normal Auger decay in near the K-edges of aqueous \ki~and \cli}
+%>>>>>>> origin/master:suppinfo - Copy.tex
 
@@
 \end{figure}
+%<<<<<<< HEAD:suppinfo.tex
+%
+%
+The intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state contrary to what is observed in \ki.
+This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$^{-1}$4p compared to the 1s$^{-1}$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
+In what follows we give a simple explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli.
+In the case of \ki, the excited electron mainly sees a $2/r$ potential.
+In addition, it sees a short range potential originating from the point-like nucleus and the screening electrons.
+The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series.
+However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant.
+As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states (here obviously 4p) \citep{buckman94:539}.
+In contrast to this, the 3d and 5p states are not bound.
+% in the continuum.}
+%=======
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Delocalization vs resonant Auger decay}
+
+The delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
+In order to estimate the delocalization rate of the core excited electron at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+
+In the case of Cl$^{-}$, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get the partial electron yield as a function of the photon energy.
+The result is shown on Fig.\ \ref{fg:si_ct_time} in the SI.
+The figure shows that there is a large overlap between the resonant and normal Auger contributions, due to the proximity of the resonance to the ionization potential and due to the very short lifetime of the corresponding states.
+At the specific photon energy corresponding to the lowest core excitation, h$\nu = 2825.2$\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel) a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV .
+The position of the first peak coincides with the $^1$D main line resulting from normal Auger decay, whereas the second peak at 2383.5\,eV corresponds to the resonant Auger decay to the 2p$^{-2}$($^1$D)4p states.
+By fitting this double-peak structure with two Voigt functions, we determine the ratio of the intensities of these peaks to be $l/d \approx 1$.
+From the ratio $l/d$ and the Auger lifetime $\tau_{\text{c}}$, one can determine the delocalization time $\tau_{\text{CT}}$ according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l/d$ \citep{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+Consequently, the delocalization time $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs.
+The fast delocalization in this case is a result of the fact that the energy splitting between the Cl$^{-}$~(1s$^{-1}$4p) resonance and the ionization threshold is 0.2\,eV, and thus, smaller than the lifetime broadening of 0.62\,eV \citep{ceolin17:263003}.
+
+For potassium, the treatment is more complex due to the presence of multiple simultaneous processes -- normal, resonant Auger decay, charge transfer from solvent.
+To extract the intensity of each component from the 2D map shown in Fig.\ \ref{fg:2dmap_k}, one needs the spectral fingerprints of each process to be separated.
+However, as can be seen, this is hardly possible especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
+For instance, at 3610.7\,eV photon energy on the high kinetic energy side of the $^1$D main line, there are contributions from the PCI tail and from the 2p$^{-2}$($^1$D)4p resonant Auger state.
+On the low kinetic energy side, the charge transfer processes lead to a very large structure whose shape unfortunately cannot be easily simulated by a known profile.
+However, the lifetime of the 1s core hole is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and, moreover, the core excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
+Therefore, one can expect much less efficient delocalization compared to Cl$^{-}_{\text{aq}}$.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
+\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}.
+The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step.
+From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau_{c} l/d$, with $\tau_{c}$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
+The green line defines the Cl$^{-}_{\text{aq}}$(1s) ionization potential.}
+\label{fg:si_ct_time}
+\end{figure}
+
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% The appropriate \bibliography command should be placed here.
+%%% Notice that the class file automatically sets \bibliographystyle
+%%% and also names the section correctly.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliography{F:/Articles/bibliography/Bibliography}

### 2018-06-08 suppinfo.tex
june 7
all of Ralph's corrections taken into account (main, SI)

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%<<<<<<< HEAD:suppinfo.tex
 \title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous solution using tender x-rays}
-%\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}
-%=======
-\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
-%\title{Tracking the hazy boundary between resonant and normal Auger decay in near the K-edges of aqueous \ki~and \cli}
-%>>>>>>> origin/master:suppinfo - Copy.tex
 
@@
 
-The theoretical X-ray absorption spectra were computed for the hexa-coordinated clusters of both ions, K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
-The two structures shown in Fig.\ \ref{fg:xas_kcl} were optimized at the DFT level of theory using the B3LYP functional and the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,Blaudeau97:5016}.
+The theoretical X-ray absorption spectra were computed for the hexa-coordinated clusters K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \ki~and \cli~\citep{Ohtaki93:1157,soper06:180,ma14:1006}.
+The two structures shown in Fig.\ \ref{fg:xas_kcl} of the main text were optimized at the DFT level of theory using the B3LYP functional and the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,Blaudeau97:5016}.
 The geometry optimization was performed with the Gaussian 09 package \citep{g09}.
 In order to obtain a realistic structure for K$^{+}$~corresponding to the bulk solution, we carried out constrained geometry optimization by choosing the equilibrium gas-phase geometries \citep{lee99:3995,lee02:5509} belonging to the D$_3$ point group and then increasing the angle $\theta$ between the K-O bond and the $C_3$ axis to 55$^{\circ}$.
-This angle was chosen such that the O-K-O angles are around the maxima of the angular distributions obtained from quantum mechanics/molecular mechanics simulations in Ref.\ \citep{ma14:1006}.
-Moreover, we fixed the K-O distance to 2.840~\AA, such that it corresponds to the distances from other theoretical and experimental works \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
+This angle was chosen such that the O-K-O angles are around the maxima of the angular distributions obtained from quantum mechanics/molecular mechanics simulations reported in Ref.\ \citep{ma14:1006}.
+Moreover, we fixed the K-O distance to 2.840~\AA, in agreement with the values obtained other theoretical and experimental works \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
 
-The energies and transition moments of the core excited states of the bare ions and microsolvated clusters were computed with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}.
+The energies and transition moments of the core-excited states of the isolated ions and microsolvated clusters were computed with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015}.
 In the case of Cl$^{-}$~the 6-311++G(3df,3pd) basis set \citep{Krishnan80:650,McLean80:5639} (excluding f functions) was used on all atoms, whereas in the case of K$^{+}$~we used the 6-311+G(2d,p) basis set \citep{Krishnan80:650,Blaudeau97:5016} on all atoms, and two additional sets of s, p and d diffuse functions were added on K.
@@
 For the calculations of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$.
-To account for the lifetime broadening due to the Auger decay of the core excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of K$^{+}$~and Cl$^{-}$, respectively \citep{Krause79:329}.
+To account for the lifetime broadening due to the Auger decay of the core-excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of K$^{+}$~and Cl$^{-}$, respectively \citep{Krause79:329}.
 Additionally, we convolved the theoretical spectra with a Gaussian profile to also account for the experimental resolution (see Fig.\ \ref{fg:xas_kcl} in the main text).
-We analyzed the core excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or Cl$^{-}$~ions, $\chi_{nl}$
+We analyzed the core-excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or Cl$^{-}$~ions, $\chi_{nl}$
 %
@@
 where $n$ and $l$ stand for the principal and orbital quantum numbers as described in Ref.\ \citep{miteva16:16671}.
-The expansion coefficients $a^{i}_{nl}$ show the degree of delocalization of the excited electron and the mixing of the core excited states in the ligand field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl}).
+The expansion coefficients $a^{i}_{nl}$ show the degree of delocalization of the excited electron and the mixing of the core-excited states in the ligand field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl}).
 
-The final states following KLL resonant Auger decay of K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$ were computed at the Configuration Interaction Singles (CIS) level using the Graphical Unitary Group Approach (GUGA) as implemented in the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS}.
+The 2p$^{-2}$nl final states following KLL resonant Auger decay of K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$ were computed at the Configuration Interaction Singles (CIS) level using the Graphical Unitary Group Approach (GUGA) as implemented in the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS}.
 In order to account for the relaxation effects upon core ionization, we employed a restricted open-shell Hartree-Fock reference wave function with a hole in the 2s orbital of both K$^{+}$~and Cl$^{-}$.
@@
 \section{PCI shift}
-In order to estimate the maximum amplitude of the PCI shift, we compare the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies h$\nu = 5$\,keV \citep{ceolin17:263003}.
-We observe a shift of $\sim$1\,eV of the maxima towards lower kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
-The magnitude of the shift is constant in the photon energy range of $\sim$8\,eV above threshold and similar for the two ions.
+The maximum amplitude of the PCI shift is estimated by comparing the positions of the normal KLL Auger lines of both Cl$^{-}_{\text{aq}}$ and K$^{+}_{\text{aq}}$ close to threshold with those recorded far from threshold, at photon energies h$\nu = 5$\,keV \citep{ceolin17:263003}.
+In this way, we found for the present spectra a shift of $\sim$1\,eV of the maxima towards higher kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
+The magnitude of the shift is similar for the two ions and constant in the photon energy range of up to about 8\,eV above threshold.
+The PCI shift of isoelectronic atom argon in the gas phase show also a maximum value of 1\,eV, however, it decreases in the first 8 eV above threshold by approximately 0.6\,eV \citep{guillemin15:012503}.
 A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314} where it was proposed that it is due to a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band, followed by normal Auger decay.
@@
 \end{figure}
-%<<<<<<< HEAD:suppinfo.tex
-%
-%
-The intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state contrary to what is observed in \ki.
+
+In the calculated spectrum of \cli~the intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state, contrary to what is observed in \ki.
 This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$^{-1}$4p compared to the 1s$^{-1}$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
@@
 However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant.
-As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states (here obviously 4p) \citep{buckman94:539}.
-In contrast to this, the 3d and 5p states are not bound.
-% in the continuum.}
-%=======
-
-In what follows we give a simple explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli.
-In the case of \ki, the excited electron mainly sees a $2/r$ potential.
-In addition, it sees a short range potential originating from the point-like nucleus and the screening electrons.
-The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series.
-However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant.
-As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states (here obviously 4p) \citep{buckman94:539}.
-In contrast to this, the 3d and 5p states are not bound.
-% in the continuum.}
+As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states, the 1s$^{-1}$4p state in the case of \cli~\citep{buckman94:539}.
+In contrast to this, the 1s$^{-1}$3d and 1s$^{-1}$5p states are not bound.
 
@@
 
-%>>>>>>> origin/master:suppinfo - Copy.tex
+\section{Delocalization vs resonant Auger decay}
 
-%\section{Delocalization vs resonant Auger decay}
-%
-%The delocalization of core excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay.
-In order to estimate the delocalization rate of the core excited electron at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
-%
-%In the case of Cl$^{-}$, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl} were isolated by fitting procedures and their intensity integrated to get the partial electron yield as a function of the photon energy.
-The result is shown on Fig.\ \ref{fg:si_ct_time} in the SI.
+In order to estimate the delocalization rate of the core-excited electron at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+In the case of Cl$^{-}$, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl}(a) of the main text were isolated by fitting procedures and their intensity integrated to get the partial electron yield as a function of the photon energy.
+The result is presented on Fig.\ \ref{fg:si_ct_time} in the SI.
 The figure shows that there is a large overlap between the resonant and normal Auger contributions, due to the proximity of the resonance to the ionization potential and due to the very short lifetime of the corresponding states.
-At the specific photon energy corresponding to the lowest core excitation, h$\nu = 2825.2$\,eV (Fig.\ \ref{fg:2dmap_cl}, upper panel) a double-peak structure is observed in the interval of kinetic energies 2380 -- 2385\,eV .
+At the specific photon energy of h$\nu = 2825.2$\,eV, i.e.\ at the maximum of the lowest core excitation 1s$^{-1}$4p, the resonant Auger spectrum exhibits a double-peak structure in the interval E$_{kin} = 2380 - 2385$\,eV (Fig.\ \ref{fg:2dmap_cl}(c) of main text).
 The position of the first peak coincides with the $^1$D main line resulting from normal Auger decay, whereas the second peak at 2383.5\,eV corresponds to the resonant Auger decay to the 2p$^{-2}$($^1$D)4p states.
-By fitting this double-peak structure with two Voigt functions, we determine the ratio of the intensities of these peaks to be $l/d \approx 1$.
-From the ratio $l/d$ and the Auger lifetime $\tau_{\text{c}}$, one can determine the delocalization time $\tau_{\text{CT}}$ according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l/d$ \citep{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
-Consequently, the delocalization time $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs.
+By fitting this double-peak structure with two Voigt functions, we determine the intensity ratio $l/d$ of the localized (2p$^{-2}$4p) and the delocalized (2p$^{-2}$) decay products at a given excitation energy.
+From this ratio and the Auger lifetime $\tau_{\text{c}}$, one can determine the photon-energy dependent delocalization time $\tau_{\text{CT}}$ according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l/d$ \citep{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+Close to the maximum of the 1s$^{-1}$4p resonance the ratio $l/d \cong 1$ and, as a consequence, the delocalization time $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs.
 The fast delocalization in this case is a result of the fact that the energy splitting between the Cl$^{-}$~(1s$^{-1}$4p) resonance and the ionization threshold is 0.2\,eV, and thus, smaller than the lifetime broadening of 0.62\,eV \citep{ceolin17:263003}.
-%
-%
-%For potassium, the treatment is more complex due to the presence of multiple simultaneous processes -- normal, resonant Auger decay, charge transfer from solvent.
-To extract the intensity of each component from the 2D map shown in Fig.\ \ref{fg:2dmap_k}, one needs the spectral fingerprints of each process to be separated.
+
+For potassium, a comparable data treatment is more complicated due to the presence of multiple simultaneous processes, namely, normal and resonant Auger decay, as well as charge transfer from solvent.
+To extract the intensity of each component from the 2D map shown in Fig.\ \ref{fg:2dmap_k}(a) of the main text, one needs the spectral fingerprints of each process to be separated.
 However, as can be seen, this is hardly possible especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
-For instance, at 3610.7\,eV photon energy on the high kinetic energy side of the $^1$D main line, there are contributions from the PCI tail and from the 2p$^{-2}$($^1$D)4p resonant Auger state.
-On the low kinetic energy side, the charge transfer processes lead to a very large structure whose shape unfortunately cannot be easily simulated by a known profile.
-However, the lifetime of the 1s core hole is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and, moreover, the core excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
-Therefore, one can expect much less efficient delocalization compared to Cl$^{-}_{\text{aq}}$.
-%
-%
-%
-%\begin{figure}[h!]
-%\centering
-%\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
-%\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}.
-The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step.
-From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau_{c} l/d$, with $\tau_{c}$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.
-The green line defines the Cl$^{-}_{\text{aq}}$(1s) ionization potential.}
-%\label{fg:si_ct_time}
-%\end{figure}
-%
-%
+For instance, at h$\nu = 3610.7$\,eV on the high kinetic-energy side of the $^1$D main line, there are contributions from the PCI tail and from the 2p$^{-2}$($^1$D)4p resonant Auger state.
+On the low kinetic energy side, the charge transfer processes lead to a very large structure whose shape unfortunately cannot be easily simulated based on known profiles.
+The lifetime of the 1s core hole is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and, moreover, the core-excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
+Therefore, one can expect much less efficient delocalization in K$^{+}_{\text{aq}}$ compared to Cl$^{-}_{\text{aq}}$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliography{F:/Articles/bibliography/Bibliography}
-%\bibliography{Bibliography}
 

### 2018-06-29 abstract.tex
june 29 (jpcl corrections)
JPCL-corrected version sent to Ralph to shorten the assignment
discussion and expand the delocalization part

@@
 In this work for the first time we use a combination of these methods in the tender x-ray regime.
-%This allowed us to explore several hitherto unaddressed electronic transitions and to probe environmental effects, specifically in the bulk of the solution.
-{\color{red}
-This allowed us to address electronic transitions including deep core levels and to probe environmental effects, specifically in the bulk of solutions since the Auger electrons created by deep core levels possess large mean free paths.
+This allowed us to address electronic transitions from deep core levels and to probe environmental effects, specifically in the bulk of the solution since the created energetic Auger electrons possess large mean free paths.
 In the considered exemplary aqueous KCl solution the solvated isoelectronic \ki~and \cli~ions exhibit notably different Auger electron spectra as a function of the photon energy.

### 2018-06-29 article_text.tex
june 29 (jpcl corrections)
JPCL-corrected version sent to Ralph to shorten the assignment
discussion and expand the delocalization part

@@
 
-X-ray absorption spectroscopy (XAS) is a powerful tool to study the nearest environment of atoms in gas phase as it probes core-excited states below threshold which are highly sensitive to the surrounding.
+%X-ray absorption spectroscopy (XAS) is a powerful tool to study the nearest environment of atoms in gas phase as it probes core-excited states below threshold which are highly sensitive to the surrounding.
 However, for atoms and molecules in liquid or solid phase, these core-excited states overlap significantly in the XAS spectra inhibiting access to the available information {\color{red}(REF)}.
@@
 
-In this work we used Auger electron spectroscopy (AES) together with XAS in the tender x-ray regime to study the electronic decay processes following x-ray absorption of aqueous potassium chloride at the K-edges of both \ki~and \cli.
+%X-ray absorption spectroscopy (XAS) applied to gas phase is a powerful tool to describe (de)localized core-excited states associated to a specific atom.
+In condensed phase studies, these core-excited states overlap significantly inhibiting a simple description of the nearest environment of the targeted atom.
+This drawback can be overcome by detecting the electrons resulting from the subsequent resonant Auger decay and by using this complementary information to separate the overlapping states \citep{goldsz16:15133}.
+{\color{red}X-ray absorption spectroscopy (XAS) in the soft x-ray regime is a powerful tool to describe core-excited states of a specific atom and thus to probe its electronic structure and the local environment surrounding it.
+In the tender and hard x-ray regimes, due to the lifetime broadening, these core-excited states overlap significantly inhibiting a simple description of the nearest environment of the targeted atom.
+This drawback can be overcome by detecting the electrons resulting from the subsequent resonant Auger decay and by using this complementary information to separate the overlapping states \citep{foehlisch05:373,goldsz16:15133}.}
+With our recently commissioned microjet setup dedicated to the study of liquids by means of the photoemission technique using tender x-rays \citep{ceolin13:188,rueff15:175}, we are now able to probe much deeper core levels and corresponding fast Auger electrons.
+This allows us to focus our investigations on the liquid bulk by strongly reducing the specific interface contributions, and also to access ultrafast dynamical processes owing to the very short lifetimes of the corresponding core-excited states.
+
+In this work we combine Auger electron spectroscopy (AES) together with XAS in the tender x-ray regime to study the electronic decay processes following x-ray absorption of aqueous potassium chloride at the K-edges of both \ki~and \cli.
 In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, core-excited states are populated.
@@
 
-The resonant and normal Auger processes are schematically shown on Fig.\ \ref{fg:auger}.
+The resonant and normal Auger spectra of K$^+_{\rm aq}$ and Cl$^-_{\rm aq}$ were measured using a newly operational microjet setup designed for the HAXPES end station of the GALAXIES beamline at the synchrotron radiation facility SOLEIL in France \citep{ceolin13:188,rueff15:175}; for details, see Supplementary Information (SI).
+{\color{red}The spectra are presented on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} as 2D maps, showing the dependence of the kinetic energy of the Auger electron on the incoming photon energy.}
+The investigated Auger processes are schematically shown on Fig.\ \ref{fg:auger}.
 The KL$_{2,3}$L$_{2,3}$ normal Auger decay of aqueous \ki~and \cli~populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
@@
 Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder on the low kinetic-energy side at $E_{\text{kin}} \cong 2965$\,eV, feature A (Fig.\ \ref{fg:2dmap_k}(a)).
-This shoulder is attributed to electron transfer from the solvent water molecules to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) resulting in K$^{2+}$(2p$^{-2}$3d)W$^{-1}$ \citep{ceolin17:263003}.
+This shoulder is attributed to electron transfer from the solvent water molecules to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) resulting in K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}.
 In the case of \cli, there is no experimental evidence of such intense electron transfer processes.
@@
 The pre-edge regions of the XAS spectra of \ki~and \cli~shown in Figs.\ \ref{fg:2dmap_k}(b) and \ref{fg:2dmap_cl}(b) do not show any clear indication of core-excited states due to their lifetime broadening and energetic proximity to the ionization threshold.
-Instead these states can be identified by their resonant Auger features, which disperse with photon energy and thus significantly differ from the normal Auger ones.
-In the 2D map of \cli~(Fig.\ \ref{fg:2dmap_cl}) there are two dispersive resonant Auger features indicated with diagonal dashed lines.
+However, these states can be identified by their resonant Auger features, which disperse with photon energy and thus significantly differ from the normal Auger ones.
+In the 2D map of \cli~(Fig.\ \ref{fg:2dmap_cl}(a)) there are two dispersive resonant Auger features indicated with diagonal dashed lines.
 Both of them have a maximum at $h\nu =  2825.2$\,eV, which is in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments on hydrated Mg and Sr chlorides\citep{sugiura82:681} and metal-chloride complexes \citep{shadle95:2259}.
-These features have $E_{\text{kin}} = 2374.6$ and 2383.4\,eV, respectively, which demonstrates that they are related to the $^1$S and $^1$D main lines.
-In the case of \ki, the dispersive line related to the $^1$S main line cannot be clearly identified due to the presence of strong background.
+The dispersive features have $E_{\text{kin}} = 2374.6$ and 2383.4\,eV relating them to the $^1$S and $^1$D main lines, respectively.
+In the case of \ki, the dispersive line related to the $^1$S main line cannot be clearly identified due to the presence of a strong background.
 Instead two dispersive features related to the $^1$D main line are observed denoted as B and C on Fig.\ \ref{fg:2dmap_k}(a).
@@
 The additional feature C appears at h$\nu = 3611.6$\,eV and $E_{\text{kin}} = 2978.1$\,eV, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.
-The positions of these two core-excited states are close to the energy of the 1s$^{-1}$4p excitation of gas-phase \ki~at 3610.7\,eV \citep{hertlein06:062715}.
+The positions of these two core-excited states are close to the energy of the 1s$^{-1}$4p excitation of gas-phase \ki~-- 3610.7\,eV \citep{hertlein06:062715}.
 
@@
 \includegraphics[scale=0.55]{figures/xas_spectra.eps}
-\caption{XAS spectra of the lowest K-shell resonant transitions in the isolated K$^{+}$ (a) and Cl$^{-}$ (b) ions and their 6-coordinated clusters ((c) and (d)).
+\caption{XAS spectra of the lowest K-shell resonant transitions in the isolated K$^{+}$ (a) and Cl$^{-}$ (b) ions and their 6-coordinated clusters, (c) and (d).
 For comparison with the experiment, the theoretical stick spectra are convolved with a Lorentzian of FWHM 0.74\,eV and 0.62\,eV representing the lifetime broadening of \ki~and \cli \citep{Krause79:329} (dashed lines) and a Voigt profile (solid line) to account for both the lifetime and the experimental broadening (see text).
@@
 
-In order to rationalize the pre-edge region of the experimental XAS spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core-excited states of the isolated \ki~and \cli~ions and their hexa-coordinated clusters (Fig.\ \ref{fg:xas_kcl}).
-The theoretical XAS spectra of the isolated ions show the two dipole-allowed states, 1s$^{-1}$4p and 1s$^{-1}$5p, which are split by 4.3\,eV and 10.8\,eV in \ki~and \cli, respectively.
+In order to rationalize the pre-edge region of the experimental XAS spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core-excited states of the isolated \ki~and \cli~ions and their hexa-coordinated clusters using the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015} (see SI for details).
+The theoretical XAS spectra of the isolated ions (Fig.\ \ref{fg:xas_kcl}(a),(b)) show the two dipole-allowed states, 1s$^{-1}$4p and 1s$^{-1}$5p, which are split by 4.3\,eV and 10.8\,eV in \ki~and \cli, respectively.
 For both ions, the energy positions of the dipole-forbidden 1s$^{-1}$3d states are marked with blue crosses.
@@
 A similar effect was observed in the XAS spectra of microsolvated clusters of Na$^{+}$ and Mg$^{2+}$ \citep{miteva16:16671}.
-Details on the calculations of the XAS spectra are given in the SI.
+%Details on the calculations of the XAS spectra are given in the SI.
 
 Further by comparing the experimental and theoretical XAS spectra, we assume that only the states of the lowest peak in the theoretical XAS spectra are populated in the experiment.
-In the 6-coordinated \ki~cluster the lowest peak in the spectrum contains three states.
-The lowest and highest lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character while the low intensity state in between has a predominantly 1s$^{-1}$3d character.
+In the 6-coordinated \ki~cluster the lowest peak in the spectrum contains three states (Fig.\ \ref{fg:xas_kcl}(c)).
+The lowest- and highest-lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character while the low-intensity state in between has a predominantly 1s$^{-1}$3d character.
 Since the dispersive feature B appears at low excitation energies, we assume that it is produced in the resonant Auger decay of the lowest core-excited states of \ki~of predominantly 1s$^{-1}$4p character.
-Moreover, we can attribute the feature C to the resonant Auger decay of the low intensity dipole-forbidden 1s$^{-1}$3d state.
+Moreover, we can attribute the feature C to the resonant Auger decay of the low-intensity dipole-forbidden 1s$^{-1}$3d state.
 Thus, we explain both the energy splitting of $\sim$400\,meV photon energy of B and C, and the fact that island C has lower intensity than B (Fig.\ \ref{fg:2dmap_k}).
-In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first state -- it has mainly \cli~1s$^{-1}$4p character with some admixture of states of the nearest water molecules.
+In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first state -- it has mainly \cli~1s$^{-1}$4p character with some admixture of states of the nearest water molecules (Fig.\ \ref{fg:xas_kcl}(d)).
 Consequently, we attribute the two dispersive features associated with the $^1$S and $^1$D main lines on the 2D map of \cli~to the resonant Auger decay of this core-excited state.
@@
 
-To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest doublet states of the type K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$.
-These states are the final states of the spectator Auger decay.
-The latter is the predominant decay process for the low-lying core-excited states in argon \citep{ceolin15:022502}, which is isoelectronic to K$^+$ and Cl$^-$.
-The energy positions of the states are adjusted to the kinetic-energy scale of the Auger spectra of both ions such that the lowest 2p$^{-2}$($^1$D)4p states coincide with the maxima of the dipsersive features related to the $^1$D main line.
-The results are shown as bars in Figs.\ \ref{fg:2dmap_k}(c) and \ref{fg:2dmap_cl}(c).
-As can be seen from the bars overlapping the Auger spectrum recorded at h$\nu = 3610.7$\,eV (Fig.\ \ref{fg:2dmap_k}(c)), the lowest 2p$^{-2}$4p states of \ki(H$_2$O)$_6$ are lower in energy by $\sim$5 and 12-13\,eV than two groups of 2p$^{-2}$3d states.
+To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest doublet states of the type K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ at the Configuration Interaction Singles (CIS) level using the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS} (see SI for details).
+These states are the final states of the spectator Auger decay, which is the predominant decay process for the low-lying core-excited states in isoelectronic argon \citep{ceolin15:022502}.
+The energy positions of the states (see bars on Figs.\ \ref{fg:2dmap_k}(c) and \ref{fg:2dmap_cl}(c)) are adjusted to the kinetic-energy scale of the Auger spectra of both ions such that the lowest 2p$^{-2}$($^1$D)4p states coincide with the maxima of the dipsersive features related to the $^1$D main line.
+For \ki(H$_2$O)$_6$ the calculated 2p$^{-2}$4p states are lower in energy by $\sim$5 and 12-13\,eV than two groups of 2p$^{-2}$3d states.
 Thus, the transitions to the group of 2p$^{-2}$3d final states at $E_{\text{kin}}\cong 2975$\,eV are closer to the kinetic energy of island C.
 Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$^{-1}$3d excitation to this group of 2p$^{-2}$3d states.
-The splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states in our calculation is smaller than the splitting between the islands B and C.
+The theoretical splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states is smaller than that between islands B and C.
 This disagreement can be explained with the fact that we consider a single geometry with a fixed number of water molecules in the first solvation shell.
@@
 Another argument supporting the assignment of feature C to the 1s$^{-1}$3d $\rightarrow$ 2p$^{-2}$3d Auger transition is the energy difference between the spectral features A and C.
-Feature A originates from electron transfer processes from water molecules (W) to the doubly core-ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{-1}$.
+Feature A originates from electron transfer processes from water molecules (W) to the doubly core-ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{+}$.
 The lowest ionization potential of liquid water is about 11.16\,eV \cite{winter04:2625} which matches well the observed A-C splitting.
@@
 
-In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (Fig.\ \ref{fg:2dmap_cl}(c)) which correspond to the 2p$^{-2}$($^1$S)4p and 2p$^{-2}$($^1$D)4p final states.
-The splitting between these two groups is in good agreement with the experimentally observed splitting between the dispersive features on the high kinetic energy sides of the $^1$S and $^1$D main peaks.
-Consequently, we assign the dispersive features on Fig.\ \ref{fg:2dmap_cl}(a) to the 1s$^{-1}$4p $\rightarrow$ 2p$^{-2}$($^1$S, $^1$D)4p resonant Auger transitions of Cl$^{-}_{\text{aq}}$.
+In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (Fig.\ \ref{fg:2dmap_cl}(c)) corresponding to the 2p$^{-2}$($^1$S)4p and 2p$^{-2}$($^1$D)4p final states.
+The calculated splitting is in good agreement with the one between the dispersive features on the high kinetic-energy sides of the $^1$S and $^1$D main peaks on Fig.\ \ref{fg:2dmap_cl}(a).
+Consequently, we assign these features to the 1s$^{-1}$4p $\rightarrow$ 2p$^{-2}$($^1$S, $^1$D)4p resonant Auger transitions of Cl$^{-}_{\text{aq}}$.
 
@@
 To estimate the delocalization time of the core-excited electron, $\tau_{\text{CT}}$, at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
-Our analysis, presented in detail in SI, shows that in the case of \cli, $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, i.e.
-$\sim$1\,fs.
+Our analysis, presented in detail in SI, shows that in the case of \cli, $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, i.e.\ $\sim$1\,fs.
 The treatment is more complex in the \ki~case due to the presence of multiple competing processes.
-However, one can expect much less efficient delocalization in \ki~because the lifetime of the K1s core hole is shorter than for chloride (0.9 vs.\ 1\,fs) and, moreover, the core-excited states appear 1.2\,eV below the ionization threshold compared to 0.2\,eV for chloride.
+However, one can expect much less efficient delocalization in \ki~because the core-excited states appear 1.2\,eV below the ionization threshold compared to 0.2\,eV for chloride and, moreover, the lifetime of the K1s core hole is shorter than for chloride (0.9 vs.\ 1\,fs).
 
-In summary, we studied the electronic structure of aqueous solution of KCl at the K-edges of both \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$ by combining XAS and AES in the tender x-ray regime, and {\it ab initio} calculations.
+In summary, we studied the electronic structure of aqueous solution of KCl at the K-edges of both K$^{+}_{\text{aq}}$ and Cl$^{-}_{\text{aq}}$ by combining XAS and AES in the tender x-ray regime, and {\it ab initio} calculations.
 The Auger electron spectra of both ions exhibit features of normal and resonant Auger processes.

### 2018-06-29 master.tex
june 29 (jpcl corrections)
JPCL-corrected version sent to Ralph to shorten the assignment
discussion and expand the delocalization part

@@
 \affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
-\email{tsveta.miteva@upmc.fr}
+\email{miteva.tsveta@gmail.com}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
+\title{The All-Seeing Eye of Resonant Auger Electron Spectroscopy: A Study on Aqueous Solution Using Tender X-Rays}
 %\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}
@@
 \abbreviations{AES,XAS}
-\keywords{Solvated ions, resonant Auger spectroscopy, X-ray absorption spectroscopy}
+\keywords{Solvated ions, Auger electron spectroscopy, x-ray absorption spectroscopy}
 
@@
 
-\includegraphics[scale=0.105]{figures/graphical.png}
+\includegraphics[scale=0.4]{figures/graphical.png}
 %Some journals require a graphical entry for the Table of Contents.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{introduction.tex}
+\input{article_text.tex}
 
-\input{methods.tex}
+%\input{methods.tex}
 
-\input{results.tex}
+%\input{results.tex}
 
-\input{conclusion.tex}
+%\input{conclusion.tex}
 
@@
 \begin{itemize}
-  \item suppinfo.pdf: contains 1) the radial density distributions of the core excited states of the bare ions; 2) partial cross sections  and charge transfer time extracted from the experimental 2D map near the Cl 1s edge.
+  \item suppinfo.pdf: contains 1) a detailed description of the experiment, as well as the {\it ab initio} calculations; 2) an explanation of the post-collision interaction shift observed in the experimental Auger spectra; 3) the radial density distributions of the core excited states of the bare ions; 4) the  partial cross sections and charge transfer time extracted from the experimental 2D map near the Cl1s edge.
 \end{itemize}

### 2018-06-29 suppinfo.tex
june 29 (jpcl corrections)
JPCL-corrected version sent to Ralph to shorten the assignment
discussion and expand the delocalization part

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous solution using tender x-rays}
+\title{The All-Seeing Eye of Resonant Auger Electron Spectroscopy: A Study on Aqueous Solution Using Tender X-Rays}
 
@@
 
-For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}.
+For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}, which is operated at the Synchrotron radiation facility SOLEIL in France.
 A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes motorized manipulator in front of the spectrometer lens.
@@
 The photon energy resolution achieved at 2.8\,keV and 3.6\,keV was about 0.3\,eV and 0.4\,eV, respectively.
-The experimental 2D maps representing the evolution of the KLL Auger spectra in the vicinity of the Cl$^{-}$ and K$^{+}$~K-edges, as a function of the photon energy, are shown in Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} in the main text, respectively.
-The aqueous K$^{+}$~and Cl$^{-}$~1s ionization potentials were measured at h$\nu = 5$\,keV and calibrated on the liquid contribution of the O1s XPS spectrum \cite{winter06:1176}.
+The experimental 2D maps representing the evolution of the KLL Auger spectra in the vicinity of the Cl$^{-}$ and K$^{+}$~K-edges, as a function of the {\color{red}incoming} photon energy, are shown in Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} in the main text.
+{\color{red}They were recorded with a photon energy step of h$\nu = 0.20$ (\ki) and 0.25\,eV (\cli).
+The 2D maps give a visual evidence of the normal and resonant Auger features.
+While the normal Auger features have a constant kinetic energy as the photon energy varies, the resonant Auger ones depend linearly on the photon energy.
+Such two-dimensional Auger spectra have been used to identify electronic state lifetime interferences in the resonant Auger decay \citep{ceolin15:022502,goldsz16:15133}, post-collision interaction effects \citep{guillemin15:012503}, or processes competing with the resonant Auger decay, such as ultrafast dissociation \citep{piancastelli13:2035}.} The aqueous K$^{+}$~and Cl$^{-}$~1s ionization potentials were measured at h$\nu = 5$\,keV and calibrated on the liquid contribution of the O1s XPS spectrum \cite{winter06:1176}.
 The maps were also calibrated using the O1s photoelectron line of liquid water but at photon energies close to the potassium and chloride 1s ionization thresholds.
@@
 
-The theoretical X-ray absorption spectra were computed for the hexa-coordinated clusters K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \ki~and \cli~\citep{Ohtaki93:1157,soper06:180,ma14:1006}.
+The theoretical x-ray absorption spectra were computed for the hexa-coordinated clusters K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$, which can be considered as representatives of the complete first solvation shell of the two ions \ki~and \cli~ \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
 The two structures shown in Fig.\ \ref{fg:xas_kcl} of the main text were optimized at the DFT level of theory using the B3LYP functional and the 6-311++G(2d,2p) basis set \citep{Krishnan80:650,Blaudeau97:5016}.
@@
 This angle was chosen such that the O-K-O angles are around the maxima of the angular distributions obtained from quantum mechanics/molecular mechanics simulations reported in Ref.\ \citep{ma14:1006}.
-Moreover, we fixed the K-O distance to 2.840~\AA, in agreement with the values obtained other theoretical and experimental works \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
+Moreover, we fixed the K-O distance to 2.840~\AA, in agreement with the values obtained in other theoretical and experimental works \citep{Ohtaki93:1157,soper06:180,ma14:1006}.
 
@@
 In our calculations the core space comprises the 1s orbital of K$^{+}$ or Cl$^{-}$, whereas the remaining occupied orbitals are included in the valence space.
-For the calculations of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$.
+For the calculation of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$.
 To account for the lifetime broadening due to the Auger decay of the core-excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of K$^{+}$~and Cl$^{-}$, respectively \citep{Krause79:329}.
 Additionally, we convolved the theoretical spectra with a Gaussian profile to also account for the experimental resolution (see Fig.\ \ref{fg:xas_kcl} in the main text).
-We analyzed the core-excited states by expanding the natural orbitals occupied by the excited electron (singly occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or Cl$^{-}$~ions, $\chi_{nl}$
+We analyzed the core-excited states by expanding the natural orbitals occupied by the excited electron (singly-occupied natural orbitals, SONOs) $\psi_{i}$ of the microsolvated clusters in the basis of SONOs of the bare K$^{+}$ or Cl$^{-}$~ions, $\chi_{\text{nl}}$
 %
 \begin{equation}
-\psi_{i} = \sum_{nl} a^{i}_{nl} \chi_{nl}
+\psi_{i} = \sum_{\text{nl}} a^{i}_{\text{nl}} \chi_{\text{nl}}
 \end{equation}
 %
-where $n$ and $l$ stand for the principal and orbital quantum numbers as described in Ref.\ \citep{miteva16:16671}.
-The expansion coefficients $a^{i}_{nl}$ show the degree of delocalization of the excited electron and the mixing of the core-excited states in the ligand field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl}).
+where n and l stand for the principal and orbital quantum numbers as described in Ref.\ \citep{miteva16:16671}.
+The squares of the expansion coefficients $|a^{i}_{\text{nl}}|^{2}$ show the degree of delocalization of the excited electron and the mixing of the core-excited states in the ligand field created by the surrounding water molecules (see Fig.\ \ref{fg:xas_kcl} of the main text).
 
@@
 The magnitude of the shift is similar for the two ions and constant in the photon energy range of up to about 8\,eV above threshold.
-The PCI shift of isoelectronic atom argon in the gas phase show also a maximum value of 1\,eV, however, it decreases in the first 8 eV above threshold by approximately 0.6\,eV \citep{guillemin15:012503}.
+The PCI shift of the isoelectronic argon in the gas phase shows also a maximum value of 1\,eV, however, it decreases in the first 8 eV above threshold by approximately 0.6\,eV \citep{guillemin15:012503}.
 A possible explanation of the shift observed in our experiment is given in Ref.\ \cite{tchaplyguine07:124314} where it was proposed that it is due to a process of internal ionization, i.e.\ excitation of the photoelectron into the conduction band, followed by normal Auger decay.
@@
 \includegraphics[scale=0.8]{figures/rad_dens_kcl.eps}
-\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$^{-1}$4p, 1s$^{-1}$3d and 1s$^{-1}$5p core excitations in \ki~(lower panel) and \cli~(upper panel).
+\caption{Radial density distributions of the singly-occupied natural orbital (SONO) occupied by the excited electron corresponding to the 1s$^{-1}$4p, 1s$^{-1}$3d and 1s$^{-1}$5p core excitations in \ki~(lower panel) and \cli~(upper panel).
 The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
@@
 
-In the calculated spectrum of \cli~the intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state, contrary to what is observed in \ki.
+In the calculated spectrum of \cli~the intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state, contrary to what is observed in neutral atoms and positively charged ions, like \ki~in our case.
 This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$^{-1}$4p compared to the 1s$^{-1}$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
 In what follows we give a simple explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli.
-In the case of \ki, the excited electron mainly sees a $2/r$ potential.
+In the present case of \ki, the excited electron mainly sees a $Z/r = 2/r$ Coulomb potential (in atomic units).
 In addition, it sees a short range potential originating from the point-like nucleus and the screening electrons.
-The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series.
-However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant.
-As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states, the 1s$^{-1}$4p state in the case of \cli~\citep{buckman94:539}.
+The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series resulting from a Coulomb potential valid for neutral atoms and positively charged ions.
+However, in case of negatively charged ions, such as \cli, the outer electron does not experience a Coulomb potential and the short range potential becomes dominant.
+As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, for example, only a finite number of bound states is present, the 1s$^{-1}$4p state in the case of \cli~\citep{buckman94:539}.
 In contrast to this, the 1s$^{-1}$3d and 1s$^{-1}$5p states are not bound.
+
+\section{Delocalization vs resonant Auger decay}
 
@@
 \includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
-\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}.
+\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}(a) of the main text.
 The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step.
@@
 
-\section{Delocalization vs resonant Auger decay}
-
 In order to estimate the delocalization rate of the core-excited electron at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
-In the case of Cl$^{-}$, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502} i.e., for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl}(a) of the main text were isolated by fitting procedures and their intensity integrated to get the partial electron yield as a function of the photon energy.
+In the case of Cl$^{-}$, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502}, i.e.\ for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl}(a) of the main text were isolated by fitting procedures and their intensity integrated to get the partial electron yield as a function of the photon energy.
 The result is presented on Fig.\ \ref{fg:si_ct_time} in the SI.
-The figure shows that there is a large overlap between the resonant and normal Auger contributions, due to the proximity of the resonance to the ionization potential and due to the very short lifetime of the corresponding states.
+The figure shows that there is a large overlap between the resonant and normal Auger contributions, due to the proximity of the resonance to the ionization threshold and due to the very short lifetime of the corresponding states.
 At the specific photon energy of h$\nu = 2825.2$\,eV, i.e.\ at the maximum of the lowest core excitation 1s$^{-1}$4p, the resonant Auger spectrum exhibits a double-peak structure in the interval E$_{kin} = 2380 - 2385$\,eV (Fig.\ \ref{fg:2dmap_cl}(c) of main text).
-The position of the first peak coincides with the $^1$D main line resulting from normal Auger decay, whereas the second peak at 2383.5\,eV corresponds to the resonant Auger decay to the 2p$^{-2}$($^1$D)4p states.
+The position of the first peak coincides with the $^1$D main line resulting from normal Auger decay, whereas the second peak at 2383.5\,eV corresponds to resonant Auger decay to the 2p$^{-2}$($^1$D)4p states.
 By fitting this double-peak structure with two Voigt functions, we determine the intensity ratio $l/d$ of the localized (2p$^{-2}$4p) and the delocalized (2p$^{-2}$) decay products at a given excitation energy.
@@
 On the low kinetic energy side, the charge transfer processes lead to a very large structure whose shape unfortunately cannot be easily simulated based on known profiles.
-The lifetime of the 1s core hole is shorter for potassium than for chloride (0.9 vs.\ 1\,fs) and, moreover, the core-excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride.
+The core-excited state appears 1.2\,eV below the ionization threshold whereas it is only 0.2\,eV for chloride and, moreover, the lifetime of the 1s core hole is shorter for potassium than for chloride (0.9 vs.\ 1\,fs).
 Therefore, one can expect much less efficient delocalization in K$^{+}_{\text{aq}}$ compared to Cl$^{-}_{\text{aq}}$.

### 2018-07-11 article_text.tex
july 11
corrections following Ralph's new version from beginning of July,
delocalization added, description shortened

@@
-Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanisms of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
-Depending on the photon energy, the absorption of an x-ray photon results in the population of core-excited or core-ionized states.
-The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decays, and it depends on the character of the initially populated states \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}.
-Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes are possible  \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003}.
+Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the
+structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanisms
+of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}. Depending on the photon
+energy, the absorption of an x-ray photon results in the population of core-excited or core-ionized
+states. The relaxation of these highly energetic states involves an ultrafast cascade of
+intraatomic processes, such as radiative and Auger decays, and it depends on the character
+of the initially populated states
+\citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,
+Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}. Furthermore,
+if the initially excited or ionized species is embedded in an environment,
+interatomic processes are possible  \citep{Pokapanich09:7264,Pokapanich11:13430,
+Stumpf16:237,unger17:708,ceolin17:263003}.
 
-%X-ray absorption spectroscopy (XAS) is a powerful tool to study the nearest environment of atoms in gas phase as it probes core-excited states below threshold which are highly sensitive to the surrounding.
-However, for atoms and molecules in liquid or solid phase, these core-excited states overlap significantly in the XAS spectra inhibiting access to the available information {\color{red}(REF)}.
-This drawback can be overcome by detecting the electrons resulting from the subsequent resonant Auger decay and thus using this complementary information to separate the overlapping states \citep{goldsz16:15133}.
-In a liquid jet, this method applied to shallow core holes (like O 1s of the water molecule) mainly provides information from sites close to the liquid-solid interface, due to the short mean free path of the low-kinetic-energy Auger electrons.
-With a recently commissioned setup using tender X-rays \citep{ceolin13:188,rueff15:175} we are now able to reach deeper core levels resulting in much faster Auger electrons, and as a consequence, one can have a significantly deeper look into the liquid.
+%X-ray absorption spectroscopy (XAS) is a powerful tool to study the nearest environment
+%of atoms in gas phase as it probes core-excited states below threshold which are highly
+%sensitive to the surrounding. However, for atoms and molecules in liquid or solid phase,
+%these core-excited states overlap significantly in the XA spectra inhibiting access
+%to the available information {\color{red}(REF)}. This drawback can be overcome by
+%detecting the electrons resulting from the subsequent resonant Auger decay and thus
+%using this complementary information to separate the overlapping states
+%\citep{goldsz16:15133}. In a liquid jet, this method applied to shallow core holes
+%(like O 1s of the water molecule) mainly provides information from sites close to
+%the liquid-solid interface, due to the short mean free path of the low-kinetic-energy
+%Auger electrons. With a recently commissioned setup using tender X-rays
+%\citep{ceolin13:188,rueff15:175} we are now able to reach deeper core levels resulting
+%in much faster Auger electrons, and as a consequence, one can have a significantly
+%deeper look into the liquid.
 
-%X-ray absorption spectroscopy (XAS) applied to gas phase is a powerful tool to describe (de)localized core-excited states associated to a specific atom.
-In condensed phase studies, these core-excited states overlap significantly inhibiting a simple description of the nearest environment of the targeted atom.
-This drawback can be overcome by detecting the electrons resulting from the subsequent resonant Auger decay and by using this complementary information to separate the overlapping states \citep{goldsz16:15133}.
-{\color{red}X-ray absorption spectroscopy (XAS) in the soft x-ray regime is a powerful tool to describe core-excited states of a specific atom and thus to probe its electronic structure and the local environment surrounding it.
-In the tender and hard x-ray regimes, due to the lifetime broadening, these core-excited states overlap significantly inhibiting a simple description of the nearest environment of the targeted atom.
-This drawback can be overcome by detecting the electrons resulting from the subsequent resonant Auger decay and by using this complementary information to separate the overlapping states \citep{foehlisch05:373,goldsz16:15133}.}
-With our recently commissioned microjet setup dedicated to the study of liquids by means of the photoemission technique using tender x-rays \citep{ceolin13:188,rueff15:175}, we are now able to probe much deeper core levels and corresponding fast Auger electrons.
-This allows us to focus our investigations on the liquid bulk by strongly reducing the specific interface contributions, and also to access ultrafast dynamical processes owing to the very short lifetimes of the corresponding core-excited states.
+%X-ray absorption spectroscopy (XAS) applied to gas phase is a powerful tool to
+%describe (de)localized core-excited states associated to a specific atom. In
+%condensed phase studies, these core-excited states overlap significantly
+%inhibiting a simple description of the nearest environment of the targeted
+%atom. This drawback can be overcome by detecting the electrons resulting
+%from the subsequent resonant Auger decay and by using this complementary
+%information to separate the overlapping states \citep{goldsz16:15133}.
+
+X-ray absorption spectroscopy (XAS) in the soft x-ray regime is a powerful tool to describe core-excited states of a specific atom and thus to probe the local environment surrounding the target atom by measuring its influence on the electronic structure of the atom.
+In the tender and hard x-ray regimes, these core-excited states overlap significantly due to the lifetime broadening, rendering an observation of the influence of the environment difficult.
+This challenge can be overcome by detecting the electrons originating from the subsequent resonant Auger decay, which allows one to separate the overlapping states \citep{foehlisch05:373,goldsz16:15133}.
+With our recently commissioned microjet setup dedicated to the study of liquids by electron spectroscopy techniques using tender x-rays \citep{ceolin13:188,rueff15:175}, we can now probe much deeper core levels and corresponding fast Auger electrons.
+This allows us to focus our investigations on the liquid bulk by strongly reducing the specific interface contributions, and also to access ultrafast dynamical processes
+owing to the very short lifetimes of the corresponding core-excited states.
 
@@
 Although the \ki~and \cli~ions are isoelectronic, they have different fingerprints in the resonant Auger spectra.
-We demonstrate that these differences result from different electronic structures of the two ions, thus confirming that the combination of XAS and AES techniques is a sensitive probe of the electronic structure of solutions.
+We demonstrate that these differences result to a large extent from different electronic structures of the two ions, thus confirming that the combination of XAS and AES techniques is a sensitive probe of the electronic structure of solutions.
 
 \begin{figure}
-\includegraphics[scale=0.8]{figures/auger_process.pdf}
-\caption{Schematic representation of the resonant (left) and normal (right) Auger processes of the isoelectronic \ki~and \cli~ions.}
+\includegraphics[scale=0.7]{figures/auger_process.pdf}
+\caption{Schematic representation of the resonant (left) and normal (right) Auger
+processes of the isoelectronic \ki~and \cli~ions.}
 \label{fg:auger}
@@
 The resonant and normal Auger spectra of K$^+_{\rm aq}$ and Cl$^-_{\rm aq}$ were measured using a newly operational microjet setup designed for the HAXPES end station of the GALAXIES beamline at the synchrotron radiation facility SOLEIL in France \citep{ceolin13:188,rueff15:175}; for details, see Supplementary Information (SI).
-{\color{red}The spectra are presented on Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} as 2D maps, showing the dependence of the kinetic energy of the Auger electron on the incoming photon energy.}
-The investigated Auger processes are schematically shown on Fig.\ \ref{fg:auger}.
-The KL$_{2,3}$L$_{2,3}$ normal Auger decay of aqueous \ki~and \cli~populates the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
-The transitions to $^3$P final states are weak since they are forbidden in LS coupling.
-For K$^{+}_{\text{aq}}$ the maxima of the $^1$S and $^1$D Auger lines for a photon energy h$\nu = 3616.0$\,eV are located at kinetic energies $E_{\text{kin}} = 2958.0$\,eV and 2968.5\,eV, respectively (Fig.\ \ref{fg:2dmap_k}(c)).
-For Cl$^{-}_{\text{aq}}$, the lines corresponding to the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at $E_{\text{kin}} = 2373.1$\,eV and 2382.0\,eV for h$\nu = 2830.0$\,eV (Fig.\ \ref{fg:2dmap_cl}(c)).
+{\color{blue} Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} show these photon-energy dependent Auger electron spectra as 2D maps where %the abscissa reprents the Auger energy and the ordinate
+%the photon energy; 
+the Auger intensities are illustrated by a color code.} The investigated Auger processes are schematically presented on Fig.\ \ref{fg:auger}.
+The KL$_{2,3}$L$_{2,3}$ normal Auger decay {\color{blue} leads to the population of the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
+For both, \ki~and \cli~the experimentally observed transitions are to the 2p$^{-2}$($^1$D, $^1$S) final states, {\color{red}whereas the transitions to $^3$P final states are weak since they are forbidden in LS coupling (see Figs.\ \ref{fg:2dmap_k}(a) and  \ref{fg:2dmap_cl}(a)).} In addition, the 2p$^{-2}$($^1$D) main line of \ki~exhibits a low-energy shoulder labeled A whose origin will be discussed below.
 Close to threshold the KL$_{2,3}$L$_{2,3}$ normal Auger lines are asymmetric and also shifted to higher kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
-This is due to post-collision interaction \citep{russek86:911,guillemin15:012503}, which is discussed in more detail in the SI.
+This is due to post-collision interaction \citep{russek86:911,guillemin15:012503} discussed in more detail in the SI.
+}
+
+%of aqueous \ki~and \cli~populates the
+%2p$^{-2}$($^3$P, $^1$D, $^1$S) final states. The transitions to $^3$P final states are
+%weak since they are forbidden in LS coupling. For K$^{+}_{\text{aq}}$ the maxima of
+%the $^1$S and $^1$D Auger lines for a photon energy h$\nu = 3616.0$\,eV are located
+%at kinetic energies $E_{\text{kin}} = 2958.0$\,eV and 2968.5\,eV, respectively
+%(Fig.\ \ref{fg:2dmap_k}(c)). For Cl$^{-}_{\text{aq}}$, the lines corresponding to
+%the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at $E_{\text{kin}} = 2373.1$\,eV
+%and 2382.0\,eV for h$\nu = 2830.0$\,eV (Fig.\ \ref{fg:2dmap_cl}(c)). Close to threshold
+%the KL$_{2,3}$L$_{2,3}$ normal Auger lines are asymmetric and also shifted to higher
+%kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
+%This is due to post-collision interaction \citep{russek86:911,guillemin15:012503},
+%which is discussed in more detail in the SI.
 
@@
 \includegraphics[scale=0.55]{figures/k_2dmap.pdf}
-\caption{(a) 2D map showing the kinetic energy of the electrons emitted in KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous K$^{+}$.
-The features A, B and C are discussed in the text.
-(b) Experimental partial electron yield spectrum of K$^{+}$ obtained after integrating over the kinetic energies of the Auger electrons.
-(c) Auger spectra at photon energies 3610.7\,eV and 3616\,eV.
-The vertical bars in the resonant Auger spectrum measured at 3610.7\,eV indicate the spectator Auger energies of the calculated doublet 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) states of K$^{+}$(H$_2$O)$_6$.}
+\caption{(a) 2D map showing the kinetic energy of the electrons emitted in
+KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous K$^{+}$. The features A, B and C are discussed in the text.
+(b) Experimental partial electron yield spectrum of K$^{+}$ obtained after
+integrating over the kinetic energies of the Auger electrons.
+(c) Auger spectra at photon energies 3610.7\,eV and 3616\,eV. The vertical bars
+in the resonant Auger spectrum measured at 3610.7\,eV indicate the spectator Auger energies of the calculated doublet 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) states of K$^{+}$(H$_2$O)$_6$.}
 \label{fg:2dmap_k}
@@
 
-Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$ by the presence of a large shoulder on the low kinetic-energy side at $E_{\text{kin}} \cong 2965$\,eV, feature A (Fig.\ \ref{fg:2dmap_k}(a)).
-This shoulder is attributed to electron transfer from the solvent water molecules to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) resulting in K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}.
-In the case of \cli, there is no experimental evidence of such intense electron transfer processes.
+%Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$
+%by the presence of a large shoulder on the low kinetic-energy side at
+%$E_{\text{kin}} \cong 2965$\,eV, feature A (Fig.\ \ref{fg:2dmap_k}(a)). This
+%shoulder is attributed to electron transfer from the solvent water molecules
+%to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) resulting in
+%K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}. In the case of \cli, there
+%is no experimental evidence of such intense electron transfer processes.
 
@@
 \includegraphics[scale=0.55]{figures/cl_2dmap.pdf}
-\caption{(a) 2D map showing the kinetic energy of the electrons emitted in KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous Cl$^{-}$. 
-(b) Experimental partial electron yield spectrum of Cl$^{-}$ obtained after integrating over the kinetic energies of the Auger electrons. 
-(c) Auger spectra at photon energies 2825.2\,eV and 2830.0\,eV.
-The vertical bars in the resonant Auger spectrum at 2825.2\,eV indicate the the spectator Auger energies of the calculated doublet 2p$^{-2}$4p states of Cl$^{-}$(H$_2$O)$_6$.}
+\caption{(a) 2D map showing the kinetic energy of the electrons emitted in
+KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the
+K-edge of aqueous Cl$^{-}$. 
+(b) Experimental partial electron yield spectrum of Cl$^{-}$ obtained after
+integrating over the kinetic energies of the Auger electrons. 
+(c) Auger spectra at photon energies 2825.2\,eV and 2830.0\,eV. The vertical
+bars in the resonant Auger spectrum at 2825.2\,eV indicate the the spectator
+Auger energies of the calculated doublet 2p$^{-2}$4p states of Cl$^{-}$(H$_2$O)$_6$.}
 \label{fg:2dmap_cl}
@@
 
-The pre-edge regions of the XAS spectra of \ki~and \cli~shown in Figs.\ \ref{fg:2dmap_k}(b) and \ref{fg:2dmap_cl}(b) do not show any clear indication of core-excited states due to their lifetime broadening and energetic proximity to the ionization threshold.
-However, these states can be identified by their resonant Auger features, which disperse with photon energy and thus significantly differ from the normal Auger ones.
-In the 2D map of \cli~(Fig.\ \ref{fg:2dmap_cl}(a)) there are two dispersive resonant Auger features indicated with diagonal dashed lines.
-Both of them have a maximum at $h\nu =  2825.2$\,eV, which is in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments on hydrated Mg and Sr chlorides\citep{sugiura82:681} and metal-chloride complexes \citep{shadle95:2259}.
-The dispersive features have $E_{\text{kin}} = 2374.6$ and 2383.4\,eV relating them to the $^1$S and $^1$D main lines, respectively.
-In the case of \ki, the dispersive line related to the $^1$S main line cannot be clearly identified due to the presence of a strong background.
-Instead two dispersive features related to the $^1$D main line are observed denoted as B and C on Fig.\ \ref{fg:2dmap_k}(a).
-Feature B exhibits a maximum at h$\nu = 3611.2$\,eV and $E_{\text{kin}} = 2969.2$\,eV.
-The additional feature C appears at h$\nu = 3611.6$\,eV and $E_{\text{kin}} = 2978.1$\,eV, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.
-The positions of these two core-excited states are close to the energy of the 1s$^{-1}$4p excitation of gas-phase \ki~-- 3610.7\,eV \citep{hertlein06:062715}.
+{\color{blue} In the pre-edge regions of the XA spectra of \ki~and \cli~displayed on Figs.\ \ref{fg:2dmap_k}(b) and \ref{fg:2dmap_cl}(b), no core-excited states are visible due to their lifetime broadening and energetic proximity to the ionization threshold.
+These states can, however, be identified by their resonant Auger features, which disperse with photon energy.
+These features are indicated by diagonal dashed lines in Figs.\ \ref{fg:2dmap_k}(a) and \ref{fg:2dmap_cl}(a).
+To identify the Auger transitions producing these features, we performed calculations of the XA spectra and the final Auger states.}
+
+{\color{blue} The XA spectra in the region of the lowest core-excited states of the isolated \ki~and \cli~ions and their hexa-coordinated clusters representing \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$ were calculated with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015} (see SI for details).}
+%In order to rationalize the pre-edge region of the experimental XA spectra
+%and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$,
+%we computed the lowest core-excited states of the isolated \ki~and \cli~ions
+%and their hexa-coordinated clusters using the algebraic diagrammatic
+%construction method for the polarization propagator \citep{sch82:2395}
+%within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038}
+%(CVS-ADC(2)x) as implemented in the Q-Chem package
+%\citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015} (see SI
+%for details). 
+The theoretical XA spectra of the isolated ions (Fig.\ \ref{fg:xas_kcl}(a),(b)) show the two dipole-allowed states, 1s$^{-1}$4p and 1s$^{-1}$5p, which are split by 4.3\,eV and 10.8\,eV in \ki~and \cli, respectively.
+For both ions, the energy position of the dipole-forbidden 1s$^{-1}$3d {\color{blue} state is} marked with blue crosses.
+{\color{blue} Its position relative to the 1s$^{-1}$4p state in \ki~and \cli~is different and as discussed below, this is crucial} for understanding the resonant Auger spectra of the two ions.
+Upon addition of water molecules, the degeneracy of the states is lifted and they interact with other states of the ion or the neighboring water molecules (Fig.\ \ref{fg:xas_kcl}(c),(d)).
+Thus, dipole-forbidden states acquire intensity in the cluster.
+A similar effect was observed in the XA spectra of microsolvated clusters of Na$^{+}$ and Mg$^{2+}$ \citep{miteva16:16671}.
+%
+%
+{\color{blue} In particular, the lowest peak in the XA spectrum of the} 6-coordinated \ki~cluster contains three states (Fig.\ \ref{fg:xas_kcl}(c)).
+The lowest- and highest-lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character while the low-intensity state in between has a predominantly 1s$^{-1}$3d character.
+In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first state -- it has mainly \cli~1s$^{-1}$4p character with some admixture of states of the nearest water molecules (Fig.\ \ref{fg:xas_kcl}(d)).
+
+{\color{blue} We also computed the lowest doublet states of the type K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ representing the final states of the spectator Auger decay, which is the predominant decay process for the low-lying core-excited states in isoelectronic argon \citep{ceolin15:022502}.
+The calculations were performed at the Configuration Interaction Singles (CIS) level using the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS} (see SI for details).} The energy positions of the states (see bars on Figs.\ \ref{fg:2dmap_k}(c) and \ref{fg:2dmap_cl}(c)) are adjusted to the kinetic-energy scale of the Auger spectra of both ions such that the lowest 2p$^{-2}$($^1$D)4p states coincide with the maxima of the dipsersive features related to the $^1$D main line.
+
+%The pre-edge regions of the XA spectra of \ki~and \cli~shown in Figs.\
+%\ref{fg:2dmap_k}(b) and \ref{fg:2dmap_cl}(b) do not show any clear indication
+%of core-excited states due to their lifetime broadening and energetic proximity
+%to the ionization threshold. However, these states can be identified by their
+%resonant Auger features, which disperse with photon energy and thus significantly
+%differ from the normal Auger ones. 
+{\color{blue} In the following we assign the dispersive features on Figs.\ \ref{fg:2dmap_k}(a) and \ref{fg:2dmap_cl}(a).
+In the 2D map of \cli~two dispersive resonant Auger features are visible.} Both of them exhibit a maximum at $h\nu =  2825.2$\,eV, {\color{blue} i.e.\ $\cong 200$ meV below the ionization threshold.
+This value agrees well with the position of the  1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments on hydrated Mg and Sr chlorides \citep{sugiura82:681} and metalchloride complexes \citep{shadle95:2259}.
+Moreover, the maxima in the kinetic energies of these dispersive features are split by $\cong$ 8.5 eV, which is in line with the calculated values for the 2p$^{-2}$($^1$S)4p and 2p$^{-2}$($^1$D)4p final states of $\cong 7$ eV.
+Consequently, we assign these features as originating from the resonant Auger decay of the 1s$^{-1}$4p excitations to the 2p$^{-2}$($^1$S, $^1$D)4p final states.}
+
+%In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two
+%groups of states split by about 7\,eV (Fig.\ \ref{fg:2dmap_cl}(c))
+%corresponding to the 2p$^{-2}$($^1$S)4p and 2p$^{-2}$($^1$D)4p final states.
+%The calculated splitting is in good agreement with the one between the
+%dispersive features on the high kinetic-energy sides of the $^1$S and $^1$D
+%main peaks on Fig.\ \ref{fg:2dmap_cl}(a). Consequently, we assign these
+%features to the 1s$^{-1}$4p $\rightarrow$ 2p$^{-2}$($^1$S, $^1$D)4p resonant
+%Auger transitions of Cl$^{-}_{\text{aq}}$.
+
+%which is
+%in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation
+%determined from Cl K-edge XAS experiments on hydrated Mg and Sr
+%chlorides\citep{sugiura82:681} and metal-chloride complexes \citep{shadle95:2259}.
+%The dispersive features have $E_{\text{kin}} = 2374.6$ and 2383.4\,eV relating
+%them to the $^1$S and $^1$D main lines, respectively.
+
+{\color{blue} The 2D map of \ki shown in Fig.\ \ref{fg:2dmap_k}(a) also displays two dispersive features.
+The line denoted as B exhibits a maximum at h$\nu = 3611.2$\,eV and $E_{\text{kin}} = 2969.2$\,eV, while the line labeled C exhibits a maximum at h$\nu = 3611.6$\,eV and $E_{\text{kin}} = 2978.1$\,eV.
+The observed energy positions relative to the \ki 1s$^{-1}$ threshold in combination with the relative energy position of the 2p$^{-2}$nl states suggest that feature B is a result of resonant Auger decay of the 1s$^{-1}$4p excitation to the 2p$^{-2}(^1$D)4p final state and feature C originates from the 1s$^{-1}$3d $\rightarrow$ 2p$^{-2}(^1$D)3d resonant Auger transition.
+The latter is dipole-forbidden in the isolated ion, which explains the low intensity of feature C.
+%This assignment is supported by the low intensity of the latter feature, which is dipole-forbidden in the isolated ion.
+Another argument in favor of this assignment is the energy difference between the spectral features A and C, which matches well the lowest ionization potential of liquid water of I$_{\rm aq} \cong 11.16$ eV \cite{winter04:2625}.
+Feature A is assigned to a charge transfer from a water molecule W to the 3d orbital of \ki~during the Auger decay, i.e.\ K$^{2+}$(1s$^{-1}$) $\rightarrow$ K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}, so that its energy position should be lower by I$_{\rm aq}$ if we take into account the small energy separation of the 1s $\rightarrow$ 3d excitation from threshold.
+Due to the high intensity of shoulder A no dispersive features related to the 2p$^{-2}(^1$S) parent state are observed in the 2D map of \ki.}
+
+%assigned to K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \cite{}
+%and C assinged to , which matches well the lowest ionization
+%potential of liquid water of $\cong 11.16$ eV \cite{winter04:2625}
+
+%This shoulder is attributed to electron transfer 
+%from the solvent water molecules to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) 
+%resulting in K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}.
+
+%Another argument supporting the assignment of feature C to the 1s$^{-1}$3d
+%$\rightarrow$ 2p$^{-2}$3d Auger transition is the energy difference between
+%the spectral features A and C. Feature A originates from electron transfer
+%processes from water molecules (W) to the doubly core-ionized potassium ion
+%and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{+}$. The lowest ionization
+%potential of liquid water is about 11.16\,eV \cite{winter04:2625} which
+%matches well the observed A-C splitting. Thus, the above energetic arguments
+%corroborate the attribution of island C as originating from resonant Auger
+%decay to the K$^{2+}$ 2p$^{-2}$3d final states.
+
+%In the case of \ki, the
+%dispersive line related to the $^1$S main line cannot be clearly identified due
+%to the presence of a strong background. Instead two dispersive features related
+%to the $^1$D main line are observed denoted as B and C on Fig.\ \ref{fg:2dmap_k}(a).
+%Feature B exhibits a maximum at h$\nu = 3611.2$\,eV and $E_{\text{kin}} = 2969.2$\,eV.
+%The additional feature C appears at h$\nu = 3611.6$\,eV and $E_{\text{kin}} = 2978.1$\,eV,
+%thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in
+%kinetic energy from the maximum of feature B. The positions of these two
+%core-excited states are close to the energy of the 1s$^{-1}$4p excitation of
+%gas-phase \ki~-- 3610.7\,eV \citep{hertlein06:062715}.
 
@@
 \includegraphics[scale=0.55]{figures/xas_spectra.eps}
-\caption{XAS spectra of the lowest K-shell resonant transitions in the isolated K$^{+}$ (a) and Cl$^{-}$ (b) ions and their 6-coordinated clusters, (c) and (d).
-For comparison with the experiment, the theoretical stick spectra are convolved with a Lorentzian of FWHM 0.74\,eV and 0.62\,eV representing the lifetime broadening of \ki~and \cli \citep{Krause79:329} (dashed lines) and a Voigt profile (solid line) to account for both the lifetime and the experimental broadening (see text).
-The colors in the stick spectrum represent the projections of the singly-occupied natural orbitals (SONOs) of the core-excited 6-coordinated clusters on the basis of SONOs belonging to the 1s$^{-1}$3d, 1s$^{-1}$4p, and 1s$^{-1}$5p states of the isolated ions.
-The remaining contributions from higher-lying atomic core excitations or from excitations to the solvent molecules are depicted as grey sticks.
-The theoretical XAS spectra of both \ki~and \cli~were shifted to higher photon energies such that the energies of the lowest core-excited states correspond to the experimentally determined ones.
+\caption{XA spectra of the lowest K-shell resonant transitions in the isolated
+K$^{+}$ (a) and Cl$^{-}$ (b) ions and their 6-coordinated clusters, (c) and (d).
+For comparison with the experiment, the theoretical stick spectra are convolved
+with a Lorentzian of FWHM 0.74\,eV and 0.62\,eV representing the lifetime
+broadening of \ki~and \cli \citep{Krause79:329} (dashed lines) and a Voigt
+profile (solid line) to account for both the lifetime and the experimental
+broadening (see text). The colors in the stick spectrum represent the projections
+of the singly-occupied natural orbitals (SONOs) of the core-excited 6-coordinated
+clusters on the basis of SONOs belonging to the 1s$^{-1}$3d, 1s$^{-1}$4p, and
+1s$^{-1}$5p states of the isolated ions. The remaining contributions from
+higher-lying atomic core excitations or from excitations to the solvent molecules
+are depicted as grey sticks. The theoretical XA spectra of both \ki~and \cli~were
+shifted to higher photon energies such that the energies of the lowest core-excited states correspond to the experimentally determined ones.
 The experimental ionization thresholds are depicted as grey boxes.}
@@
 
-In order to rationalize the pre-edge region of the experimental XAS spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core-excited states of the isolated \ki~and \cli~ions and their hexa-coordinated clusters using the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015} (see SI for details).
-The theoretical XAS spectra of the isolated ions (Fig.\ \ref{fg:xas_kcl}(a),(b)) show the two dipole-allowed states, 1s$^{-1}$4p and 1s$^{-1}$5p, which are split by 4.3\,eV and 10.8\,eV in \ki~and \cli, respectively.
-For both ions, the energy positions of the dipole-forbidden 1s$^{-1}$3d states are marked with blue crosses.
-It is noteworthy that the positions of the 1s$^{-1}$4p and 1s$^{-1}$3d states are inverted in \ki~and \cli, and moreover, the splitting between these states is about two times smaller in \ki.
-These findings are crucial for understanding the Auger spectra of the two ions as shown below.
-Upon addition of water molecules, the degeneracy of the states is lifted and they interact with other states of the ion or the neighboring water molecules (Fig.\ \ref{fg:xas_kcl}(c),(d)).
-Thus, dipole-forbidden states acquire intensity in the cluster.
-A similar effect was observed in the XAS spectra of microsolvated clusters of Na$^{+}$ and Mg$^{2+}$ \citep{miteva16:16671}.
-%Details on the calculations of the XAS spectra are given in the SI.
+{\color{blue} We note that the resonances of K$^{+}_{\text{aq}}$ and Cl$^{-}_{\text{aq}}$ calculated to be above the corresponding ionization threshold, (Fig.\ \ref{fg:xas_kcl}(c,d)), are not experimentally observed.
+This might be due to the fact that the corresponding resonant Auger spectra are energetically too close to the more intense normal Auger main lines.}
 
-Further by comparing the experimental and theoretical XAS spectra, we assume that only the states of the lowest peak in the theoretical XAS spectra are populated in the experiment.
-In the 6-coordinated \ki~cluster the lowest peak in the spectrum contains three states (Fig.\ \ref{fg:xas_kcl}(c)).
-The lowest- and highest-lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character while the low-intensity state in between has a predominantly 1s$^{-1}$3d character.
-Since the dispersive feature B appears at low excitation energies, we assume that it is produced in the resonant Auger decay of the lowest core-excited states of \ki~of predominantly 1s$^{-1}$4p character.
-Moreover, we can attribute the feature C to the resonant Auger decay of the low-intensity dipole-forbidden 1s$^{-1}$3d state.
-Thus, we explain both the energy splitting of $\sim$400\,meV photon energy of B and C, and the fact that island C has lower intensity than B (Fig.\ \ref{fg:2dmap_k}).
-In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first state -- it has mainly \cli~1s$^{-1}$4p character with some admixture of states of the nearest water molecules (Fig.\ \ref{fg:xas_kcl}(d)).
-Consequently, we attribute the two dispersive features associated with the $^1$S and $^1$D main lines on the 2D map of \cli~to the resonant Auger decay of this core-excited state.
+%Further by comparing the experimental and theoretical XA spectra, we
+%assume that only the states of the lowest peak in the theoretical XAS
+%spectra are populated in the experiment.
+
+%In the 6-coordinated \ki~cluster
+%the lowest peak in the spectrum contains three states (Fig.\
+%\ref{fg:xas_kcl}(c)). The lowest- and highest-lying states are split
+%by approximately 0.5\,eV and they have mixed 4p and 5p character while
+%the low-intensity state in between has a predominantly 1s$^{-1}$3d
+%character. 
+%Since the dispersive feature B appears at low excitation
+%energies, we assume that it is produced in the resonant Auger decay
+%of the lowest core-excited states of \ki~of predominantly 1s$^{-1}$4p
+%character. Moreover, we can attribute the feature C to the resonant
+%Auger decay of the low-intensity dipole-forbidden 1s$^{-1}$3d state.
+%Thus, we explain both the energy splitting of $\sim$400\,meV photon
+%energy of B and C, and the fact that island C has lower intensity than
+%B (Fig.\ \ref{fg:2dmap_k}). 
+%In the hexa-coordinated cluster of \cli,
+%the solvent molecules have little influence on the position and character
+%of the first state -- it has mainly \cli~1s$^{-1}$4p character with some
+%admixture of states of the nearest water molecules (Fig.\
+%\ref{fg:xas_kcl}(d)). 
+%Consequently, we attribute the two dispersive
+%features associated with the $^1$S and $^1$D main lines on the 2D map of
+%\cli~to the resonant Auger decay of this core-excited state.
 %involving mostly the 4p orbitals of chloride.
 
-To fully characterize the dispersive features on the experimental 2D maps, we also computed the lowest doublet states of the type K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ at the Configuration Interaction Singles (CIS) level using the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS} (see SI for details).
-These states are the final states of the spectator Auger decay, which is the predominant decay process for the low-lying core-excited states in isoelectronic argon \citep{ceolin15:022502}.
-The energy positions of the states (see bars on Figs.\ \ref{fg:2dmap_k}(c) and \ref{fg:2dmap_cl}(c)) are adjusted to the kinetic-energy scale of the Auger spectra of both ions such that the lowest 2p$^{-2}$($^1$D)4p states coincide with the maxima of the dipsersive features related to the $^1$D main line.
-For \ki(H$_2$O)$_6$ the calculated 2p$^{-2}$4p states are lower in energy by $\sim$5 and 12-13\,eV than two groups of 2p$^{-2}$3d states.
-Thus, the transitions to the group of 2p$^{-2}$3d final states at $E_{\text{kin}}\cong 2975$\,eV are closer to the kinetic energy of island C.
-Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$^{-1}$3d excitation to this group of 2p$^{-2}$3d states.
-The theoretical splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states is smaller than that between islands B and C.
-This disagreement can be explained with the fact that we consider a single geometry with a fixed number of water molecules in the first solvation shell.
-Moreover, we do not theoretically account for the effect of distant solvent shells.
-We assume that the transitions to the 2p$^{-2}$3d states with kinetic energies between 2982 and 2983\,eV have negligible Auger rates since no additional experimental features are observed.
+%For \ki(H$_2$O)$_6$
+%the calculated 2p$^{-2}$4p states are lower in energy by $\sim$5 and
+%12-13\,eV than two groups of 2p$^{-2}$3d states. Thus, the transitions to
+%the group of 2p$^{-2}$3d final states at $E_{\text{kin}}\cong 2975$\,eV are
+%closer to the kinetic energy of island C. Consequently, we attribute this
+%dispersive feature as originating from the resonant Auger decay of the
+%1s$^{-1}$3d excitation to this group of 2p$^{-2}$3d states. The theoretical
+%splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states is smaller than
+%that between islands B and C. This disagreement can be explained with the
+%fact that we consider a single geometry with a fixed number of water
+%molecules in the first solvation shell. Moreover, we do not theoretically
+%account for the effect of distant solvent shells. We assume that the
+%transitions to the 2p$^{-2}$3d states with kinetic energies between 2982
+%and 2983\,eV have negligible Auger rates since no additional experimental
+%features are observed.
 
-Another argument supporting the assignment of feature C to the 1s$^{-1}$3d $\rightarrow$ 2p$^{-2}$3d Auger transition is the energy difference between the spectral features A and C.
-Feature A originates from electron transfer processes from water molecules (W) to the doubly core-ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{+}$.
-The lowest ionization potential of liquid water is about 11.16\,eV \cite{winter04:2625} which matches well the observed A-C splitting.
-Thus, the above energetic arguments corroborate the attribution of island C as originating from resonant Auger decay to the K$^{2+}$ 2p$^{-2}$3d final states.
-
-In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (Fig.\ \ref{fg:2dmap_cl}(c)) corresponding to the 2p$^{-2}$($^1$S)4p and 2p$^{-2}$($^1$D)4p final states.
-The calculated splitting is in good agreement with the one between the dispersive features on the high kinetic-energy sides of the $^1$S and $^1$D main peaks on Fig.\ \ref{fg:2dmap_cl}(a).
-Consequently, we assign these features to the 1s$^{-1}$4p $\rightarrow$ 2p$^{-2}$($^1$S, $^1$D)4p resonant Auger transitions of Cl$^{-}_{\text{aq}}$.
-
-The delocalization of core-excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay \citep{Nordlund07:217406,ottosson12:1}.
+%The delocalization of core-excited electrons in aqueous solutions is ultrafast and as such it competes with the resonant Auger decay \citep{Nordlund07:217406,ottosson12:1}.
 To estimate the delocalization time of the core-excited electron, $\tau_{\text{CT}}$, at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
@@
 However, one can expect much less efficient delocalization in \ki~because the core-excited states appear 1.2\,eV below the ionization threshold compared to 0.2\,eV for chloride and, moreover, the lifetime of the K1s core hole is shorter than for chloride (0.9 vs.\ 1\,fs).
+
+{\color{red}
+An important aspect of the study of core-excited states in aqueous solutions is the possibility of ultrafast delocalization of the core-excited electron which competes with the resonant Auger decay \citep{Nordlund07:217406,ottosson12:1}.
+The photon-energy dependent Auger spectra contain information about the delocalization time thus providing a convenient alternative to the more challenging time-domain experiments in the (sub?)femtosecond regime.
+To estimate the photon-energy dependent delocalization time of the core-excited electron, $\tau_{\text{CT}} (E_{\text{ph}})$, at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+Within this method, $\tau_{\text{CT}} (E_{\text{ph}})$ can be determined from the lifetime of the core hole $\tau_{\text{c}}$ and the ratio of the intensities of the normal ($d$) and resonant ($l$) Auger peaks according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l(E_{\text{ph}})/d(E_{\text{ph}})$ \citep{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+In the case of Cl$^{-}$, we performed the same data treatment as in Ref.\ \cite{ceolin15:022502} to extract the intensities $l(E_{\text{ph}})$ and $d(E_{\text{ph}})$ as a function of the photon energy (see Fig.\ \ref{fg:si_ct_time} in the SI).
+% Due to the proximity of the resonance to the ionization threshold and due to the very short lifetime of the corresponding states, there is a large overlap between the resonant and normal Auger contributions.
+At the specific photon energy of h$\nu = 2825.2$\,eV, i.e.\ at the maximum of the lowest core excitation 1s$^{-1}$4p, $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, $\cong$1\,fs.
+This is manifested as a double-peak structure in the resonant Auger spectrum in the interval E$_{kin} = 2380 - 2385$\,eV (Fig.\ \ref{fg:2dmap_cl}(c)).
+The position of the first peak coincides with the $^1$D main line resulting from normal Auger decay, whereas the second peak at 2383.5\,eV corresponds to resonant Auger decay to the 2p$^{-2}$($^1$D)4p states.
+The fast delocalization in this case is a result of the fact that the energy splitting between the Cl$^{-}$~(1s$^{-1}$4p) resonance and the ionization threshold is 0.2\,eV, and thus, smaller than the lifetime broadening of 0.62\,eV \citep{ceolin17:263003}.
+
+For potassium, a comparable data treatment is more complicated due to the presence of multiple simultaneous processes, namely, normal and resonant Auger decay, as well as charge transfer from solvent and PCI effect.
+To extract the intensity of each component from the 2D map (Fig.\ \ref{fg:2dmap_k}(a)), one needs the spectral fingerprints of each process to be separated.
+As can be seen, this is hardly possible especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
+However, one can expect much less efficient delocalization in \ki~compared to \cli~because the core-excited states appear 1.2\,eV below the ionization threshold compared to 0.2\,eV for chloride and, moreover, because the lifetime of the K1s core hole is shorter than that of chloride (0.9 vs.\ 1\,fs).}
 

### 2018-07-11 suppinfo.tex
july 11
corrections following Ralph's new version from beginning of July,
delocalization added, description shortened

@@
 In our calculations the core space comprises the 1s orbital of K$^{+}$ or Cl$^{-}$, whereas the remaining occupied orbitals are included in the valence space.
-For the calculation of the XAS spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$.
+For the calculation of the XA spectra we used the C$_2$ point group in the case of K$^{+}$(H$_2$O)$_6$ and Cl$^{-}$(H$_2$O)$_6$.
 To account for the lifetime broadening due to the Auger decay of the core-excited states, we convolved the theoretical spectra with a Lorentzian function of FWHM 0.74\,eV and 0.62\,eV in the case of K$^{+}$~and Cl$^{-}$, respectively \citep{Krause79:329}.
@@
 \end{figure}
-
-In order to estimate the delocalization rate of the core-excited electron at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+%
+%
+%In order to estimate the delocalization rate of the core-excited electron at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
 In the case of Cl$^{-}$, it was possible to perform the same data treatment as in Ref.\ \cite{ceolin15:022502}, i.e.\ for each photon energy step, all components of the 2D map shown in Fig.\ \ref{fg:2dmap_cl}(a) of the main text were isolated by fitting procedures and their intensity integrated to get the partial electron yield as a function of the photon energy.
@@
 The fast delocalization in this case is a result of the fact that the energy splitting between the Cl$^{-}$~(1s$^{-1}$4p) resonance and the ionization threshold is 0.2\,eV, and thus, smaller than the lifetime broadening of 0.62\,eV \citep{ceolin17:263003}.
-
-For potassium, a comparable data treatment is more complicated due to the presence of multiple simultaneous processes, namely, normal and resonant Auger decay, as well as charge transfer from solvent.
+%
+%
+%For potassium, a comparable data treatment is more complicated due to the presence of multiple simultaneous processes, namely, normal and resonant Auger decay, as well as charge transfer from solvent.
 To extract the intensity of each component from the 2D map shown in Fig.\ \ref{fg:2dmap_k}(a) of the main text, one needs the spectral fingerprints of each process to be separated.

### 2018-07-16 abstract.tex
july 12

@@
 In this work for the first time we use a combination of these methods in the tender x-ray regime.
-This allowed us to address electronic transitions from deep core levels and to probe environmental effects, specifically in the bulk of the solution since the created energetic Auger electrons possess large mean free paths.
+This allowed us to address electronic transitions from deep core levels, to probe environmental effects, specifically in the bulk of the solution since the created energetic Auger electrons possess large mean free paths, {\color{red}and moreover, to obtain dynamical information about the ultrafast delocalization of the core-excited electron}.
 In the considered exemplary aqueous KCl solution the solvated isoelectronic \ki~and \cli~ions exhibit notably different Auger electron spectra as a function of the photon energy.

### 2018-07-16 article_text.tex
july 12

@@
-Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the
-structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanisms
-of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}. Depending on the photon
-energy, the absorption of an x-ray photon results in the population of core-excited or core-ionized
-states. The relaxation of these highly energetic states involves an ultrafast cascade of
-intraatomic processes, such as radiative and Auger decays, and it depends on the character
-of the initially populated states
-\citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,
-Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}. Furthermore,
-if the initially excited or ionized species is embedded in an environment,
-interatomic processes are possible  \citep{Pokapanich09:7264,Pokapanich11:13430,
-Stumpf16:237,unger17:708,ceolin17:263003}.
+Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanisms of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}.
+Depending on the photon energy, the absorption of an x-ray photon results in the population of core-excited or core-ionized states.
+The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decays, and it depends on the character of the initially populated states \citep{stoychev08:074307,Demekhin08:043421,Demekhin09:104303,Ouchi11:053415,Miteva14:164303,travnikova16:213001,Gokhberg14:661,Trinter14:664}.
+Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes are possible \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003}.
 
-%X-ray absorption spectroscopy (XAS) is a powerful tool to study the nearest environment
-%of atoms in gas phase as it probes core-excited states below threshold which are highly
-%sensitive to the surrounding. However, for atoms and molecules in liquid or solid phase,
-%these core-excited states overlap significantly in the XA spectra inhibiting access
-%to the available information {\color{red}(REF)}. This drawback can be overcome by
-%detecting the electrons resulting from the subsequent resonant Auger decay and thus
-%using this complementary information to separate the overlapping states
-%\citep{goldsz16:15133}. In a liquid jet, this method applied to shallow core holes
-%(like O 1s of the water molecule) mainly provides information from sites close to
-%the liquid-solid interface, due to the short mean free path of the low-kinetic-energy
-%Auger electrons. With a recently commissioned setup using tender X-rays
-%\citep{ceolin13:188,rueff15:175} we are now able to reach deeper core levels resulting
-%in much faster Auger electrons, and as a consequence, one can have a significantly
-%deeper look into the liquid.
-
-%X-ray absorption spectroscopy (XAS) applied to gas phase is a powerful tool to
-%describe (de)localized core-excited states associated to a specific atom. In
-%condensed phase studies, these core-excited states overlap significantly
-%inhibiting a simple description of the nearest environment of the targeted
-%atom. This drawback can be overcome by detecting the electrons resulting
-%from the subsequent resonant Auger decay and by using this complementary
-%information to separate the overlapping states \citep{goldsz16:15133}.
-
-X-ray absorption spectroscopy (XAS) in the soft x-ray regime is a powerful tool to describe core-excited states of a specific atom and thus to probe the local environment surrounding the target atom by measuring its influence on the electronic structure of the atom.
-In the tender and hard x-ray regimes, these core-excited states overlap significantly due to the lifetime broadening, rendering an observation of the influence of the environment difficult.
+X-ray absorption spectroscopy (XAS) in the soft x-ray regime is a powerful tool to describe core-excited states of a specific atom and thus to probe the local environment surrounding the target atom by measuring its influence on the electronic structure.
+In the tender and hard x-ray regimes, these core-excited states overlap significantly due to the lifetime broadening, rendering studies on the influence of the environment difficult.
 This challenge can be overcome by detecting the electrons originating from the subsequent resonant Auger decay, which allows one to separate the overlapping states \citep{foehlisch05:373,goldsz16:15133}.
@@
 
-In this work we combine Auger electron spectroscopy (AES) together with XAS in the tender x-ray regime to study the electronic decay processes following x-ray absorption of aqueous potassium chloride at the K-edges of both \ki~and \cli.
+In this work we combine Auger electron spectroscopy (AES) together with XAS in the tender x-ray regime to study the electronic decay processes following x-ray absorption of aqueous potassium chloride at the K-edges of both \ki~and \cli~(schematically presented in Fig.\ \ref{fg:auger}).
 In particular, we demonstrate experimentally that at photon energies below the K-edges of the two ions, core-excited states are populated.
 These states undergo resonant Auger decay within less than 1\,fs \citep{ceolin17:263003}.
-Although the \ki~and \cli~ions are isoelectronic, they have different fingerprints in the resonant Auger spectra.
-We demonstrate that these differences result to a large extent from different electronic structures of the two ions, thus confirming that the combination of XAS and AES techniques is a sensitive probe of the electronic structure of solutions.
+{\color{red}In both ions, there is a competition between resonant Auger decay and delocalization of the excited electron.
+Using the core-hole clock method we show that in \ki~delocalization at the pre-edge is slow, whereas in the case of \cli~the delocalization time is of the same order as that of the resonant Auger process.} Although the \ki~and \cli~ions are isoelectronic, they have different fingerprints in the resonant Auger spectra.
+Our analysis reveals that these differences result to a large extent from different electronic structures of the two ions, thus confirming that the combination of XAS and AES techniques is a sensitive probe of the electronic structure of solutions.
 
@@
 
-The resonant and normal Auger spectra of K$^+_{\rm aq}$ and Cl$^-_{\rm aq}$ were measured using a newly operational microjet setup designed for the HAXPES end station of the GALAXIES beamline at the synchrotron radiation facility SOLEIL in France \citep{ceolin13:188,rueff15:175}; for details, see Supplementary Information (SI).
-{\color{blue} Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} show these photon-energy dependent Auger electron spectra as 2D maps where %the abscissa reprents the Auger energy and the ordinate
-%the photon energy; 
-the Auger intensities are illustrated by a color code.} The investigated Auger processes are schematically presented on Fig.\ \ref{fg:auger}.
-The KL$_{2,3}$L$_{2,3}$ normal Auger decay {\color{blue} leads to the population of the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
-For both, \ki~and \cli~the experimentally observed transitions are to the 2p$^{-2}$($^1$D, $^1$S) final states, {\color{red}whereas the transitions to $^3$P final states are weak since they are forbidden in LS coupling (see Figs.\ \ref{fg:2dmap_k}(a) and  \ref{fg:2dmap_cl}(a)).} In addition, the 2p$^{-2}$($^1$D) main line of \ki~exhibits a low-energy shoulder labeled A whose origin will be discussed below.
-Close to threshold the KL$_{2,3}$L$_{2,3}$ normal Auger lines are asymmetric and also shifted to higher kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
+{\color{blue}
+The photon-energy dependent resonant and normal Auger spectra of K$^+_{\rm aq}$ and Cl$^-_{\rm aq}$ are shown in Figs.\ \ref{fg:2dmap_k} and \ref{fg:2dmap_cl} as 2D maps where the Auger intensities are illustrated by a color code.
+These spectra were measured using a newly operational microjet setup designed for the HAXPES end station of the GALAXIES beamline at the synchrotron radiation facility SOLEIL in France \citep{ceolin13:188,rueff15:175}; for details, see Supplementary Information (SI).
+The KL$_{2,3}$L$_{2,3}$ normal Auger decay leads to the population of the 2p$^{-2}$($^3$P, $^1$D, $^1$S) final states.
+For both, \ki~and \cli~the experimentally observed transitions are to the 2p$^{-2}$($^1$D, $^1$S) final states, whereas the transitions to $^3$P final states are weak since they are forbidden in LS coupling (see Figs.\ \ref{fg:2dmap_k}(a) and  \ref{fg:2dmap_cl}(a)).
+In addition, the 2p$^{-2}$($^1$D) main line of \ki~exhibits a low-energy shoulder labeled A whose origin will be discussed below.} Close to threshold the KL$_{2,3}$L$_{2,3}$ normal Auger lines are asymmetric (see Figs.\ \ref{fg:2dmap_k}(c) and \ref{fg:2dmap_cl}(c)) and also shifted to higher kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
 This is due to post-collision interaction \citep{russek86:911,guillemin15:012503} discussed in more detail in the SI.
-}
-
-%of aqueous \ki~and \cli~populates the
-%2p$^{-2}$($^3$P, $^1$D, $^1$S) final states. The transitions to $^3$P final states are
-%weak since they are forbidden in LS coupling. For K$^{+}_{\text{aq}}$ the maxima of
-%the $^1$S and $^1$D Auger lines for a photon energy h$\nu = 3616.0$\,eV are located
-%at kinetic energies $E_{\text{kin}} = 2958.0$\,eV and 2968.5\,eV, respectively
-%(Fig.\ \ref{fg:2dmap_k}(c)). For Cl$^{-}_{\text{aq}}$, the lines corresponding to
-%the Cl$^{+}$ 2p$^{-2}$($^1$S) and ($^1$D) states are located at $E_{\text{kin}} = 2373.1$\,eV
-%and 2382.0\,eV for h$\nu = 2830.0$\,eV (Fig.\ \ref{fg:2dmap_cl}(c)). Close to threshold
-%the KL$_{2,3}$L$_{2,3}$ normal Auger lines are asymmetric and also shifted to higher
-%kinetic energies as compared to the spectra reported in \citep{ceolin17:263003}.
-%This is due to post-collision interaction \citep{russek86:911,guillemin15:012503},
-%which is discussed in more detail in the SI.
 
@@
 \includegraphics[scale=0.55]{figures/k_2dmap.pdf}
-\caption{(a) 2D map showing the kinetic energy of the electrons emitted in
-KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous K$^{+}$. The features A, B and C are discussed in the text.
-(b) Experimental partial electron yield spectrum of K$^{+}$ obtained after
-integrating over the kinetic energies of the Auger electrons.
-(c) Auger spectra at photon energies 3610.7\,eV and 3616\,eV. The vertical bars
-in the resonant Auger spectrum measured at 3610.7\,eV indicate the spectator Auger energies of the calculated doublet 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) states of K$^{+}$(H$_2$O)$_6$.}
+\caption{(a) 2D map showing the kinetic energy of the electrons emitted in KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous K$^{+}$.
+The features A, B and C are discussed in the text.
+(b) Experimental partial electron yield spectrum of K$^{+}$ obtained after integrating over the kinetic energies of the Auger electrons.
+(c) Auger spectra at photon energies 3610.7\,eV and 3616\,eV.
+The vertical bars in the resonant Auger spectrum measured at 3610.7\,eV indicate the spectator Auger energies of the calculated doublet 2p$^{-2}$ 3d (blue) and 2p$^{-2}$4p (red) states of K$^{+}$(H$_2$O)$_6$.}
 \label{fg:2dmap_k}
 \end{figure}
-
-%Finally, the normal Auger $^1$D main line of K$^{+}$ differs from that of Cl$^{-}$
-%by the presence of a large shoulder on the low kinetic-energy side at
-%$E_{\text{kin}} \cong 2965$\,eV, feature A (Fig.\ \ref{fg:2dmap_k}(a)). This
-%shoulder is attributed to electron transfer from the solvent water molecules
-%to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) resulting in
-%K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}. In the case of \cli, there
-%is no experimental evidence of such intense electron transfer processes.
 
@@
 \includegraphics[scale=0.55]{figures/cl_2dmap.pdf}
-\caption{(a) 2D map showing the kinetic energy of the electrons emitted in
-KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the
-K-edge of aqueous Cl$^{-}$. 
-(b) Experimental partial electron yield spectrum of Cl$^{-}$ obtained after
-integrating over the kinetic energies of the Auger electrons. 
-(c) Auger spectra at photon energies 2825.2\,eV and 2830.0\,eV. The vertical
-bars in the resonant Auger spectrum at 2825.2\,eV indicate the the spectator
-Auger energies of the calculated doublet 2p$^{-2}$4p states of Cl$^{-}$(H$_2$O)$_6$.}
+\caption{(a) 2D map showing the kinetic energy of the electrons emitted in KL$_{2,3}$L$_{2,3}$ Auger decay vs the photon energy in the vicinity of the K-edge of aqueous Cl$^{-}$. 
+(b) Experimental partial electron yield spectrum of Cl$^{-}$ obtained after integrating over the kinetic energies of the Auger electrons. 
+(c) Auger spectra at photon energies 2825.2\,eV and 2830.0\,eV.
+The vertical bars in the resonant Auger spectrum at 2825.2\,eV indicate the the spectator Auger energies of the calculated doublet 2p$^{-2}$4p states of Cl$^{-}$(H$_2$O)$_6$.}
 \label{fg:2dmap_cl}
@@
 These features are indicated by diagonal dashed lines in Figs.\ \ref{fg:2dmap_k}(a) and \ref{fg:2dmap_cl}(a).
-To identify the Auger transitions producing these features, we performed calculations of the XA spectra and the final Auger states.}
+To assign these features, we calculated the XA spectra, representing the initial states, and the final states of the Auger process.}
 
-{\color{blue} The XA spectra in the region of the lowest core-excited states of the isolated \ki~and \cli~ions and their hexa-coordinated clusters representing \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$ were calculated with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015} (see SI for details).}
-%In order to rationalize the pre-edge region of the experimental XA spectra
-%and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$,
-%we computed the lowest core-excited states of the isolated \ki~and \cli~ions
-%and their hexa-coordinated clusters using the algebraic diagrammatic
-%construction method for the polarization propagator \citep{sch82:2395}
-%within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038}
-%(CVS-ADC(2)x) as implemented in the Q-Chem package
-%\citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015} (see SI
-%for details). 
+{\color{blue} The XA spectra in the region of the lowest core-excited states of isolated \ki~and \cli~and their hexa-coordinated clusters representing \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$ were calculated with the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015} (see SI for details).}
+%In order to rationalize the pre-edge region of the experimental XA spectra and the differences in the AES spectra of \ki$_{\text{aq}}$ and \cli$_{\text{aq}}$, we computed the lowest core-excited states of the isolated \ki~and \cli~ions and their hexa-coordinated clusters using the algebraic diagrammatic construction method for the polarization propagator \citep{sch82:2395} within the core-valence separation approximation \citep{bar85:867,ced80:206,ced81:1038} (CVS-ADC(2)x) as implemented in the Q-Chem package \citep{Wenzel14:1900,Wenzel14:4583,Wormit14:774,QChem2015} (see SI for details).
 The theoretical XA spectra of the isolated ions (Fig.\ \ref{fg:xas_kcl}(a),(b)) show the two dipole-allowed states, 1s$^{-1}$4p and 1s$^{-1}$5p, which are split by 4.3\,eV and 10.8\,eV in \ki~and \cli, respectively.
-For both ions, the energy position of the dipole-forbidden 1s$^{-1}$3d {\color{blue} state is} marked with blue crosses.
-{\color{blue} Its position relative to the 1s$^{-1}$4p state in \ki~and \cli~is different and as discussed below, this is crucial} for understanding the resonant Auger spectra of the two ions.
+{\color{blue}The excitation energies of the dipole-forbidden 1s$^{-1}$3d states are marked with blue crosses.
+Their positions relative to the 1s$^{-1}$4p states in \ki~and \cli~is different and as discussed below, this is important} for understanding the resonant Auger features of \ki.
 Upon addition of water molecules, the degeneracy of the states is lifted and they interact with other states of the ion or the neighboring water molecules (Fig.\ \ref{fg:xas_kcl}(c),(d)).
@@
 
-{\color{blue} We also computed the lowest doublet states of the type K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ representing the final states of the spectator Auger decay, which is the predominant decay process for the low-lying core-excited states in isoelectronic argon \citep{ceolin15:022502}.
-The calculations were performed at the Configuration Interaction Singles (CIS) level using the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS} (see SI for details).} The energy positions of the states (see bars on Figs.\ \ref{fg:2dmap_k}(c) and \ref{fg:2dmap_cl}(c)) are adjusted to the kinetic-energy scale of the Auger spectra of both ions such that the lowest 2p$^{-2}$($^1$D)4p states coincide with the maxima of the dipsersive features related to the $^1$D main line.
+{\color{blue} We also computed the lowest doublet states of the type K$^{2+}$[2p$^{-2}$nl](H$_2$O)$_6$ and Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$.
+They represent the final states of the spectator Auger decay, which is the predominant decay process for the low-lying core-excited states in isoelectronic argon \citep{ceolin15:022502}.
+The calculations were performed at the Configuration Interaction Singles (CIS) level using the GAMESS-US package \citep{GUGA_PhysScr_21,GUGA_JCP_70,GUS} (see SI for details).} The energy positions of the states (see bars on Figs.\ \ref{fg:2dmap_k}(c) and \ref{fg:2dmap_cl}(c)) are adjusted to the kinetic-energy scale of the Auger spectra of both ions such that the lowest 2p$^{-2}$($^1$D)4p states coincide with the maxima of the dipsersive features close to the $^1$D main line.
 
@@
 In the 2D map of \cli~two dispersive resonant Auger features are visible.} Both of them exhibit a maximum at $h\nu =  2825.2$\,eV, {\color{blue} i.e.\ $\cong 200$ meV below the ionization threshold.
-This value agrees well with the position of the  1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments on hydrated Mg and Sr chlorides \citep{sugiura82:681} and metalchloride complexes \citep{shadle95:2259}.
+The former value agrees well with the position of the  1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments on hydrated Mg and Sr chlorides \citep{sugiura82:681} and metalchloride complexes \citep{shadle95:2259}.
 Moreover, the maxima in the kinetic energies of these dispersive features are split by $\cong$ 8.5 eV, which is in line with the calculated values for the 2p$^{-2}$($^1$S)4p and 2p$^{-2}$($^1$D)4p final states of $\cong 7$ eV.
@@
 
-%In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two
-%groups of states split by about 7\,eV (Fig.\ \ref{fg:2dmap_cl}(c))
-%corresponding to the 2p$^{-2}$($^1$S)4p and 2p$^{-2}$($^1$D)4p final states.
-%The calculated splitting is in good agreement with the one between the
-%dispersive features on the high kinetic-energy sides of the $^1$S and $^1$D
-%main peaks on Fig.\ \ref{fg:2dmap_cl}(a). Consequently, we assign these
-%features to the 1s$^{-1}$4p $\rightarrow$ 2p$^{-2}$($^1$S, $^1$D)4p resonant
-%Auger transitions of Cl$^{-}_{\text{aq}}$.
+%In the computed Cl$^{0}$[2p$^{-2}$nl](H$_2$O)$_6$ spectrum there are two groups of states split by about 7\,eV (Fig.\ \ref{fg:2dmap_cl}(c)) corresponding to the 2p$^{-2}$($^1$S)4p and 2p$^{-2}$($^1$D)4p final states.
+The calculated splitting is in good agreement with the one between the dispersive features on the high kinetic-energy sides of the $^1$S and $^1$D main peaks on Fig.\ \ref{fg:2dmap_cl}(a).
+Consequently, we assign these features to the 1s$^{-1}$4p $\rightarrow$ 2p$^{-2}$($^1$S, $^1$D)4p resonant Auger transitions of Cl$^{-}_{\text{aq}}$.
 
-%which is
-%in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation
-%determined from Cl K-edge XAS experiments on hydrated Mg and Sr
-%chlorides\citep{sugiura82:681} and metal-chloride complexes \citep{shadle95:2259}.
-%The dispersive features have $E_{\text{kin}} = 2374.6$ and 2383.4\,eV relating
-%them to the $^1$S and $^1$D main lines, respectively.
+%which is in good agreement with the position of the Cl$^{-}$ 1s$^{-1}$4p excitation determined from Cl K-edge XAS experiments on hydrated Mg and Sr chlorides\citep{sugiura82:681} and metal-chloride complexes \citep{shadle95:2259}.
+The dispersive features have $E_{\text{kin}} = 2374.6$ and 2383.4\,eV relating them to the $^1$S and $^1$D main lines, respectively.
 
@@
 The line denoted as B exhibits a maximum at h$\nu = 3611.2$\,eV and $E_{\text{kin}} = 2969.2$\,eV, while the line labeled C exhibits a maximum at h$\nu = 3611.6$\,eV and $E_{\text{kin}} = 2978.1$\,eV.
-The observed energy positions relative to the \ki 1s$^{-1}$ threshold in combination with the relative energy position of the 2p$^{-2}$nl states suggest that feature B is a result of resonant Auger decay of the 1s$^{-1}$4p excitation to the 2p$^{-2}(^1$D)4p final state and feature C originates from the 1s$^{-1}$3d $\rightarrow$ 2p$^{-2}(^1$D)3d resonant Auger transition.
+The observed energy positions relative to the \ki 1s$^{-1}$ threshold in combination with the relative energy position of the 2p$^{-2}$nl states suggest that feature B is a result of resonant Auger decay of the 1s$^{-1}$4p excitation to the 2p$^{-2}(^1$D)4p final state, whereas feature C originates from the 1s$^{-1}$3d $\rightarrow$ 2p$^{-2}(^1$D)3d resonant Auger transition.
 The latter is dipole-forbidden in the isolated ion, which explains the low intensity of feature C.
 %This assignment is supported by the low intensity of the latter feature, which is dipole-forbidden in the isolated ion.
-Another argument in favor of this assignment is the energy difference between the spectral features A and C, which matches well the lowest ionization potential of liquid water of I$_{\rm aq} \cong 11.16$ eV \cite{winter04:2625}.
-Feature A is assigned to a charge transfer from a water molecule W to the 3d orbital of \ki~during the Auger decay, i.e.\ K$^{2+}$(1s$^{-1}$) $\rightarrow$ K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}, so that its energy position should be lower by I$_{\rm aq}$ if we take into account the small energy separation of the 1s $\rightarrow$ 3d excitation from threshold.
-Due to the high intensity of shoulder A no dispersive features related to the 2p$^{-2}(^1$S) parent state are observed in the 2D map of \ki.}
+Another argument in favor of this assignment is the energy difference between the spectral features A and C, which matches well the lowest ionization potential of liquid water I$_{\rm aq} \cong 11.16$\,eV \cite{winter04:2625}.
+Feature A is assigned to a charge transfer from a water molecule W to the 3d orbital of \ki~during the Auger decay, i.e.\ K$^{2+}$(1s$^{-1}$) $\rightarrow$ K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}, so that its energy position should be lower by I$_{\rm aq}$ if we take into account the small energy separation of the 1s$^{-1}$3d excitation from threshold.
+No dispersive features related to the 2p$^{-2}(^1$S) parent state are observed in the 2D map due to the high intensity and broadening of shoulder A.}
 
-%assigned to K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \cite{}
-%and C assinged to , which matches well the lowest ionization
-%potential of liquid water of $\cong 11.16$ eV \cite{winter04:2625}
+%assigned to K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \cite{} and C assinged to , which matches well the lowest ionization potential of liquid water of $\cong 11.16$ eV \cite{winter04:2625}
 
-%This shoulder is attributed to electron transfer 
-%from the solvent water molecules to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) 
-%resulting in K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}.
+%This shoulder is attributed to electron transfer from the solvent water molecules to the unoccupied 3d orbitals of K$^{3+}$(2p$^{-2}$) resulting in K$^{2+}$(2p$^{-2}$3d)W$^{+}$ \citep{ceolin17:263003}.
 
-%Another argument supporting the assignment of feature C to the 1s$^{-1}$3d
-%$\rightarrow$ 2p$^{-2}$3d Auger transition is the energy difference between
-%the spectral features A and C. Feature A originates from electron transfer
-%processes from water molecules (W) to the doubly core-ionized potassium ion
-%and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{+}$. The lowest ionization
-%potential of liquid water is about 11.16\,eV \cite{winter04:2625} which
-%matches well the observed A-C splitting. Thus, the above energetic arguments
-%corroborate the attribution of island C as originating from resonant Auger
-%decay to the K$^{2+}$ 2p$^{-2}$3d final states.
+%Another argument supporting the assignment of feature C to the 1s$^{-1}$3d $\rightarrow$ 2p$^{-2}$3d Auger transition is the energy difference between the spectral features A and C.
+Feature A originates from electron transfer processes from water molecules (W) to the doubly core-ionized potassium ion and has the configuration K$^{2+}$(2p$^{-2}$3d)W$^{+}$.
+The lowest ionization potential of liquid water is about 11.16\,eV \cite{winter04:2625} which matches well the observed A-C splitting.
+Thus, the above energetic arguments corroborate the attribution of island C as originating from resonant Auger decay to the K$^{2+}$ 2p$^{-2}$3d final states.
 
-%In the case of \ki, the
-%dispersive line related to the $^1$S main line cannot be clearly identified due
-%to the presence of a strong background. Instead two dispersive features related
-%to the $^1$D main line are observed denoted as B and C on Fig.\ \ref{fg:2dmap_k}(a).
-%Feature B exhibits a maximum at h$\nu = 3611.2$\,eV and $E_{\text{kin}} = 2969.2$\,eV.
-%The additional feature C appears at h$\nu = 3611.6$\,eV and $E_{\text{kin}} = 2978.1$\,eV,
-%thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in
-%kinetic energy from the maximum of feature B. The positions of these two
-%core-excited states are close to the energy of the 1s$^{-1}$4p excitation of
-%gas-phase \ki~-- 3610.7\,eV \citep{hertlein06:062715}.
+%In the case of \ki, the dispersive line related to the $^1$S main line cannot be clearly identified due to the presence of a strong background.
+Instead two dispersive features related to the $^1$D main line are observed denoted as B and C on Fig.\ \ref{fg:2dmap_k}(a).
+Feature B exhibits a maximum at h$\nu = 3611.2$\,eV and $E_{\text{kin}} = 2969.2$\,eV.
+The additional feature C appears at h$\nu = 3611.6$\,eV and E_{\text{kin}} = 2978.1$\,eV, thus it is separated by approximately 400\,meV in photon energy and 8.3\,eV in kinetic energy from the maximum of feature B.
+The positions of these two core-excited states are close to the energy of the 1s$^{-1}$4p excitation of gas-phase \ki~-- 3610.7\,eV \citep{hertlein06:062715}.
 
@@
 \centering
-\includegraphics[scale=0.55]{figures/xas_spectra.eps}
-\caption{XA spectra of the lowest K-shell resonant transitions in the isolated
-K$^{+}$ (a) and Cl$^{-}$ (b) ions and their 6-coordinated clusters, (c) and (d).
-For comparison with the experiment, the theoretical stick spectra are convolved
-with a Lorentzian of FWHM 0.74\,eV and 0.62\,eV representing the lifetime
-broadening of \ki~and \cli \citep{Krause79:329} (dashed lines) and a Voigt
-profile (solid line) to account for both the lifetime and the experimental
-broadening (see text). The colors in the stick spectrum represent the projections
-of the singly-occupied natural orbitals (SONOs) of the core-excited 6-coordinated
-clusters on the basis of SONOs belonging to the 1s$^{-1}$3d, 1s$^{-1}$4p, and
-1s$^{-1}$5p states of the isolated ions. The remaining contributions from
-higher-lying atomic core excitations or from excitations to the solvent molecules
-are depicted as grey sticks. The theoretical XA spectra of both \ki~and \cli~were
-shifted to higher photon energies such that the energies of the lowest core-excited states correspond to the experimentally determined ones.
+\includegraphics[scale=0.55]{figures/xas_spectra_jul12.eps}
+\caption{XA spectra of the lowest K-shell resonant transitions in the isolated K$^{+}$ (a) and Cl$^{-}$ (b) ions and their 6-coordinated clusters, (c) and (d).
+For comparison with the experiment, the theoretical stick spectra are convolved with a Lorentzian of FWHM 0.74\,eV and 0.62\,eV representing the lifetime broadening of \ki~and \cli \citep{Krause79:329} (dashed lines) and a Voigt profile (solid line) to account for both the lifetime and the experimental broadening (see text).
+The colors in the stick spectrum represent the projections of the singly-occupied natural orbitals (SONOs) of the core-excited 6-coordinated clusters on the basis of SONOs belonging to the 1s$^{-1}$3d, 1s$^{-1}$4p, and 1s$^{-1}$5p states of the isolated ions.
+The remaining contributions from higher-lying atomic core excitations or from excitations to the solvent molecules are depicted as grey sticks.
+The theoretical XA spectra of both \ki~and \cli~were shifted to higher photon energies such that the energies of the lowest core-excited states correspond to the experimentally determined ones.
 The experimental ionization thresholds are depicted as grey boxes.}
@@
 
-{\color{blue} We note that the resonances of K$^{+}_{\text{aq}}$ and Cl$^{-}_{\text{aq}}$ calculated to be above the corresponding ionization threshold, (Fig.\ \ref{fg:xas_kcl}(c,d)), are not experimentally observed.
-This might be due to the fact that the corresponding resonant Auger spectra are energetically too close to the more intense normal Auger main lines.}
+{\color{blue} We note that the resonances of K$^{+}_{\text{aq}}$ and Cl$^{-}_{\text{aq}}$ calculated to be above the corresponding ionization threshold (Fig.\ \ref{fg:xas_kcl}(c,d)) are not experimentally observed.
+This might be due to the fact that the corresponding resonant Auger spectra cannot be separated energetically from the more intense normal Auger main lines.}
 
@@
 
-%In the 6-coordinated \ki~cluster
-%the lowest peak in the spectrum contains three states (Fig.\
-%\ref{fg:xas_kcl}(c)). The lowest- and highest-lying states are split
-%by approximately 0.5\,eV and they have mixed 4p and 5p character while
-%the low-intensity state in between has a predominantly 1s$^{-1}$3d
-%character. 
-%Since the dispersive feature B appears at low excitation
-%energies, we assume that it is produced in the resonant Auger decay
-%of the lowest core-excited states of \ki~of predominantly 1s$^{-1}$4p
-%character. Moreover, we can attribute the feature C to the resonant
-%Auger decay of the low-intensity dipole-forbidden 1s$^{-1}$3d state.
-%Thus, we explain both the energy splitting of $\sim$400\,meV photon
-%energy of B and C, and the fact that island C has lower intensity than
-%B (Fig.\ \ref{fg:2dmap_k}). 
-%In the hexa-coordinated cluster of \cli,
-%the solvent molecules have little influence on the position and character
-%of the first state -- it has mainly \cli~1s$^{-1}$4p character with some
-%admixture of states of the nearest water molecules (Fig.\
-%\ref{fg:xas_kcl}(d)). 
-%Consequently, we attribute the two dispersive
-%features associated with the $^1$S and $^1$D main lines on the 2D map of
-%\cli~to the resonant Auger decay of this core-excited state.
-%involving mostly the 4p orbitals of chloride.
+%In the 6-coordinated \ki~cluster the lowest peak in the spectrum contains three states (Fig.\ \ref{fg:xas_kcl}(c)).
+The lowest- and highest-lying states are split by approximately 0.5\,eV and they have mixed 4p and 5p character while the low-intensity state in between has a predominantly 1s$^{-1}$3d character.
+Since the dispersive feature B appears at low excitation energies, we assume that it is produced in the resonant Auger decay of the lowest core-excited states of \ki~of predominantly 1s$^{-1}$4p character.
+Moreover, we can attribute the feature C to the resonant Auger decay of the low-intensity dipole-forbidden 1s$^{-1}$3d state.
+Thus, we explain both the energy splitting of $\sim$400\,meV photon energy of B and C, and the fact that island C has lower intensity than B (Fig.\ \ref{fg:2dmap_k}).
+In the hexa-coordinated cluster of \cli, the solvent molecules have little influence on the position and character of the first state -- it has mainly \cli~1s$^{-1}$4p character with some admixture of states of the nearest water molecules (Fig.\ \ref{fg:xas_kcl}(d)).
+Consequently, we attribute the two dispersive features associated with the $^1$S and $^1$D main lines on the 2D map of \cli~to the resonant Auger decay of this core-excited state.
+involving mostly the 4p orbitals of chloride.
 
-%For \ki(H$_2$O)$_6$
-%the calculated 2p$^{-2}$4p states are lower in energy by $\sim$5 and
-%12-13\,eV than two groups of 2p$^{-2}$3d states. Thus, the transitions to
-%the group of 2p$^{-2}$3d final states at $E_{\text{kin}}\cong 2975$\,eV are
-%closer to the kinetic energy of island C. Consequently, we attribute this
-%dispersive feature as originating from the resonant Auger decay of the
-%1s$^{-1}$3d excitation to this group of 2p$^{-2}$3d states. The theoretical
-%splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states is smaller than
-%that between islands B and C. This disagreement can be explained with the
-%fact that we consider a single geometry with a fixed number of water
-%molecules in the first solvation shell. Moreover, we do not theoretically
-%account for the effect of distant solvent shells. We assume that the
-%transitions to the 2p$^{-2}$3d states with kinetic energies between 2982
-%and 2983\,eV have negligible Auger rates since no additional experimental
-%features are observed.
+%For \ki(H$_2$O)$_6$ the calculated 2p$^{-2}$4p states are lower in energy by $\sim$5 and 12-13\,eV than two groups of 2p$^{-2}$3d states.
+Thus, the transitions to the group of 2p$^{-2}$3d final states at $E_{\text{kin}}\cong 2975$\,eV are closer to the kinetic energy of island C.
+Consequently, we attribute this dispersive feature as originating from the resonant Auger decay of the 1s$^{-1}$3d excitation to this group of 2p$^{-2}$3d states.
+The theoretical splitting between the 2p$^{-2}$4p and 2p$^{-2}$3d states is smaller than that between islands B and C.
+This disagreement can be explained with the fact that we consider a single geometry with a fixed number of water molecules in the first solvation shell.
+Moreover, we do not theoretically account for the effect of distant solvent shells.
+We assume that the transitions to the 2p$^{-2}$3d states with kinetic energies between 2982 and 2983\,eV have negligible Auger rates since no additional experimental features are observed.
 
@@
 
-{\color{red}
-An important aspect of the study of core-excited states in aqueous solutions is the possibility of ultrafast delocalization of the core-excited electron which competes with the resonant Auger decay \citep{Nordlund07:217406,ottosson12:1}.
-The photon-energy dependent Auger spectra contain information about the delocalization time thus providing a convenient alternative to the more challenging time-domain experiments in the (sub?)femtosecond regime.
-To estimate the photon-energy dependent delocalization time of the core-excited electron, $\tau_{\text{CT}} (E_{\text{ph}})$, at the pre-edges of K$^{+}$~and Cl$^{-}$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
-Within this method, $\tau_{\text{CT}} (E_{\text{ph}})$ can be determined from the lifetime of the core hole $\tau_{\text{c}}$ and the ratio of the intensities of the normal ($d$) and resonant ($l$) Auger peaks according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l(E_{\text{ph}})/d(E_{\text{ph}})$ \citep{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
-In the case of Cl$^{-}$, we performed the same data treatment as in Ref.\ \cite{ceolin15:022502} to extract the intensities $l(E_{\text{ph}})$ and $d(E_{\text{ph}})$ as a function of the photon energy (see Fig.\ \ref{fg:si_ct_time} in the SI).
-% Due to the proximity of the resonance to the ionization threshold and due to the very short lifetime of the corresponding states, there is a large overlap between the resonant and normal Auger contributions.
+{\color{blue}
+An important aspect of the study of core-excited states in aqueous solutions is the effect of ultrafast delocalization of the excited electron which competes with the resonant Auger decay \citep{Nordlund07:217406,ottosson12:1}.
+The photon-energy dependent Auger spectra also contain information about the delocalization time thus providing a convenient alternative to the more challenging time-domain experiments in the 1\,fs regime.
+To estimate the photon-energy dependent delocalization time of the core-excited electron, $\tau_{\text{CT}} ($h$\nu)$, we used the core-hole clock method \cite{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+Within this method, $\tau_{\text{CT}} ($h$\nu)$ can be determined from the lifetime of the core hole $\tau_{\text{c}}$ and the ratio of the intensities of the normal ($d$) and resonant ($l$) Auger peaks according to the relation $\tau_{\text{CT}} = \tau_{\text{c}}l($h$\nu)/d($h$\nu)$ \citep{bjorneholm92:1892,karis96:1380,wurth00:141,bruehwiler02:703,foehlisch05:373}.
+In the case of Cl$^{-}$, we performed the same data treatment as in Ref.\ \cite{ceolin15:022502} to extract the intensities $l($h$\nu)$ and $d($h$\nu)$ (see Fig.\ \ref{fg:si_ct_time} in the SI).
 At the specific photon energy of h$\nu = 2825.2$\,eV, i.e.\ at the maximum of the lowest core excitation 1s$^{-1}$4p, $\tau_{\text{CT}}$ is of the same order as the Auger lifetime, $\cong$1\,fs.
-This is manifested as a double-peak structure in the resonant Auger spectrum in the interval E$_{kin} = 2380 - 2385$\,eV (Fig.\ \ref{fg:2dmap_cl}(c)).
+This is manifested as a double-peak structure in the Auger spectrum in the interval E$_{kin} = 2380 - 2385$\,eV (Fig.\ \ref{fg:2dmap_cl}(c)).
 The position of the first peak coincides with the $^1$D main line resulting from normal Auger decay, whereas the second peak at 2383.5\,eV corresponds to resonant Auger decay to the 2p$^{-2}$($^1$D)4p states.
@@
 
-For potassium, a comparable data treatment is more complicated due to the presence of multiple simultaneous processes, namely, normal and resonant Auger decay, as well as charge transfer from solvent and PCI effect.
-To extract the intensity of each component from the 2D map (Fig.\ \ref{fg:2dmap_k}(a)), one needs the spectral fingerprints of each process to be separated.
-As can be seen, this is hardly possible especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
-However, one can expect much less efficient delocalization in \ki~compared to \cli~because the core-excited states appear 1.2\,eV below the ionization threshold compared to 0.2\,eV for chloride and, moreover, because the lifetime of the K1s core hole is shorter than that of chloride (0.9 vs.\ 1\,fs).}
+For potassium, a comparable data treatment is more complicated due to the smaller splitting between the 1s$^{-1} \rightarrow$ 2p$^{-2}$($^1$D) normal Auger and  1s$^{-1}$4p $ \rightarrow$ 2p$^{-2}$($^1$D)4p resonant Auger lines as well as the presence of contributions caused by charge transfer from the solvent.
+This hinders the extraction of reliable intensities for the different contributions visible in the 2D map (Fig.\ \ref{fg:2dmap_k}(a)), especially close to threshold in the kinetic energy region 2965 -- 2970\,eV.
+However, one can expect much less efficient delocalization in \ki~compared to \cli~because the lowest core-excited state appears 0.7\,eV below the ionization threshold compared to 0.2\,eV for chloride and, moreover, because the lifetime of the K1s core hole is shorter than that of chloride (0.9 vs.\ 1\,fs).}
 
@@
 The spectator Auger decay of this state produces an additional feature which is well separated from the remaining Auger features.
-These results are an important first step in the study of relaxation cascades triggered by x-ray photoabsorption in liquids.
+{\color{red} Another substantial difference between the two ions is the time of delocalization of the core-excited electron at the pre-edge region.
+Using the core-hole clock method, we extracted information about the delocalization dynamics from the photon-energy dependent Auger spectra.
+In the case of \cli, the resonant Auger decay and the delocalization of the excited electron occur on a comparable timescale, whereas in \ki, a much less efficient delocalization is expected.} These results are an important first step in the study of relaxation cascades triggered by x-ray photoabsorption in liquids.
 The Auger processes considered here are inevitably followed by multiple intra- and interatomic electronic decays, such as interatomic Coulombic decay (ICD) and electron-transfer mediated decay (ETMD) \citep{unger17:708,Stumpf16:237}.
